### 2015-10-12 manuscript/text_reuse.tex
initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article} %a4paper

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{pa}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
\date{\today}
\author{}

\maketitle

\begin{abstract}
Much research has been focused on the diffusion of policy ideas in US state
legislatures. Most of this research uses hand coded data sets that identify
equivalent bills and analyze patterns of adoption of these bills. Bills on
equivalent policies often contain the same language, since legislators use past
legislation from other states or model legislation from interest groups as
templates when drafting new bills or model legislation from interest groups. In
this paper we evaluate the effectives of text reuse measures to detect bills
that address the same policy issues... 
\end{abstract}

\section{Introduction}

\bibliographystyle{chicago}
\bibliography{bibliography}

\end{document}

### 2015-10-12 exploration/explore_network.R
adds some EDA code

@@ -1,0 +1,41 @@
+library(dplyr)
+library(sna)
+library(network)
+
+# Load data
+df <- tbl_df(read.csv('alignment_scores_only.csv', header = TRUE, 
+                      stringsAsFactors = FALSE)
+             )
+
+# Extract some additional info
+ret_first <- function(x) return(x[1])
+df <- mutate(df, edge_id = paste0(left_doc_id, '_', right_doc_id),
+             alignmen_score = as.numeric(alignment_score),
+             left_state = sapply(strsplit(df$left_doc_id, '_'), ret_first),
+             right_state = sapply(strsplit(df$right_doc_id, '_'), ret_first))
+        
+# Aggregate the bills
+df_bills <- group_by(df, edge_id) %>% 
+    summarize(num_alignments = n(),
+    sum_score = sum(alignment_score),
+    states_id = paste0(left_state[1], right_state[1]),
+    left_state = left_state[1],
+    right_state = right_state[1])
+    
+n_nodes <- length(unique(c(df$left_doc_id, df$right_doc_id)))
+
+# Aggregate states
+df_states <- group_by(df_bills, states_id) %>%
+    summarize(alignments = sum(num_alignments),
+              total_alignment_score = sum(sum_score),
+              left_state = left_state[1],
+              right_state = right_state[1])
+
+# Store the aggregated dfs
+write.csv(df_bills, file = 'bill_network.csv', row.names = FALSE)
+write.csv(df_states, file = 'states_network.csv', row.names = FALSE)
+
+# Visualize the states network
+states <- network(df_states[, c("left_state", "right_state", "alignments")], 
+                  matrix.type = "edgelist")
+

### 2015-10-12 exploration/extract_alignment_scores.py

@@ -1,0 +1,22 @@
+# Extract only bill ids and alignment scores (remove the alignment text from the
+# alignment dataset)
+import csv
+import sys
+
+# Increase maximum csv field size (very long alignments)
+csv.field_size_limit(sys.maxsize)
+
+
+with open('bill_to_bill_alignments.csv', 'r') as infile, open('alignment_scores_only.csv', 'a') as outfile:
+
+    reader = csv.reader(infile, delimiter = ',', quotechar = '"')
+    writer = csv.writer(outfile, delimiter = ',', quotechar = '"')
+    header = ['left_doc_i', 'right_doc_i', 'alignment_score']
+    #writer.writerow(header)
+    
+    errors = 0
+    for index, row in enumerate(reader):
+        out_row = [row[0], row[1], row[4]]
+        writer.writerow(out_row)
+        if index % 100000 == 0:
+            print 'Done with {} of 7930050'.format(index)

### 2015-10-13 manuscript/text_reuse.tex
update on data

@@
 this paper we evaluate the effectives of text reuse measures to detect bills
-that address the same policy issues... 
+that address the same policy issues. We find that... 
 \end{abstract}
@@
 \section{Introduction}
+
+...
+
+\section{Data}
+
+We will rely on two main data sources to assess the reliability of text reuse to
+identify substantively equivalent bills.
+
+One is a data base of bill text that was extracted through the sunlight
+foundation's Open States API. This data base contains approximately 500,000
+bills from 2009 to 2015. From this database we will extract the bills for which we
+have ground truth on policy equivalence. 
+Once we obtained these bills, we will use the local alignment algorithm
+implemented by (Burgess et al. 2015) in order to obtain alignment scores for
+these bills. 
+Information on which bills implement equivalent policies is obtained from
+several sources. One option is to rely on datasets compiled by scholars who have
+studied policy diffusion in the past. Another option is to rely on materials
+compiled by the National Conference of State Legislatures (NCSL). The NCSL keeps
+track of specific policies and regulations across states. However, the tables
+compiled by the NCSL most often refer to the relevant sections in the states'
+statutes instead of to the bills that these sections are based on. In order to
+use these material we would have to find a way to link statute sections to their
+original bills.
 

### 2015-10-13 manuscript/text_reuse.tex
updated with tasks

@@
 
+\subsection{Tasks}
+\begin{itemize}
+\item Write paragraph about how it would be great if text-reuse could be used to classify policy overlap (BD)
+\item Write paragraph on why this is not easy (FL)
+\item Summarize what we do to solve problem and validate (FL)
+\end{itemize}
+
 ...
+
+\section{Background}
+
+\subsection{Tasks}
+\begin{itemize}
+\item Policy diffusion (BD get papers)
+\item Text re-use in CBP in bills 
+\item Text re-use in general
+\begin{itemize}
+\item Plaigirism
+\item Alignment
+\end{itemize} 
+\item Discussion of text-based classification
+\end{itemize}
 
@@
 foundation's Open States API. This data base contains approximately 500,000
-bills from 2009 to 2015. From this database we will extract the bills for which we
+bills from 2008 to 2015. From this database we will extract the bills for which we
 have ground truth on policy equivalence. 
@@
 
+\subsection{Tasks}
+\begin{itemize}
+\item Scrape Google urls for NCSL tables (FL)
+\item Extract state  \& bill \# from tables (FL)
+\end{itemize}
+
+\section{Analysis}
+
+\subsection{Tasks}
+\begin{itemize}
+\item Alternative validation options (BD)
+\end{itemize}
+
 \bibliographystyle{chicago}

### 2015-10-16 manuscript/text_reuse.tex
added a bit to the introduction

@@
 \item Write paragraph on why this is not easy (FL)
-\item Summarize what we do to solve problem and validate (FL)
 \end{itemize}
+How ever, it is not clear, how well text reuse is suited to to detect real
+policy diffusion. There are several complications that we are addressing in this
+paper. First, every bill has procedural content that is not related to the
+policy content of the bill. Since every state legislature has a set of such
+standard or boiler plate text in each bill, there will be significant text reuse
+between bills in the same state and possibly also between bills from different
+states. Second, it is not obvious how much text reuse will mean substantive
+policy overlap. Given that each bill pair has a continuous proportion of
+overlapping text, setting the threshold too low might mean to classify bills as
+equivalent that are only in the same policy area, or are on a similar issue, but
+are opposed in content. On the other hand, setting the threshold too high could
+mean overlooking equivalent bills because of small insignificant changes to the
+text.
 
-...
+In this paper we address these issues and evaluate how much policy overlap can
+be detected using text reuse measures. Following Wilkerson et al. (2015) we use
+supervised machine learning to separate boiler plate from substantive text. We
+further more use an original data set on policy diffusion to evaluate how much
+equivalent policy can be detected using measures of text reuse. Using the system
+developed by Burges et al. (2015) we calculate text reuse scores for all pairs
+of bills in our dataset. We then use these scores in a model that classifies
+bills as equivalent and evaluate its performance with the validation data set.
+
+This work has several important implications. First, it allows us to estimate,
+how policies are transferred between states. Do state legislators work mainly
+from templates from other states or interest groups, or to what extent do
+legislators draft their own bill text. Furthermore, text reuse is a relatively
+simple metric to calculate for large amounts of text. Previous scholars of
+policy diffusion mainly relied on case studies or manually coded data sets of
+policy diffusion in few policy areas. If working copying text forms a
+significant portion of how legislators adopt policies from other states, text
+reuse can be used to easily gather comprehensive data sets on policy diffusion.
+
+[This might be overlapping a bit with your part]
 
@@
 \begin{itemize}
-\item Scrape Google urls for NCSL tables (FL)
+\item Scrape Google urls for NCSL tables (
 \item Extract state  \& bill \# from tables (FL)

### 2015-10-19 manuscript/text_reuse.tex
added ideas to the analysis section

@@
 \begin{itemize}
-\item Scrape Google urls for NCSL tables (
-\item Extract state  \& bill \# from tables (FL)
+\item Scrape Google urls for NCSL tables (FL) -- lower priority
+\item Extract state  \& bill \# from tables (FL) -- lower priority
+\item See tasks in analysis -- create metadata file and dyadic file, then put them on the ACI (FL).
+\item Store MALP data on ACI and make sure the identifiers match those in the bill data (FL). 
+\item Put policy diffusion data in project folder on ACI (BD).
 \end{itemize}
@@
 \section{Analysis}
+ Below we list X separate analyses designed to test the degree to which measuring text reuse measures policy overlap/diffusion.
+
+\begin{itemize}
+\item We use statistical topic modeling to assess the major content areas represented by the text identified in the alignment algorithm.
+We consider whether the resultant topics align with policy areas.
+\item The Measuring American Legislators Project (MALP) provides data that we will use to assess the significance of text re-use in US state legislation \citet{shor2011}.
+The most recent release of the MALP data covers 1993-2014.
+The MALP data provide ideological scores of legislators on an annual basis.
+We conduct a bill-level statistical network analysis to see whether the rate of bill-to-bill alignment is positively related to the ideological similarity of their sponsors.
+\item We conduct a state-level analysis to see whether the volume of state-to-state text alignment is positively related to the policy diffusion networks inferred in \citet{desmarais2015}.
+\end{itemize}
 
@@
 \begin{itemize}
-\item Alternative validation options (BD)
+\item Develop bill metadata dataset (FL)
+\begin{itemize}
+\item unique bill identifier
+\item sponsor identifier from  MALP data
+\item state identifier
+\item chamber identifier
+\item Introduction date
+\item Anything else, even if some is missing (status, committees, etc)
+\end{itemize}
+\item Develop bill-to-bill edgelists (FL)
+\begin{itemize}
+\item Sparse dyadic dataset (i.e., no observations when there is 0 alignment/overlap)
+\item alignment score(s)
+\item name of a text file in which aligned text is stored
+\end{itemize}
+\item Topic models, possibly of a relational form, applied to aligned text
+\item Computationally intensive analysis of bill-to-bill alignment and sponsor ideology.
+\item Analysis of alignment aggregated at the state level.
+
 \end{itemize}

### 2015-10-20 data_collection/ncsl_tables/extract_title.py
google scrape with api

@@ -1,0 +1,14 @@
+from __future__ import unicode_literals
+import io
+
+
+with io.open('ncsl_table_urls.txt', 'r') as infile, io.open('tables.csv', 'w+') as outfile:
+    outfile.write('title, url\n')
+    for line in infile:
+        line = line.replace('\n', '')
+        els = line.split('/')
+
+        title = els[-1].replace('.aspx', '')
+        title = title.replace('-', ' ')
+        newline = '{},{}\n'.format(title, line)
+        outfile.write(newline)

### 2015-10-20 manuscript/text_reuse.tex
progress update on manuscript

@@
 
-One is a data base of bill text that was extracted through the sunlight
-foundation's Open States API. This data base contains approximately 500,000
-bills from 2008 to 2015. From this database we will extract the bills for which we
-have ground truth on policy equivalence. 
-Once we obtained these bills, we will use the local alignment algorithm
-implemented by (Burgess et al. 2015) in order to obtain alignment scores for
-these bills. 
-Information on which bills implement equivalent policies is obtained from
-several sources. One option is to rely on datasets compiled by scholars who have
-studied policy diffusion in the past. Another option is to rely on materials
-compiled by the National Conference of State Legislatures (NCSL). The NCSL keeps
-track of specific policies and regulations across states. However, the tables
-compiled by the NCSL most often refer to the relevant sections in the states'
-statutes instead of to the bills that these sections are based on. In order to
-use these material we would have to find a way to link statute sections to their
-original bills.
+In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000
+bills from 2008 to 2015.
+The available metadata for the bills includes a timestamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.
+
+For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.
+The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.
+
+We additionally construct a validation dataset of equivalent bills from information obtained from the National Conference of State Legislatures (NCSL).
+The NCSL publishes summary tables on specific policies, citing the relevant bills or sections in the state statutes of the states that have implemented regulations on this policy.
+We collected all these tables, and extracted all bills that address the same policy measure and that overlap with the time frame covered by our bill database.
 
@@
 \item Scrape Google urls for NCSL tables (FL) -- lower priority
+    \begin{enumerate}
+        \item Scraped 64 urls. 
+        \item Can't get around the Google API limitation yet. Also get blocked when trying to scrape the search result.
+    \end{enumerate}
+
 \item Extract state  \& bill \# from tables (FL) -- lower priority
+    \begin{enumerate}
+        \item Didn't do this yet, let's first check how many are potentially suitable and then probably better to do by hand
+    \end{enumerate}
 \item See tasks in analysis -- create metadata file and dyadic file, then put them on the ACI (FL).
+    \begin{enumerate}
+        \item We have a preliminary dyadic file for all similar bill pairs and their alignment scores (this is from the LID approach: each bill is only compared to the 100 most similar ones)
+        \item Matt transfering the database to a new server at the moment, it is therefore unavailable. Should be online again sometime today.
+    \end{enumerate}
 \item Store MALP data on ACI and make sure the identifiers match those in the bill data (FL). 
+    \begin{enumerate}
+        \item data is on aci
+        \item Most Legislators can probably be matched by Name, Pary, State, Time in Office
+    \end{enumerate}
 \item Put policy diffusion data in project folder on ACI (BD).

### 2015-10-20 manuscript/text_reuse.tex
another small update

@@
 \usepackage{hyperref}
-\usepackage{pa}
 
@@
 
+In order to detect text reuse between bills we follow \citet{wilderson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.
+
 \section{Data}
@@
         \item data is on aci
-        \item Most Legislators can probably be matched by Name, Pary, State, Time in Office
+        \item Legislators can be matched by Name, State, Pary and Term.
+This information should be contained in the database.
+If not, the open state api has a legislator search method, that returns all necessary information.
     \end{enumerate}

### 2015-10-26 manuscript/text_reuse.tex
added literature on policy diffusion

@@
 
+Public policy diffusion -- the process by which policymakers emulate the policies implemented outside of their jurisdictions -- is a firmly established area of research in both Comparative \citep{simmons2004,gilardi2009} and American politics \citep{walker1969,berry1990,shipan2006,nicholson-crotty2009}.
+Until recently, policy diffusion studies have deployed quantitative research designs in which the relational component of policy diffusion (i.e., which jurisdiction is being emulated in a given diffusion instance), has been treated as completely unobservable or assumed to align with the geographic adjacency network (i.e., jurisdictions only emulate their geographic neighbors) \citep{volden2006,boehmke2009}.
+Recognizing the limitations in this approach, scholars have recently taken on the task of directly measuring the latent networks through which policies diffuse.
+\cite{desmarais2015} apply network inference algorithms to US state adoption sequences in over 100 policy domains to empirically infer the underlying network through which policies diffuse.
+\cite{garrett2015} analyze the text of US state legislation to measure the diffusion of policy in one domain -- restrictions on insurance coverage for abortion -- and identify the influence of model legislation, as introduced by interest groups.
+
+In order to detect text reuse between bills we follow \citet{wilkerson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.
+
 \subsection{Tasks}
 \begin{itemize}
-\item Policy diffusion (BD get papers)
+\item Policy diffusion (FL expand paragraph)
 \item Text re-use in CBP in bills 
@@
 \item Plaigirism
-\item Alignment
+\item Alignment (FL expand review of Wilkerson et al)
 \end{itemize} 
@@
 \end{itemize}
-
-In order to detect text reuse between bills we follow \citet{wilderson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.
 

### 2015-10-26 manuscript/text_reuse.tex
added intro paragraph

@@
 \end{itemize}
+
+Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets encode when one or a handful of policies were adopted by each jurisdiction \citep{boehmke2012}.
+Scholars of public policy diffusion have recently turned their attention to the empirical identification of emulation ties connecting policy jurisdictions \citep{volden2006,boehmke2009,desmarais2015,garrett2015}.
+Identifying instances of policy emulation and explicit diffusion ties opens policy diffusion scholarship to an entirely new set of questions and theories that can be approached empirically.
+In this paper we draw upon a massive and nearly all-encompassing source of data from which to infer diffusion ties -- the text of legislation.
+If the computer-based analysis of bill text can be tuned to successfully identify policy adoption and emulation, we will be able to vastly scale up both the scale of data gathered and the precision of diffusion inferences.
+
 How ever, it is not clear, how well text reuse is suited to to detect real

### 2015-10-26 data_collection/get_bill_metadata.py
working script to extract metadata from ES

@@ -1,23 +1,78 @@
-from __future__ import division, unicode_literals, print_function
-from pprint import pprint
+from __future__ import division, print_function, unicode_literals
 from elasticsearch import Elasticsearch
 import json
 import io
+import time
+from pprint import pprint
+import warnings
 
 # CONFIG
+# ============================================================================== 
 OUTFILE = '../data/lid/all_bills_metadata.csv'
 ELASTICIP = '54.244.236.175'
-ELASTICPORT = '9200'
+ELASTICPORT = 9200
 IDFILE = '../data/lid/bill_ids.txt'
-LIMIT = 10
+LIMIT = 2000
+FIELDS = ['bill_id', 'unique_id', 'short_title',  'bill_type', 'date_created', 'date_introduced', 
+        'date_signed', 'session', 'state']
+BATCHSIZE = 1000
+# ==============================================================================
 
-outfile = io.open(OUTFILE, 'w+', encoding='utf-8')
-idfile = io.open(IDFILE, 'r', encoding='utf-8')
+def write_batch(results, outfile):
+    for result in results:
+        cells = [0] * len(FIELDS)
+        for i, field in enumerate(FIELDS):
 
-for index, id_ in idfile:
-    
+            try:
+                cell = result['fields'][field] 
+            except KeyError:
+                cell = 'NA'
+            if cell is None:
+                cell = 'NA'
+            elif isinstance(cell, list) and len(cell) == 1:
+                cell = cell[0]
+            elif isinstance(cell, list) and len(cell) > 1:
+                msg = 'Warning: Multiple entries in field. Bill: {0}, field: {1}'.format(result['_id'], field)
+                warnings.warn(msg)
+            elif isinstance(cell, str) or isinstance(cell, unicode):
+                pass
+            else:
+                msg = 'Unexpected field type. Bill: {0}, field: {1}'.format(result['_id'], field)
+                raise ValueError(msg)
 
+            cells[i] = cell
+        row = ','.join(cells) + '\n'
+        outfile.write(row)
 
+if __name__ == '__main__':
 
-id_file.close()
-outfile.close() 
+    outfile = io.open(OUTFILE, 'w+', encoding='utf-8')
+    idfile = io.open(IDFILE, 'r', encoding='utf-8')
+
+    ec = Elasticsearch([{'host': ELASTICIP, 'port': ELASTICPORT}])
+
+    # Write csv header
+    header = ','.join(FIELDS) + '\n'
[…]

### 2015-10-26 manuscript/text_reuse.tex
added info on bill metadata

--- 2015-10-20 manuscript/text_reuse.tex
@@
 
+This collection of bills is based on all bills that are available through the \url{openstates.org} API.
+Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics.
+The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states.
+This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted.
+The database contains the full bill text and the following additional metadata:
+\begin{itemize}
+    \item action_dates:
+        \begin{itemize}
+            \item first
+            \item last
+            \item passed lower
+            \item passed upper
+            \item signed
+        \end{itemize}
+    \item actions (a list of legislative actions. E.g. referred to a committee)
+        \begin{itemize}
+            \item actor
+            \item date 
+            \item related_entities 
+            \item type
+        \end{itemize}
+    \item bill document first
+    \item bill document last
+    \item bill id
+    \item bill title
+    \item date created
+    \item date introduced
+    \item date signed
+    \item date updated
+    \item session
+    \item short title
+    \item state
+    \item summary
+    \item sunlight_id
+    \item unique id
+\end{itemize}
+
 For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.

### 2015-11-02 manuscript/text_reuse.tex
added results from diffusion analysis and cleaned up data list

@@
 \begin{itemize}
-\item Write paragraph about how it would be great if text-reuse could be used to classify policy overlap (BD)
-\item Write paragraph on why this is not easy (FL)
+\item
 \end{itemize}
@@
 The database contains the full bill text and the following additional metadata:
+
 \begin{itemize}
-    \item action_dates:
+    \item action\_dates:
         \begin{itemize}
@@
             \item date 
-            \item related_entities 
+            \item related\_entities 
             \item type
@@
     \item summary
-    \item sunlight_id
+    \item sunlight\_id
     \item unique id
@@
 
+\subsection{Diffusion networks and Text re-use}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrr}
+  \hline
+ & Coefficient & p-value \\ 
+  \hline
+Intercept & 141.0802 & 0.0000 \\ 
+  Diffusion Tie & 5.7258 & 0.0708 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
 \subsection{Tasks}
@@
 \item Computationally intensive analysis of bill-to-bill alignment and sponsor ideology.
+\begin{itemize}
+\item Get big sample of bills
+\item Assess relationship between alignment between bills and ideological similarity between sponsors
+\end{itemize}
 \item Analysis of alignment aggregated at the state level.
+\begin{itemize}
+\item How do we score overlap at the bill and state level?
+\end{itemize}
 

### 2015-11-02 analysis/dyadic_analysis.R

@@ -66,4 +66,8 @@ diag(align_amat) <- 0
 # Run ols with qap uncertainty
 bivariate_qap <- netlm(align_amat,diff_amat,mode="graph",reps=10000)
 
-results <- cbind()
+results <- cbind(bivariate_qap$coefficients,bivariate_qap$pgreqabs)
+library(xtable)
+rownames(results) <- c("Intercept","Diffusion Tie")
+colnames(results) <- c("Coefficient","p-value")
+xtable(results,dig=4)

### 2015-11-02 manuscript/text_reuse.tex
further updates to dyadic diffusion analysis

@@
 
+To evaluate whether text re-use corresponds to the transfer of policy, we test whether the presence of a diffusion network tie between two states is a predictor of text reuse.
+We use the policy diffusion networks inferred in \citet{desmarais2015}.
+We use [FL FILL IN] to measure the incidence of dyadic text alignment between all state bills covering the time period 200--[??].
+For each bill, we first gather the 100 closest bills based on cosine similarity in the term vectors characterizing the bills.
+We then represent a dyad of bills by the text alignments between them.
+For each state-pair we calculate the number of alignments between bills from each state.
+
 \begin{table}[ht]
@@
   \hline
-Intercept & 141.0802 & 0.0000 \\ 
-  Diffusion Tie & 5.7258 & 0.0708 \\ 
+Intercept & 5717.1836 & 0.0002 \\ 
+  Diffusion Tie & 2416.9969 & 0.0303 \\ 
    \hline

### 2015-11-02 analysis/dyadic_analysis.R

@@ -38,12 +38,18 @@ for(i in 1:length(files)){
   state1 <- substr(align_dati$left_doc_id,1,2)
   state2 <- substr(align_dati$right_doc_id,1,2)
   ## create the weight according to which each alignment will contribute
-  alignment_weight <- 1
+  alignment_weight <- rep(1,length(state1))
   ## add in the weight
-  align_amat[cbind(state1,state2)] <- align_amat[cbind(state1,state2)] + alignment_weight 
-  align_amat[cbind(state2,state1)] <- align_amat[cbind(state2,state1)] + alignment_weight
+  for(j in 1:length(alignment_weight)){
+    align_amat[cbind(state1[j],state2[j])] <- align_amat[cbind(state1[j],state2[j])] + alignment_weight[j] 
+    align_amat[cbind(state2[j],state1[j])] <- align_amat[cbind(state2[j],state1[j])] + alignment_weight[j]
+  }
   ## print to assess timing
-  if(i/5==round(i/5)) print(i)
+  if(i/5==round(i/5)){
+    print(i)
+    diag(align_amat) <- NA
+    hist(align_amat)
+  }
 }
 
 # subset to 2008 edges
@@ -64,10 +70,21 @@ library(sna)
 diag(diff_amat) <- 0
 diag(align_amat) <- 0
 # Run ols with qap uncertainty
-bivariate_qap <- netlm(align_amat,diff_amat,mode="graph",reps=10000)
-
+set.seed(5)
+bivariate_qap <- netlm(align_amat,diff_amat,mode="graph",reps=5000)
 results <- cbind(bivariate_qap$coefficients,bivariate_qap$pgreqabs)
-library(xtable)
 rownames(results) <- c("Intercept","Diffusion Tie")
 colnames(results) <- c("Coefficient","p-value")
-xtable(results,dig=4)
+
+###  on log scale
+set.seed(5)
+bivariate_qap_log <- netlm(log(align_amat),diff_amat,mode="graph",reps=5000)
+results_log <- cbind(bivariate_qap_log$coefficients,bivariate_qap_log$pgreqabs)
+rownames(results_log) <- c("Intercept","Diffusion Tie")
+colnames(results_log) <- c("Coefficient","p-value")
+
+library(xtable)
+results_all <- cbind(results,results_log)
+
+
+

### 2015-11-02 analysis/dyadic_analysis.R
finished dyadic analysis write-up

@@ -83,8 +83,16 @@ results_log <- cbind(bivariate_qap_log$coefficients,bivariate_qap_log$pgreqabs)
 rownames(results_log) <- c("Intercept","Diffusion Tie")
 colnames(results_log) <- c("Coefficient","p-value")
 
+## Prepare results for table
 library(xtable)
 results_all <- cbind(results,results_log)
+xtable(results_all,dig=4)
+
+## Descriptive statistics
+diag(align_amat) <- NA
+median(align_amat,na.rm=T)
+mean(align_amat,na.rm=T)
+sd(align_amat,na.rm=T)
 
 
 

### 2015-11-03 manuscript/text_reuse.tex

@@
 \usepackage{setspace}
+\usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{amsmath}
@@
 For each state-pair we calculate the number of alignments between bills from each state.
+The median number of alignments between states is 3,491 with a mean of 6,309 and standard deviation of 8,809.
+The ``Diffusion Ties'' variable measures the number of diffusion edges between states in the 2008 diffusion network, as measured by \citet{desmarais2015}.
+The number of diffusion edges between two states is either 0, 1, or 2.
+The diffusion network in 2008 is inferred using policy adoptions in the 35 years preceding (and excluding) 2008.
+As such, we do not risk double-counting bills in the policy adoption and text re-use data.
+There is one observation in the analysis for each of the 1,225 unique state-pairs.
+Since this is dyadic data, we use a matrix permutation method, quadratic assignment procedure, to calculate $p$-values \citep{krackhardt1988}.
+As a robustness check, we run the model with both the identity and log link.\footnote{The $p$-values were calculated using 5,000 random matrix permutations.}
 
@@
 \centering
-\begin{tabular}{rrr}
+\begin{tabular}{rrrrr}
 \hline
- & Coefficient & p-value \\ 
+& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
   \hline
-Intercept & 5717.1836 & 0.0002 \\ 
-  Diffusion Tie & 2416.9969 & 0.0303 \\ 
+ & Coefficient & p-value & Coefficient & p-value \\ 
+  \hline
+Intercept & 5717.18 & 0.0000 & 8.0431 & 0.0000 \\ 
+  Diffusion Ties & 2417.00 & 0.0308 & 0.3288 & 0.0452 \\ 
    \hline
 \end{tabular}
+\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
+\label{tab:qap.diffusion}
 \end{table}
+
+Results of the simple dyadic regression are presented in Table \ref{tab:qap.diffusion}.
+In both specifications there is a positive relationship between the number of diffusion ties and the number of alignments, and the relationship is statistically significant at the 0.05 level (two-tailed).
+Furthermore, the magnitudes of the relationships are substantively significant.
+A shift from the minimum to the maximum number of diffusion ties corresponds to more than a half of a standard deviation increase in the expected number of cross-state alignments.
+On the log scale, the addition of a diffusion tie corresponds to a 40\% increase in the expected number of cross-state alignments.\footnote{Calculated as $100\times \left[ \exp(0.3288)-1\right] = 38.93$}.
 

### 2015-11-03 manuscript/text_reuse.tex
updated paper and one new figure

@@
 
-\subsection{Tasks}
-\begin{itemize}
-\item
-\end{itemize}
-
 Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets encode when one or a handful of policies were adopted by each jurisdiction \citep{boehmke2012}.
@@
 states. Second, it is not obvious how much text reuse will mean substantive
+
 policy overlap. Given that each bill pair has a continuous proportion of
@@
 \item Alignment (FL expand review of Wilkerson et al)
+
+\citet{wilkerson2015tracing} use the
+
 \end{itemize} 
@@
 
-In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000
-bills from 2008 to 2015.
+\textit{Bill text}\\
+In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al.
+(2015) and the Sunlight foundation.
+This data base contains approximately 500,000 bills from 2008 to 2015.
 The available metadata for the bills includes a timestamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.
-
 This collection of bills is based on all bills that are available through the \url{openstates.org} API.
@@
 This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted.
-The database contains the full bill text and the following additional metadata:
+The database contains the bill text as well as additional information on the legislative process for the bill.
+We have the first and the last version of the bill text, the sponsor of the bill and all legislative action that was taken on the bill.
+
+\textit{Alignments}\\
+The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences.
+The same algorithm has been used by \citet{wilkerson2015tracing} to trace bills through the legislative process in congress.
+When considering two bills, the algorithm treats each bill as a sequence of words and tries to find the best alignment between these two sequences.
+\citet{wilkerson2015tracing} split the bills into sections and search for text reuse across sections.
+Since this results in about 7 billion possible pairs, first filter out pairs that don't have an exact match of a sequence of at least ten words.
+We encounter the same problem in our analysis to a greater extent.
+Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.
+
+In order to assess the computational burden the local alignment algorithm poses we test the implementation of the alignment algorithm (Burgess et al.
+2015) on a set of 1000 randomly selected bills.
+In a first pass we calculate the alignments  between all pairs of the full bills (not divided into sections).
+Figure \ref{fig:time_size} displays the relationship between bill length and computation time.
+As expected the time increases exponentially with the length of the bills.
+Figure \ref{fig:time} displays a histogram of the logarithm of the computation time (in seconds).
+Computation time varies between $0.001s$ and $1,650s$ with $75\%$ of the distribution below $0.1s$ and a median time of $0.03s$.
+This shows that an exhaustive comparison of just the full bills (not separated into sections) would take about 100 years on a single machine.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time_size_selection.png}}
+\caption{Computation time for selection of bills.
+The Colors correspond to five selected bills (focus bill or left bill).
+For each of the bills, the best alignment with 1000 randomly selected bills (right bills) are calculated.
+The size of the dots corresponds to the logarithm of the length of the focus bill (in number of words), the x-axis corresponds to the logarithm of the size of the comparison bill and the y-axis corresponds to the logarithm of the computation time (in seconds).}
+\label{fig:time_size}
+\end{figure}
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time.png}}
+\caption{Histogram of computation time for all analyzed bills.}
+\label{fig:time} 
+\end{figure}
+
+Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 10 words).
+Alignments between almost all bills are found and most of the alignments are procedural language.
+This is apparent in Figure \ref{fig:state_to_state} which displays the average alignment score for bills from Illinois (left panel) and Washington (right panel) for all other states in the sampled data set (x-axis).
+Especially for Illinois there is a much higher alignment score for bills from the same state.
+This shows that a minimum threshold and a classifier for procedural language are necessary.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/state_to_state.png}}
+\caption{Average alignment scores between states.
+The left panel corresponds to `left bills' from Illinois, the right panel to bills from Washington.
+Each bar displays the average score of the best alignment found between bills of the states.}
+\label{fig:state_to_state} 
+\end{figure}
+
+In order to make the computation more feasible, we rely on a similar strategy as \citet{wilkerson2015tracing}.
+Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents.
+Since the seraching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre selection of similar bills that are then exhaustively checked for text reuse:
+
+\begin{enumerate}
+\item All bills are stored in the database in n-grams of size 2-5
+\item Select the 25 n-grams with the highest tf-idf score in the query document
+\item Calculate a score slightly adapted cosine similarity score between the selected n-gram vector and all full document n-gram vectors in the database\footnote{See \url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html} for details on the similarity scoring in Elastic Search}
+\end{enumerate}
+
+\subsection*{Tasks}
 
 \begin{itemize}
-    \item action\_dates:
-        \begin{itemize}
-            \item first
-            \item last
-            \item passed lower
-            \item passed upper
-            \item signed
-        \end{itemize}
-    \item actions (a list of legislative actions. E.g. referred to a committee)
-        \begin{itemize}
-            \item actor
-            \item date 
-            \item related\_entities 
-            \item type
-        \end{itemize}
-    \item bill document first
-    \item bill document last
-    \item bill id
-    \item bill title
-    \item date created
-    \item date introduced
-    \item date signed
-    \item date updated
-    \item session
-    \item short title
-    \item state
-    \item summary
-    \item sunlight\_id
-    \item unique id
+    \item Augment the timing dataset with the document similarity scores
+    \item
+
 \end{itemize}
 
+\textit{Ideological Scores}\\
 For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.

### 2015-11-09 alignments/alignment_timing.py
more rearranging

@@ -1,0 +1,93 @@
+from __future__ import unicode_literals, print_function
+import sys
+from pprint import pprint
+import numpy as np
+import io
+from elasticsearch import Elasticsearch
+import json
+import time
+import copy
+
+sys.path.append('../../../policy_diffusion/lid/')
+from text_alignment import LocalAligner, AffineLocalAligner
+from database import ElasticConnection
+from utils.text_cleaning import clean_document
+from utils.general_utils import alignment_tokenizer
+
+# Select 1000 random bills
+np.random.seed(234234)
+n_bills = 1200 # 10% bills are empty so I choose a higher number
+random_lines = np.random.choice(a=565970, size=n_bills, replace=False).tolist()
+random_lines.sort()
+j = 0
+bill_ids = []
+with open('../../data/lid/bill_ids.txt', 'r') as id_file:
+    for i, line in enumerate(id_file):
+        if i == random_lines[j]:
+            bill_ids.append({'_id': line.strip('\n')})
+            j += 1
+            if j == n_bills:
+                break
+        else:
+            continue
+
+# Get them from the database
+
+ec = Elasticsearch([{'host': '54.244.236.175', 'port': 9200}])
+results = ec.mget(body={'docs': bill_ids}, index='state_bills', 
+                  doc_type='bill_document', fields=['bill_document_last'])
+
+# Extract relevant info and clean text
+bills = []
+no_text = []
+for result in results['docs']:
+    try:
+        doc = {}
+        doc['id_'] = result['_id']
+        doc['state'] = result['_id'].split('_')[0]
+        text = result['fields']['bill_document_last'][0]
+        doc['text'] = clean_document(text, doc_type='state_bill',
+                                     state_id=doc['state'], )
+        doc['tokenized'] = [alignment_tokenizer(s) for s in doc['text']]
+        doc['size'] = len(doc['tokenized'])
+        bills.append(doc)
+    except KeyError as e:
+        no_text.append(result['_id'])
+        continue
+       
+ 
+aligner = AffineLocalAligner()
+outfile = io.open('../../data/lid/alignment_timing.csv', 'w+', encoding='utf-8')
+outfile.write('focus_bill,right_bill,score,time,alignment_length,left_bill_length, right_bill_lenght\n')
+alignment_file = io.open('../../data/lid/alignment_text.csv', 'w+', encoding='utf-8')
[…]

### 2015-11-09 alignments/explore_alignment_timing.R

@@ -1,0 +1,42 @@
+library(ggplot2)
+library(dplyr)
+
+FIG_DIR <- '../../manuscript/figures/'
+DATA <- '../../data/lid/alignment_timing.csv'
+
+df <- tbl_df(read.csv(DATA, header = TRUE))
+
+# Remove identical bill pairs
+df <- filter(df, as.character(focus_bill) != as.character(right_bill))
+df$total_length = df$left_bill_length + df$right_bill_lenght
+
+
+ggplot(df[c(1:5000), ]) + geom_point(aes(x = log(right_bill_lenght), y = log(time),
+                                     color = focus_bill, size = log(left_bill_length)),
+                                     alpha = 0.3) + 
+    guides(color = guide_legend(override = list(alpha = 1)),
+           size = guide_legend(override = list(alpha = 1))) + 
+    theme_bw()
+ggsave(paste0(FIG_DIR, 'time_size_selection.png'))
+
+ggplot(df) + geom_point(aes(x = log(right_bill_lenght), y = log(time),
+                                   size = log(left_bill_length)),
+                                   alpha = 0.1) + 
+    guides(color = guide_legend(override = list(alpha = 1)),
+           size = guide_legend(override = list(alpha = 1))) + 
+    theme_bw()
+ggsave(paste0(FIG_DIR, 'time_size_all.png'))
+
+ggplot(df) + geom_histogram(aes(log(time)), color = 'white') + 
+    theme_bw()
+ggsave(paste0(FIG_DIR, 'time.png'))
+
+ggplot(df) + geom_histogram(aes(log(alignment_length)), color = 'white') + 
+    theme_bw()
+ggsave(paste0(FIG_DIR, 'alignment_scores.png'))
+
+ggplot(df) + geom_point(aes(y = log(score), x = log(alignment_length),
+                            size = log(total_length)), alpha = 0.1)
+ggsave(paste0(FIG_DIR, 'alignment_length_score.png'))
+
+# Look at the states

### 2015-11-09 alignments/lu_al_score_explore.R

@@ -1,0 +1,24 @@
+library(dplyr)
+library(ggplot2)
+
+
+df <- tbl_df(read.csv('../data/lid/lu_al_score_metadata.csv', header = TRUE,
+                      stringsAsFactors = FALSE))
+df_sample <- df[sample(c(1:nrow(df)), 10000), ]
+#il_93rd_HB2871,il_93rd_HB2871,2380,2439,897.0,3.730505,19.1226098537,1.55033898354
+
+# Plot some stuff
+
+## Distributions
+ggplot(df) + geom_histogram(aes(x = log(alignment_score)), color = 'white')
+ggplot(df) + geom_histogram(aes(x = log(lucene_score)), color = 'white')
+
+## Lucene score and alignment score
+pdat <- filter(df, focus_bill_id == unique(df$focus_bill_id)[4])
+pdat$focus_state <- substr(pdat$focus_bill_id, 1,2)
+pdat$right_state <- substr(pdat$right_bill_id, 1,2)
+pdat$same_state <- pdat$focus_state == pdat$right_state
+ggplot(pdat) + geom_point(aes(x = log(alignment_score), 
+                              y = log(lucene_score), 
+                              color = same_state), 
+                              alpha = 0.5)

### 2015-11-09 analysis/dyadic_analysis.R
adding other weight options

@@ -15,8 +15,12 @@ state_diffusion_edges <- read.csv("/Users/bdesmarais/Dropbox/professional/Resear
 ustates <- sort(unique(tolower(state_diffusion_edges$state_01)))
 ## correctly sized empty matrix
 align_amat <- matrix(0,length(ustates),length(ustates))
+align_amat_score <- matrix(0,length(ustates),length(ustates))
+align_amat_threshold <- matrix(0,length(ustates),length(ustates))
 ## row names
 rownames(align_amat) <- colnames(align_amat) <- ustates
+rownames(align_amat_score) <- colnames(align_amat_score) <- ustates
+rownames(align_amat_threshold) <- colnames(align_amat_threshold) <- ustates
 
 # Iteratively read in 100,000 rows at a time to build adjacency matrices
 ## all of the split files begin with x
@@ -33,22 +37,25 @@ for(i in 1:length(files)){
   state1 <- substr(align_dati$left_doc_id,1,2)
   state2 <- substr(align_dati$right_doc_id,1,2)
   ## subset to actual states (i.e., exclude dc and any other non-state jurisdictions)
-  align_dati <- subset(align_dati,is.element(state1,ustates) & is.element(state2,ustates))
+  align_dati <- subset(align_dati,is.element(state1,ustates) & is.element(state2,ustates) & state1 != state2)
   ## extract state ids from subsetted dataset
   state1 <- substr(align_dati$left_doc_id,1,2)
   state2 <- substr(align_dati$right_doc_id,1,2)
   ## create the weight according to which each alignment will contribute
-  alignment_weight <- rep(1,length(state1))
+  alignment_score <- align_dati$alignment_score
+  alignment_threshold <- 1*(align_dati$alignment_score > 100)
   ## add in the weight
   for(j in 1:length(alignment_weight)){
-    align_amat[cbind(state1[j],state2[j])] <- align_amat[cbind(state1[j],state2[j])] + alignment_weight[j] 
-    align_amat[cbind(state2[j],state1[j])] <- align_amat[cbind(state2[j],state1[j])] + alignment_weight[j]
+    align_amat[cbind(state1[j],state2[j])] <- align_amat[cbind(state1[j],state2[j])] + 1
+    align_amat[cbind(state2[j],state1[j])] <- align_amat[cbind(state2[j],state1[j])] + 1
[…]

### 2015-11-09 manuscript/text_reuse.tex

@@
 developed by Burges et al. (2015) we calculate text reuse scores for all pairs
-of bills in our dataset. We then use these scores in a model that classifies
-bills as equivalent and evaluate its performance with the validation data set.
+of bills in our dataset.
+
+We will then assess the scientific value of the text reuse scores in several different ways.
+First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text.
+Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills.
+Third, we assess the how well policy diffusion networks that have been established by previous research can be discovered using the amount of text reuse between states.
+And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.
 
@@
 
-[This might be overlapping a bit with your part]
-
 \section{Background}
@@
 
-In order to detect text reuse between bills we follow \citet{wilkerson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.
+Previous research on policy diffusion relies almost exclusively on small subsamples of legislation and hand coded data.
+Little work has been invested in investigating automated ways of detecting equivalent bills in order to measure policy diffusion.
+\citet{wilkerson2015tracing} use the Smith-Waterman local alignment algorithm 
+\citep{smith1981identification} to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US congress.
 
@@
 \begin{itemize}
+\item Discuss and find some literature on copying legislative language: 
+    \begin{itemize}
+        \item Interest groups and model legislation
+        \item Legislator's resources
+    \end{itemize}
 \item Policy diffusion (FL expand paragraph)
@@
 \item Text re-use in general
-\begin{itemize}
-\item Plaigirism
 \item Alignment (FL expand review of Wilkerson et al)
-
-\citet{wilkerson2015tracing} use the
-
-\end{itemize} 
 \item Discussion of text-based classification
@@
 
-Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 10 words).
+Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 5 matching 10-grams).
 Alignments between almost all bills are found and most of the alignments are procedural language.
@@
 Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents.
-Since the seraching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre selection of similar bills that are then exhaustively checked for text reuse:
+Since seaching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre-selection of similar bills that are then exhaustively checked for text reuse:
 
@@
 \begin{itemize}
-    \item Augment the timing dataset with the document similarity scores
-    \item
-
+    \item For the 1000 bill sample, retrieve the 100 most similar bills from the database 
+    \item Calculate the alignments between the focus bills and the retrieved bills
+    \item Assess the relationship of the search score with the alignment scores
 \end{itemize}

### 2015-11-10 manuscript/text_reuse.tex
updates to the paper

@@
 
-\textit{Alignments}\\
+\textit{Ideological Scores}\\
+For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.
+The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.
+
+We additionally construct a validation dataset of equivalent bills from information obtained from the National Conference of State Legislatures (NCSL).
+The NCSL publishes summary tables on specific policies, citing the relevant bills or sections in the state statutes of the states that have implemented regulations on this policy.
+We collected all these tables, and extracted all bills that address the same policy measure and that overlap with the time frame covered by our bill database.
+
+\section{Alignments}
+
 The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences.
@@
 Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time_size_selection.png}}
+\caption{Computation time for selection of bills.
+The Colors correspond to five selected bills (focus bill or left bill).
+For each of the bills, the best alignment with 1000 randomly selected bills (right bills) are calculated.
+The size of the dots corresponds to the logarithm of the length of the focus bill (in number of words), the x-axis corresponds to the logarithm of the size of the comparison bill and the y-axis corresponds to the logarithm of the computation time (in seconds).}
+\label{fig:time_size}
+\end{figure}
 
@@
 This shows that an exhaustive comparison of just the full bills (not separated into sections) would take about 100 years on a single machine.
-
-\begin{figure}[ht!]
-    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time_size_selection.png}}
-\caption{Computation time for selection of bills.
-The Colors correspond to five selected bills (focus bill or left bill).
-For each of the bills, the best alignment with 1000 randomly selected bills (right bills) are calculated.
-The size of the dots corresponds to the logarithm of the length of the focus bill (in number of words), the x-axis corresponds to the logarithm of the size of the comparison bill and the y-axis corresponds to the logarithm of the computation time (in seconds).}
-\label{fig:time_size}
-\end{figure}
 
@@
 
-\subsection*{Tasks}
+In order to evaluate how well the pre screening algorithms performs we select 1000 focus bills at random and retrieve the 1000 most similar bills according to the lucene score (described above).
+We then calculate find the best alignments between the sections of the focus bill and the section of each of the retrieved bills.
+This procedure generates a dataset of approximately 4 million alignments.
 
+For a first assessment of the usefulness of the lucene scores to select document that align well, we investigate the relationship of these scores with the alignment scores.
+Figure \ref{fig:lu_al_scores} displays the lucene scores against the alignment scores for a random sample of 500,000 alignments.
+The color indicates if the bills from which the alignment was genrated are from the same state, the larger triangles indicate scores for a bill compared to itself.
+In order to assess which alignments would get selected if thresholding, that is selecting for example the 100 closest bills according to the lucene score, we plotted all alignments for a sample of 9 focus bills.
+The green points indicate alignments from the 100 bills with the highest lucene scores for the respective focus bill.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/lu_al_scores.png}}
+    \caption{Alignment scores and lucene scores for a sample of 500,000 alignments (sections).
+The color indicates if the bills of the alignment are from the same state.
+The larger triangles indicate alignment and lucene scores for sections of bills compared to themselves.}
+\label{fig:lu_al_scores} 
+\end{figure}
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/closest100.png}}
+    \caption{Alignment and lucene scores for a sample of nine focus bills (panels).
+Each point in the plot is an alignment for a section of one comparison bill.
+The color indicates, if the section comes from a bill that is among the 100 bills with the highest lucene score for the specific focus bill.
+The large triangles indicate that an alignment is from a comparison of the focus bill with itself.}
+\label{fig:closest100} 
+\end{figure}
+
+\textit{Identifying procedural alignment text}
+
+Bills share a lot of language that is not related to the policy content of the bill.
+Especially within states bills have similar headers or formatting content.
+Further more there is procedural language and common phrases that are used across many, substantively unrelated bills and across states.
+In order to identify such alignments, we use the fact that we know that within states these matches are so common.
+We use the following procedure:
+
+For each state:\\
 \begin{itemize}
-    \item For the 1000 bill sample, retrieve the 100 most similar bills from the database 
-    \item Calculate the alignments between the focus bills and the retrieved bills
-    \item Assess the relationship of the search score with the alignment scores
+    \item sample n bills
+    \item calculate alignments between all sections of these bills
+    \item Identify matching alignments with one of the following:
+        \begin{itemize}
+            \item Perfect string match
+            \item length normalized alignment score (threshold?)
+            \item String similarity measure (threshold?)
         \end{itemize}
-
-\textit{Ideological Scores}\\
-For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.
-The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.
-
-We additionally construct a validation dataset of equivalent bills from information obtained from the National Conference of State Legislatures (NCSL).
-The NCSL publishes summary tables on specific policies, citing the relevant bills or sections in the state statutes of the states that have implemented regulations on this policy.
-We collected all these tables, and extracted all bills that address the same policy measure and that overlap with the time frame covered by our bill database.
+    \item label these alignments as boilerplate
+    \item (Optional:) Train classifier on this labeled data
+    \item For all alignments found remove the ones that are labeled as boilerplate by the classifier
+\end{itemize}
 

### 2015-11-11 alignments/lu_al_scores.py
all updates besides .rdata

@@ -1,0 +1,148 @@
+# Calculate alignments and lucene scores for sample of bills
+
+from __future__ import unicode_literals, print_function
+import sys
+from pprint import pprint
+import numpy as np
+import io
+from elasticsearch import Elasticsearch
+import json
+import time
+import copy
+import multiprocessing as mp
+
+sys.path.append('../../../policy_diffusion/lid/')
+from text_alignment import LocalAligner, AffineLocalAligner
+from database import ElasticConnection
+from utils.text_cleaning import clean_document
+from utils.general_utils import alignment_tokenizer
+from lid import LID
+
+# ==========================================================================
+# Config
+# --------------------------------------------------------------------------
+
+N_FOCUS_BILLS = 1000
+N_RIGHT_BILLS = 1000
+
+PROCESSES = 8
+
+META_FILE = '../../data/lid/lu_al_score_metadata.csv'
+TEXT_FILE = '../../data/lid/lu_al_score_text.txt'
+
+# ==========================================================================
+
+# Total timer
+start = time.time()
+
+# Select 1000 random bills
+np.random.seed(234234)
+random_lines = np.random.choice(a=565970, size=N_FOCUS_BILLS, replace=False).tolist()
+random_lines.sort()
+j = 0
+bill_ids = []
+with open('../../data/lid/bill_ids.txt', 'r') as id_file:
+    for i, line in enumerate(id_file):
+        if i == random_lines[j]:
+            bill_ids.append({'_id': line.strip('\n')})
+            j += 1
+            if j == N_FOCUS_BILLS:
+                break
+        else:
+            continue
+
+# Get them from the database
+print("Getting Focus bills from DB...")
+ec = Elasticsearch([{'host': '54.244.236.175', 'port': 9200}])
+results = ec.mget(body={'docs': bill_ids}, index='state_bills', 
+                  doc_type='bill_document', fields=['bill_document_last'])
+
+# Extract relevant info and clean text
+print("Extracting info...")
+bills = []
+for result in results['docs']:
+    doc = {}
+    doc['id_'] = result['_id']
+    doc['state'] = result['_id'].split('_')[0]
+    try:
+        doc['text'] = result['fields']['bill_document_last'][0] 
+        bills.append(doc)
+    except KeyError:
+        pass
+
+lid = LID(elastic_host='54.244.236.175', query_results_limit=N_RIGHT_BILLS, 
+          lucene_score_threshold=float('-Inf'))
+
[…]

### 2015-11-11 analysis/dyadic_analysis.R

@@ -15,13 +15,22 @@ state_diffusion_edges <- read.csv("/Users/bdesmarais/Dropbox/professional/Resear
 ustates <- sort(unique(tolower(state_diffusion_edges$state_01)))
 ## correctly sized empty matrix
 align_amat <- matrix(0,length(ustates),length(ustates))
+align_amat_score <- matrix(0,length(ustates),length(ustates))
+align_amat_threshold <- matrix(0,length(ustates),length(ustates))
 ## row names
 rownames(align_amat) <- colnames(align_amat) <- ustates
+rownames(align_amat_score) <- colnames(align_amat_score) <- ustates
+rownames(align_amat_threshold) <- colnames(align_amat_threshold) <- ustates
 
 # Iteratively read in 100,000 rows at a time to build adjacency matrices
 ## all of the split files begin with x
 files <- dir()
 files <- files[which(substr(files,1,1)=="x")]
+
+nwords <- function(text_vector){
+	nw <- unlist(lapply(strsplit(text_vector," "),"length"))
+	nw
+}
 
 # loop over files
 for(i in 1:length(files)){
@@ -33,22 +42,25 @@ for(i in 1:length(files)){
   state1 <- substr(align_dati$left_doc_id,1,2)
   state2 <- substr(align_dati$right_doc_id,1,2)
   ## subset to actual states (i.e., exclude dc and any other non-state jurisdictions)
-  align_dati <- subset(align_dati,is.element(state1,ustates) & is.element(state2,ustates))
+  align_dati <- subset(align_dati,is.element(state1,ustates) & is.element(state2,ustates) & state1 != state2)
   ## extract state ids from subsetted dataset
   state1 <- substr(align_dati$left_doc_id,1,2)
   state2 <- substr(align_dati$right_doc_id,1,2)
   ## create the weight according to which each alignment will contribute
-  alignment_weight <- rep(1,length(state1))
+  alignment_score <- align_dati$alignment_score
+  alignment_threshold <- 1*(align_dati$alignment_score > 100)
   ## add in the weight
   for(j in 1:length(alignment_weight)){
-    align_amat[cbind(state1[j],state2[j])] <- align_amat[cbind(state1[j],state2[j])] + alignment_weight[j] 
-    align_amat[cbind(state2[j],state1[j])] <- align_amat[cbind(state2[j],state1[j])] + alignment_weight[j]
[…]

### 2015-11-11 analysis/dyadic_analysis_exploring_scoring.R

@@ -1,0 +1,112 @@
+# Set my working directory
+setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
+
+# Note, the line below need only be run once, to split the big CSV into smaller files, sending to command line
+# pipe("split -l 100000 bill_to_bill_alignments.csv","r")
+
+# Read in sample of data on which to base variable names
+sample_dat <- read.csv("bill_to_bill_alignments.csv",nrows=10,stringsAsFactors=F)
+
+# Read in complete dyadic dataset from APSR 
+state_diffusion_edges <- read.csv("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
+
+# Create empty adjacency matrix in which to store alignment scores
+## unique state names
+ustates <- sort(unique(tolower(state_diffusion_edges$state_01)))
+## correctly sized empty matrix
+align_amat <- matrix(0,length(ustates),length(ustates))
+align_amat_score <- matrix(0,length(ustates),length(ustates))
+align_amat_threshold <- matrix(0,length(ustates),length(ustates))
+## row names
+rownames(align_amat) <- colnames(align_amat) <- ustates
+rownames(align_amat_score) <- colnames(align_amat_score) <- ustates
+rownames(align_amat_threshold) <- colnames(align_amat_threshold) <- ustates
+
+# Iteratively read in 100,000 rows at a time to build adjacency matrices
+## all of the split files begin with x
+files <- dir()
+files <- files[which(substr(files,1,1)=="x")]
+
+nwords <- function(text_vector){
+	nw <- unlist(lapply(strsplit(text_vector," "),"length"))
+	nw
+}
+
+# loop over files
+#for(i in 1:length(files)){
+i = 1	
+  ## read in 100k rows
+  align_dati <- read.csv(files[i],stringsAsFactors=F,header=ifelse(i==1,T,F))
+  ## make sure variables have the right names
+  names(align_dati) <- names(sample_dat)
+  ## extract state ids from bill labels
+  state1 <- substr(align_dati$left_doc_id,1,2)
+  state2 <- substr(align_dati$right_doc_id,1,2)
[…]

### 2015-11-11 analysis/topic_modeling.R

@@ -1,0 +1,33 @@
+load("~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/text_for_mallet.RData")
+
+library(mallet)
+
+set.seed(10)
+samp.ind <- sample(1:length(filenames),200000,rep=T)
+
+filenamesRS <- filenames[samp.ind]
+aligned_textRS <- aligned_text[samp.ind]
+
+mallet.instances <- mallet.import(filenamesRS,aligned_textRS,"~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/en.txt")
+
+topic.model <- MalletLDA(num.topics=20)
+	
+topic.model$loadDocuments(mallet.instances)
+	
+vocabulary <- topic.model$getVocabulary()
+word.freqs <- mallet.word.freqs(topic.model)
+
+topic.model$setAlphaOptimization(20, 50)
+
+topic.model$train(200)
+	
+topic.model$maximize(10)
+	
+doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
+topic.words <- mallet.topic.words(topic.model, smoothed=T, normalized=T)
+
+topic.probs <- apply(doc.topics,2,mean)
+
+mallet.top.words(topic.model, topic.words[6,],20)
+
+

### 2015-11-11 analysis/topic_modeling_prep.R

@@ -1,0 +1,56 @@
+# Set my working directory
+setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
+
+# Note, the line below need only be run once, to split the big CSV into smaller files, sending to command line
+# pipe("split -l 100000 bill_to_bill_alignments.csv","r")
+
+# Read in sample of data on which to base variable names
+sample_dat <- read.csv("bill_to_bill_alignments.csv",nrows=10,stringsAsFactors=F)
+
+# Iteratively read in 100,000 rows at a time to build adjacency matrices
+## all of the split files begin with x
+files <- dir()
+files <- files[which(substr(files,1,1)=="x")]
+
+library(mallet)
+
+aligned_text <- NULL
+filenames <- NULL
+
+# loop over files
+for(i in 1:length(files)){	
+  ## read in 100k rows
+  align_dati <- read.csv(files[i],stringsAsFactors=F,header=ifelse(i==1,T,F))
+  ## make sure variables have the right names
+  names(align_dati) <- names(sample_dat)
+  
+  filenames <- c(filenames,paste("~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/alignment_files/all_alignments/",align_dati$left_doc_id,align_dati$right_doc_id,align_dati$alignment_section_index,".txt",sep=""))
+  
+  aligned_text <- c(aligned_text,align_dati$left_alignment_text)
+  
+  if(i/5==round(i/5)) print(i)
+  
+  }
+ 
+save(list=c("filenames","aligned_text"),file="~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/text_for_mallet.RData")
+
+  mallet.instances <- mallet.import(filenames[1:100000],aligned_text[1:100000],"~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/en.txt")
+
+
+	topic.model <- MalletLDA(num.topics=20)
+	
+	topic.model$loadDocuments(mallet.instances)
+	
+	vocabulary <- topic.model$getVocabulary()
+	word.freqs <- mallet.word.freqs(topic.model)
+
+	topic.model$setAlphaOptimization(20, 50)
+	
+	topic.model$maximize(10)
+	
+	doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
[…]

### 2015-11-11 data_collection/alignments/alignment_timing.R

@@ -1,32 +1,0 @@
-library(ggplot2)
-library(dplyr)
-
-df <- tbl_df(read.csv('../../data/lid/alignment_timing.csv', header = TRUE))
-
-df <- filter(df, as.character(focus_bill) != as.character(right_bill))
-# Remove identity bill pairs
-
-df$total_length = df$left_bill_length + df$right_bill_lenght
-
-ggplot(df[c(1:5000), ]) + geom_point(aes(x = log(right_bill_lenght), y = log(time),
-                                     color = focus_bill, size = log(left_bill_length)),
-                                     alpha = 0.3) + 
-    guides(color = guide_legend(override = list(alpha = 1)),
-           size = guide_legend(override = list(alpha = 1))) + 
-    theme_bw()
-
-ggplot(df) + geom_point(aes(x = log(right_bill_lenght), y = log(time),
-                                   size = log(left_bill_length)),
-                                   alpha = 0.1) + 
-    guides(color = guide_legend(override = list(alpha = 1)),
-           size = guide_legend(override = list(alpha = 1))) + 
-    theme_bw()
-
-ggplot(df) + geom_histogram(aes(log(time)), color = 'white') + 
-    theme_bw()
-
-ggplot(df) + geom_histogram(aes(log(alignment_length)), color = 'white') + 
-    theme_bw()
-
-ggplot(df) + geom_point(aes(y = log(score), x = log(alignment_length),
-                            size = log(total_length)), alpha = 0.1)

### 2015-11-11 manuscript/text_reuse.tex
updated ms

@@
 \usepackage{multirow}
+\usepackage{rotating}
 \usepackage{amsmath}
@@
 
+\subsection{Topic Modeling}
+
+Topics of 20 inferred on 200,000 alignments.
+
+\begin{sidewaystable}
+\centering
+\scalebox{.425}{
+\begin{tabular}{rllllllllllllllllllll}
+  \hline
+ & 0.135 & 0.119 & 0.087 & 0.073 & 0.067 & 0.058 & 0.054 & 0.053 & 0.043 & 0.043 & 0.041 & 0.037 & 0.034 & 0.033 & 0.032 & 0.027 & 0.026 & 0.021 & 0.012 & 0.007 \\ 
+  \hline
+1 & board & state & general & tax & state & property & section & child & means & health & medical & vehicle & employer & states & feet & benefit & commission & insurer & salts & state \\ 
+  2 & department & enacted & assembly & section & court & person & information & person & sale & care & person & insurance & individual & united & distance & school & state & insurance & isomers & party \\
+  3 & state & legislature & senate & income & order & principal & electronic & abortion & product & patient & department & motor & employee & state & amended & corporation & interstate & commissioner & substances & ring \\
+  4 & public & people & enacted & amount & person & interest & statement & medical & person & plan & applicant & policy & employment & member & point & public & compact & information & substance & consumer \\
+  5 & education & section & state & year & action & power & act & woman & manufacturer & services & patient & portable & service & presidential & read & student & member & section & preparation & jwh \\
+  6 & county & act & appointed & qualified & section & real & notice & parent & device & section & license & electronics & work & official & section & charter & states & company & compound & nurse \\ 
+  7 & services & firearm & house & revenue & law & company & date & degree & products & physician & marijuana & coverage & employees & election & south & district & rules & policy & mixture & substituted \\
+  8 & program & amended & members & taxable & violation & attorney & security & age & dealer & provider & qualifying & person & business & vote & west & director & compacting & association & controlled & extent \\
+  9 & director & read & member & credit & support & trust & record & physical & including & medical & identification & driver & performed & agreement & north & section & effective & contract & chemical & food \\
+  10 & office & ammunition & force & code & attorney & agent & subsection & physician & food & individual & application & travel & benefits & president & line & students & duties & state & quantity & practice \\
+  11 & local & represented & representatives & years & enforcement & agreement & provided & section & facility & act & registration & insurer & period & popular & minutes & specific & bylaws & life & material & indole \\
+  12 & agency & york & task & investment & jurisdiction & authority & service & death & equipment & person & section & vendor & services & votes & degrees & purpose & date & subsection & schedule & methyl \\
+  13 & fund & firearms & governor & internal & proceeding & owner & address & performed & drug & treatment & card & transportation & labor & slate & east & directors & law & financial & including & licensure \\
+  14 & year & texas & speaker & community & petition & entity & effective & means & retail & licensed & registry & customer & compensation & national & seconds & general & provided & contracts & specifically & information \\
+  15 & division & relating & committee & excess & subsection & means & financing & family & sold & coverage & registered & commercial & section & constitution & street & articles & act & subject & oil & compact \\
+  16 & health & chapter & court & percent & tribunal & business & person & abuse & energy & practice & gift & service & sex & article & code & interests & article & person & plant & agency \\ 
+  17 & secretary & arizona & commonwealth & january & act & limited & number & condition & distributor & provide & information & enrolled & race & elector & traffic & religious & members & including & listed & states \\
+  18 & fiscal & manufactured & president & date & civil & act & law & drug & system & qualified & caregiver & liability & time & number & adding & officer & rule & risk & grams & home \\ 
+  19 & provide & related & term & entity & subject & liability & debtor & unborn & property & provided & criminal & company & sexual & chief & intersection & report & person & documents & excepted & substitution \\
+  20 & city & federal & resolved & beginning & party & estate & days & years & include & means & board & section & organization & candidate & quarter & person & executive & report & milligrams & reporting \\
+   \hline
+\end{tabular}
+}
+\end{sidewaystable}
+
 \subsection{Diffusion networks and Text re-use}

### 2015-11-17 manuscript/text_reuse.tex
added topic model write up

--- 2015-11-10 manuscript/text_reuse.tex
@@
 
+\subsection{Topic Modeling}
+
+We apply statistical topic modeling via Latent Dirichlet Allocation (LDA) \citep{blei2003} to the alignment text with two objectives.\footnote{We use the R package \texttt{mallet} \citep{mallet} for the topic modeling application.} First, we want to see whether the major topical themes that emerge are consistent with policy domains that we would expect to be prominently featured in texts that capture the diffusion of public policy.
+Second, we want to see whether we can identify topics that correspond to boilerplate/procedural text, which we may want to remove from the alignments to focus the analysis on substantive policy language.
+In our first cut we use a model with 20 topics.
+The average alignment is short, with little more than 25\% exceeding 140 characters -- the maximum length of a Tweet.
+There are 52,735 unique terms in our vocabulary, after removing a standard list of stop words.
+In Table \ref{tab:top100words} we present the top 100 terms appearing in our corpus.
+
+\begin{table}[ht]
+\rule{\textwidth}{1pt} \\ \vspace{-1cm}
+\begin{quotation}
+\noindent state person section states act means health public member general commission department law information provided insurance including board subsection legislature benefit court individual property order services care action business time pursuant united date year subject interstate federal compact school insurer corporation required medical chapter provide party entity vehicle amount notice people assembly agreement tax qualified provisions attorney agency limited made service authority child purposes years commissioner education report days policy employer members company code contract employee interest authorized effective statement district purpose ii application period number credit plan include senate income system amended issued reasonable part program director patient requirements
+\end{quotation} \vspace{-.5cm}
+\rule{\textwidth}{1pt} \vspace{-.2cm}
+\caption{Top 100 words, listed left-to-right, in the alignments corpus.}
+\label{tab:top100words}
+\end{table}
+
+The topic modeling results are presented in Table \ref{tab:topics}.
+We see that most topics correspond to recognizable policy domains.
+However, some topics, such as Topic 9, which appears to be a mix of automobile policy and abortion policy, appear to consist of more than one distinct policy domain.
+As such, we should try running this with more topics.
+Topic 17 appears to be a boilerplate topic.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rl}
+  \hline
+  \hline
+6 & benefit corporation public director officer specific interests directors person purpose \\ 
+  16 & state order child section support law application employer enforcement court \\ 
+  14 & salts isomers food substances substance means preparation product compound mixture \\ 
+  3 & court state order person petition section proceeding law appraisal jurisdiction \\ 
+  8 & feet distance medical patient marijuana point qualifying south north west \\ 
+  20 & information electronic consumer service section insurance notice portable electronics means \\ 
+  9 & vehicle motor person means abortion woman medical child dealer death \\ 
+  18 & property interest statement section person trust real transfer agreement financing \\ 
+  5 & person offense age sexual years criminal court officer sex guilty \\ 
+  15 & states united state presidential election official member vote president popular \\ 
+  17 & state enacted legislature general assembly people amended section read senate \\ 
+  2 & action person section court state civil violation attorney reasonable degree \\ 
+  7 & qualified tax section investment revenue entity credit amount fund code \\ 
+  19 & health care patient practice medical physician licensed person means services \\ 
+  12 & department health state services act public year federal care program \\ 
+  4 & appointed members house attorney senate power principal member authority representatives \\ 
+  1 & individual employer year years taxable service income employee period january \\ 
+  10 & insurance insurer policy commissioner company section coverage contract state plan \\ 
+  11 & state commission interstate compact member states rules compacting effective law \\ 
+  13 & school student board district education public charter state students county \\ 
+   \hline
+\end{tabular}
+\caption{Results from 200 iterations of LDA with 10 iterations of hyper parameter optimization.
+Top 10 words in each topic listed for each topic.
+Topics listed in order of frequency of appearance within documents, beginning in the first row of the table with the most frequent topic.}
+\label{tab:topics}
+\end{table}
+
+\begin{table}[ht]
+\rule{\textwidth}{1pt} \\ \vspace{-1cm}
+\begin{quotation}
+\noindent state person section states act means health public member general commission department law information provided insurance including board subsection legislature benefit court individual property order services care action business time pursuant united date year subject interstate federal compact school insurer corporation required medical chapter provide party entity vehicle amount notice people assembly agreement tax qualified provisions attorney agency limited made service authority child purposes years commissioner education report days policy employer members company code contract employee interest authorized effective statement district purpose ii application period number credit plan include senate income system amended issued reasonable part program director patient requirements
+\end{quotation} \vspace{-.5cm}
+\rule{\textwidth}{1pt} \vspace{-.2cm}
+\caption{Top 100 words, listed left-to-right, in the alignments corpus.}
+\label{tab:top100words}
+\end{table}
+
 \subsection{Diffusion networks and Text re-use}

### 2015-11-30 manuscript/tables/ideology_regressions.tex
First cut at ideology analysis
- see updated datasets on HPC

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Nov 30, 2015 - 11:50:41
\begin{table}[!htbp] \centering 
  \caption{Regression results for log-linear models for ideology
analysis. The models from left to right: 1) Alignment score
by section (dependence not considered yet),
2) Sum of alignment scores of all sections of
bill dyads, 3) Number of alignments of bill dyad, 4)
mean alignment score of dyad, 5) penalized mean alignment
score of dyad, 5) maximum alignment score of dyad. } 
  \label{tab:ideo_reg} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & Score & Sum & Number & Mean & Penal & Max \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ideology\_dist & $-$0.029$^{***}$ & $-$0.034$^{***}$ & $-$0.009$^{***}$ & $-$0.025$^{***}$ & 0.002 & $-$0.031$^{***}$ \\ 
  & (0.0003) & (0.0005) & (0.0003) & (0.0004) & (0.002) & (0.0004) \\ 
  & & & & & & \\ 
 Constant & 3.745$^{***}$ & 4.300$^{***}$ & 0.486$^{***}$ & 3.814$^{***}$ & 2.982$^{***}$ & 3.972$^{***}$ \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) & (0.004) & (0.001) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 3,957,875 & 1,745,336 & 1,745,336 & 1,745,336 & 1,745,336 & 1,745,336 \\ 
Adjusted R$^{2}$ & 0.003 & 0.003 & 0.001 & 0.003 & 0.00000 & 0.003 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2015-11-30 manuscript/text_reuse.tex
First cut at ideology analysis
- see updated datasets on HPC

@@
 
+\subsection{Ideological Distance of Aligned Bills}
+
+The MALP dataset contains ideal points for about $20,000$ state legislators.
+The \texttt{openstates} API contains data and identifiers on $12,000$ legislators.
+Of these we where able to uniquely match about $8,000$ legislators.
+This allowed us to obtain ideal points for 395,474 ($69\%$) bills and 1,745,336 ($50\%$) pairs of bills.
+
+In order to assess the validity of text reuse as a measure of substantive policy overlap, we expect the quality of the alignments to be inversely correlated to the distance of the bills sponsors' ideal points.
+The MALP ideal points are located on a common scale across all states, the distance between sponsors from different states is therefore meaningful.
+
+In the following sections we present several analyses to assess this correlation.
+When we are generating the alignments the bills are split up into sections.
+Table \ref{tab:ideo_reg} displays results for several methods of combining multiple alignments across sections of the same bill dyad as well as treating sections as the unit of analysis.
+For the case where we aggregate to the bill level, simple bivariate linear regression is used to test for a correlation.
+For the section level results we estimate a hierarchical model with section pairs nested within bill pairs.
+
+\input{tables/ideology_regressions.tex}
+
 \subsection{Tasks}
 \begin{itemize}
-\item Develop bill metadata dataset (FL)
-\begin{itemize}
-\item unique bill identifier
-\item sponsor identifier from  MALP data
-\item state identifier
-\item chamber identifier
-\item Introduction date
-\item Anything else, even if some is missing (status, committees, etc)
-\end{itemize}
-\item Develop bill-to-bill edgelists (FL)
-\begin{itemize}
-\item Sparse dyadic dataset (i.e., no observations when there is 0 alignment/overlap)
-\item alignment score(s)
-\item name of a text file in which aligned text is stored
-\end{itemize}
 \item Topic models, possibly of a relational form, applied to aligned text

### 2015-11-30 analysis/ideology/ideology.R

@@ -1,0 +1,143 @@
+library(dplyr)
+library(ggplot2)
+library(lme4)
+library(stargazer)
+
+# ==============================================================================
+# Data preprocessing
+# ==============================================================================
+
+# Metadata
+meta <- read.csv('../../data/bill_metadata.csv', stringsAsFactors = FALSE,
+                 header = TRUE, quote = '"')
+
+## Clean it up
+meta$session <- NULL
+### Make 'None' NA
+meta[meta == 'None'] <- NA
+### Fix column classes
+for(i in grep("date_", names(meta))){
+    var <- sapply(as.character(meta[, i]), substr, 1, 10)
+    var
+    meta[, i] <- as.Date(x = var)
+}
+for(col in c("state", "chamber", "bill_type")){
+    meta[, col] <- as.factor(meta[, col])
+}
+meta$sponsor_idology <- as.numeric(meta$sponsor_idology)
+meta$num_sponsors <- as.integer(meta$num_sponsors)
+
+## Make dplyr object
+meta <- tbl_df(meta)
+
+# Alignments
+alignments <- tbl_df(read.csv('../../data/lid/bill_to_bill_scores_only.csv', 
+                              colClasses = c("factor", "factor", "numeric"),
+                              skip = 1) )
+
+## Match alignments with ideology scores
+temp <- mutate(meta, left_doc_id = unique_id, left_ideology = sponsor_idology) %>%
+    select(left_doc_id, left_ideology)
+df <- left_join(alignments, temp, by = "left_doc_id")
+temp <- mutate(meta, right_doc_id = unique_id, right_ideology = sponsor_idology) %>%
+    select(right_doc_id, right_ideology)
+df <- left_join(df, temp, by = "right_doc_id")
+rm(temp)
+df <- mutate(df, ideology_dist = (left_ideology - right_ideology)^2,
+             dyad_id = as.factor(paste0(left_doc_id, right_doc_id)))
+df_nona <- filter(df, !is.na(ideology_dist))
+
+## Aggregate to bill level
+penal_mean <- function(x) sum(x) / exp(length(x) - 1)
+aggr <- group_by(df, left_doc_id, right_doc_id) %>%
+    summarize(sum_score = sum(alignment_score), n_align = n(),
+              mean_score = mean(alignment_score), 
+              penal_score = penal_mean(alignment_score),
+              max_score = max(alignment_score),
+              ideology_dist = ideology_dist[1])
+
+# ==============================================================================
+# Descriptives
+# ==============================================================================
+
[…]

### 2015-11-30 etl/sep_sl_scores_text.py

@@ -1,0 +1,20 @@
+# Split up the bill to bill alignment score data set to have a smaller dataset
+# without the alignment text
+
+from __future__ import unicode_literals
+import io
+import time
+
+infile = io.open('../data/lid/bill_to_bill_alignments.csv', 'r', encoding = 'utf-8')
+outfile = io.open('../data/lid/bill_to_bill_scores_only.csv', 'w+', encoding = 'utf-8')
+
+outfile.write('left_doc_id,right_doc_id,alignment_score\n')
+for i,line in enumerate(infile):
+    els = line.split(',')
+    new_line = '{},{},{}\n'.format(els[0], els[1], els[-2])
+    outfile.write(new_line)
+    if i % 10000 == 0:
+        print i
+
+infile.close()
+outfile.close()

### 2015-12-08 manuscript/text_reuse.tex
pointer to R script in ideology analysis
cleaned up the paper a bit and added some content

@@
 \mmddyyyydate
+\doublespacing
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \date{\today}
-\author{}
+\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}
 
@@
 
-\begin{abstract}
-Much research has been focused on the diffusion of policy ideas in US state
-legislatures. Most of this research uses hand coded data sets that identify
-equivalent bills and analyze patterns of adoption of these bills. Bills on
-equivalent policies often contain the same language, since legislators use past
-legislation from other states or model legislation from interest groups as
-templates when drafting new bills or model legislation from interest groups. In
-this paper we evaluate the effectives of text reuse measures to detect bills
-that address the same policy issues. We find that... 
+\begin{abstract} Much research has been focused on the diffusion of policy ideas in US state legislatures.
+Most of this research uses hand coded data sets that identify equivalent bills and analyze patterns of adoption of these bills.
+Bills on equivalent policies often contain the same language, since legislators use past legislation from other states or model legislation from interest groups as templates when drafting new bills or model legislation from interest groups.
+In this paper we evaluate the effectives of text reuse measures to detect bills that address the same policy issues.
+We find that...
 \end{abstract}
@@
 
-How ever, it is not clear, how well text reuse is suited to to detect real
-policy diffusion. There are several complications that we are addressing in this
-paper. First, every bill has procedural content that is not related to the
-policy content of the bill. Since every state legislature has a set of such
-standard or boiler plate text in each bill, there will be significant text reuse
-between bills in the same state and possibly also between bills from different
-states. Second, it is not obvious how much text reuse will mean substantive
-
-policy overlap. Given that each bill pair has a continuous proportion of
-overlapping text, setting the threshold too low might mean to classify bills as
-equivalent that are only in the same policy area, or are on a similar issue, but
-are opposed in content. On the other hand, setting the threshold too high could
-mean overlooking equivalent bills because of small insignificant changes to the
-text.
-
-In this paper we address these issues and evaluate how much policy overlap can
-be detected using text reuse measures. Following Wilkerson et al. (2015) we use
-supervised machine learning to separate boiler plate from substantive text. We
-further more use an original data set on policy diffusion to evaluate how much
-equivalent policy can be detected using measures of text reuse. Using the system
-developed by Burges et al. (2015) we calculate text reuse scores for all pairs
-of bills in our dataset.
-
+ How ever, it is not clear, how well text reuse is suited to to detect real policy diffusion.
+There are several complications that we are addressing in this paper.
+First, every bill has procedural content that is not related to the policy content of the bill.
+Since every state legislature has a set of such standard or boiler plate text in each bill, there will be significant text reuse between bills in the same state and possibly also between bills from different states.
+Second, it is not obvious how much text reuse will mean substantive policy overlap.
+Given that each bill pair has a continuous proportion of overlapping text, setting the threshold too low might mean to classify bills as equivalent that are only in the same policy area, or are on a similar issue, but are opposed in content.
+On the other hand, setting the threshold too high could mean overlooking equivalent bills because of small insignificant changes to the text.
+ In this paper we address these issues and evaluate how much policy overlap can be detected using text reuse measures.
+Following Wilkerson et al.
+(2015) we use supervised machine learning to separate boiler plate from substantive text.
+We further more use an original data set on policy diffusion to evaluate how much equivalent policy can be detected using measures of text reuse.
+Using the system developed by Burges et al.
+(2015) we calculate text reuse scores for all pairs of bills in our dataset.
 We will then assess the scientific value of the text reuse scores in several different ways.
@@
 
-This work has several important implications. First, it allows us to estimate,
-how policies are transferred between states. Do state legislators work mainly
-from templates from other states or interest groups, or to what extent do
-legislators draft their own bill text. Furthermore, text reuse is a relatively
-simple metric to calculate for large amounts of text. Previous scholars of
-policy diffusion mainly relied on case studies or manually coded data sets of
-policy diffusion in few policy areas. If working copying text forms a
-significant portion of how legislators adopt policies from other states, text
-reuse can be used to easily gather comprehensive data sets on policy diffusion.
+This work has several important implications.
+First, it allows us to estimate, how policies are transferred between states.
+Do state legislators work mainly from templates from other states or interest groups, or to what extent do legislators draft their own bill text.
+Furthermore, text reuse is a relatively simple metric to calculate for large amounts of text.
+Previous scholars of policy diffusion mainly relied on case studies or manually coded data sets of policy diffusion in few policy areas.
+If working copying text forms a significant portion of how legislators adopt policies from other states, text reuse can be used to easily gather comprehensive data sets on policy diffusion.
 
@@
 Little work has been invested in investigating automated ways of detecting equivalent bills in order to measure policy diffusion.
-\citet{wilkerson2015tracing} use the Smith-Waterman local alignment algorithm 
-\citep{smith1981identification} to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US congress.
+\citet{wilkerson2015tracing} use the Smith-Waterman local alignment algorithm (SW algorithm) \citep{smith1981identification} to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US congress.
 
-\subsection{Tasks}
-\begin{itemize}
-\item Discuss and find some literature on copying legislative language: 
-    \begin{itemize}
-        \item Interest groups and model legislation
-        \item Legislator's resources
-    \end{itemize}
-\item Policy diffusion (FL expand paragraph)
-\item Text re-use in CBP in bills 
-\item Text re-use in general
-\item Alignment (FL expand review of Wilkerson et al)
-\item Discussion of text-based classification
-\end{itemize}
+\section{Detecting Text Reuse}
+
+In this study we use the same algorithm as \citet{wilkerson2015tracing} to detect matching sequences of text in state bills.
+We also follow their procedure in splitting the bills up in sections as the unit of analysis.
+However, our procedure differs in the pre-screening of sections that are compared with the Smith-Waterman algorithm and in the procedure to identify boiler plate text.
+
+\citet{wilkerson2015tracing}'s criterion for pre-screening bills is that they have to match at least 5 10-grams.
+This means that there has to be a minimum of a 15 character exact match between two bill sections in order to consider them for more in depth analysis with the SW algorithm.
+We see this as a too restrictive criterion and choose a different approach instead.
+Our text data is stored in an Elastic Search database.
+Elastic search is an open source web search engine which is designed to find document that match a search query.
+We utilize the `more like this' search engine, which is designed to find documents that are similar to a given document [FILL IN CITATION].
+In principle it works in the following way: From the focus document, the $k$ n-grams with the highest tf-idf scores\footnote{[Explain these terms in this footnote]} are selected and transformed into a search vector.
+Then, for each document in the collection, a variation of the cosine similarity\footnote{[explain cosine similarity, and reference the exact fromula from the documentation]} is calculated and the $n$ with the highest scores are selected.
+This procedure is necessary, since the SW algorithm is computationally demanding and an exhaustive comparison is not feasible (we have about $500,000$ bills, assuming each bill consists on average of four sections this would amount to about $2 * 10^{12}$ comparisons).
+[FILL IN PARAMETER VALUES]
+
+Furthermore, we do not rely on human coders to extract and classify boiler plate text.
+We identified two types of boiler plate text: 1) Procedural language like bill and section headers, common legislative phrases etc.
+2) Topic specific boiler plate, like definitions of tax brackets, [another example], etc.
+In order to detect these kinds of boiler plate language, we pre-screen all bill and discard $?-grams$ with a tf-idf score below a certain threshold.
+Boiler plate text is expected to have very low tf-idf scores, since it appears often across bills but with low frequency within bills.
+Additonally, in order to detect the second kind of boiler plate, we exclude $?-grams$ that where passes several times in the same legislature, assuming that the exact same provisions will not be introduced several times in the same legislature.
 
@@
 
-\begin{figure}[ht!]
-    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time_size_selection.png}}
-\caption{Computation time for selection of bills.
-The Colors correspond to five selected bills (focus bill or left bill).
-For each of the bills, the best alignment with 1000 randomly selected bills (right bills) are calculated.
-The size of the dots corresponds to the logarithm of the length of the focus bill (in number of words), the x-axis corresponds to the logarithm of the size of the comparison bill and the y-axis corresponds to the logarithm of the computation time (in seconds).}
-\label{fig:time_size}
-\end{figure}
+\section{Analysis}
 
-In order to assess the computational burden the local alignment algorithm poses we test the implementation of the alignment algorithm (Burgess et al.
-2015) on a set of 1000 randomly selected bills.
-In a first pass we calculate the alignments  between all pairs of the full bills (not divided into sections).
-Figure \ref{fig:time_size} displays the relationship between bill length and computation time.
-As expected the time increases exponentially with the length of the bills.
-Figure \ref{fig:time} displays a histogram of the logarithm of the computation time (in seconds).
-Computation time varies between $0.001s$ and $1,650s$ with $75\%$ of the distribution below $0.1s$ and a median time of $0.03s$.
-This shows that an exhaustive comparison of just the full bills (not separated into sections) would take about 100 years on a single machine.
-
-\begin{figure}[ht!]
-    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time.png}}
-\caption{Histogram of computation time for all analyzed bills.}
-\label{fig:time} 
-\end{figure}
-
-Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 5 matching 10-grams).
-Alignments between almost all bills are found and most of the alignments are procedural language.
-This is apparent in Figure \ref{fig:state_to_state} which displays the average alignment score for bills from Illinois (left panel) and Washington (right panel) for all other states in the sampled data set (x-axis).
-Especially for Illinois there is a much higher alignment score for bills from the same state.
-This shows that a minimum threshold and a classifier for procedural language are necessary.
-
-\begin{figure}[ht!]
-    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/state_to_state.png}}
-\caption{Average alignment scores between states.
-The left panel corresponds to `left bills' from Illinois, the right panel to bills from Washington.
-Each bar displays the average score of the best alignment found between bills of the states.}
-\label{fig:state_to_state} 
-\end{figure}
-
-In order to make the computation more feasible, we rely on a similar strategy as \citet{wilkerson2015tracing}.
-Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents.
-Since seaching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre-selection of similar bills that are then exhaustively checked for text reuse:
-
-\begin{enumerate}
-\item All bills are stored in the database in n-grams of size 2-5
-\item Select the 25 n-grams with the highest tf-idf score in the query document
-\item Calculate a score slightly adapted cosine similarity score between the selected n-gram vector and all full document n-gram vectors in the database\footnote{See \url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html} for details on the similarity scoring in Elastic Search}
-\end{enumerate}
-
-In order to evaluate how well the pre screening algorithms performs we select 1000 focus bills at random and retrieve the 1000 most similar bills according to the lucene score (described above).
-We then calculate find the best alignments between the sections of the focus bill and the section of each of the retrieved bills.
-This procedure generates a dataset of approximately 4 million alignments.
-
-For a first assessment of the usefulness of the lucene scores to select document that align well, we investigate the relationship of these scores with the alignment scores.
-Figure \ref{fig:lu_al_scores} displays the lucene scores against the alignment scores for a random sample of 500,000 alignments.
-The color indicates if the bills from which the alignment was genrated are from the same state, the larger triangles indicate scores for a bill compared to itself.
-In order to assess which alignments would get selected if thresholding, that is selecting for example the 100 closest bills according to the lucene score, we plotted all alignments for a sample of 9 focus bills.
-The green points indicate alignments from the 100 bills with the highest lucene scores for the respective focus bill.
-
-\begin{figure}[ht!]
-    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/lu_al_scores.png}}
-    \caption{Alignment scores and lucene scores for a sample of 500,000 alignments (sections).
-The color indicates if the bills of the alignment are from the same state.
-The larger triangles indicate alignment and lucene scores for sections of bills compared to themselves.}
-\label{fig:lu_al_scores} 
-\end{figure}
-
-\begin{figure}[ht!]
-    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/closest100.png}}
-    \caption{Alignment and lucene scores for a sample of nine focus bills (panels).
-Each point in the plot is an alignment for a section of one comparison bill.
-The color indicates, if the section comes from a bill that is among the 100 bills with the highest lucene score for the specific focus bill.
-The large triangles indicate that an alignment is from a comparison of the focus bill with itself.}
-\label{fig:closest100} 
-\end{figure}
-
-\textit{Identifying procedural alignment text}
-
-Bills share a lot of language that is not related to the policy content of the bill.
-Especially within states bills have similar headers or formatting content.
-Further more there is procedural language and common phrases that are used across many, substantively unrelated bills and across states.
-In order to identify such alignments, we use the fact that we know that within states these matches are so common.
-We use the following procedure:
-
-For each state:\\
-\begin{itemize}
-    \item sample n bills
-    \item calculate alignments between all sections of these bills
-    \item Identify matching alignments with one of the following:
-        \begin{itemize}
-            \item Perfect string match
-            \item length normalized alignment score (threshold?)
-            \item String similarity measure (threshold?)
-        \end{itemize}
-    \item label these alignments as boilerplate
-    \item (Optional:) Train classifier on this labeled data
-    \item For all alignments found remove the ones that are labeled as boilerplate by the classifier
-\end{itemize}
-
-\subsection{Tasks}
-\begin{itemize}
-\item Scrape Google urls for NCSL tables (FL) -- lower priority
-    \begin{enumerate}
-        \item Scraped 64 urls. 
-        \item Can't get around the Google API limitation yet. Also get blocked when trying to scrape the search result.
-    \end{enumerate}
-
-\item Extract state  \& bill \# from tables (FL) -- lower priority
-    \begin{enumerate}
-        \item Didn't do this yet, let's first check how many are potentially suitable and then probably better to do by hand
-    \end{enumerate}
-\item See tasks in analysis -- create metadata file and dyadic file, then put them on the ACI (FL).
-    \begin{enumerate}
-        \item We have a preliminary dyadic file for all similar bill pairs and their alignment scores (this is from the LID approach: each bill is only compared to the 100 most similar ones)
-        \item Matt transfering the database to a new server at the moment, it is therefore unavailable. Should be online again sometime today.
-    \end{enumerate}
-\item Store MALP data on ACI and make sure the identifiers match those in the bill data (FL). 
-    \begin{enumerate}
-        \item data is on aci
-        \item Legislators can be matched by Name, State, Pary and Term.
-This information should be contained in the database.
-If not, the open state api has a legislator search method, that returns all necessary information.
-    \end{enumerate}
-\item Put policy diffusion data in project folder on ACI (BD).
-\end{itemize}
-
-\section{Analysis}
-Below we list X separate analyses designed to test the degree to which measuring text reuse measures policy overlap/diffusion.
-
-\begin{itemize}
-\item We use statistical topic modeling to assess the major content areas represented by the text identified in the alignment algorithm.
-We consider whether the resultant topics align with policy areas.
-\item The Measuring American Legislators Project (MALP) provides data that we will use to assess the significance of text re-use in US state legislation \citet{shor2011}.
-The most recent release of the MALP data covers 1993-2014.
-The MALP data provide ideological scores of legislators on an annual basis.
-We conduct a bill-level statistical network analysis to see whether the rate of bill-to-bill alignment is positively related to the ideological similarity of their sponsors.
-\item We conduct a state-level analysis to see whether the volume of state-to-state text alignment is positively related to the policy diffusion networks inferred in \citet{desmarais2015}.
-\end{itemize}
+We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence.
+First, we apply topic models to the sequences that are identified by the SW algorithm as matching sequences.
+This provides a rough idea of how many of the alignments are substantial and how much procedural language and not substantively significant language gets picked up by the algorithm.
+Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}.
+And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores.
+If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
 
@@
 
+%R script for this analysis: '/analysis/ideology.R'
+
 The MALP dataset contains ideal points for about $20,000$ state legislators.
@@
 Table \ref{tab:ideo_reg} displays results for several methods of combining multiple alignments across sections of the same bill dyad as well as treating sections as the unit of analysis.
-For the case where we aggregate to the bill level, simple bivariate linear regression is used to test for a correlation.
-For the section level results we estimate a hierarchical model with section pairs nested within bill pairs.
+For the case where we aggregate to the bill level, simple bivariate linear regression is used to test for a correlation, since the data has network structure we calculate standard errors with the quadratic assignment procedure (QAP) [note, Table \ref{tab:ideo_reg} still has normal standard errors, we are runnign the QAP at the moment] \citep{krackardt1987qap}.
+There are six models in Table \ref{tab:ideo_reg}.
+The unit of analysis of the first model is the bill section, the other five models are on the bill level.
+Model (1) has the alignment score of the section dyad as the dependent variable, models (2) - (5) use different methods to aggregate the scores on the section - dyad level to the bill - dyad level.
 
@@
 
-\subsection{Tasks}
-\begin{itemize}
-\item Topic models, possibly of a relational form, applied to aligned text
-\item Computationally intensive analysis of bill-to-bill alignment and sponsor ideology.
-\begin{itemize}
-\item Get big sample of bills
-\item Assess relationship between alignment between bills and ideological similarity between sponsors
-\end{itemize}
-\item Analysis of alignment aggregated at the state level.
-\begin{itemize}
-\item How do we score overlap at the bill and state level?
-\end{itemize}
-
-\end{itemize}
+\clearpage
 
@@
 
+\section{Appendix}
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time_size_selection.png}}
+\caption{Computation time for selection of bills.
+The Colors correspond to five selected bills (focus bill or left bill).
+For each of the bills, the best alignment with 1000 randomly selected bills (right bills) are calculated.
+The size of the dots corresponds to the logarithm of the length of the focus bill (in number of words), the x-axis corresponds to the logarithm of the size of the comparison bill and the y-axis corresponds to the logarithm of the computation time (in seconds).}
+\label{fig:time_size}
+\end{figure}
+
+In order to assess the computational burden the local alignment algorithm poses we test the implementation of the alignment algorithm (Burgess et al.
+2015) on a set of 1000 randomly selected bills.
+In a first pass we calculate the alignments  between all pairs of the full bills (not divided into sections).
+Figure \ref{fig:time_size} displays the relationship between bill length and computation time.
+As expected the time increases exponentially with the length of the bills.
+Figure \ref{fig:time} displays a histogram of the logarithm of the computation time (in seconds).
+Computation time varies between $0.001s$ and $1,650s$ with $75\%$ of the distribution below $0.1s$ and a median time of $0.03s$.
+This shows that an exhaustive comparison of just the full bills (not separated into sections) would take about 100 years on a single machine.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time.png}}
+\caption{Histogram of computation time for all analyzed bills.}
+\label{fig:time} 
+\end{figure}
+
+Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 5 matching 10-grams).
+Alignments between almost all bills are found and most of the alignments are procedural language.
+This is apparent in Figure \ref{fig:state_to_state} which displays the average alignment score for bills from Illinois (left panel) and Washington (right panel) for all other states in the sampled data set (x-axis).
+Especially for Illinois there is a much higher alignment score for bills from the same state.
+This shows that a minimum threshold and a classifier for procedural language are necessary.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/state_to_state.png}}
+\caption{Average alignment scores between states.
+The left panel corresponds to `left bills' from Illinois, the right panel to bills from Washington.
+Each bar displays the average score of the best alignment found between bills of the states.}
+\label{fig:state_to_state} 
+\end{figure}
+
+In order to make the computation more feasible, we rely on a similar strategy as \citet{wilkerson2015tracing}.
+Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents.
+Since seaching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre-selection of similar bills that are then exhaustively checked for text reuse:
+
+\begin{enumerate}
+\item All bills are stored in the database in n-grams of size 2-5
+\item Select the 25 n-grams with the highest tf-idf score in the query document
+\item Calculate a score slightly adapted cosine similarity score between the selected n-gram vector and all full document n-gram vectors in the database\footnote{See \url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html} for details on the similarity scoring in Elastic Search}
+\end{enumerate}
+
+In order to evaluate how well the pre screening algorithms performs we select 1000 focus bills at random and retrieve the 1000 most similar bills according to the lucene score (described above).
+We then calculate find the best alignments between the sections of the focus bill and the section of each of the retrieved bills.
+This procedure generates a dataset of approximately 4 million alignments.
+
+For a first assessment of the usefulness of the lucene scores to select document that align well, we investigate the relationship of these scores with the alignment scores.
+Figure \ref{fig:lu_al_scores} displays the lucene scores against the alignment scores for a random sample of 500,000 alignments.
+The color indicates if the bills from which the alignment was genrated are from the same state, the larger triangles indicate scores for a bill compared to itself.
+In order to assess which alignments would get selected if thresholding, that is selecting for example the 100 closest bills according to the lucene score, we plotted all alignments for a sample of 9 focus bills.
+The green points indicate alignments from the 100 bills with the highest lucene scores for the respective focus bill.
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/lu_al_scores.png}}
+    \caption{Alignment scores and lucene scores for a sample of 500,000 alignments (sections).
+The color indicates if the bills of the alignment are from the same state.
+The larger triangles indicate alignment and lucene scores for sections of bills compared to themselves.}
+\label{fig:lu_al_scores} 
+\end{figure}
+
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/closest100.png}}
+    \caption{Alignment and lucene scores for a sample of nine focus bills (panels).
+Each point in the plot is an alignment for a section of one comparison bill.
+The color indicates, if the section comes from a bill that is among the 100 bills with the highest lucene score for the specific focus bill.
+The large triangles indicate that an alignment is from a comparison of the focus bill with itself.}
+\label{fig:closest100} 
+\end{figure}
+
 \end{document}

### 2015-12-11 manuscript/tables/ideology_regs.tex
updated paper with new qap results

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Fri Dec 11 14:49:58 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & Intercept & Estimate & Std.Error \\ 
  \hline
Sum & 4.300 & -0.034 & 0.001 \\ 
  Mean & 3.814 & -0.025 & 0.001 \\ 
  Max & 3.972 & -0.031 & 0.001 \\ 
  No. Alignments & 0.486 & -0.009 & 0.001 \\ 
   \hline
\end{tabular}
\caption{Log-Linear models for alignment and euclidian distance in ideology. Standard errors are generated from quadratic assignment procedure with 1000 iterations. The rows correspond to different methods of aggregating the section alignments to bill allignments: \textit{Sum}: Sum of alignment scores of all alignments, \textit{Mean}: Average alignment score accross secion pairs bill dyad, \textit{Max}: Highest alignment score seciton pairs of bill dyad, \textit{No. Alignments}: Number of alignments for bill dyad.} 
\label{tab:ideology_regs}
\end{table}

### 2015-12-11 manuscript/text_reuse.tex
updated paper with new qap results

@@
 \usepackage{hyperref}
+\usepackage{xr}
 
@@
 \doublespacing
+\externaldocument{tables/ideology_regs.tex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 When we are generating the alignments the bills are split up into sections.
-Table \ref{tab:ideo_reg} displays results for several methods of combining multiple alignments across sections of the same bill dyad as well as treating sections as the unit of analysis.
-For the case where we aggregate to the bill level, simple bivariate linear regression is used to test for a correlation, since the data has network structure we calculate standard errors with the quadratic assignment procedure (QAP) [note, Table \ref{tab:ideo_reg} still has normal standard errors, we are runnign the QAP at the moment] \citep{krackardt1987qap}.
-There are six models in Table \ref{tab:ideo_reg}.
-The unit of analysis of the first model is the bill section, the other five models are on the bill level.
-Model (1) has the alignment score of the section dyad as the dependent variable, models (2) - (5) use different methods to aggregate the scores on the section - dyad level to the bill - dyad level.
+Table \ref{tab:ideology_regs} displays results for several methods of combining multiple alignments across sections of the same bill dyad.
+Specifically we investigate four different ways of aggregating to the bill level: the sum of the alignment scores of the sections of a bill dyad, the mean of these scores, the maximum of the scores, and the number of alignments between two bills.
 
-\input{tables/ideology_regressions.tex}
+Each model is a log-linear model regressing the logarithm of the aggregated measure on the ideological distance between the ideal point of the two bills forming the dyad.
+The ideal point of the bill is derived from the ideal point of the bill sponsor.
+In cases where several legislators sponsor a bill we use the average of all sponsors' ideal points as a summary.
+
+The single observations (bill dyads) are not independent, due to the network structure of the data.
+In order to avoid spurious results, we use the quadratic assignment procedure (QAP), a common tool to control for spurious correlation in social network analysis \citet{krackardt1987qap}.
+We use 1000 QAP iterations for each model.
+
+The results in Table \ref{tab:ideology_regs} clearly show that there is a significant correlation between the ideological distance of the bills' sponsors and their text alignment score, regardless of the aggregation method.
+
+\input{tables/ideology_regs.tex}
 

### 2015-12-11 manuscript/make_diff.sh

@@ -1,12 +1,18 @@
 # Generate and compile latex diff to verion of the manuscript in
 # a commit. Commit SHA (id) to compare to is taken as commandline argument
 
+# Get the old version from the relevant commit 
 git checkout $1 text_reuse.tex
+# Store it in temporary file
 cp text_reuse.tex temp
+# Restore the most recent version under the original filename
 git checkout HEAD text_reuse.tex
+# Make the latex diff
 latexdiff temp text_reuse.tex > weekly_diff.tex
+# Compile latex
 pdflatex weekly_diff.tex
 bibtex weekly_diff
 pdflatex weekly_diff.tex
 pdflatex weekly_diff.tex
+# Remove temporary file
 rm temp

### 2015-12-11 analysis/ideology/ideology.R
some older small changes

@@ -166,14 +166,14 @@ load('qap_results.RData')
 # res <- data.frame(Intercept = sapply(mods, function(x) x$coef[1]),
 #                   Estimate = sapply(mods, function(x) x$coef[2]),
 #                   Std.Error = sapply(perms, function(x) sqrt(var(x))))
-# rownames(res) <- c("Sum", "Mean", "Max", "# Alignments")
 #
 # # Store results to disk
 # save(list = c("res", "perms"), file = "qap_results.RData")
 
 # Make latex results table
-sink(file = '../../manuscript/tables/qap_tab.tex')
-xtable(res, digits = 3, caption = "Log-Linear models for alignment and euclidian distance in ideology. Standard errors are generated from quadratic assignment procedure with 1000 iterations. The rows correspond to different methods of aggregating the section alignments to bill allignments: \\textit{Sum}: Sum of alignment scores of all alignments, \\textit{Mean}: Average alignment score accross secion pairs bill dyad, \\textit{Max}: Highest alignment score seciton pairs of bill dyad, \\textit{# Alignments}: Number of alignments for bill dyad.",
+rownames(res) <- c("Sum", "Mean", "Max", "No. Alignments")
+sink(file = '../../manuscript/tables/ideology_regs.tex')
+xtable(res, digits = 3, caption = "Log-Linear models for alignment and euclidian distance in ideology. Standard errors are generated from quadratic assignment procedure with 1000 iterations. The rows correspond to different methods of aggregating the section alignments to bill allignments: \\textit{Sum}: Sum of alignment scores of all alignments, \\textit{Mean}: Average alignment score accross secion pairs bill dyad, \\textit{Max}: Highest alignment score seciton pairs of bill dyad, \\textit{No. Alignments}: Number of alignments for bill dyad.",
        label = "tab:ideology_regs")
 sink()
 

### 2015-12-11 etl/extract_bill_metadata.py

@@ -9,6 +9,7 @@ from pprint import pprint
 import pandas as pd
 import numpy as np
 import time
+import re
 
 BILL_FILE = '../data/extracted_bills_with_sponsers.json'
 OUTFILE = '../data/bill_metadata.csv'
@@ -22,6 +23,10 @@ header = ['unique_id', 'date_introduced', 'date_signed', 'date_last_action',
 header = ','.join(header)
 # Get a set of all legislators that we have ideology for
 known_legis = set(legislators['id'])
+
+# Regex to remove chars that mess up the csv
+re_nchar = re.compile(r'[,"\']')
+
 
 with io.open(BILL_FILE, 'r', encoding='utf-8') as infile,\
         io.open(OUTFILE, 'w+', encoding='utf-8') as outfile:
@@ -45,9 +50,9 @@ with io.open(BILL_FILE, 'r', encoding='utf-8') as infile,\
 
         # Take quote characters out of string fields
         if doc['short_title'] is not None:
-            doc['short_title'] = doc['short_title'].strip('"')
+            doc['short_title'] = re_nchar.sub('', doc['short_title'])
         if doc['bill_title'] is not None:
-            doc['bill_title'] = doc['bill_title'].strip('"')
+            doc['bill_title'] = re_nchar.sub('', doc['bill_title'])
         
         row = [doc['unique_id'], doc['date_introduced'], doc['date_signed'],
                doc['action_dates']['last'], doc['action_dates']['passed_upper'],

### 2016-01-06 manuscript/apsa_submission/abstract_submission.tex
apsa exteded abstract

\documentclass[12pt]{article} %a4paper

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xr}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
\doublespacing

\begin{document}

\begin{center}
    \begin{Large}
    Finding Similar Bills. Assessing the Validity of Text Reuse to Measure Policy Similarity 
    \end{Large}

\end{center}

Much political science research relies on identifying the substantive similarity of bills. Especially in the study of policy diffusion identification of which bills are describing equivalent policy is crucial. Scholars of policy diffusion mostly rely on hand-coded datasets of equivalent bills. However, in order to study policy diffusion more broadly, for example by extending the study to multiple policy areas, large amounts of legislative text have would have to be analyzed manually. To find bills that describe the same or very similar policies very fine-grained analysis of the bills is necessary, because not only the exact topic, but also the same provisions have to be identified. Common text analysis algorithms such as topic models or bag-of-words based text similarity measures are therefore too coarse to identify policy similarity. However, legislators often directly use text from bills introduced in other legislatures or bill text provided by interest groups (model legislation) if they are drafting bills on policies that have been introduced in other states already. We use this fact, and propose to use text-sequencing algorithms to find such matching text between bills. We describe a new approach of how to apply sequence alignment algorithms to large amounts of legislative text, and assess the validity of text reuse as a measure of substantive bill similarity. We demonstrate the validity of text reuse as a measure of policy similarity on a database of ca. 500,000 bills from US-state legislatures.

Sequencing algorithms, namely the Smith-Waterman local alignment algorithm, originate from DNA sequence matching and has been applied to text in the past, mostly for plagiarism detection \citep{su2008plagiarism, irving2008plagiarism}. In political science, it has been used to track the legislative history of congressional bills \citep{wilkerson2015tracing}. There are two major challenges for the application of the local alignment algorithm to detect policy similarity: First, the algorithm does an exhaustive search for all potential matches between two text sequences, and it is therefore computationally unfeasible to calculate all pairwise similarities for large collections of bills. Second, a lot of text that is reused in bills is not of substantive interest. This boilerplate text, bill headers and footers and other procedural text, as well as reoccurring definitions or policy area specific phrases, is not indicative of bills having similar content. \citet{wilkerson2015tracing} tackled these problems by restrictively preselecting text that is analyzed with the local alignment algorithm and through selection of non-boilerplate text using supervised machine learning.

We propose a novel way to approach these problems. Our approach does not require the manual coding of text for the supervised classification of boilerplate text, and is less restrictive in the pre-selection of bills. Specifically, we apply a 3-step procedure that reduces the computational load as well as the amount of boilerplate text that is detected by the algorithm. First, we preselect bills that are analyzed with the alignment algorithm with a measure related to cosine similarity. After this we remove all text with a tf-idf score lower than a certain threshold to avoid analyzing clear boilerplate text and then apply the algorithm to this reduced data.

The second part of our analysis then focuses on how well the alignment between bills captures substantive policy similarity. In a first step we apply topic models to the identified text alignments in order to check whether the reused text captures substantively relevant policy language, or boilerplate text. If a clear boilerplate topic emerges we can quantify how large a portion of the identified alignments is policy relevant compared to boilerplate.

Furthermore, we use a hand-coded dataset of equivalent bills to investigate how well the local alignment algorithm predicts actual policy equivalence. In order to evaluate the validity of the text reuse measure on a basis broader then would be possible with hand-coded ground truth datasets, we assess the predictive validity of the measure. We do so in two ways: First, we asses how the measure performs in predicting policy diffusion ties between states as established by \citet{desmarais2015}. If two states have a strong diffusion tie, higher numbers of aligned bills would be expected. And second, we assess how well the similarity measure on the bill level predicts the ideological distance between the bills' sponsors using state legislators' ideal points \citep{shor2011}. That is, if two bills are sponsored by ideologically close legislators, we expect more text alignment than between bills of ideologically close legislators.

Our analyses show that the local alignment algorithm in combination with our pre and post processing procedure produces valid measures of policy similarity between bills. We aim to publish a dyadic dataset of similarity measures in order to allow a broad range of political scientists to use them for substantive research on US state politics.

\clearpage

\bibliographystyle{chicago}
\bibliography{../bibliography}

\end{document}

### 2016-01-07 manuscript/apsa_submission/abstract_submission.tex
updated the abstract

@@
     \begin{Large}
-    Finding Similar Bills. Assessing the Validity of Text Reuse to Measure Policy Similarity 
+    Automated Measurement of Policy Similarity in Legislation: Revealing Patterns of Text Reuse
     \end{Large}
@@
 
-Much political science research relies on identifying the substantive similarity of bills.
-Especially in the study of policy diffusion identification of which bills are describing equivalent policy is crucial.
-Scholars of policy diffusion mostly rely on hand-coded datasets of equivalent bills.
-However, in order to study policy diffusion more broadly, for example by extending the study to multiple policy areas, large amounts of legislative text have would have to be analyzed manually.
-To find bills that describe the same or very similar policies very fine-grained analysis of the bills is necessary, because not only the exact topic, but also the same provisions have to be identified.
-Common text analysis algorithms such as topic models or bag-of-words based text similarity measures are therefore too coarse to identify policy similarity.
-However, legislators often directly use text from bills introduced in other legislatures or bill text provided by interest groups (model legislation) if they are drafting bills on policies that have been introduced in other states already.
-We use this fact, and propose to use text-sequencing algorithms to find such matching text between bills.
-We describe a new approach of how to apply sequence alignment algorithms to large amounts of legislative text, and assess the validity of text reuse as a measure of substantive bill similarity.
-We demonstrate the validity of text reuse as a measure of policy similarity on a database of ca.
-500,000 bills from US-state legislatures.
+{\bf abstract start} \\
+Much political science research relies on identifying the substantive similarity of legislation, especially in the study of policy diffusion.
+Scholars mostly rely on hand-coded datasets.
+However, in order to study policy diffusion more broadly, for example by extending the study to dozens or more policy domains, prohibitive volumes of legislative text would have to be analyzed manually.
+Common text analysis algorithms such as topic models or bag-of-words based text similarity measures are too coarse to identify policy similarity.
+However, legislators often directly use text from bills introduced in other legislatures or bill text provided by interest groups in model legislation.
+We propose the use of text-sequencing algorithms to find matching text between bills.
+We describe a new approach to the application of sequence alignment algorithms to large amounts of legislative text, and assess the validity of text reuse as a measure of substantive bill similarity.
+Three key results, drawn from an analysis of 500,000 bills from US-state legislatures, demonstrate the validity of text reuse as a measure of policy similarity.
+First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse.
+Second, we show that the main topical themes underlying strings of reused text map closely onto major areas of public policy in the US States.
+Third, we show that rates of text reuse across state borders correlates strongly with the state policy diffusion ties data recently introduced by Desmarais, Harden and Boehmke (APSR, 2015).
+\\
+{\bf abstract end}
 

### 2016-01-07 analysis/dyadic_analysis.R

@@ -1,5 +1,5 @@
 # Set my working directory
-setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
+setwd("/Volumes/Data/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
 
 # Note, the line below need only be run once, to split the big CSV into smaller files, sending to command line
 # pipe("split -l 100000 bill_to_bill_alignments.csv","r")
@@ -8,7 +8,7 @@ setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks
 sample_dat <- read.csv("bill_to_bill_alignments.csv",nrows=10,stringsAsFactors=F)
 
 # Read in complete dyadic dataset from APSR 
-state_diffusion_edges <- read.csv("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
+state_diffusion_edges <- read.csv("/Volumes/Data/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
 
 # Create empty adjacency matrix in which to store alignment scores
 ## unique state names
@@ -17,10 +17,15 @@ ustates <- sort(unique(tolower(state_diffusion_edges$state_01)))
 align_amat <- matrix(0,length(ustates),length(ustates))
 align_amat_score <- matrix(0,length(ustates),length(ustates))
 align_amat_threshold <- matrix(0,length(ustates),length(ustates))
+nbills_amat <- matrix(0,length(ustates),length(ustates))
 ## row names
 rownames(align_amat) <- colnames(align_amat) <- ustates
 rownames(align_amat_score) <- colnames(align_amat_score) <- ustates
 rownames(align_amat_threshold) <- colnames(align_amat_threshold) <- ustates
+rownames(nbills_amat) <- colnames(nbills_amat) <- ustates
+
+left_doc <- NULL
+right_doc <- NULL
 
 # Iteratively read in 100,000 rows at a time to build adjacency matrices
 ## all of the split files begin with x
@@ -46,11 +51,13 @@ for(i in 1:length(files)){
   ## extract state ids from subsetted dataset
[…]

### 2016-01-12 manuscript/tables/ideology_regs.tex
more on substantive interprtation of regression results

@@
 % latex table generated in R 3.2.2 by xtable 1.7-4 package
-% Fri Dec 11 14:49:58 2015
+% Mon Dec 21 04:04:01 2015
 \begin{table}[ht]
 \centering
-\begin{tabular}{rrrr}
+\begin{tabular}{rrrrr}
   \hline
- & Intercept & Estimate & Std.Error \\ 
+ & Intercept & Estimate & Std.Dev & p.value \\ 
   \hline
-Sum & 4.300 & -0.034 & 0.001 \\ 
-  Mean & 3.814 & -0.025 & 0.001 \\ 
-  Max & 3.972 & -0.031 & 0.001 \\ 
-  No. Alignments & 0.486 & -0.009 & 0.001 \\ 
+Sum & 4.300 & -0.034 & 0.001 & 0.000 \\ 
+  Mean & 3.814 & -0.025 & 0.001 & 0.000 \\ 
+  Max & 3.972 & -0.031 & 0.001 & 0.000 \\ 
+  No. Alignments & 0.486 & -0.009 & 0.001 & 0.000 \\ 
    \hline
 \end{tabular}
-\caption{Log-Linear models for alignment and euclidian distance in ideology.
-Standard errors are generated from quadratic assignment procedure with 1000 iterations.
-The rows correspond to different methods of aggregating the section alignments to bill allignments: \textit{Sum}: Sum of alignment scores of all alignments, \textit{Mean}: Average alignment score accross secion pairs bill dyad, \textit{Max}: Highest alignment score seciton pairs of bill dyad, \textit{No.
-Alignments}: Number of alignments for bill dyad.}
+\caption{Log-Linear models for alignment and euclidian
+distance in ideology. Two tailed p-values are generated from quadratic
+assignment procedure with 1000 iterations. Std.Dev is the standard
+deviation of the null distribution. The rows correspond to
+different methods of aggregating the section alignments to bill
+allignments: \textit{Sum}: Sum of alignment scores of all alignments,
+\textit{Mean}: Average alignment score accross secion pairs bill dyad,
+\textit{Max}: Highest alignment score seciton pairs of bill dyad,
+\textit{No. Alignments}: Number of alignments for bill dyad.} 
 \label{tab:ideology_regs}

### 2016-01-12 manuscript/text_reuse.tex
update to paper
more on substantive interprtation of regression results

@@
 \usepackage{xr}
+\usepackage{subfig}
 
@@
 
-\begin{abstract} Much research has been focused on the diffusion of policy ideas in US state legislatures.
-Most of this research uses hand coded data sets that identify equivalent bills and analyze patterns of adoption of these bills.
-Bills on equivalent policies often contain the same language, since legislators use past legislation from other states or model legislation from interest groups as templates when drafting new bills or model legislation from interest groups.
-In this paper we evaluate the effectives of text reuse measures to detect bills that address the same policy issues.
-We find that...
+\begin{abstract} 
+ Much political science research relies on identifying the substantive similarity of legislation, especially in the study of policy diffusion.
+Scholars mostly rely on hand-coded datasets.
+However, in order to study policy diffusion more broadly, for example by extending the study to dozens or more policy domains, prohibitive volumes of legislative text would have to be analyzed manually.
+Common text analysis algorithms such as topic models or bag-of-words based text similarity measures are too coarse to identify policy similarity.
+However, legislators often directly use text from bills introduced in other legislatures or bill text provided by interest groups in model legislation.
+We propose the use of text-sequencing algorithms to find matching text between bills.
+We describe a new approach to the application of sequence alignment algorithms to large amounts of legislative text, and assess the validity of text reuse as a measure of substantive bill similarity.
+Three key results, drawn from an analysis of 500,000 bills from US-state legislatures, demonstrate the validity of text reuse as a measure of policy similarity.
+First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse.
+Second, we show that the main topical themes underlying strings of reused text map closely onto major areas of public policy in the US States.
+Third, we show that rates of text reuse across state borders correlates strongly with the state policy diffusion ties data recently introduced by Desmarais, Harden and Boehmke (APSR, 2015).
 \end{abstract}
@@
 The ideal point of the bill is derived from the ideal point of the bill sponsor.
-In cases where several legislators sponsor a bill we use the average of all sponsors' ideal points as a summary.
+In cases where several legislators sponsor a bill we use the average of all sponsors' ideal points to obtain a single measure.
 
@@
 
+\input{tables/ideology_regs.tex}
+
 The results in Table \ref{tab:ideology_regs} clearly show that there is a significant correlation between the ideological distance of the bills' sponsors and their text alignment score, regardless of the aggregation method.
+For each aggregation method, assuming the null hypothesis of no correlation, the probability for the observed estimate estimated as zero.
+This is also clear from Figure \ref{fig:qap_dist}, which shows histograms of the permutation distributions of the regression coefficients and the actual estimates as a red line.
 
-\input{tables/ideology_regs.tex}
+\begin{figure}[ht!]
+    \makebox[\textwidth]{\includegraphics[width=0.9\textwidth]{figures/qap_dist.png}}
+\caption{Statistical significance of regression results.
+The histogram in black shows the distribution of regression coefficients obtained from 1000 qap permutations.
+The red line displays the estimate obtained from the actual non-permuted network.}
+\label{fig:qap_dist}
+\end{figure}
+
+To asses the substantive importance of the effect size, Figure \ref{fig:ideo_interpret} displays the estimated decrease in mean alignment score when increasing the ideological distance of the bills.
+The vertical lines correspond to the ideological distances between the median democrat and republican, the 0.05 quantile and the 0.95 quantile of the total distribution of ideal points and the minimum and maximum of the total distribution.
+[FILL IN MORE INTERPRETATION WHEN NEW RESULTS ARE IN]
+
+\begin{figure}[H]%
+\centering
+\subfloat[Substantive effects]{\includegraphics[width=0.5\textwidth]{figures/log_lin_effects.png}}
+\subfloat[Distribution of legislator ideal points]{\includegraphics[width=0.5\textwidth]{figures/ideo_distri.png}}
+\caption{Substantive interpretation of the effect size of the regression results.
+The left panel displays the predicted difference in mean alignment score for a change in the ideological distance of the bill.
+The colored lines connect the distance values to the political landscape.
+The first line corresponds to the distance between the median democrat and the median republican (across all states), that second line corresponds to the distance between the 0.05 and the 0.95 quantile of the full distribution of legislators' ideal points, and the third line corresponds to the distance from the leftmost to the rightmost legislator.
+For reference, the left panel displays the kernel density estimate of the distribution of ideal points by party.
+The vertical lines mark the median ideology for each party.
+The dependent variable in this illustration is the mean score.
+Results for different aggregation methods are similar.
+}
+\label{fig:ideo_interpret}
+\end{figure}
 

### 2016-01-12 analysis/ideology/ideology.R

@@ -1,9 +1,13 @@
 library(dplyr)
 library(ggplot2)
 library(xtable)
+library(MCMCpack)
 
 source("qap.R")
 
+#Plotting colors
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2",
+               "#D55E00", "#CC79A7")
 # ==============================================================================
 # Data preprocessing
 # ==============================================================================
@@ -132,7 +136,7 @@ load('qap_results.RData')
 # ## Number of qap permutations
 # n_qap_perm <- 1000
 # ## Number of cores for permutations
-# n_cores <- 36
+# n_cores <- 4
 # 
 # ## Linear model for sum aggregation (with qap standard errors)
 # sum_score <- lm(log(sum_score) ~ ideology_dist, data = aggr)
@@ -140,7 +144,7 @@ load('qap_results.RData')
 # perm_dist_sum <- qap(edges, ideologies, nperm = n_qap_perm, cores = n_cores)
 # 
 # ## Linear model for mean aggregation (with qap standard errors)
-# mean_score <- lm(log(mean_score) ~ ideology_dist, data = aggr)
+mean_score <- lm(log(mean_score) ~ ideology_dist, data = aggr)
 # edges[, 3] <- aggr$mean_score
 # perm_dist_mean <- qap(edges, ideologies, nperm = n_qap_perm, cores = n_cores)
 # 
@@ -153,9 +157,9 @@ load('qap_results.RData')
 # n_align <- lm(log(n_align) ~ ideology_dist, data = aggr)
 # edges[, 3] <- aggr$n_align
 # perm_dist_n_align <- qap(edges, ideologies, nperm = n_qap_perm, cores = n_cores)
-# 
-# 
-# # ==============================================================================
+
+
+# ==============================================================================
 # # Output results
 # # ==============================================================================
 # 
@@ -163,20 +167,33 @@ load('qap_results.RData')
 # mods <- list(sum_score, mean_score, max_score, n_align)
 # perms <- list(perm_dist_sum, perm_dist_mean, perm_dist_max, perm_dist_n_align)
 # 
+
 # res <- data.frame(Intercept = sapply(mods, function(x) x$coef[1]),
 #                   Estimate = sapply(mods, function(x) x$coef[2]),
-#                   Std.Error = sapply(perms, function(x) sqrt(var(x))))
+#                   Std.Dev = sapply(perms, function(x) sqrt(var(x))))
[…]

### 2016-01-12 analysis/ideology/qap.R

@@ -2,8 +2,9 @@
 
 # Arguments:
 
-# bill_similarity: data.frame, left_id (chr), right_id(chr), score(dbl)
-# ideology: dataframe, mapping bill_id (chr) to ideology (dbl)
+# edges: Edgelist for similarity network. Bill IDs must be integers 
+# ideology: numeric vector of bill ideologies. Must be in same order as integer
+#   bill ids
 # nperm: number of quap iterations
 # cores: number of cores for parallelization of nperm loop
 

### 2016-01-13 manuscript/apsa_submission/abstract_submission.tex
updating the dyadic analysis

@@
 
-{\bf abstract start} \\
+%{\bf abstract start} \\
 Much political science research relies on identifying the substantive similarity of legislation, especially in the study of policy diffusion.
@@
 \\
-{\bf abstract end}
+%{\bf abstract end}
+\end{document}
 
@@
 \bibliography{../bibliography}
-
-\end{document}

### 2016-01-13 analysis/dyadic_analysis.R

@@ -1,5 +1,5 @@
 # Set my working directory
-setwd("/Volumes/Data/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
+setwd("~/dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
 
 # Note, the line below need only be run once, to split the big CSV into smaller files, sending to command line
 # pipe("split -l 100000 bill_to_bill_alignments.csv","r")
@@ -8,7 +8,7 @@ setwd("/Volumes/Data/Dropbox/professional/Research/Active/Diffusion_Networks/tex
 sample_dat <- read.csv("bill_to_bill_alignments.csv",nrows=10,stringsAsFactors=F)
 
 # Read in complete dyadic dataset from APSR 
-state_diffusion_edges <- read.csv("/Volumes/Data/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
+state_diffusion_edges <- read.csv("~/dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
 
 # Create empty adjacency matrix in which to store alignment scores
 ## unique state names
@@ -71,15 +71,31 @@ for(i in 1:length(files)){
   }
 }
 
-# subset to 2008 edges
-state_diffusion_edges2008 <- subset(state_diffusion_edges,year==2008)
+# number of bills in each state
+all_bills <- unique(c(left_doc,right_doc))
+bill_states <- substr(all_bills,1,2)
+nbills <- numeric(length(ustates))
+for(i in 1:length(ustates)){
+	nbills[i] <- length(which(bill_states==ustates[i]))
+}
+
+nbills_cov <- matrix(0,length(nbills),length(nbills))
+for(i in 2:length(nbills)){
+	for(j in 1:(i-1)){
+		nbills_cov[i,j] <- nbills_cov[j,i] <- nbills[i]+nbills[j]
+	}
+}
+
+
+# subset to 2009 edges
+state_diffusion_edges2009 <- subset(state_diffusion_edges,year==2009)
 
 # create diffusion adjacency matrix
 diff_amat <- matrix(0,length(ustates),length(ustates))
 # assure the nodes are consistent
[…]

### 2016-01-18 etl/ncsl_tables/get_table_urls.py
bing scraper for ncsl legilation urls

@@ -1,0 +1,49 @@
+from __future__ import unicode_literals
+import urllib2
+import json
+from pprint import pprint
+import io
+import time
+import re
+
+def bing_request(offset, keyBing):
+    credentialBing = 'Basic ' + (':%s' % keyBing).encode('base64')[:-1] # the "-1" is to remove the trailing "\n" which encode adds
+    searchString = '%27site%3Ancsl.org%20%22legislation.aspx%22%27'
+    top = 50
+    url = 'https://api.datamarket.azure.com/Bing/Search/Web?' + \
+          'Query=%s&$top=%d&$skip=%d&$format=json' % (searchString, top, offset)
+    request = urllib2.Request(url)
+    request.add_header('Authorization', credentialBing)
+    requestOpener = urllib2.build_opener()
+    response = requestOpener.open(request) 
+    response = json.load(response)
+    return response
+
+outfile = io.open('../../data/ncsl/scraped_table_urls.csv', 'w+', encoding='utf-8')
+outfile.write('id,title,url,description,uri\n')
+offset = 0
+punct = re.compile(r'[,;\t|]')
+key = io.open('bing_key.txt').read().strip('\n')
+
+while True:
+    
+    print 'Requesting results {} to {}'.format(offset, (offset + 50))
+    response = bing_request(offset, key)
+    
+    for result in response['d']['results']:
+        # Extract info
+        id_ = result['ID']
+        title = punct.sub('', result['Title'])
+        url_ = result['Url']
+        description = punct.sub('', result['Description'])
+        
+        # Write row to file
+        row = '{},{},{},{},{}\n'.format(id_,title,url_,description,uri)
+        outfile.write(row)
+
+    if '__next' not in response['d'].keys():
+        break
+    else:
+        offset += 50
+    
+outfile.close()

### 2016-01-20 manuscript/text_reuse.tex
updated intro

@@
 
-Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets encode when one or a handful of policies were adopted by each jurisdiction \citep{boehmke2012}.
-Scholars of public policy diffusion have recently turned their attention to the empirical identification of emulation ties connecting policy jurisdictions \citep{volden2006,boehmke2009,desmarais2015,garrett2015}.
-Identifying instances of policy emulation and explicit diffusion ties opens policy diffusion scholarship to an entirely new set of questions and theories that can be approached empirically.
-In this paper we draw upon a massive and nearly all-encompassing source of data from which to infer diffusion ties -- the text of legislation.
-If the computer-based analysis of bill text can be tuned to successfully identify policy adoption and emulation, we will be able to vastly scale up both the scale of data gathered and the precision of diffusion inferences.
+The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}.
+Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}.
+In this paper we draw upon a massive and nearly all-encompassing source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures.
+We take an automated, computer-based, approach to the analysis of bill text.
+This vastly increases the volume of data that can be included in policy diffusion research.
 
- How ever, it is not clear, how well text reuse is suited to to detect real policy diffusion.
-There are several complications that we are addressing in this paper.
-First, every bill has procedural content that is not related to the policy content of the bill.
-Since every state legislature has a set of such standard or boiler plate text in each bill, there will be significant text reuse between bills in the same state and possibly also between bills from different states.
-Second, it is not obvious how much text reuse will mean substantive policy overlap.
-Given that each bill pair has a continuous proportion of overlapping text, setting the threshold too low might mean to classify bills as equivalent that are only in the same policy area, or are on a similar issue, but are opposed in content.
-On the other hand, setting the threshold too high could mean overlooking equivalent bills because of small insignificant changes to the text.
- In this paper we address these issues and evaluate how much policy overlap can be detected using text reuse measures.
-Following Wilkerson et al.
-(2015) we use supervised machine learning to separate boiler plate from substantive text.
-We further more use an original data set on policy diffusion to evaluate how much equivalent policy can be detected using measures of text reuse.
-Using the system developed by Burges et al.
-(2015) we calculate text reuse scores for all pairs of bills in our dataset.
-We will then assess the scientific value of the text reuse scores in several different ways.
+Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles.
+The central methodological puzzles are two-fold.
+First, we need to extract the substantive text of the legislation---minimizing the affect of procedural text on our measures of text reuse.
+Second, we need to develop a method for quantitatively scoring the reused text between bills.
+The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purpose of policy diffusion research.
+We cannot define a standard in the literature according to which two policies can be deemed equivalent, and argue instead for conceptualizing policy diffusion in terms of a continuum of similar policy rather than a dichotomy of equivalence.
+
+We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws.
 First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text.
 Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills.
-Third, we assess the how well policy diffusion networks that have been established by previous research can be discovered using the amount of text reuse between states.
+Third, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states.
 And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.
@@
 We then represent a dyad of bills by the text alignments between them.
-For each state-pair we calculate the number of alignments between bills from each state.
-The median number of alignments between states is 3,491 with a mean of 6,309 and standard deviation of 8,809.
+For each state-pair we calculate the sum of the natural logs of the alignment scores.
 The ``Diffusion Ties'' variable measures the number of diffusion edges between states in the 2008 diffusion network, as measured by \citet{desmarais2015}.
@@
   \hline
-Intercept & 5717.18 & 0.0000 & 8.0431 & 0.0000 \\ 
-  Diffusion Ties & 2417.00 & 0.0308 & 0.3288 & 0.0452 \\ 
+Intercept & 21220.1435 & 0.0000 & 9.3643 & 0.0000 \\ 
+  Diffusion Ties & 8551.8602 & 0.0352 & 0.3190 & 0.0494 \\ 
    \hline

### 2016-01-20 analysis/dyadic_analysis.R

@@ -119,6 +119,11 @@ library(xtable)
 results_all <- cbind(results,results_log)
 xtable(results_all,dig=4)
 
+# boxplots 
+x <- diff_amat[lower.tri(diff_amat)]
+y <- log(align_amat_score)[lower.tri(align_amat_score)]
+
+
 ## Descriptive statistics
 diag(align_amat) <- NA
 median(align_amat,na.rm=T)

### 2016-01-20 manuscript/text_reuse.tex
updated title
a little descriptive plot

@@
 
-\title{Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
+\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
 \date{\today}
@@
 We have the first and the last version of the bill text, the sponsor of the bill and all legislative action that was taken on the bill.
+
+Figure \ref{fig:bill_desc} displays the year ranges and number of bills in the bill data base.
+
+\begin{figure}[]
+    \centering
+    \includegraphics{figures/year_count_by_state.png}
+    \caption{Description of the bill database.
+The horizontal bars display the time range for which bills are available for each state.
+The color of the bar indicates how many bills are available for this state.}
+    \label{fig:bill_desc}
+\end{figure}<++>
 

### 2016-01-20 analysis/exploratory/bill_meta_exp.R

@@ -1,0 +1,45 @@
+library(dplyr)
+library(ggplot2)
+
+df <- tbl_df(read.csv(file = '../../data/bill_metadata.csv', header = TRUE,
+                      stringsAsFactors = FALSE))
+
+# Get bill prefixes
+f <- function(x) return(x[length(x)])
+df <- mutate(df, id = sapply(strsplit(unique_id, "_"), f),
+             prefix = gsub("[[:digit:]-]", "", id))
+    
+prefixes <- group_by(df, state, prefix) %>% summarize(count = n())
+
+# State distribution
+state_desc <- mutate(df, date_introduced = as.Date(df$date_introduced)) %>%
+    mutate(year_introduced = format(date_introduced, "%Y")) %>%
+    group_by(state) %>% 
+    summarize(year_min = min(year_introduced, na.rm = TRUE),
+              year_max = max(year_introduced, na.rm = TRUE),
+              count = n())
+
+regions <- data.frame(region = c(rep("Northeast", 9),
+                                 rep("Midwest", 12),
+                                 rep("South", 18),
+                                 rep("West", 13)),
+                      state = c("ct", "me", "ma", "nh", "ri", "vt", "nj", "ny",
+                                "pa", "il", "in", "mi", "oh", "wi", "ia", "ks",
+                                "mn", "mo", "ne", "nd", "sd", "de", "fl", "ga",
+                                "md", "nc", "sc", "va", "dc", "wv", "al", "ky",
+                                "ms", "tn", "ar", "la", "pr", "ok", "tx", "az", "co",
+                                "id", "mt", "nv", "nm", "ut", "wy", "ak", "ca",
+                                "hi", "or", "wa"))
+regions <- regions[order(regions$state), ]
+state_desc$region <- regions$region
+
+## Plot all states
+ggplot(state_desc) +
+    geom_segment(aes(x = year_min, xend = year_max, y = seq(1,length(state)), 
+                     yend = seq(1,length(state)), color = count), size = 2) + 
+    theme_bw() + xlab("Year") + ylab("State") +
+    scale_color_continuous(name = "# of Bils") + 
+    guides(size = FALSE) +
+ggsave('../../manuscript/figures/year_count_by_state.png')
+
+

### 2016-01-20 etl/ncsl_tables/get_table_urls.py
weekly diff

@@ -8,7 +8,7 @@ import re
 
 def bing_request(offset, keyBing):
     credentialBing = 'Basic ' + (':%s' % keyBing).encode('base64')[:-1] # the "-1" is to remove the trailing "\n" which encode adds
-    searchString = '%27site%3Ancsl.org%20%22legislation.aspx%22%27'
+    searchString = '%27site%3Ancsl.org%20%22laws.aspx%22%27'
     top = 50
     url = 'https://api.datamarket.azure.com/Bing/Search/Web?' + \
           'Query=%s&$top=%d&$skip=%d&$format=json' % (searchString, top, offset)
@@ -19,7 +19,7 @@ def bing_request(offset, keyBing):
     response = json.load(response)
     return response
 
-outfile = io.open('../../data/ncsl/scraped_table_urls.csv', 'w+', encoding='utf-8')
+outfile = io.open('../../data/ncsl/scraped_table_urls_laws.csv', 'w+', encoding='utf-8')
 outfile.write('id,title,url,description,uri\n')
 offset = 0
 punct = re.compile(r'[,;\t|]')
@@ -38,7 +38,7 @@ while True:
         description = punct.sub('', result['Description'])
         
         # Write row to file
-        row = '{},{},{},{},{}\n'.format(id_,title,url_,description,uri)
+        row = '{},{},{},{}\n'.format(id_,title,url_,description)
         outfile.write(row)
 
     if '__next' not in response['d'].keys():

### 2016-01-20 analysis/analysis/dyadic_analysis.R
cleaned up files

@@ -1,110 +1,0 @@
-# Set my working directory
-setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
-
-# Note, the line below need only be run once, to split the big CSV into smaller files, sending to command line
-# pipe("split -l 100000 bill_to_bill_alignments.csv","r")
-
-# Read in sample of data on which to base variable names
-sample_dat <- read.csv("bill_to_bill_alignments.csv",nrows=10,stringsAsFactors=F)
-
-# Read in complete dyadic dataset from APSR 
-state_diffusion_edges <- read.csv("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
-
-# Create empty adjacency matrix in which to store alignment scores
-## unique state names
-ustates <- sort(unique(tolower(state_diffusion_edges$state_01)))
-## correctly sized empty matrix
-align_amat <- matrix(0,length(ustates),length(ustates))
-align_amat_score <- matrix(0,length(ustates),length(ustates))
-align_amat_threshold <- matrix(0,length(ustates),length(ustates))
-## row names
-rownames(align_amat) <- colnames(align_amat) <- ustates
-rownames(align_amat_score) <- colnames(align_amat_score) <- ustates
-rownames(align_amat_threshold) <- colnames(align_amat_threshold) <- ustates
-
-# Iteratively read in 100,000 rows at a time to build adjacency matrices
-## all of the split files begin with x
-files <- dir()
-files <- files[which(substr(files,1,1)=="x")]
-
-nwords <- function(text_vector){
-	nw <- unlist(lapply(strsplit(text_vector," "),"length"))
-	nw
-}
-
-# loop over files
-for(i in 1:length(files)){
-  ## read in 100k rows
-  align_dati <- read.csv(files[i],stringsAsFactors=F,header=ifelse(i==1,T,F))
-  ## make sure variables have the right names
-  names(align_dati) <- names(sample_dat)
-  ## extract state ids from bill labels
-  state1 <- substr(align_dati$left_doc_id,1,2)
-  state2 <- substr(align_dati$right_doc_id,1,2)
[…]

### 2016-01-20 analysis/analysis/topic_modeling.R

@@ -1,39 +1,0 @@
-setwd("/storage/group/bbd5087_collab/text_reuse/analysis")
-load("text_for_mallet.RData")
-
-options( java.parameters = "-Xmx80g" )
-
-#install.packages("mallet",lib="/storage/group/bbd5087_collab/r_packages",repos="http://cran.stat.ucla.edu/")
-
-.libPaths("/storage/group/bbd5087_collab/r_packages")
-
-library(mallet)
-
-set.seed(10)
-
-filenamesRS <- filenames
-aligned_textRS <- aligned_text
-
-mallet.instances <- mallet.import(filenamesRS,aligned_textRS,"en.txt")
-
-topic.model <- MalletLDA(num.topics=20)
-	
-topic.model$loadDocuments(mallet.instances)
-	
-vocabulary <- topic.model$getVocabulary()
-word.freqs <- mallet.word.freqs(topic.model)
-
-topic.model$setAlphaOptimization(20, 50)
-
-topic.model$train(300)
-	
-topic.model$maximize(10)
-	
-doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
-topic.words <- mallet.topic.words(topic.model, smoothed=T, normalized=T)
-
-topic.probs <- apply(doc.topics,2,mean)
-
-mallet.top.words(topic.model, topic.words[6,],20)
-
-save(list=c("topic.model","doc.topics","topic.words","topic.probs","vocabulary","word.freqs"),file="topic_model_results.RData")

### 2016-01-20 analysis/topic_modeling_ICS.R

@@ -1,33 +1,0 @@
-load("~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/text_for_mallet.RData")
-options(java.parameters = "-Xmx7g" )
-library(mallet)
-
-set.seed(10)
-samp.ind <- sample(1:length(filenames),100000,rep=T)
-
-filenamesRS <- filenames[samp.ind]
-aligned_textRS <- aligned_text[samp.ind]
-
-mallet.instances <- mallet.import(filenamesRS,aligned_textRS,"~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/en.txt")
-
-topic.model <- MalletLDA(num.topics=20)
-	
-topic.model$loadDocuments(mallet.instances)
-	
-vocabulary <- topic.model$getVocabulary()
-word.freqs <- mallet.word.freqs(topic.model)
-
-topic.model$setAlphaOptimization(20, 50)
-
-topic.model$train(200)
-	
-topic.model$maximize(10)
-	
-doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
-topic.words <- mallet.topic.words(topic.model, smoothed=T, normalized=T)
-
-topic.probs <- apply(doc.topics,2,mean)
-
-mallet.top.words(topic.model, topic.words[6,],20)
-
-

### 2016-01-20 analysis/topic_modeling_prep.R

@@ -1,56 +1,0 @@
-# Set my working directory
-setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/lid/")
-
-# Note, the line below need only be run once, to split the big CSV into smaller files, sending to command line
-# pipe("split -l 100000 bill_to_bill_alignments.csv","r")
-
-# Read in sample of data on which to base variable names
-sample_dat <- read.csv("bill_to_bill_alignments.csv",nrows=10,stringsAsFactors=F)
-
-# Iteratively read in 100,000 rows at a time to build adjacency matrices
-## all of the split files begin with x
-files <- dir()
-files <- files[which(substr(files,1,1)=="x")]
-
-library(mallet)
-
-aligned_text <- NULL
-filenames <- NULL
-
-# loop over files
-for(i in 1:length(files)){	
-  ## read in 100k rows
-  align_dati <- read.csv(files[i],stringsAsFactors=F,header=ifelse(i==1,T,F))
-  ## make sure variables have the right names
-  names(align_dati) <- names(sample_dat)
-  
-  filenames <- c(filenames,paste("~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/alignment_files/all_alignments/",align_dati$left_doc_id,align_dati$right_doc_id,align_dati$alignment_section_index,".txt",sep=""))
-  
-  aligned_text <- c(aligned_text,align_dati$left_alignment_text)
-  
-  if(i/5==round(i/5)) print(i)
-  
-  }
- 
-save(list=c("filenames","aligned_text"),file="~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/text_for_mallet.RData")
-
-  mallet.instances <- mallet.import(filenames[1:100000],aligned_text[1:100000],"~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/en.txt")
-
-
-	topic.model <- MalletLDA(num.topics=20)
-	
-	topic.model$loadDocuments(mallet.instances)
-	
-	vocabulary <- topic.model$getVocabulary()
-	word.freqs <- mallet.word.freqs(topic.model)
-
-	topic.model$setAlphaOptimization(20, 50)
-	
-	topic.model$maximize(10)
-	
-	doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
[…]

### 2016-01-20 manuscript/text_reuse.tex
fig too large
fixed citations

@@
 Second, we show that the main topical themes underlying strings of reused text map closely onto major areas of public policy in the US States.
-Third, we show that rates of text reuse across state borders correlates strongly with the state policy diffusion ties data recently introduced by Desmarais, Harden and Boehmke (APSR, 2015).
+Third, we show that rates of text reuse across state borders correlates strongly with the state policy diffusion ties data recently introduced by \citet{desmarais2015}.
 \end{abstract}
@@
 
-\begin{figure}[]
+\begin{figure}[ht!]
     \centering
-    \includegraphics{figures/year_count_by_state.png}
+    \includegraphics[width=0.9\textwidth]{figures/year_count_by_state.png}
     \caption{Description of the bill database.
@@
     \label{fig:bill_desc}
-\end{figure}<++>
+\end{figure}
 

### 2016-01-29 manuscript/text_reuse.tex
ncsl table sampling

@@
 
-We additionally construct a validation dataset of equivalent bills from information obtained from the National Conference of State Legislatures (NCSL).
-The NCSL publishes summary tables on specific policies, citing the relevant bills or sections in the state statutes of the states that have implemented regulations on this policy.
-We collected all these tables, and extracted all bills that address the same policy measure and that overlap with the time frame covered by our bill database.
+\textit{Ground truth - NCSL Tables}\\
+
+To build a ground truth data set, we rely on thematic tables published by the National Council of State Legislatures\footnote{\url{www.ncsl.org}} (NCSL).
+We collected a sample of these tables with the following procedure:
+
+\begin{singlespacing}
+
+\begin{enumerate}
+    \item Collect all urls returned by the web search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
+    \item Sample 50 urls
+    \item Select bills that fulfill these three conditions:
+        \begin{enumerate}
+            \item The website is a NCSL table
+            \item The table refers (at least in part) to legislation introduced 2011 or later
+            \item The table contains less than 100 individual bills
+        \end{enumerate}
+    \item Scrape all information from these tables
+\end{enumerate}
+
+\end{singlespacing}
+
+Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership.
+The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}).
+We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad.
+We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
+The web query from step 1 returned 266 urls.
+From the 50 sampled urls 22 fulfilled the three criteria.
+From these 23 tables we constructed a dataset of [???] bills, of wich we could match [???] to our data base of bill text.
 

### 2016-01-29 analysis/exploratory/bill_meta_exp.R

@@ -39,7 +39,7 @@ ggplot(state_desc) +
                      yend = seq(1,length(state)), color = count), size = 2) + 
     theme_bw() + xlab("Year") + ylab("State") +
     scale_color_continuous(name = "# of Bils") + 
-    guides(size = FALSE) +
+    guides(size = FALSE)
 ggsave('../../manuscript/figures/year_count_by_state.png')
 
 

### 2016-01-29 etl/ncsl_tables/sample_tables.R

@@ -1,0 +1,30 @@
+
+urls <- read.csv('../../data/ncsl/checked_urls.csv',
+                 header = TRUE, stringsAsFactors = FALSE)
+
+# Selection criteria:
+# - Comes from the query "site:ncsl.org "legislation.aspx""
+# - Must be a ncsl topic table
+# - Less than 100 bills on in the table
+# - Must contain bills (not statutes or codes)
+# - After 2011
+
+# Select ursl from correct query
+urls <- urls[grepl('legislation.aspx', urls$url), ]
+
+
+# Take a sample
+n <- 50 # no of bills to sample
+set.seed(82096)
+sampled_urls <- urls[sample(c(1:nrow(urls)), n), ]
+write.csv(sampled_urls, '../../data/ncsl/sampled_urls.csv', row.names = FALSE)
+
+# Coding of the sampled urls was done in a table editor
+
+coded_urls <- read.csv('../../data/ncsl/sampled_urls.csv', header = TRUE, 
+                       stringsAsFactors = FALSE)
+
+coded_urls$all_conditions <- ifelse(coded_urls$is_table + coded_urls$right_size + 
+    coded_urls$after_2010 == 3, 1, 0)
+
+length(which(coded_urls$all_conditions == 1))

### 2016-02-03 etl/ncsl_tables/match_bills.R
matching ncsl bills to db

@@ -1,0 +1,98 @@
+library(dplyr)
+library(lubridate)
+
+ncsl_bills <- read.csv('../../data/ncsl/ncsl_data_from_sample.csv', 
+                       header = TRUE, stringsAsFactors = FALSE)
+db_bills <- read.csv('../../data/bill_metadata.csv', header = TRUE,
+                     stringsAsFactors = FALSE)
+
+
+# Preprocess db bills
+
+## Extract id from unique id
+db_bills$id <- unlist(lapply(strsplit(db_bills$unique_id, '_'), 
+                             function(x) x[length(x)]))
+
+## Split into numeric and letter components
+db_bills$num_id <- as.integer(gsub('[[:alpha:]]', '', db_bills$id))
+db_bills$let_id <- gsub('[[:digit:]]', '', db_bills$id)
+
+## Extract year of introduction
+db_bills$year <- as.integer(sapply(strsplit(db_bills$date_introduced, '-'), 
+                                   function(x) x[1]))
+
+# Preprocess ncsl ids
+## Split into components
+ncsl_bills$num_id <- as.integer(gsub('[[:alpha:]]', '', ncsl_bills$id))
+ncsl_bills$let_id <- gsub('[[:digit:]]', '', ncsl_bills$id)
+
+
+# Matching
+db_bills <- tbl_df(db_bills) %>% select(state, year, id, num_id, let_id)
+no_match <- 0
+multi_match <- 0
+one_match <- 0
+
+for(i in 1:nrow(ncsl_bills)) {
+    id_ <- ncsl_bills$id[i]
+    num_ <- ncsl_bills$num_id[i]
+    let_ <- ncsl_bills$let_id[i]
+    state_ <- tolower(ncsl_bills$state[i])
+    year_ <- ncsl_bills$year[i]
+    
+    # Get relevant subset
+    subs <- filter(db_bills, state == state_, year == year_, num_id == num_)
+    if(nrow(subs) == 0) {
+        print(paste('(LVL1)No match for:', state_, id_))
+        no_match <- no_match + 1
+        next
+    } else {
+        if(nrow(subs) == 1) {
+            print(paste('(LVL2)Found match for:', state_, id_, year_))
+            one_match <- one_match + 1
+        } else {
+            # Match multiple
+            subs_ <- filter(subs, let_id == let_)
+            if(nrow(subs_) == 1) {
+                print(paste('(LVL3)Found match for:', state_, id_, year_))
+                one_match <- one_match + 1
+            } else {
[…]

### 2016-02-03 manuscript/text_reuse.tex
matching ncsl bills to db
added policy definition start

@@
 
+\section{Considering  Policy Similarity}
+
+Before
+
+Active within a domain, but possibly moving the status quo in opposite directions. (Glick)
+Moving the status quo in a uniform direction, but with different specific policies. (berry berry)
+Qualitative classification of the properties of bills adopted within a policy domain (Volden 2006)
+Quantitative coding of an important dimension of legislation (e.g., abortion bill restrictiveness) (Mooney and Lee 1992)
+
+In past research on policy adoption, studies have varied in terms of the degrees of similarity between policies
+
 \section{Detecting Text Reuse}
@@
 From the 50 sampled urls 22 fulfilled the three criteria.
-From these 23 tables we constructed a dataset of [???] bills, of wich we could match [???] to our data base of bill text.
+From these 23 tables we constructed a dataset of 950 bills, of which we could match 581 to our bill database.
 

### 2016-02-03 analysis/topic_modeling/topic_modeling.R

@@ -1,0 +1,39 @@
+setwd("/storage/group/bbd5087_collab/text_reuse/analysis")
+load("text_for_mallet.RData")
+
+options( java.parameters = "-Xmx80g" )
+
+#install.packages("mallet",lib="/storage/group/bbd5087_collab/r_packages",repos="http://cran.stat.ucla.edu/")
+
+.libPaths("/storage/group/bbd5087_collab/r_packages")
+
+library(mallet)
+
+set.seed(10)
+
+filenamesRS <- filenames
+aligned_textRS <- aligned_text
+
+mallet.instances <- mallet.import(filenamesRS,aligned_textRS,"en.txt")
+
+topic.model <- MalletLDA(num.topics=20)
+	
+topic.model$loadDocuments(mallet.instances)
+	
+vocabulary <- topic.model$getVocabulary()
+word.freqs <- mallet.word.freqs(topic.model)
+
+topic.model$setAlphaOptimization(20, 50)
+
+topic.model$train(300)
+	
+topic.model$maximize(10)
+	
+doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
+topic.words <- mallet.topic.words(topic.model, smoothed=T, normalized=T)
+
+topic.probs <- apply(doc.topics,2,mean)
+
+mallet.top.words(topic.model, topic.words[6,],20)
+
+save(list=c("topic.model","doc.topics","topic.words","topic.probs","vocabulary","word.freqs"),file="topic_model_results.RData")

### 2016-02-03 analysis/topic_modeling/topic_modeling40.R

@@ -1,0 +1,39 @@
+setwd("/storage/group/bbd5087_collab/text_reuse/analysis")
+load("text_for_mallet.RData")
+
+options( java.parameters = "-Xmx40g" )
+
+#install.packages("mallet",lib="/storage/group/bbd5087_collab/r_packages",repos="http://cran.stat.ucla.edu/")
+
+.libPaths("/storage/group/bbd5087_collab/r_packages")
+
+library(mallet)
+
+set.seed(10)
+
+filenamesRS <- filenames
+aligned_textRS <- aligned_text
+
+mallet.instances <- mallet.import(filenamesRS,aligned_textRS,"en.txt")
+
+topic.model <- MalletLDA(num.topics=40)
+	
+topic.model$loadDocuments(mallet.instances)
+	
+vocabulary <- topic.model$getVocabulary()
+word.freqs <- mallet.word.freqs(topic.model)
+
+topic.model$setAlphaOptimization(20, 50)
+
+topic.model$train(300)
+	
+topic.model$maximize(10)
+	
+doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
+topic.words <- mallet.topic.words(topic.model, smoothed=T, normalized=T)
+
+topic.probs <- apply(doc.topics,2,mean)
+
+mallet.top.words(topic.model, topic.words[6,],20)
+
+save(list=c("topic.model","doc.topics","topic.words","topic.probs","vocabulary","word.freqs"),file="topic_model_results40.RData")

### 2016-02-08 etl/ncsl_tables/match_bills.R
fixed bug in ncsl - lid billmatching

@@ -1,5 +1,4 @@
 library(dplyr)
-library(lubridate)
 
 ncsl_bills <- read.csv('../../data/ncsl/ncsl_data_from_sample.csv', 
                        header = TRUE, stringsAsFactors = FALSE)
@@ -27,7 +26,7 @@ ncsl_bills$let_id <- gsub('[[:digit:]]', '', ncsl_bills$id)
 
 
 # Matching
-db_bills <- tbl_df(db_bills) %>% select(state, year, id, num_id, let_id)
+db_bills <- tbl_df(db_bills) %>% select(state, year, id, num_id, let_id, unique_id)
 no_match <- 0
 multi_match <- 0
 one_match <- 0
@@ -50,14 +49,14 @@ for(i in 1:nrow(ncsl_bills)) {
         if(nrow(subs) == 1) {
             print(paste('(LVL2)Found match for:', state_, id_, year_))
             one_match <- one_match + 1
-            ncsl_bills$matched_from_db[i] <- subs$id
+            ncsl_bills$matched_from_db[i] <- subs$unique_id
         } else {
             # Match multiple
             subs_ <- filter(subs, let_id == let_)
             if(nrow(subs_) == 1) {
                 print(paste('(LVL3)Found match for:', state_, id_, year_))
                 one_match <- one_match + 1
-                ncsl_bills$matched_from_db[i] <- subs_$id
+                ncsl_bills$matched_from_db[i] <- subs_$unique_id
             } else {
                 if(nrow(subs_) == 0) {
                     # Distance matching procedure
@@ -69,7 +68,7 @@ for(i in 1:nrow(ncsl_bills)) {
                         print(paste('(LVL4)Found match for:', state_, id_, 
                                     year_))
                         one_match <- one_match + 1
-                        ncsl_bills$matched_from_db[i] <- subs$id
+                        ncsl_bills$matched_from_db[i] <- subs$unique_id
                     } else {
                         if(nrow(subs) == 0){
                             print(paste('(LVL4)No match for:', state_, id_, 

### 2016-02-08 manuscript/tables/ideology_regs.tex
ideology analysis only with sum scores now, paper updated

@@
 % latex table generated in R 3.2.2 by xtable 1.7-4 package
-% Mon Dec 21 04:04:01 2015
+% Mon Feb  8 18:23:42 2016
 \begin{table}[ht]
@@
   \hline
- & Intercept & Estimate & Std.Dev & p.value \\ 
+ & Intercept & Estimate & Std.Dev & p \\ 
   \hline
-Sum & 4.300 & -0.034 & 0.001 & 0.000 \\ 
-  Mean & 3.814 & -0.025 & 0.001 & 0.000 \\ 
-  Max & 3.972 & -0.031 & 0.001 & 0.000 \\ 
-  No. Alignments & 0.486 & -0.009 & 0.001 & 0.000 \\ 
+1 & 4.300 & -0.034 & 0.001 & 0.000 \\ 
    \hline
 \end{tabular}
-\caption{Log-Linear models for alignment and euclidian
+\caption{Log-Linear model for alignment and euclidian
 distance in ideology. Two tailed p-values are generated from quadratic
 assignment procedure with 1000 iterations. Std.Dev is the standard
-deviation of the null distribution. The rows correspond to
-different methods of aggregating the section alignments to bill
-allignments: \textit{Sum}: Sum of alignment scores of all alignments,
-\textit{Mean}: Average alignment score accross secion pairs bill dyad,
-\textit{Max}: Highest alignment score seciton pairs of bill dyad,
-\textit{No. Alignments}: Number of alignments for bill dyad.} 
+deviation of the null distribution.} 
 \label{tab:ideology_regs}

### 2016-02-08 manuscript/text_reuse.tex
fixed bug in ncsl - lid billmatching
ideology analysis only with sum scores now, paper updated

@@
 From the 50 sampled urls 22 fulfilled the three criteria.
-From these 23 tables we constructed a dataset of 950 bills, of which we could match 581 to our bill database.
+From these 22 tables we constructed a dataset of 950 bills, of which we could match 707 to our bill database.
 
@@
 When we are generating the alignments the bills are split up into sections.
-Table \ref{tab:ideology_regs} displays results for several methods of combining multiple alignments across sections of the same bill dyad.
-Specifically we investigate four different ways of aggregating to the bill level: the sum of the alignment scores of the sections of a bill dyad, the mean of these scores, the maximum of the scores, and the number of alignments between two bills.
-
-Each model is a log-linear model regressing the logarithm of the aggregated measure on the ideological distance between the ideal point of the two bills forming the dyad.
+We generate an alignment score for a bill dyad by summing over all section dyads of the bill dyad.
+Table \ref{tab:ideology_regs} displays regression results from a log-linear model regressing the logarithm of the bill dyad alignment score on the ideological distance between the ideal point of the two bills forming the dyad.
 The ideal point of the bill is derived from the ideal point of the bill sponsor.
@@
 
-The results in Table \ref{tab:ideology_regs} clearly show that there is a significant correlation between the ideological distance of the bills' sponsors and their text alignment score, regardless of the aggregation method.
-For each aggregation method, assuming the null hypothesis of no correlation, the probability for the observed estimate estimated as zero.
+The results in Table \ref{tab:ideology_regs} clearly show that there is a significant correlation between the ideological distance of the bills' sponsors and their text alignment score The null hypothesis of no correlation, the probability for the observed estimate estimated as zero.
 This is also clear from Figure \ref{fig:qap_dist}, which shows histograms of the permutation distributions of the regression coefficients and the actual estimates as a red line.
@@
 
-To asses the substantive importance of the effect size, Figure \ref{fig:ideo_interpret} displays the estimated decrease in mean alignment score when increasing the ideological distance of the bills.
+To asses the substantive importance of the effect size, Figure \ref{fig:ideo_interpret} displays the estimated decrease in alignment score when increasing the ideological distance of the bills.
 The vertical lines correspond to the ideological distances between the median democrat and republican, the 0.05 quantile and the 0.95 quantile of the total distribution of ideal points and the minimum and maximum of the total distribution.

### 2016-02-08 analysis/ideology/ideology.R

@@ -43,26 +43,21 @@ load("qap_data.RData")
 # 
 # # Alignments
 # alignments <- tbl_df(read.csv('../../data/lid/bill_to_bill_scores_only.csv', 
-#                               colClasses = c("factor", "factor", "numeric"),
-#                               skip = 1, 
-#                               #nrows = 1000
-#                               ) )
+#                               header = TRUE, stringsAsFactors = FALSE))
 # 
 # ## Match alignments with ideology scores
 # temp <- mutate(meta, left_doc_id = unique_id, left_ideology = sponsor_idology) %>%
-#     select(left_doc_id, left_ideology)
+#     dplyr::select(left_doc_id, left_ideology)
 # df <- left_join(alignments, temp, by = "left_doc_id")
 # temp <- mutate(meta, right_doc_id = unique_id, right_ideology = sponsor_idology) %>%
-#     select(right_doc_id, right_ideology)
+#     dplyr::select(right_doc_id, right_ideology)
 # df <- left_join(df, temp, by = "right_doc_id")
 # df <- mutate(df, ideology_dist = (left_ideology - right_ideology)^2,
 #              dyad_id = as.factor(paste0(left_doc_id, right_doc_id)))
 # 
-# ## Aggregate to bill level
+# # Aggregate to bill level
 # aggr <- group_by(df, left_doc_id, right_doc_id) %>%
-#     summarize(sum_score = sum(alignment_score), n_align = n(),
-#               mean_score = mean(alignment_score), 
-#               max_score = max(alignment_score),
+#     summarize(sum_score = sum(alignment_score), 
 #               ideology_dist = ideology_dist[1],
 #               left_ideology = left_ideology[1],
 #               right_ideology = right_ideology[1]) %>% 
@@ -71,19 +66,19 @@ load("qap_data.RData")
 # rm(df, alignments, temp)
 # gc()
 # 
-# # ==============================================================================
-# # Descriptives
-# # ==============================================================================
-# 
-# # Number of bills with ideology scores
-# length(which(!is.na(meta$sponsor_idology))) / nrow(meta)
-# 
-# # Number of dyads with ideology distance
-# length(which(!is.na(aggr$ideology_dist))) / nrow(aggr)
-# 
-# # Distribution of distance and log(score)
-# ggplot(aggr) + geom_histogram(aes(ideology_dist), color = "white")
-# 
[…]

### 2016-02-08 analysis/ncsl/ncsl_analysis.R

@@ -43,4 +43,10 @@ gc()
 df <- mutate(bill_pairs, alignment_score_zeros = ifelse(is.na(alignment_score), 
                                                         0, alignment_score))
 
-ggplot(df) + geom_histogram(aes(x = alignment_score_zeros, fill = same_table))
+# Exclue one big outlier
+df <- df[-which.max(df$alignment_score), ]
+
+ggplot(df) + 
+    geom_point(aes(x = same_table, y = alignment_score_zeros), 
+               position = "jitter", alpha = 0.6, size = 0.4) +
+    scale_y_log10()

### 2016-02-10 manuscript/text_reuse.tex
revised intro

@@
 
-\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
+\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse}
 \date{\today}
@@
 The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}.
-Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}.
-In this paper we draw upon a massive and nearly all-encompassing source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures.
-We take an automated, computer-based, approach to the analysis of bill text.
-This vastly increases the volume of data that can be included in policy diffusion research.
+Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}.
+In this paper we draw upon a voluminous and comprehensive source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures.
+We take an automated, text-as-data, approach to the analysis of bill text.
+This vastly increases the volume of data that can be included in policy adoption research.
 
@@
 The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purpose of policy diffusion research.
-We cannot define a standard in the literature according to which two policies can be deemed equivalent, and argue instead for conceptualizing policy diffusion in terms of a continuum of similar policy rather than a dichotomy of equivalence.
+Considering precedents in the literature, we argue for conceptualizing policy adoption in terms of a continuum of similar policy rather than a dichotomy of equivalence.
 
 We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws.
-First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text.
+First, we use topic modeling on the discovered reused text sequences to assess whether the content of the matching text follows major themes of public policy.
 Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills.
@@
 And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.
-
-This work has several important implications.
-First, it allows us to estimate, how policies are transferred between states.
-Do state legislators work mainly from templates from other states or interest groups, or to what extent do legislators draft their own bill text.
-Furthermore, text reuse is a relatively simple metric to calculate for large amounts of text.
-Previous scholars of policy diffusion mainly relied on case studies or manually coded data sets of policy diffusion in few policy areas.
-If working copying text forms a significant portion of how legislators adopt policies from other states, text reuse can be used to easily gather comprehensive data sets on policy diffusion.
 

### 2016-02-13 analysis/ncsl/ncsl_analysis.R
ncsl analysis w/o same state dyads

@@ -1,6 +1,6 @@
 library(dplyr)
-library(network)
 library(ggplot2)
+library(xtable)
 
 # Load and preprocess data
 alignments <- tbl_df(read.csv('../../data/lid/bill_to_bill_scores_only.csv',
@@ -15,6 +15,11 @@ ncsl_bills <- tbl_df(read.csv('../../data/ncsl/ncsl_data_from_sample_matched.csv
 bill_pairs <- tbl_df(as.data.frame(t(combn(ncsl_bills$matched_from_db, 2))))
 colnames(bill_pairs) <- c("left_doc_id", "right_doc_id") 
 
+# Remove pairs from same state
+incl <- substr(as.character(bill_pairs$left_doc_id), 1, 2) != 
+    substr(as.character(bill_pairs$right_doc_id), 1, 2)
+bill_pairs <- bill_pairs[incl, ]
+
 
 # Get 'same-table-indicator'
 ## Join with topic tables
@@ -25,9 +30,6 @@ temp <- mutate(ncsl_bills, right_doc_id = matched_from_db, right_table = topic) 
     select(right_doc_id, right_table)
 df <- left_join(df, temp, by = "right_doc_id") %>% 
     mutate(same_table = ifelse(left_table == right_table, 1, 0))
-rm(temp)
-gc()
-
 
 # Join with alignment data
 ## Calculate bill level alignments
@@ -37,11 +39,16 @@ bill_alignments <- group_by(alignments, left_doc_id, right_doc_id) %>%
 ## Join
 bill_pairs <- left_join(df, alignments, 
                         by = c("left_doc_id", "right_doc_id"))
-rm(df)
-gc()
+df <- mutate(bill_pairs, alignment_score_NA = ifelse(is.na(alignment_score), 
+                                                        1, 0))
+eda_tab <- xtabs( ~ same_table + alignment_score_NA, data = df)
 
-df <- mutate(bill_pairs, alignment_score_zeros = ifelse(is.na(alignment_score), 
-                                                        0, alignment_score))
+sink(file = '../../manuscript/tables/ncsl_crosstab.tex')
+xtable(eda_tab, caption = "Crosstable of being in the same table against having 
+       an alignment score for all bill dyads in the ncsl dataset.", 
+       label = "tab:ncsl_crosstab")
+sink()
+
 
 # Exclue one big outlier
 df <- df[-which.max(df$alignment_score), ]

### 2016-02-13 manuscript/text_reuse.tex
title
updated ncsl results
ncsl analysis w/o same state dyads
updated policy description

@@
 
-\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse}
+\title{Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse}
 \date{\today}
@@
 
-Before
+Before we describe the algorithm we use for detecting text re-use, and validate that algorithm, we should clearly define the latent variable we seek to measure through the assessment of text overlap.
+The latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}.
+The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein.
+These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation.
+We do not claim that the re-use of text can be used to measure these dimensions in a specific, disaggregated way.
+Rather, text re-use serves as a summary measure of similarity across all relevant policy dimensions represented in legislative text.
 
@@
 If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
+\subsection{NCSL Tables}
+
+\begin{table}[ht!]
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{lll}
+               & alignment & no alignment \\
+not same table & 11        & 232287       \\
+same table     & 3083      & 20639       
+\end{tabular}
+\end{table}
 

### 2016-02-13 manuscript/text_reuse.tex
updating policy similarity

@@
 \externaldocument{tables/ideology_regs.tex}
+\externaldocument{tables/ncsl_crosstab.tex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Rather, text re-use serves as a summary measure of similarity across all relevant policy dimensions represented in legislative text.
+With reference to existing literature, we show that studies of policy adoption and diffusion have typically focused on classes of similar policies, rather than looking for the adoption of {\em equivalent} policies.
 
@@
 
-In past research on policy adoption, studies have varied in terms of the degrees of similarity between policies
+Drawing upon this general concept of similarity, we derive three empirical expectations regarding the behavior of text re-use as an effective measure of policy similarity.
+These will serve as validity tests going forward.
 
@@
 
-\begin{table}[ht!]
-\centering
-\caption{My caption}
-\label{my-label}
-\begin{tabular}{lll}
-               & alignment & no alignment \\
-not same table & 11        & 232287       \\
-same table     & 3083      & 20639       
-\end{tabular}
-\end{table}
+\input{tables/ncsl_crosstab.tex}
 

### 2016-02-13 manuscript/text_reuse.tex
finished policy similarity section

@@
 
-Active within a domain, but possibly moving the status quo in opposite directions. (Glick)
-Moving the status quo in a uniform direction, but with different specific policies. (berry berry)
-Qualitative classification of the properties of bills adopted within a policy domain (Volden 2006)
-Quantitative coding of an important dimension of legislation (e.g., abortion bill restrictiveness) (Mooney and Lee 1992)
+In past work on policy adoption, researchers have drawn upon varying levels of similarity to define the policies of focus.
+Perhaps the broadest approach---studying policies adopted within a domain, but moving the status quo in opposite directions---is represented by \citet{glick1992judicial}.
+Glick studies judicial enactments related to the ``right to die''---the right of patients or their representatives to end the use of life-preserving medical technology.
+He considers an adoption to include any judicial enactment on this topic, whether they restrict medical providers' deference to the patients or enact broad patients' rights.
+\citet{berry1990} look at policy change in a uniform direction---states' adoption of lotteries.
+Lotteries, of course, vary in terms of their rules and financial models, but all of the policies studied by \citet{berry1990} moved the status quo from no state lottery to the existence of a state lottery.
+\citet{volden2006} considers a broad array of state laws---those implemented for the Federal Health and Human Services Children's Health Insurance Program (CHIP).
+CHIP laws were coded for six policy characteristics and then analyzed for diffusion dynamics.
+Lastly, \citet{mooney1995legislative} provides an example of quantitative coding of policies adopted in a given domain.
+They code the permissiveness of state abortion laws (pre Roe v.
+Wade) on a five-point scale.
+These examples convey the variability with which scholars have defined the set of policies that are considered suitable for comparison in policy adoption studies.
 
-Drawing upon this general concept of similarity, we derive three empirical expectations regarding the behavior of text re-use as an effective measure of policy similarity.
-These will serve as validity tests going forward.
+Drawing upon this general concept of similarity, we see that policies that are considered comparable in the context of diffusion exhibit two qualities.
+First, they often, but do not always, move the status quo in a similar direction.
+This could be thought of as ideological similarity.
+Second, they enact policy in similar domains---either narrowly or broadly conceived.
+If measuring text re-use is an effective measure of the concepts underlying policy diffusion, we should see the volume of text re-use correlate with the ideological and policy domain similarities of state bills.
+We will revisit these two dimensions when describing our validation tests below.
+But first we define the algorithms we use for the analysis of text reuse.
 

### 2016-02-14 manuscript/text_reuse.tex
revised abstract

@@
 \setlength{\parindent}{0.0in}
-\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
+\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
 \mmddyyyydate
@@
 
+\singlespacing
 \begin{abstract} 
-    Much political science research relies on identifying the substantive similarity of legislation, especially in the study of policy diffusion.
-Scholars mostly rely on hand-coded datasets.
-However, in order to study policy diffusion more broadly, for example by extending the study to dozens or more policy domains, prohibitive volumes of legislative text would have to be analyzed manually.
-Common text analysis algorithms such as topic models or bag-of-words based text similarity measures are too coarse to identify policy similarity.
+    \noindent The identification of substantively similar legislation is important to scholars of public policy diffusion and state legislative politics.
+The conventional approach involves hand-coding a small number of policy issues.
+However, in order to study policy more broadly, prohibitive volumes of legislative text would have to be analyzed manually.
+Common bag-of-words based text analysis algorithms text similarity measures are too coarse to identify policy similarity.
 However, legislators often directly use text from bills introduced in other legislatures or bill text provided by interest groups in model legislation.
@@
 First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse.
-Second, we show that the main topical themes underlying strings of reused text map closely onto major areas of public policy in the US States.
+Second, we show that bills classified by the National Council of State Legislatures as covering the same policy areas exhibit a high degree of text re-use.
 Third, we show that rates of text reuse across state borders correlates strongly with the state policy diffusion ties data recently introduced by \citet{desmarais2015}.
 \end{abstract}
+\doublespacing
+\clearpage
 
-\section{Introduction}
-
-The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}.
+\section{Introduction} The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}.
 Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}.
@@
 
-We will rely on two main data sources to assess the reliability of text reuse to
+We will rely on three main data sources to assess the reliability of text reuse to
 identify substantively equivalent bills.
 
-\textit{Bill text}\\
+\subsection{Bill text}\\
 In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al.
@@
 
-\textit{Ideological Scores}\\
+\subsection{Ideological Scores}\\
 For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.
@@
 
-\textit{Ground truth - NCSL Tables}\\
+\subsection{Ground truth - NCSL Tables}\\
 
-To build a ground truth data set, we rely on thematic tables published by the National Council of State Legislatures\footnote{\url{www.ncsl.org}} (NCSL).
-We collected a sample of these tables with the following procedure:
+To build a ground truth data set, we rely on thematic tables published by the National Council of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}}  We collected a sample of these tables with the following procedure:
 

### 2016-02-14 manuscript/text_reuse.tex
re-arranged sections and added conclusion

@@
 \usepackage{booktabs}
+\usepackage{color}
 \usepackage{multirow}
@@
 \setlength{\parindent}{0.0in}
-\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
+\setlength{\parskip}{1.5ex plus 0.5ex minus 0.2ex}
 \mmddyyyydate
@@
 
-Previous research on policy diffusion relies almost exclusively on small subsamples of legislation and hand coded data.
-Little work has been invested in investigating automated ways of detecting equivalent bills in order to measure policy diffusion.
-\citet{wilkerson2015tracing} use the Smith-Waterman local alignment algorithm (SW algorithm) \citep{smith1981identification} to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US congress.
-
-\section{Considering Policy Similarity}
-
 Before we describe the algorithm we use for detecting text re-use, and validate that algorithm, we should clearly define the latent variable we seek to measure through the assessment of text overlap.
@@
 
+Previous research on policy diffusion relies almost exclusively on small subsamples of legislation and hand coded data.
+Little work has been invested in investigating automated ways of detecting equivalent bills in order to measure policy diffusion.
+\citet{wilkerson2015tracing} use the Smith-Waterman local alignment algorithm (SW algorithm) \citep{smith1981identification} to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US congress.
+
 In this study we use the same algorithm as \citet{wilkerson2015tracing} to detect matching sequences of text in state bills.
@@
 
-\section{Data}
+\section{Bill Alignments}
 
-We will rely on three main data sources to assess the reliability of text reuse to
-identify substantively equivalent bills.
-
-\subsection{Bill text}\\
 In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al.
@@
 
-\subsection{Ideological Scores}\\
-For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.
-The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.
+The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences.
+The same algorithm has been used by \citet{wilkerson2015tracing} to trace bills through the legislative process in congress.
+When considering two bills, the algorithm treats each bill as a sequence of words and tries to find the best alignment between these two sequences.
+\citet{wilkerson2015tracing} split the bills into sections and search for text reuse across sections.
+Since this results in about 7 billion possible pairs, first filter out pairs that don't have an exact match of a sequence of at least ten words.
+We encounter the same problem in our analysis to a greater extent.
+Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.
 
-\subsection{Ground truth - NCSL Tables}\\
+{\bf \textcolor{red}{Put in some example allignments}}: Possibly finding a few that appear in bills across several states.
+
+\section{Validation Analysis}
+
+We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence.
+First, we evaluate whether there is a disproportionately high number of alignments between bills on the same policy area.
+This is done using the NCSL tables to identify bills on the same policy area.
+Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}.
+And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores.
+If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
+\subsection{NCSL Tables}
 
@@
 
-\section{Alignments}
-
-The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences.
-The same algorithm has been used by \citet{wilkerson2015tracing} to trace bills through the legislative process in congress.
-When considering two bills, the algorithm treats each bill as a sequence of words and tries to find the best alignment between these two sequences.
-\citet{wilkerson2015tracing} split the bills into sections and search for text reuse across sections.
-Since this results in about 7 billion possible pairs, first filter out pairs that don't have an exact match of a sequence of at least ten words.
-We encounter the same problem in our analysis to a greater extent.
-Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.
-
-\section{Analysis}
-
-We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence.
-First, we apply topic models to the sequences that are identified by the SW algorithm as matching sequences.
-This provides a rough idea of how many of the alignments are substantial and how much procedural language and not substantively significant language gets picked up by the algorithm.
-Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}.
-And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores.
-If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
-\subsection{NCSL Tables}
-
 \input{tables/ncsl_crosstab.tex}
-
-\subsection{Topic Modeling}
-
-We apply statistical topic modeling via Latent Dirichlet Allocation (LDA) \citep{blei2003} to the alignment text with two objectives.\footnote{We use the R package \texttt{mallet} \citep{mallet} for the topic modeling application.} First, we want to see whether the major topical themes that emerge are consistent with policy domains that we would expect to be prominently featured in texts that capture the diffusion of public policy.
-Second, we want to see whether we can identify topics that correspond to boilerplate/procedural text, which we may want to remove from the alignments to focus the analysis on substantive policy language.
-In our first cut we use a model with 20 topics.
-The average alignment is short, with little more than 25\% exceeding 140 characters -- the maximum length of a Tweet.
-There are 52,735 unique terms in our vocabulary, after removing a standard list of stop words.
-In Table \ref{tab:top100words} we present the top 100 terms appearing in our corpus.
-
-\begin{table}[ht]
-\rule{\textwidth}{1pt} \\ \vspace{-1cm}
-\begin{quotation}
-\noindent state person section states act means health public member general commission department law information provided insurance including board subsection legislature benefit court individual property order services care action business time pursuant united date year subject interstate federal compact school insurer corporation required medical chapter provide party entity vehicle amount notice people assembly agreement tax qualified provisions attorney agency limited made service authority child purposes years commissioner education report days policy employer members company code contract employee interest authorized effective statement district purpose ii application period number credit plan include senate income system amended issued reasonable part program director patient requirements
-\end{quotation} \vspace{-.5cm}
-\rule{\textwidth}{1pt} \vspace{-.2cm}
-\caption{Top 100 words, listed left-to-right, in the alignments corpus.}
-\label{tab:top100words}
-\end{table}
-
-The topic modeling results are presented in Table \ref{tab:topics}.
-We see that most topics correspond to recognizable policy domains.
-However, some topics, such as Topic 9, which appears to be a mix of automobile policy and abortion policy, appear to consist of more than one distinct policy domain.
-As such, we should try running this with more topics.
-Topic 17 appears to be a boilerplate topic.
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{rl}
-  \hline
-  \hline
-6 & benefit corporation public director officer specific interests directors person purpose \\ 
-  16 & state order child section support law application employer enforcement court \\ 
-  14 & salts isomers food substances substance means preparation product compound mixture \\ 
-  3 & court state order person petition section proceeding law appraisal jurisdiction \\ 
-  8 & feet distance medical patient marijuana point qualifying south north west \\ 
-  20 & information electronic consumer service section insurance notice portable electronics means \\ 
-  9 & vehicle motor person means abortion woman medical child dealer death \\ 
-  18 & property interest statement section person trust real transfer agreement financing \\ 
-  5 & person offense age sexual years criminal court officer sex guilty \\ 
-  15 & states united state presidential election official member vote president popular \\ 
-  17 & state enacted legislature general assembly people amended section read senate \\ 
-  2 & action person section court state civil violation attorney reasonable degree \\ 
-  7 & qualified tax section investment revenue entity credit amount fund code \\ 
-  19 & health care patient practice medical physician licensed person means services \\ 
-  12 & department health state services act public year federal care program \\ 
-  4 & appointed members house attorney senate power principal member authority representatives \\ 
-  1 & individual employer year years taxable service income employee period january \\ 
-  10 & insurance insurer policy commissioner company section coverage contract state plan \\ 
-  11 & state commission interstate compact member states rules compacting effective law \\ 
-  13 & school student board district education public charter state students county \\ 
-   \hline
-\end{tabular}
-\caption{Results from 200 iterations of LDA with 10 iterations of hyper parameter optimization.
-Top 10 words in each topic listed for each topic.
-Topics listed in order of frequency of appearance within documents, beginning in the first row of the table with the most frequent topic.}
-\label{tab:topics}
-\end{table}
-
-\begin{table}[ht]
-\rule{\textwidth}{1pt} \\ \vspace{-1cm}
-\begin{quotation}
-\noindent state person section states act means health public member general commission department law information provided insurance including board subsection legislature benefit court individual property order services care action business time pursuant united date year subject interstate federal compact school insurer corporation required medical chapter provide party entity vehicle amount notice people assembly agreement tax qualified provisions attorney agency limited made service authority child purposes years commissioner education report days policy employer members company code contract employee interest authorized effective statement district purpose ii application period number credit plan include senate income system amended issued reasonable part program director patient requirements
-\end{quotation} \vspace{-.5cm}
-\rule{\textwidth}{1pt} \vspace{-.2cm}
-\caption{Top 100 words, listed left-to-right, in the alignments corpus.}
-\label{tab:top100words}
-\end{table}
 
@@
 %R script for this analysis: '/analysis/ideology.R'
+
+For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}.
+The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.
 
@@
 
+\section{Applying Bill Similarity: Association with Campaign Contributions}
+
+\section{Conclusion}
+
+Scholarship on public policy and legislative politics relies heavily on measuring the content of legislation, especially with a relative or comparative approach.
+Manual comparison of bills is prohibitively time consuming when it comes to covering a large proportion of legislation introduced in one or more legislatures.
+We show that the automated detection of
+
 \clearpage
@@
 
-\section{Appendix}
+\section*{Appendix}
 
@@
 \end{document}
+
+\subsection{Topic Modeling}
+
+We apply statistical topic modeling via Latent Dirichlet Allocation (LDA) \citep{blei2003} to the alignment text with two objectives.\footnote{We use the R package \texttt{mallet} \citep{mallet} for the topic modeling application.} First, we want to see whether the major topical themes that emerge are consistent with policy domains that we would expect to be prominently featured in texts that capture the diffusion of public policy.
+Second, we want to see whether we can identify topics that correspond to boilerplate/procedural text, which we may want to remove from the alignments to focus the analysis on substantive policy language.
+In our first cut we use a model with 20 topics.
+The average alignment is short, with little more than 25\% exceeding 140 characters -- the maximum length of a Tweet.
+There are 52,735 unique terms in our vocabulary, after removing a standard list of stop words.
+In Table \ref{tab:top100words} we present the top 100 terms appearing in our corpus.
+
+\begin{table}[ht]
+\rule{\textwidth}{1pt} \\ \vspace{-1cm}
+\begin{quotation}
+\noindent state person section states act means health public member general commission department law information provided insurance including board subsection legislature benefit court individual property order services care action business time pursuant united date year subject interstate federal compact school insurer corporation required medical chapter provide party entity vehicle amount notice people assembly agreement tax qualified provisions attorney agency limited made service authority child purposes years commissioner education report days policy employer members company code contract employee interest authorized effective statement district purpose ii application period number credit plan include senate income system amended issued reasonable part program director patient requirements
+\end{quotation} \vspace{-.5cm}
+\rule{\textwidth}{1pt} \vspace{-.2cm}
+\caption{Top 100 words, listed left-to-right, in the alignments corpus.}
+\label{tab:top100words}
+\end{table}
+
+The topic modeling results are presented in Table \ref{tab:topics}.
+We see that most topics correspond to recognizable policy domains.
+However, some topics, such as Topic 9, which appears to be a mix of automobile policy and abortion policy, appear to consist of more than one distinct policy domain.
+As such, we should try running this with more topics.
+Topic 17 appears to be a boilerplate topic.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rl}
+  \hline
+  \hline
+6 & benefit corporation public director officer specific interests directors person purpose \\ 
+  16 & state order child section support law application employer enforcement court \\ 
+  14 & salts isomers food substances substance means preparation product compound mixture \\ 
+  3 & court state order person petition section proceeding law appraisal jurisdiction \\ 
+  8 & feet distance medical patient marijuana point qualifying south north west \\ 
+  20 & information electronic consumer service section insurance notice portable electronics means \\ 
+  9 & vehicle motor person means abortion woman medical child dealer death \\ 
+  18 & property interest statement section person trust real transfer agreement financing \\ 
+  5 & person offense age sexual years criminal court officer sex guilty \\ 
+  15 & states united state presidential election official member vote president popular \\ 
+  17 & state enacted legislature general assembly people amended section read senate \\ 
+  2 & action person section court state civil violation attorney reasonable degree \\ 
+  7 & qualified tax section investment revenue entity credit amount fund code \\ 
+  19 & health care patient practice medical physician licensed person means services \\ 
+  12 & department health state services act public year federal care program \\ 
+  4 & appointed members house attorney senate power principal member authority representatives \\ 
+  1 & individual employer year years taxable service income employee period january \\ 
+  10 & insurance insurer policy commissioner company section coverage contract state plan \\ 
+  11 & state commission interstate compact member states rules compacting effective law \\ 
+  13 & school student board district education public charter state students county \\ 
+   \hline
+\end{tabular}
+\caption{Results from 200 iterations of LDA with 10 iterations of hyper parameter optimization.
+Top 10 words in each topic listed for each topic.
+Topics listed in order of frequency of appearance within documents, beginning in the first row of the table with the most frequent topic.}
+\label{tab:topics}
+\end{table}
+
+\begin{table}[ht]
+\rule{\textwidth}{1pt} \\ \vspace{-1cm}
+\begin{quotation}
+\noindent state person section states act means health public member general commission department law information provided insurance including board subsection legislature benefit court individual property order services care action business time pursuant united date year subject interstate federal compact school insurer corporation required medical chapter provide party entity vehicle amount notice people assembly agreement tax qualified provisions attorney agency limited made service authority child purposes years commissioner education report days policy employer members company code contract employee interest authorized effective statement district purpose ii application period number credit plan include senate income system amended issued reasonable part program director patient requirements
+\end{quotation} \vspace{-.5cm}
+\rule{\textwidth}{1pt} \vspace{-.2cm}
+\caption{Top 100 words, listed left-to-right, in the alignments corpus.}
+\label{tab:top100words}
+\end{table}

### 2016-02-14 manuscript/text_reuse.tex
finished brief conclusion

@@
 
-\section{Validation Analysis}
+\section{Evaluation of Validity}
 
@@
 
+{\bf \textcolor{red}{Need clarity on multiple sponsors}}: If this is frequently a big list of co-sponsors, we should limit to just the first, if the first is the lead sponsor.
+
 The single observations (bill dyads) are not independent, due to the network structure of the data.
@@
 Manual comparison of bills is prohibitively time consuming when it comes to covering a large proportion of legislation introduced in one or more legislatures.
-We show that the automated detection of
+We show that the automated detection of similar text strings in bills provides an effective approach to comparing bill contents.
+The log alignment scores serve as a highly valid summary measure of the similarity of two bills.
+We show high validity of this measure in three complimentary tests.
+First, it correlates with the presence of a diffusion tie inferred from patterns of policy diffusion.
+Second, it correlates with the ideological similarity between bill sponsors.
+Third, it exhibits extremely high precision in predicting whether two bills are listed in the NCSL policy area tables.
+We demonstrate the potential for using this data to test new or unexplored hypotheses on lawmaking in the states by testing whether bill text similarity correlates with campaign contributions to US state legislators.
 

### 2016-07-07 analysis/ideology/ideology_regression.R
chnges to ideo regression plot

@@ -123,12 +123,18 @@ pdat <- tbl_df(data.frame(coefs = out$base_model,
                           lower = apply(out$bootstrap_results, 1, quantile, 0.025)
                           )
                ) %>%
-    mutate(quantile_fctr = as.factor(quantile))
+    mutate(quantile_fctr = as.factor(quantile),
+           significant = as.factor(ifelse(upper < 0, 1, 0)))
+
 
 source('../plot_theme.R')
 ggplot(pdat) +
-    geom_point(aes(x = quantile_fctr, y = coefs)) +
-    geom_segment(aes(x = quantile_fctr, xend = quantile_fctr, y = lower, yend = upper)) +
+    geom_point(aes(x = quantile_fctr, y = coefs, color = significant)) +
+    geom_segment(aes(x = quantile_fctr, xend = quantile_fctr, y = lower, 
+                     yend = upper, color = significant)) +
+    scale_color_manual(values = c(cbPalette[1], "black")) +
+    guides(color = FALSE) +
+    geom_hline(aes(yintercept = 0), linetype = 2, color = "grey") + 
     coord_flip() + ylab("Quantile Regression Coefficient") +
     xlab("Quantile") + plot_theme
 ggsave('../../4344753rddtnd/figures/quantile_regression.png', width = p_width,

### 2016-07-07 analysis/ncsl/ncsl_analysis.R

@@ -2,8 +2,7 @@ library(dplyr)
 library(ggplot2)
 library(xtable)
 
-cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2",
-               "#D55E00", "#CC79A7")
+source('../plot_theme.R')
 
 # Load and preprocess data
 alignments <- tbl_df(read.csv('../../data/lid/alignments_1000_b2b_ns.csv',
@@ -100,8 +99,9 @@ df <- data.frame(value = c(prec_rec[, 1], prec_rec[, 2]),
 ggplot(df) + 
     geom_line(aes(y = value, x = threshold, color = type)) + 
     scale_color_manual(values = cbPalette[-1]) +
-    theme_bw() + 
-    xlab("Score threshold") + ylab("Value") + labs(color = "")
+    xlab("Score threshold") + ylab("Value") + labs(color = "") +
+    plot_theme
+    
     #facet_wrap(~ type, scales = "free")
 ggsave('../../4344753rddtnd/figures/ncsl_prec_rec.png')
 

### 2016-07-07 manuscript/main.tex
added manuscript as simple subfolder

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article} %a4paper

\usepackage{graphicx} 
%\usepackage{subfig} 
\usepackage{pdflscape} 
\usepackage{booktabs} 
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{color}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xr}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{amsfonts}
\usepackage{subfigure}

\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}

\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={red!50!black},
    urlcolor={blue!80!black}
}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{1.5ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
\doublespacing
\setlength{\columnseprule}{1pt}

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\externaldocument{tables/ideology_regressions.tex}
\externaldocument{tables/ncsl_crosstab.tex}
\externaldocument{tables/time_diff_reg.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse}
\date{\today}
\author{Fridolin Linder, Bruce Desmarais, Matt Burgess, Eugenia Giraudi}

\maketitle

\singlespacing
\begin{abstract} 
    \noindent The identification of substantively similar policy proposals in both proposed and adopted legislation is important to scholars of public policy diffusion and legislative politics. Conventional, manual, approaches are prohibitively costly in constructing datasets that accurately represent policymaking across policy domains, geographic units, and/or time. We propose the use of text-sequencing algorithms, applied to legislative text, to identify bills that introduce similar policy proposals. We present three ground truth tests, applied to a corpus of 500,000 bills from US-state legislatures. First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse. Second, we show that bills classified by the National Council of State Legislatures as covering the same policies exhibit a high degree of text re-use. Third, we show that rates of text reuse across state borders correlate strongly with the diffusion networks recently introduced by Desmarais, Harden and Boehmke (2015).

\end{abstract}

\doublespacing
\clearpage

\section{Introduction} The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}. Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}. In this paper we draw upon a voluminous and comprehensive source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures. We take an automated, text-as-data, approach to the analysis of bill text. This vastly increases the volume of data that can be included in policy adoption research.

Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles. The central methodological puzzles are two-fold. First, we need to extract segments of text in pieces of legislation that communicate similar policy enactments. Second, we need to develop a method for quantitatively scoring the reused text between bills. The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purposes of policy diffusion research. Considering precedents in the literature, we argue for conceptualizing policy adoption in terms of a continuum of similarity rather than a dichotomy of equivalence.

We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws. First, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Second, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states. And third, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap. We find that a high degree of text reuse between bills provides a precise signal of the presence of similar policies within the bills.

\section{Background}

%%%  Purposes of policy measurement %%% 
The measurement task on which we are focused is the identification of comparable policy actions (e.g., adoption, consideration) across jurisdictions---US states in particular. Scholars of public policy, legislative politics, and related areas have used measurements of comparable policy actions in a variety of research tasks. These include the study of policy diffusion \citep{karch2007emerging}, the comparison of policies on a select legislative issue \citep[e.g., ][]{huber2001legislatures,mycoff2009empirical}, and influence/adoption of model legislation introduced by advocacy organizations \citep[e.g., ][]{garrett2015,burgess2016legislative}. In each of these areas of research, scholars make use of measurements of consistent policy actions across jurisdictions. Below we review a variety of methods, and conceptual definitions that researchers have used in measuring consistent policy actions.

%%% Mechanics of policy measurement %%% 
Public policy research on cross-jurisdiction comparable policy actions has conventionally involved the manual identification of related policies across states, countries or local governments in one or a handful of policy areas \citep[e.g., ][]{walker1969,berry1990,simmons2004,gilardi2009,krause2011policy}. This is a manual approach to measurement at the monadic level. In the area of policy diffusion research, recognizing the limitations of monadic levels of measurement, researchers have developed dyadic approaches to studying the diffusion relationships between states \citep{volden2006,boehmke2009}. In the most recent iteration of dyadic approaches, \cite{desmarais2015} apply network inference algorithms to US state adoption sequences in over 100 policy domains to empirically infer the underlying network through which policies diffuse. In another recent innovation in measurement for policy analysis, \cite{garrett2015} analyze the text of US state legislation to identify the influence of model legislation, as introduced by interest groups.

 %%% How has policy similarity been defined, conceptually %%% 
We now consider the coding rules used in past research to define sets of equivalent, or at least similar, policies. Perhaps the broadest approach---studying policies adopted within a domain, but moving the status quo in opposite directions---is represented by \citet{glick1992judicial}. Glick studies judicial enactments related to the ``right to die''---the right of patients or their representatives to end the use of life-preserving medical technology. He considers an adoption to include any judicial enactment on this topic, whether they restrict medical providers' deference to the patients or enact broad patients' rights.  \citet{berry1990} look at policy change in a uniform direction---states' adoption of lotteries. Lotteries, of course, vary in terms of their rules and financial models, but all of the policies studied by \citet{berry1990} moved the status quo from no state lottery to the existence of a state lottery. \citet{volden2006} considers a broad array of state laws---those implemented for the Federal Health and Human Services Children's Health Insurance Program (CHIP). CHIP laws were coded for six policy characteristics and then analyzed for diffusion dynamics. Lastly, \citet{mooney1995legislative} provides an example of quantitative coding of policies adopted in a given domain. They code the permissiveness of state abortion laws (pre Roe v. Wade) on a five-point scale. These examples convey the variability with which scholars have defined the set of policies that are considered to be comparable across state borders.

\section{Detecting Policy Similarity through Text Reuse}

The above review of the ways in which researchers have defined comparable policies offers clarity regarding the implicit concepts underlying policy comparability. We see that policies that are considered comparable exhibit two qualities. First, they often, but do not always, move the status quo in a similar direction. This could be thought of as ideological similarity. Second, they enact policy in similar domains---either narrowly or broadly conceived. Before we describe the algorithm we use for detecting text re-use, and validate that algorithm, we draw upon these two concepts to define the latent variable we seek to measure through the assessment of text overlap. Specifically, we are motivated by the fact that researchers do not typically focus on strictly equivalent policies. Rather, they deem policies comparable if they are highly similar along one or two dimensions---policy domain and (optionally) ideological direction.

We see past work that has identified sets of comparable policies as focusing on sets of policies that meet some threshold of similarity. As such, the latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}. The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein. These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation. We do not claim that the re-use of text can be used to measure these dimensions in a specific, dis-aggregated way. Rather, text re-use serves as a summary measure of the greatest overlap observed across all relevant policy dimensions represented in legislative text.

\subsection{Detecting Text Reuse}
To assess the maximal similarity of policies proposed in two pieces of legislation, we seek to identify large segments of equivalent or highly similar text (i.e., text reuse between bills). Alignment algorithms for discovering similar long sequences of text stand in contrast to bag-of-words methods, which are based on the comparison of word occurrence frequencies in documents. Bag-of-words methods may be effective for capturing broad topical areas in legislation, but will provide results that are too coarse for precisely assessing policy overlap. For example, in modeling bills in the US Congress using statistical topic models, arguably the canonical bag-of-words method for text analysis, \citet{gerrish2011predicting} find that topic models for legislative text perform most effectively when parameterized with 64 topics to model a corpus of 4,447 bills. While 64 topics provides a fairly detailed categorization of the domains covered in legislation, it is unrealistic to think that this method can isolate individual policy proposals.  Considering \citeapos{gerrish2011predicting} results again, that would mean that the US Congress considers nearly seventy bills, on average, for each specific policy proposed.

There are a variety of algorithms designed to automatically detect text reuse between documents mostly originating in the plagiarism detection literature \citep[see e.g.][for an overview]{potthast2013overview}. In political science, \citet{wilkerson2015tracing} introduced the Smith-Waterman local alignment algorithm (SW algorithm) to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US Congress. We use the same algorithm to detect text reuse in US state bills, however, our implementation of the algorithm differs slightly. The SW algorithm was developed by \citet{smith1981identification} in molecular biology, in order to match genetic sequences. Given two sequences (of genes or words) it calculates the optimal alignment (match) between these sequences.

Sequences in text that convey equivalent content matter often do not match perfectly. Formatting, white space, typographical errors, etc. would decrease the precision dramatically if only exact matches were used. The SW algorithm, therefore, returns the optimal alignment while allowing for mismatches and gaps. The extent to which such imperfections are tolerated is governed by parameters that are set by the researcher. There are three such parameters: the match score (reward for exactly matching words), the mismatch score (penalty for including words that do not match), and the gap score (penalty for including placeholder words in matching a shorter sequence to a longer sequence). The goal of the algorithm is to return the the alignment with the highest score given the input sequences and the parameters. Consider the following two excerpts from Alaska State Bill 203 (28th session) and North Carolina House Bill 366 (2015) respectively:

\begin{quote}
\textit{"section 1.AS44.99 is amended by adding new sections to read: article 6. compact for a balanced budget (...)"} \\
\textit{"chapter 143 is amended by adding a new article to read: article 80. compact for a balanced budget (...)"}
\end{quote}

There is a large number of possibilities of how these sequences could be aligned. There is a trade-off between short sequences that match perfectly, and longer sequences with imperfections. For example, we could match just ``is amended by adding new'' or ``compact for a balanced budget''. However, by adding a gap between ``adding'' and ``new'' in the first sequence and accepting the mismatches ``article''-``section'' and ``6.''-``80.'', a longer alignment can be obtained: ``is amended by adding \textit{(a)} new \textit{(article/section)} to read: article \textit{(6./80.)}''.

Because there are so many different possibilities, it is computationally demanding to find the optimal alignment. \citet{smith1981identification} therefore proposed a dynamic programming approach that is illustrated in Figure \ref{fig:score_matrix}. Dynamic programming refers to algorithms that divide a problem into sub-problems and store results of previous calculations for later ones. In the case of the SW algorithm, the property that makes it a dynamic problem is the fact that all the alignments of shorter sub-sequences of an optimal alignment of a sequence are themselves optimal. Intuitively, if the benefits of including a sub-sequence in an alignment outweigh the penalties from mismatches and gaps in that sub-sequence, that sub-sequence will contribute positively to longer alignments to which it is appended. To make this clearer consider the beginning of the sequences in the example above:

\begin{quote}
\textit{``section 1.AS44.99 is amended''}\\
\textit{``chapter 143 is amended''}
\end{quote}

It is obvious that the best local alignment of the first three elements would be just "is" - "is" since the first two elements don't match and therefore would just reduce the overall quality of the alignment. If we now consider the alignment of the first four words we know that we can discard all possible alignments that involve the first two elements because the quality of every alignment that involves these elements could be improved by dropping them. Re-using the result from the first three elements, the problem of aligning the first four elements is now reduced to the single decision about the elements ``amended'' and ``amended''. This decision is easy to make because we only have to consider four possibilities: We match the elements and they are actually the same, we match the elements and they are not the same, we introduce a gap in one of the sequences or we decide to stop the alignment.

If the next two elements match, the decision is easy - we add them and increase the total alignment score. However, if they do not match the decision is more difficult. We only want to introduce a gap or mismatch if it pays off later (that is if we thereby can `reach' another part of the sequence that matches again). But we only know that once we went through the whole sequence. The central idea is therefore to find all optimal alignments ending in all possible spots, keep these scores and after everything is calculated finding the alignment that maximizes the overall quality. Therefore, after the decision is made the same procedure is applied to the next pair of sequence elements, and repeated until the end of both sequences is reached.

This intuition can be formalized in an algorithm that is based on a dynamic programming matrix that contains all optimal sub-alignments. A matrix is created where each combination of elements of the two sequences is assigned a cell. And an additional row and column of 0 is appended to the beginning of each sequence (to allow for a gap in the beginning of one sequence). The quality or alignment score of every possible alignment is then calculated cumulatively with the following algorithm. Denote the two sequences as $\mathcal{A} = (a_1, a_2, ... a_n)$ and $\mathcal{B} = (b_1, b_2, ..., b_k)$. Additionally let $\delta$, $\epsilon$ and $\gamma$ be the match, mismatch and gap scores. Define the scoring function:
\begin{equation}
	\label{eqn:scoring}
	S(a_i, b_j) = \delta^{\mathbb{I}(a_i = b_j)} + \epsilon^{\mathbb{I}(a_i \neq b_j)}
\end{equation} 
Where $\mathbb{I}(.)$ is the indicator function. Then the entry for each cell $M_{i,j}$, $i=1,2,...,n$ and $j=1,2,...,k$ of the matrix is filled by the following rule:
\begin{equation}
	\label{eqn:fill}
	M_{i,j} = \max(M_{i-1,j-1} + S(a_i, b_j), M_{i-1,j} + \gamma, M_{i,j-1} + \gamma, 0)
\end{equation}

The algorithm is visualized for the example above in Figure \ref{fig:score_matrix}. \footnote{An interactive version can be found at [FILL IN URL].}. Each row corresponds to a word in the sentence from the Alaska bill and each column to the sentence from the North Carolina bill. On the right side of the matrix the optimal alignment is displayed.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=1.05\textwidth]{figures/sm.png}
    \caption{Dynamic programming array of local alignment algorithm. The parameters in this instance are: Match Score: 5, Mismatch Score: -2, Gap Score: -1. The optimal alignment is displayed on the right side of the matrix. The left column corresponds to the text sequence in the rows of the matrix, the right column to the sequence in the columns. Mismatches are colored in red, gaps are indicated by "-" and orange color. The blue cells in the matrix display the path of the optimal alignment.}
    \label{fig:score_matrix}
\end{figure}

The four values of which the maximum is chosen in Equation \ref{eqn:fill} describe four steps in this dynamic programming array. The first value corresponds to a diagonal step which means in the resulting alignment sequence elements $a_i$ and $b_j$ are matched and the score of the alignment is either increased by $\delta$ if they match or decreased by $\epsilon$ if they don't match. The second and third value describe a gap step either in horizontal or vertical direction. That is, if we move from cell $(i,j)$ to cell $(i+1,j)$, in the resulting alignment sequence element $a_{i+1}$ is matched with a gap. On the other hand, if we move to cell $(i, j+1)$ sequence element $b_{j+1}$ is matched with a gap in the resulting alignment. If the first three values are all $<= 0$, the score in the cell is 0 meaning that no step is taken and every potential alignment stops at this point. This can be observed on the example from above in Figure \ref{fig:score_matrix}. The blue path describes the optimal alignment. The first two elements in both sequences don't match, therefore the score remains zero. Therefore the resulting alignment starts at the fourth element of each sequence with four diagonal steps, each adding points $(\delta = 5)$ to the final score which reaches 20 at the alignment ending in ``adding''-``adding''. After that, a step to the right is taken, meaning that the additional ``a'' in the column sequence is matched with a gap in the row sequence (indicated by ``-'' and orange coloring in the result on the right hand side). The cumulative score of the alignment is reduced by $\gamma = -1$ to 19. After that only diagonal steps are taken. Note that there are two mismatches each of which reduces the score by $\epsilon = -2$.

The optimal alignment is identified by finding the highest score in the matrix, at which the alignment ends, and back-tracing the path of the alignment. The steps in the path are chosen using Equation \ref{eqn:fill}, and are indicated in Figure \ref{fig:score_matrix} by lines pointing to the left, the upper left, up or no line. The back-tracing continues until a  zero is encountered.

This algorithm is computationally intensive ($\mathcal{O}(nk)$ in time and space), but returns the globally optimal local alignment given the scoring parameters. We provide a proof of this in the appendix. The property follows from the recursive relation used to fill the dynamic programming matrix. An alignment that is constructed by adding one element to an already optimal alignment is optimal itself. Starting by aligning the first two elements of the sequence optimally (which is trivial), a globally optimal can be found by iteratively adding to this alignment.

In our analyses we use a slightly modified version of the local alignment algorithm, in which the first gap in a series of multiple gaps receives a higher penalty then the following ones \citep[][use the same modification]{wilkerson2015tracing}. This penalizes many small gaps and makes the algorithm produce longer gaps. The idea behind this modification is that someone who changes text in a bill might insert several words into an existing piece of text. The fact that something was inserted should weigh heavier than the length of the insertion which is achieved by down-weighting gap extensions.

\section{Policy Similarity in US State Legislation}
% What we will provide through the application of the SW algorithm?
Through the application of the SW algorithm to US state legislation, we will provide a quantitative measure of policy similarity between bill sections. We follow \citet{wilkerson2015tracing} in focusing on sections, as bills can contain many separate policy proposals. The similarity measures between sections that we identify can be aggregated up to the bill, legislator or state levels. The measures we provide can be used to test hypotheses regarding, among other topics, public policy diffusion, legislative politics, political parties, and interest groups.

\subsection{Data}
We apply the SW algorithm to a database of US state bills, collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000 bills from 2008 to 2015. Not all bills from all states are available for the whole time period. Figure \ref{fig:bill_desc} displays the year ranges and number of bills in the bill data base. This collection of bills is based on all bills that are available through the \url{openstates.org} API. \url{openstates.org} is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation uses web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bills that are still in the legislative process, or where not enacted. %The database contains the bill text as well as additional information on the legislative process for the bill. We have the first and the last version of the bill text, the sponsor of the bill and all legislative action that was taken on the bill. %The available meta-data for the bills includes a time-stamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.65\textwidth]{figures/year_count_by_state.png}
    \caption{Description of the bill database. The horizontal bars display the time range for which bills are available for each state. The color of the bar indicates how many bills are available for this state.}
    \label{fig:bill_desc}
\end{figure}

Our approach of applying the SW algorithm is similar to \citet{wilkerson2015tracing} but differs in several key respects. The analysis consists of three major steps: 1) Pre processing and selection of documents to compare, 2) alignment computation, 3) post hoc refinement (boiler plate removal).

\subsection{Pre Processing and Selection}

All bills are split up into sections in order to be able to detect all alignments between two bills. Because the SW algorithm only returns the one best alignment between two sequences, relevant information might be lost when considering every bill as one large sequence of words. 
The SW algorithm is computationally demanding and an exhaustive comparison of all possible bill-section-pairs is not feasible (with $500,000$ bills, assuming each bill consists on average of four sections this would amount to about $2 * 10^{12}$ comparisons). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with similar language. We store all available bills in an Elastic Search database. Elastic search is an open source web search engine which is designed to find document that match a search query \citep{gormley2015elasticsearch}. We utilize the `more like this' query, which is designed to find documents that are similar to a given document. It works in the following way: From the focus document, the $k$ $n$-grams with the highest tf-idf scores are selected and transformed into a search vector that is representative of the query document. Then, for each document in the collection, a variation of the cosine similarity is calculated and the $m$ bills with the highest scores are selected for further analysis. For this analysis we set $k$ to 25, $n$ to 5 and $m$ to 100\footnote{This pre-selection potentially introduces selection bias into our later analyses. In order to assess if the 100 closest bills are a sufficiently large number we repeat our analyses for a smaller sub-sample, choosing the 1000 most similar bills. [THESE RESULTS ARE NOT IN YET]}

\subsection{Bill Alignment Computation}

Once the candidate sections are selected, the alignments are calculated for all possible bill-section-dyads, section-pairs from the same bill and section pairs from the same state are excluded. We exclude same-state comparisons in the current analysis since our validation exercises are focused on cross-state comparisons. We refer to the two sections involved in each alignment process as `left' and `right' sections. The algorithm returns parts of the left and right section that are determined to be aligned as well as a score. We refer to these three pieces of information as an alignment.

\clearpage

\begin{table}[ht!]
\centering
\caption{Alignment Examples. Yellow highlighting shows matching sections. Dashes stand for gaps introduced by the alignment algorithm. Non highlighted text are mismatches.}
\label{tab:alignment_examples}
\bgroup
\def\arraystretch{2}
\begin{tabular}{p{0.45\textwidth}|p{0.45\textwidth}|p{0.1\textwidth}}
Left Text & Right Text & Score\\
\hline

\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the} renewable energy property \hl{is placed in service but must be taken in five equal} - \hl{installments beginning with the taxable year in which the} renewable energy property \hl{is placed in service. if, in one of the years in which the installment of a credit accrues, the} renewable energy property \hl{with respect to which the credit was claimed is disposed of}, \hl{taken out of service, or moved out of state, the credit expires and the taxpayer may not take any remaining installment of the credit. the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & \textbf{nc\_2011\_SB747}: "\hl{the entire credit may not be taken for the taxable year in which the} facility - - \hl{is placed in service but must be taken in five equal} annual \hl{installments beginning with the taxable year in which the} facility - - \hl{is placed in service. if, in one of the years in which the installment of a credit accrues,} the facility - - \hl{with respect to which the credit was claimed is disposed} - - - \hl{of} - \hl{or taken out of service, the credit expires and the taxpayer may not take any remaining installment of the credit. the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & $388$ \\

\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the} taxable \hl{year in which the} renewable energy \hl{property is placed in service but must be taken in} five \hl{equal installments} - - - - - \hl{beginning with the taxable year in which the}" & \textbf{ga\_2011\_12\_HB146}: "\hl{the entire credit may not be taken for the} - \hl{year in which the} - - \hl{property is placed in service but must be taken in} four \hl{equal installments} over four successive taxable years \hl{beginning with the taxable year in which the}" & 110 \\

\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the}" renewable energy property is placed in service \hl{but must be taken in five equal installments beginning with the taxable year in which the} & \textbf{nc\_2009\_SB305}: "\hl{the entire credit may not be taken for the taxable year in which the} costs are paid - - - - \hl{but must be taken in five equal installments beginning with the taxable year in which the}" & 108\\
\hline
\end{tabular}
\egroup
\end{table}

\clearpage

From this procedure we obtain ca. 8 million individual alignments (that is, shared text between two sections of two bills) or 1.7 million bill dyads. We use the alignment score as the quantitative measure of policy similarity. However, as we discuss below, due to the presence of extreme outliers, we work with this measure on the log scale. In order to aggregate the alignments to the bill level, we sum the alignment scores for each section pair of the corresponding bill dyad. Table \ref{tab:alignment_examples} displays three examples of section alignments. The `Left Text' and `Right Text' columns display the optimal alignment for the two sections the alignment score is displayed in the `Score' column. This example shows the reuse of legislative text in three states (New Jersey, North Carolina and Georgia).

\subsection{Boiler Plate Removal}

Boiler plate can be procedural language like headers, section titles, common phrases or topic specific phrases such as definitions of legal terms, tax brackets, etc. \citet{wilkerson2015tracing} rely on human coders to identify alignment text that is boiler plate, and then use a machine learning algorithm to extrapolate to all alignments based on the bag-of-words features.
We also rely on an automatic classifier, but we propose a novel approach for generating training data without relying on human coders. We use the fact that boiler plate language is highly repetitive within states. Furthermore, language that is passed several times within the same state is likely to be not substantively relevant. Using these facts allows us to accumulate a large amount of labeled data which we use to train a machine learning classifier to automatically weed out boiler plate from our alignments. In addition to the text itself, we use the position in the text as a feature in the classification task [PUT SOME NUMBERS HERE ONCE THE RESULTS ARE IN].

\section{Evaluation of Validity}

We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence. First, we evaluate whether there is a disproportionately high number of alignments between bills on the same policy area. Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we study the relationship between the ideological distance between the sponsors of bills and the alignment scores between those bills. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect an inverse relationship between these two measures.

\subsection{NCSL Tables}

In our first validation exercise, we consider whether high alignment scores provide a reliable signal of similar policy proposals. To build a ground truth data set in terms of policy proposal, we rely on thematic tables published by the National Council of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}}  We collected a sample of these tables with the following procedure:

\begin{singlespacing}

\begin{enumerate}
    \item Collect all urls returned by the bing search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
    \item Sample 50 urls
    \item Select bills that fulfill these three conditions:
        \begin{enumerate}
            \item The website is a NCSL table
            \item The table refers (at least in part) to legislation introduced in 2011 or later.             \item The table contains less than 100 individual bills. 
        \end{enumerate}
    \item Scrape all information from these tables
\end{enumerate}

\end{singlespacing}

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22 fulfilled the three criteria. From these 22 tables we constructed a dataset of 950 bills, of which we could match 707 to our bill database.

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score in predicting if two bills are in the same NCSL table. We present precision---the proportion of bill pairs with a given alignment score that exceed the threshold on the $x$-axis that are in the same NCSL table, and recall---the proportion of same-NCSL-table pairs that exceed a given alignment score threshold. We see generally high precision---over 80\% with moderate to high alignment scores [X \% of bill-dyad alignment scores fall into this category]. When alignment scores are very high (over 100) we see extremely high precision [X \% of bill-dyad alignment scores fall into this category]. Recall is generally low, but that is expected for our case, as (1) the introduction of similar policies in bills in tow different states is a rare event, and relatedly, (2) the appearance of two bills in the same NCSL table is a rare event [X \% in the current analysis]; and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}. Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.

{\bf Frido, would you take care of these points?}
\begin{itemize}
\item Put the x-axis of Figure 3 on the log scale
\item Increase the font size for the axis and tick labels (note, text in all figures should always be approximately equal to the font size used in the MS).
\item Fill in numbers from above paragraph.
\item One bigger question. I wonder how this analysis would change if the log alignemnt scores were taken at the section level before summing. Logging eliminates outliers in cross-bill comparisons, but doesn't help in establishing bill-specific sections. Section-pair-specific outliers could be throwing this off.
\end{itemize}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ncsl_prec_rec.png}
    \caption{Description of the bill database. The horizontal bars display the time range for which bills are available for each state. The color of the bar indicates how many bills are available for this state.}
    \label{fig:ncsl_prec_rec}
\end{figure}

\subsection{Diffusion networks and Text re-use}

To evaluate whether text re-use corresponds to the transfer of policy, we test whether the presence of a diffusion network tie between two states is a predictor of text reuse. We use the policy diffusion networks inferred in \citet{desmarais2015}. The diffusion networks were inferred using policy adoption sequences, and the network inference algorithm developed by \citet{gomez2010inferring}. A tie from state $i$ to state $j$ in the diffusion network indicates that state $j$ has frequently emulated state $i$'s policies in the preceding thirty-five years. To calculate an aggregate alignment score for each state-pair we calculate the sum of the natural logs of the alignment scores associated with each pair of bills across the two states. We use the log since a handful of large alignment scores lead to extreme outliers on the original scales. The ``Diffusion Ties'' variable indicates the presence of a diffusion edge between states in the 2008 diffusion network, as measured by \citet{desmarais2015}. The diffusion network in 2008 is inferred using policy adoptions in the 35 years preceding (and excluding) 2008.  There is one observation in the analysis for each of the 1,225 unique state-pairs. Since this is dyadic data, we use a matrix permutation method, quadratic assignment procedure, to calculate $p$-values \citep{krackhardt1988}. As a robustness check, we run the model with both the identity and log link.\footnote{The $p$-values were calculated using 5,000 random matrix permutations.}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
 & Coefficient & p-value & Coefficient & p-value \\ 
  \hline
Intercept & -6760712.2229 & 0.0048 & 8.2122 & 0.0000 \\ 
  Diffusion Tie & 498466.2990 & 0.0496 & 0.2683 & 0.0968 \\ 
  Coverage & 2199070.8445 & 0.0000 & 1.4324 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

Results of the dyadic regression are presented in Table \ref{tab:qap.diffusion}. In both specifications there is a positive relationship between the number of diffusion ties and the number of alignments. The relationship is statistically significant at the 0.05 level with the identity link and at the 0.10 level with the log link. Furthermore, the magnitudes of the relationships are substantively significant. With the identity link, the presence of a diffusion tie leads to a 0.25 standard deviation increase in the expected aggregate alignment score.Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.2683)-1\right] = 30.77$}. These results offer further evidence of the validity of quantifying text re-use as a measure of policy similarity, as the aggregate volume of text re-use between states is positively associated with previously-identified diffusion ties between states.

\subsection{Ideological Distance of Aligned Bills}

In the previous two validity tests, we focused mainly on the policy domain aspect of policy similarity, rather than ideological similarity. In the third and final validity test we ask whether we observe a greater volume of text reuse between bills introduced by legislators who are ideologically similar. For calculating ideological distance, we rely on latent ideology scores measured by \citep{shor2011}. The data set contains scores for 20,738 legislators from 50 state legislatures. The \texttt{openstates} API, which we can match to our bills data, contains data and identifiers on $12,000$ legislators. Of these, we where able to uniquely match about $8,000$ legislators to their records in the ideal point data. This allowed us to obtain ideal points for the sponsors of $58\%$ of bills and 1,745,336 ($37\%$) pairs of bills.[{\bf Frido, should these numbers be updated? They seem to be disconnected from the numbers below.}] In order to assess the validity of text reuse as a measure of substantive policy overlap, we expect the quality of the alignments to be inversely correlated to the distance between the bills sponsors' ideal points. The ideal points are located on a common scale across all states, the distance between sponsors from different states is therefore meaningful.

In the following sections we present several analyses to assess this correlation. When we are generating the alignments the bills are split up into sections. We generate an alignment score for a bill dyad by first taking the logarithm and then summing over all section dyads of the bill dyad. The ideal point of the bill is derived from the ideal point of the primary bill sponsor. For bills with several primary sponsors we use the average of those sponsors' ideal points to obtain a single measure. Figure \ref{fig:ideology_quantile_plot} displays the distribution of ideological distance and log-alignment score for the roughly 50 million dyads in the dataset. Each dot is a hexagonal tile, the color of the tile represents the number of dyads in that area. Two major observations can be made in this plot. First, the vast majority of alignment scores are close to zero. Second, the triangular shape of the distribution indicates the high precision - low recall character of the alignment score discussed above: few bills exhibit meaningful policy overlap with other bills, but in the region of lower ideological distance we observe a greater occurrence of positive outliers, which arise from significant policy overlap.

In order to investigate this pattern more closely, we additionally provide lines for quantile regressions in the Figure \ref{fig:ideology_quantile_plot}. Figure \ref{fig:quantile_regression} displays more details about these regression. Figure \ref{fig:ideology_plot} displays the distribution without the quantile regression lines. Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap proposed by \citet{harden2011bootstrap}. We see that there is no relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases---especially above the 90th percentile, we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse asa measure of policy similarity.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads.}
    \label{fig:ideology_plot}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ideology_quantile_plot.png}
    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads. The lines indicate different quantiles of the distribution of alignment scores conditional on the ideological distance. See Figure \ref{fig:quantile_regression} for exact quantiles, coefficients and uncertainty.}
    \label{fig:ideology_quantile_plot}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/quantile_regression.png}
    \caption{Coefficients of quantile regression for alignment score on ideological distance. Dots indicate the point estimate. Horizontal bar represent 95\% confidence intervals obtained via the clustered bootstrap, [using X iterations]. Note that the x-axis is not in a natural scale}
    \label{fig:quantile_regression}
\end{figure}

\clearpage

\section{Conclusion}
Scholarship on public policy and legislative politics relies heavily on measuring the content of legislation, especially with a relative or comparative approach. Manual comparison of bills is prohibitively time consuming when it comes to covering a large proportion of legislation introduced in one or more legislatures. We show that the automated detection of similar text strings in bills provides an effective approach to comparing bill contents. The log alignment scores serve as a highly valid summary measure of the similarity of two bills. We show high validity of this measure in three complimentary tests. First, it correlates with the presence of a diffusion tie inferred from patterns of policy diffusion. Second, it correlates with the ideological similarity between bill sponsors. Third, it exhibits extremely high precision in predicting whether two bills are listed in the NCSL policy area tables. We demonstrate the potential for using this data to test new or unexplored hypotheses on lawmaking in the states by testing whether bill text similarity correlates with campaign contributions to US state legislators.

The log alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time. Where and when do similar policies cross state borders? Which legislators introduce similar legislation? Does lobbying by pressure groups result in the adoption of similar policies across states? Do similar patterns of campaign contributions to legislators predict similar policies in proposed legislation? Questions such as these can be directly investigated using the policy similarity measures we introduce.

A consistent result in our analysis is that the measure of policy similarity based on text reuse is high precision and low recall.  As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments, especially when considering measurements at the bill-level. This can be done through the use of quantile regression, or through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.

\clearpage

\bibliographystyle{chicago}
\bibliography{bibliography}

\clearpage

\section*{Appendix}

\textit{Sketch for a proof that SW alignment is globally optimal}

Notation $F_i$ is the alignment of size $i$ with $i = 1,2,...,(n + k - 1)$. $S(F_i)$ is the score of the alignment.

First show that the score in each cell is optimal:
\begin{enumerate}
\item There are three options for $F_1$ (Gap in $\mathcal{A}$, Gap in $\mathcal{B}$, . This alignment is optimal when $S(F_1)$ is maximized
\item Every alignment's score $S(F_i)$ with $i > 1$ when maximized, is composed of the score of the `one-shorter' alignment $S(F_{i-1})$ and the score of the $i$-th element. If not the score could be increased by choosing a different $F_{i-1}$ that has a higher score.
\item The dp matrix contains all possible alignments. Since every cell is optimal, the highest score in the dp matrix must be globally optimal
\end{enumerate}

\end{document}

### 2016-07-07 analysis/ideology/ideology_quantile_plot.R
changed filepaths for new manuscript folder

@@ -32,7 +32,7 @@ p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) +
     guides(fill=guide_legend(title="Count")) +
     plot_theme
 cat('Saving plot...\n')
-ggsave(plot = p, '../../4344753rddtnd/figures/ideology_plot.png', 
+ggsave(plot = p, '../../manuscript/figures/ideology_plot.png', 
        width = p_width, height = 0.65 * p_width)
 
 p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) + 
@@ -47,5 +47,5 @@ p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) +
     plot_theme
 
 cat('Saving plot...\n')
-ggsave(plot = p, '../../4344753rddtnd/figures/ideology_quantile_plot.png', 
+ggsave(plot = p, '../../manuscript/figures/ideology_quantile_plot.png', 
        width = p_width, height = 0.65 * p_width)

### 2016-07-07 analysis/ideology/ideology_regression.R

@@ -137,5 +137,5 @@ ggplot(pdat) +
     geom_hline(aes(yintercept = 0), linetype = 2, color = "grey") + 
     coord_flip() + ylab("Quantile Regression Coefficient") +
     xlab("Quantile") + plot_theme
-ggsave('../../4344753rddtnd/figures/quantile_regression.png', width = p_width,
+ggsave('../../manuscript/figures/quantile_regression.png', width = p_width,
        height = 0.8 * p_width)

### 2016-07-07 analysis/ncsl/ncsl_analysis.R

@@ -103,7 +103,7 @@ ggplot(df) +
     plot_theme
     
     #facet_wrap(~ type, scales = "free")
-ggsave('../../4344753rddtnd/figures/ncsl_prec_rec.png')
+ggsave('../../manuscript/figures/ncsl_prec_rec.png')
 
 
 # F1 score
@@ -128,4 +128,4 @@ ggplot(df2) +
                    fill = cbPalette[1], color = "white", bins=30) +
     theme_bw() + facet_wrap(~group, ncol=1) + 
     ylab("Proportion") + xlab("Alignment Score")
-ggsave('../../4344753rddtnd/figures/align_distri_ncsl_tables.png')
+ggsave('../../manuscript/figures/align_distri_ncsl_tables.png')

### 2016-07-07 manuscript/main.tex
updated ncsl section

@@
 
-The algorithm is visualized for the example above in Figure \ref{fig:score_matrix}.
-\footnote{An interactive version can be found at [FILL IN URL].}.
+The algorithm is visualized for the example above in Figure
+\ref{fig:score_matrix}\footnote{An interactive version can be found at
+    \url{http://fridolin-linder.com/2016/03/30/local-alignment.html}.}.
 Each row corresponds to a word in the sentence from the Alaska bill and each column to the sentence from the North Carolina bill.
@@
 
-The four values of which the maximum is chosen in Equation \ref{eqn:fill} describe four steps in this dynamic programming array.
-The first value corresponds to a diagonal step which means in the resulting alignment sequence elements $a_i$ and $b_j$ are matched and the score of the alignment is either increased by $\delta$ if they match or decreased by $\epsilon$ if they don't match.
-The second and third value describe a gap step either in horizontal or vertical direction.
-That is, if we move from cell $(i,j)$ to cell $(i+1,j)$, in the resulting alignment sequence element $a_{i+1}$ is matched with a gap.
-On the other hand, if we move to cell $(i, j+1)$ sequence element $b_{j+1}$ is matched with a gap in the resulting alignment.
-If the first three values are all $<= 0$, the score in the cell is 0 meaning that no step is taken and every potential alignment stops at this point.
-This can be observed on the example from above in Figure \ref{fig:score_matrix}.
+The four values of which the maximum is chosen in Equation \ref{eqn:fill}
+describe four steps in this dynamic programming array. The first value
+corresponds to a diagonal step which means in the resulting alignment sequence
+elements $a_i$ and $b_j$ are matched and the score of the alignment is either
+increased by $\delta$ if they match or decreased by $\epsilon$ if they don't
+match. The second and third value describe a gap step either in horizontal or
+vertical direction. That is, if we move from cell $(i,j)$ to cell $(i+1,j)$, in
+the resulting alignment sequence element $a_{i+1}$ is matched with a gap. On the
+other hand, if we move to cell $(i, j+1)$ sequence element $b_{j+1}$ is matched
+with a gap in the resulting alignment. If the first three values are all $<= 0$,
+the score in the cell is 0 meaning that no step is taken and every potential
+alignment stops at this point.
+This can be observed in Figure \ref{fig:score_matrix}.
 The blue path describes the optimal alignment.
@@
 
-The optimal alignment is identified by finding the highest score in the matrix, at which the alignment ends, and back-tracing the path of the alignment.
-The steps in the path are chosen using Equation \ref{eqn:fill}, and are indicated in Figure \ref{fig:score_matrix} by lines pointing to the left, the upper left, up or no line.
-The back-tracing continues until a  zero is encountered.
+The optimal alignment is identified by finding the highest score in the matrix,
+at which the alignment ends, and back-tracing the path of the alignment. The
+steps in the path are chosen using Equation \ref{eqn:fill}, and are indicated in
+Figure \ref{fig:score_matrix} by arrows pointing to the left, the upper left, up
+or no arrow. The back-tracing continues until a  zero is encountered.
 
-This algorithm is computationally intensive ($\mathcal{O}(nk)$ in time and space), but returns the globally optimal local alignment given the scoring parameters.
+This algorithm is computationally intensive ($\mathcal{O}(nk)$ in computation
+time and memory demand), but returns the globally optimal local alignment given the scoring parameters.
 We provide a proof of this in the appendix.
@@
 \subsection{Data}
-We apply the SW algorithm to a database of US state bills, collected by Burgess et al.
-(2015) and the Sunlight foundation.
-This data base contains approximately 500,000 bills from 2008 to 2015.
-Not all bills from all states are available for the whole time period.
-Figure \ref{fig:bill_desc} displays the year ranges and number of bills in the bill data base.
-This collection of bills is based on all bills that are available through the \url{openstates.org} API.
+We apply the SW algorithm to a database of US state bills, collected by
+\citet{burgess2016legislative} and the Sunlight
+Foundation\footnote{\url{http://sunlightfoundation.com/}}. This data base
+contains approximately 500,000 bills from 2008 to 2015. Not all bills from all
+states are available for the whole time period. Figure \ref{fig:bill_desc}
+displays the year ranges and number of bills in the bill data base. This
+collection of bills is based on all bills that are available through the
+Sunlight Foundation's \url{openstates.org} API.
 \url{openstates.org} is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics.
@@
 
-Our approach of applying the SW algorithm is similar to \citet{wilkerson2015tracing} but differs in several key respects.
-The analysis consists of three major steps: 1) Pre processing and selection of documents to compare, 2) alignment computation, 3) post hoc refinement (boiler plate removal).
+Our approach of applying the SW algorithm is similar to
+\citet{wilkerson2015tracing} but differs in several key respects. The analysis
+consists of three major steps: 1) Pre-processing and selection of documents to compare, 2) alignment computation, 3) post hoc refinement (boiler plate removal).
 
@@
 Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc.
-Instead we choose to rely on a procedure that is based on finding bills with similar language.
-We store all available bills in an Elastic Search database.
-Elastic search is an open source web search engine which is designed to find document that match a search query \citep{gormley2015elasticsearch}.
-We utilize the `more like this' query, which is designed to find documents that are similar to a given document.
-It works in the following way: From the focus document, the $k$ $n$-grams with the highest tf-idf scores are selected and transformed into a search vector that is representative of the query document.
-Then, for each document in the collection, a variation of the cosine similarity is calculated and the $m$ bills with the highest scores are selected for further analysis.
-For this analysis we set $k$ to 25, $n$ to 5 and $m$ to 100\footnote{This pre-selection potentially introduces selection bias into our later analyses.
-In order to assess if the 100 closest bills are a sufficiently large number we repeat our analyses for a smaller sub-sample, choosing the 1000 most similar bills.
-[THESE RESULTS ARE NOT IN YET]}
+Instead we choose to rely on a procedure that is based on finding bills with
+similar language. We store all available bills in an Elastic Search database.
+Elastic search is an open source web search engine which is designed to find
+document that match a search query \citep{gormley2015elasticsearch}. We utilize
+the `more like this' query, which is designed to find documents that are similar
+to a given document. It works in the following way: From the focus document, the
+$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
+search vector that is representative of the query document. Then, for each
+document in the collection, a variation of the cosine similarity is calculated
+and the $m$ bills with the highest scores are selected for further analysis. For
+this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
+details on the exact algorithm we refer the reader to the elastic search
+documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
+documentation
+(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
+In order to account for the possibility of selection bias being introduced to
+our analyses through the cap of 1000 similar bills, we analyzed the results with
+different numbers of pre-selected bills. We find that this parameter, when set
+to a sufficiently high value, does not lead to such bias because the set of
+potentially relevant bills is always much smaller than 1000.}
 
@@
 
-From this procedure we obtain ca.
-8 million individual alignments (that is, shared text between two sections of two bills) or 1.7 million bill dyads.
+From this procedure we obtain ca. $10^9$ individual alignments (that is, shared
+text between two sections of two bills) which corresponds to about $2 * 10^6$ bill dyads
+($1.3 * 10^6$ bill dyads excluding within state alignments). Figure
+\ref{fig:alignment_score_distribution} displays the cumulative frequency
+distribution of the alignments. The vast majority of alignments are very small
+(less than 10).
 We use the alignment score as the quantitative measure of policy similarity.
@@
 This example shows the reuse of legislative text in three states (New Jersey, North Carolina and Georgia).
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/alignment_score_distribution.png}
+    \caption{Cumulative frequency distribution of the dyad level alignment
+    scores. The x-axis represents the dyad level alignment score on the
+    $log_{10}$ scale.}
+    \label{fig:alignment_score_distribution}
+\end{figure}
 
@@
 We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
-The web query from step 1 returned 266 urls.
-From the 50 sampled urls 22 fulfilled the three criteria.
-From these 22 tables we constructed a dataset of 950 bills, of which we could match 707 to our bill database.
+The web query from step 1 returned 266 urls. From the 50 sampled urls 22
+fulfilled the three criteria. From these 22 tables we constructed a dataset of
+950 bills, of which we could match 704 to our bill database. For all bill pairs
+that we do not have alignment scores for (i.e. the bills did not get matched by
+the pre-selection algorithm) we assume a score of 0\footnote{If a bill is not selected in the pre-selection step, this means
+that there are basically no matching sequences in this dyad.}.
 
-Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score in predicting if two bills are in the same NCSL table.
-We present precision---the proportion of bill pairs with a given alignment score that exceed the threshold on the $x$-axis that are in the same NCSL table, and recall---the proportion of same-NCSL-table pairs that exceed a given alignment score threshold.
-We see generally high precision---over 80\% with moderate to high alignment scores [X \% of bill-dyad alignment scores fall into this category].
-When alignment scores are very high (over 100) we see extremely high precision [X \% of bill-dyad alignment scores fall into this category].
-Recall is generally low, but that is expected for our case, as (1) the introduction of similar policies in bills in tow different states is a rare event, and relatedly, (2) the appearance of two bills in the same NCSL table is a rare event [X \% in the current analysis]; and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}.
+Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
+in predicting if two bills are in the same NCSL table. We present
+precision---the proportion of bill pairs with a given alignment score that
+exceed the threshold on the $x$-axis that are in the same NCSL table, and
+recall---the proportion of same-NCSL-table pairs that exceed a given alignment
+score threshold. We see generally high precision---over 80\% with moderate
+(higher than 50) to high alignment scores (about 3\% of bill-dyad alignment
+scores fall into this category). When alignment scores are very high (over 100)
+we see extremely high precision (1\% of bill-dyad alignment scores fall into
+this category). Recall is generally low, but that is expected for our case, as
+(1) the introduction of similar policies in bills in tow different states is a
+rare event, and relatedly, (2) the appearance of two bills in the same NCSL
+table is a rare event ($3*10^{-4}$\% in the current analysis); and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}.
 Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.
-
-{\bf Frido, would you take care of these points?}
-\begin{itemize}
-\item Put the x-axis of Figure 3 on the log scale
-\item Increase the font size for the axis and tick labels (note, text in all figures should always be approximately equal to the font size used in the MS).
-\item Fill in numbers from above paragraph.
-\item One bigger question.
-I wonder how this analysis would change if the log alignemnt scores were taken at the section level before summing.
-Logging eliminates outliers in cross-bill comparisons, but doesn't help in establishing bill-specific sections.
-Section-pair-specific outliers could be throwing this off.
-\end{itemize}
 
@@
     \includegraphics[width=0.8\textwidth]{figures/ncsl_prec_rec.png}
-    \caption{Description of the bill database.
-The horizontal bars display the time range for which bills are available for each state.
-The color of the bar indicates how many bills are available for this state.}
+    \caption{Precision-Recall curve for classifying two bills being in the same
+    ncsl table by thresholding the bill-dyad alignment score. The x axis
+displays the threshold, the y axis represents precision and recall. The shaded
+area in the background displays the frequency distribution of the alignment
+scores. Note that the figure does not include alignments with score exactly 0.}
     \label{fig:ncsl_prec_rec}
@@
     \includegraphics[width=0.8\textwidth]{figures/quantile_regression.png}
-    \caption{Coefficients of quantile regression for alignment score on ideological distance.
-Dots indicate the point estimate.
-Horizontal bar represent 95\% confidence intervals obtained via the clustered bootstrap, [using X iterations].
-Note that the x-axis is not in a natural scale}
+    \caption{Coefficients of quantile regression for alignment score on
+    ideological distance. Dots indicate the point estimate. Horizontal bar
+represent 95\% confidence intervals obtained via the clustered bootstrap, [using
+500 iterations]. Note that the x-axis is not in a natural scale}
     \label{fig:quantile_regression}

### 2016-07-07 analysis/ncsl/ncsl_analysis.R

@@ -2,11 +2,17 @@ library(dplyr)
 library(ggplot2)
 library(xtable)
 
-source('../plot_theme.R')
-
 # Load and preprocess data
+# ==============================================================================
+
+# Load ncsl_analysis.RData to skip processing (takes a long time)
+
 alignments <- tbl_df(read.csv('../../data/lid/alignments_1000_b2b_ns.csv',
                               stringsAsFactors = FALSE, header = TRUE))
+
+
+
+
 ncsl_bills <- tbl_df(read.csv('../../data/ncsl/ncsl_data_from_sample_matched.csv',
                               stringsAsFactors = FALSE, header = TRUE)) %>% 
     filter(!is.na(matched_from_db)) %>%
@@ -21,12 +27,6 @@ reverse <- data.frame("left_doc_id" = bill_pairs$right_doc_id,
                       "right_doc_id" = bill_pairs$left_doc_id)
 bill_pairs <- tbl_df(rbind(bill_pairs, reverse))
 
-# Remove pairs from same state
-# incl <- substr(as.character(bill_pairs$left_doc_id), 1, 2) != 
-#     substr(as.character(bill_pairs$right_doc_id), 1, 2)
-# bill_pairs <- bill_pairs[incl, ]
-
-
 # Get 'same-table-indicator'
 ## Join with topic tables
 temp <- mutate(ncsl_bills, left_doc_id = matched_from_db, left_table = topic) %>%
@@ -37,48 +37,61 @@ temp <- mutate(ncsl_bills, right_doc_id = matched_from_db, right_table = topic) 
 df <- left_join(df, temp, by = "right_doc_id") %>% 
     mutate(same_table = ifelse(left_table == right_table, 1, 0))
 
-# Join with alignment data
-## Calculate bill level alignments
-# bill_alignments <- group_by(alignments, left_doc_id, right_doc_id) %>% 
-#     summarize(alignment_score_sum = sum(alignment_score))
-
-
 ## Join
 bill_pairs <- left_join(df, alignments, 
                         by = c("left_doc_id", "right_doc_id"))
-
 df <- mutate(bill_pairs, alignment_score_NA = ifelse(is.na(alignment_score), 
                                                         1, 0))
-eda_tab <- xtabs( ~ same_table + alignment_score_NA, data = df)
-
-sink(file = '../../manuscript/tables/ncsl_crosstab.tex')
[…]

### 2016-07-20 analysis/ncsl/ncsl_analysis.R
Refactored data preprocessing for anlyses
- preprocessing for ideology and ncsl analysis is now done in one script:
- `/etl/make_analysis_datasets.R`
- This script also produces descriptive statistics for the general alignment
  dataset `/etl/alignemtn_descriptives.txt` the ideology dataset
  `/analysis/ideology/??.txt` and the ncsl dataset `/analysis/ncsl/??.txt`
- Resultfiles added to gitignore

@@ -2,92 +2,13 @@ library(dplyr)
 library(ggplot2)
 library(xtable)
 
-# Load and preprocess data
-# ==============================================================================
-
-# Load ncsl_analysis.RData to skip processing (takes a long time)
-
-alignments <- tbl_df(read.csv('../../data/lid/alignments_1000_b2b_ns.csv',
-                              stringsAsFactors = FALSE, header = TRUE))
-
-
-
-
-ncsl_bills <- tbl_df(read.csv('../../data/ncsl/ncsl_data_from_sample_matched.csv',
-                              stringsAsFactors = FALSE, header = TRUE)) %>% 
-    filter(!is.na(matched_from_db)) %>%
-    select(-description, -table) 
-
-
-# Data Frame of all pairs we have table information of (with the matched db ids)
-bill_pairs <- tbl_df(as.data.frame(t(combn(ncsl_bills$matched_from_db, 2))))
-colnames(bill_pairs) <- c("left_doc_id", "right_doc_id") 
-# Also use the reversed combinations
-reverse <- data.frame("left_doc_id" = bill_pairs$right_doc_id,
-                      "right_doc_id" = bill_pairs$left_doc_id)
-bill_pairs <- tbl_df(rbind(bill_pairs, reverse))
-
-# Get 'same-table-indicator'
-## Join with topic tables
-temp <- mutate(ncsl_bills, left_doc_id = matched_from_db, left_table = topic) %>%
-    select(left_doc_id, left_table)
-df <- left_join(bill_pairs, temp, by = "left_doc_id")
-temp <- mutate(ncsl_bills, right_doc_id = matched_from_db, right_table = topic) %>%
-    select(right_doc_id, right_table)
-df <- left_join(df, temp, by = "right_doc_id") %>% 
-    mutate(same_table = ifelse(left_table == right_table, 1, 0))
-
-## Join
-bill_pairs <- left_join(df, alignments, 
-                        by = c("left_doc_id", "right_doc_id"))
-df <- mutate(bill_pairs, alignment_score_NA = ifelse(is.na(alignment_score), 
-                                                        1, 0))
-rm(bill_pairs)
-
-## Put zero for NA alignment score
-df$alignment_score_nona <- ifelse(is.na(df$alignment_score), 0.0001,
-                                          df$alignment_score)
-
-# Numbers for the ncsl section in the paper
[…]

### 2016-07-20 etl/make_analysis_datasets.R

@@ -1,0 +1,208 @@
+library(dplyr)
+library(ggplot2)
+
+args <- commandArgs(trailingOnly = TRUE)
+SMALL <- as.logical(args[1])
+
+# Load Alignments and lucene scores
+cat("Loading alignment data...\n")
+
+if(SMALL) {
+    alignments <- tbl_df(read.csv('../data/lid/alignments_1000_b2b_ns.csv', 
+                         header = TRUE, stringsAsFactors = FALSE, nrows = 50000))
+    lucene_scores <- tbl_df(read.csv('../data/lid/lucene_scores_1000.csv',            #still contains same-state dyads
+                         header = TRUE, stringsAsFactors = FALSE, nrows = 50000))
+} else {
+    alignments <- tbl_df(read.csv('../data/lid/alignments_1000_b2b_ns.csv', 
+                         header = TRUE, stringsAsFactors = FALSE))
+    lucene_scores <- tbl_df(read.csv('../data/lid/lucene_scores_1000.csv', 
+                         header = TRUE, stringsAsFactors = FALSE))
+}
+
+# Merge them and discard lucene
+alignments <- left_join(alignments, lucene_scores, by = c("left_doc_id",
+                                                          "right_doc_id"))
+rm(lucene_scores)
+gc()
+
+# ==============================================================================
+# Descriptive statistics for alignments
+# ==============================================================================
+
+# Descriptive stats for alignment dataset
+sink('alignments_descriptives.txt')
+cat(paste0("Number of bill dyads: ", nrow(alignments), '\n'))
+cat(paste0("Mean score: ", mean(alignments$alignment_score), '\n'))
+cat(paste0("Median score: ", median(alignments$alignment_score), '\n'))
+sink()
+
+# Distribution of alignment scores
+r <- range(alignments$alignment_score)
+thresholds <- exp(seq(log(r[1]), log(r[2]), length.out = 100))
+
+hm <- function(threshold) sum(alignments$alignment_score < threshold) / nrow(alignments)
+cumdist <- sapply(thresholds, hm)
+pdat <- tbl_df(data.frame("Proportion" = cumdist, "Score" = thresholds))
+
+# Load commont theme elements for plots
+source('../analysis/plot_theme.R')
+
+p <- ggplot(pdat) + 
+    geom_line(aes(x = Score, y = Proportion), size = 1.2) + 
+    scale_x_log10(breaks = c(1, 10, 100, 1000, 10000)) + 
+    xlab("X") +
[…]

### 2016-07-20 manuscript/main.tex
new ncsl figure w/o log scale

@@
 text between two sections of two bills) which corresponds to about $2 * 10^6$ bill dyads
-($1.3 * 10^6$ bill dyads excluding within state alignments). Figure
+($1.3 * 10^6$ bill dyads excluding within-state alignments). Figure
 \ref{fig:alignment_score_distribution} displays the cumulative frequency
@@
 \citet{wilkerson2015tracing} rely on human coders to identify alignment text that is boiler plate, and then use a machine learning algorithm to extrapolate to all alignments based on the bag-of-words features.
-We also rely on an automatic classifier, but we propose a novel approach for generating training data without relying on human coders.
-We use the fact that boiler plate language is highly repetitive within states.
-Furthermore, language that is passed several times within the same state is likely to be not substantively relevant.
-Using these facts allows us to accumulate a large amount of labeled data which we use to train a machine learning classifier to automatically weed out boiler plate from our alignments.
-In addition to the text itself, we use the position in the text as a feature in the classification task [PUT SOME NUMBERS HERE ONCE THE RESULTS ARE IN].
+We also rely on an automatic classifier, but we propose a novel approach for
+generating training data without relying on human coders. We use the fact that
+boiler plate language is highly repetitive within-states. Furthermore, language
+that is passed several times within the same state is likely to be not
+substantively relevant. Using these facts allows us to accumulate a large amount
+of labeled data which we use to train a machine learning classifier to
+automatically weed out boiler plate from our alignments. In addition to the text
+itself, we use the position in the text as a feature in the classification task.
 
@@
 However, as the quantile we model increases---especially above the 90th percentile, we see that the relationship grows strong and negative in magnitude, and is statistically significant.
-These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse asa measure of policy similarity.
+These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.
 

### 2016-07-21 manuscript/main.tex
updates to paper

@@
 
-In the previous two validity tests, we focused mainly on the policy domain aspect of policy similarity, rather than ideological similarity.
-In the third and final validity test we ask whether we observe a greater volume of text reuse between bills introduced by legislators who are ideologically similar.
-For calculating ideological distance, we rely on latent ideology scores measured by \citep{shor2011}.
-The data set contains scores for 20,738 legislators from 50 state legislatures.
-The \texttt{openstates} API, which we can match to our bills data, contains data and identifiers on $12,000$ legislators.
-Of these, we where able to uniquely match about $8,000$ legislators to their records in the ideal point data.
-This allowed us to obtain ideal points for the sponsors of $58\%$ of bills and 1,745,336 ($37\%$) pairs of bills.[{\bf Frido, should these numbers be updated?
-They seem to be disconnected from the numbers below.}] In order to assess the validity of text reuse as a measure of substantive policy overlap, we expect the quality of the alignments to be inversely correlated to the distance between the bills sponsors' ideal points.
+In the previous two validity tests, we focused mainly on the policy domain
+aspect of policy similarity, rather than ideological similarity. In the third
+and final validity test we ask whether we observe a greater volume of text reuse
+between bills introduced by legislators who are ideologically similar. For
+calculating ideological distance, we rely on latent ideology scores measured by
+\citep{shor2011}. The data set contains scores for 20,738 legislators from 50
+state legislatures. The \texttt{openstates} API, which we can match to our bills
+data, contains data and identifiers on $12,000$ legislators. Of these, we where
+able to uniquely match about $8,000$ legislators to their records in the ideal
+point data. This allowed us to obtain ideal points for the sponsors of $58\%$ of
+bills and $48*10^6$ ($38\%$) pairs of bills.
+In order to assess the validity of text reuse as a measure of substantive policy overlap, we expect the quality of the alignments to be inversely correlated to the distance between the bills sponsors' ideal points.
 The ideal points are located on a common scale across all states, the distance between sponsors from different states is therefore meaningful.
@@
     \label{fig:ideology_plot}
-\end{figure}
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/ideology_quantile_plot.png}
-    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads.
-The lines indicate different quantiles of the distribution of alignment scores conditional on the ideological distance.
-See Figure \ref{fig:quantile_regression} for exact quantiles, coefficients and uncertainty.}
-    \label{fig:ideology_quantile_plot}
 \end{figure}

### 2016-08-25 manuscript/main.tex
revised boilerplate section

@@
 
-\subsection{Boiler Plate Removal}
+\subsection{Approaches to Adjusting for Boiler Plate Text}
 
-Boiler plate can be procedural language like headers, section titles, common phrases or topic specific phrases such as definitions of legal terms, tax brackets, etc.
-\citet{wilkerson2015tracing} rely on human coders to identify alignment text that is boiler plate, and then use a machine learning algorithm to extrapolate to all alignments based on the bag-of-words features.
-We also rely on an automatic classifier, but we propose a novel approach for
-generating training data without relying on human coders. We use the fact that
-boiler plate language is highly repetitive within-states. Furthermore, language
-that is passed several times within the same state is likely to be not
-substantively relevant. Using these facts allows us to accumulate a large amount
-of labeled data which we use to train a machine learning classifier to
-automatically weed out boiler plate from our alignments. In addition to the text
-itself, we use the position in the text as a feature in the classification task.
+Legislation is full of textual content that is not very useful in identifying the novel policy proposal(s) offered by the bill.
+Such text includes procedural language, headers, section titles, and common phrases such as definitions of legal terms, tax brackets, etc.
+Text that is irrelevant to specific policy proposals represents a major---perhaps the primary---limitation on the capacity for text reuse to identify the emulation of policies across bills.
+\citet{wilkerson2015tracing} use human coders to identify alignment text that is unrelated to policy content.
+They call this text ``boiler plate.'' Given a large set of hand-labeled alignments, they use a machine learning algorithm to classify text as either boiler plate or not based on the textual content of the alignment, and exclude alignments labeled as boiler plate.
+This represents one possible approach, but has two limitations.
+The first is that the use of human coders to label data to train the classifier is costly.
+The second is that the classification and exclusion approach treats legislative text as conforming to a procedural-or-not dichotomy, where language in a bill may be situated on a continuum in terms of the degree to which it is specific to the policy proposal(s) offered in the bill.
+We discuss two alternative approaches to adjusting for boiler plate text in alignments.
+
+The first approach also relies on an automatic classifier, but we propose a novel approach for
+generating training data without relying on human coders. We posit that boiler plate language is highly repetitive within states. Furthermore, language
+that is passed several times (i.e., in separate bills) within the same state is likely to be
+substantively irrelevant.
+Using these facts allows us to accumulate a large amount of labeled data---all alignments between bills that have both passed in the same state---which we use to train a machine learning classifier to exclude boiler plate alignments.
+In addition to the text
+itself, we use the position in the text as a feature in the classifier.
+This approach is very similar to that taken by \citet{wilkerson2015tracing}, except we would not use human coders to label boiler plate alignments.
+
+In the second approach we describe, which we have implemented in one analysis below, we do not exclude boiler plate according to a classification dichotomy.
+Rather, we down-weight common alignments in calculating similarity between bills.
+Alignments are identified at the section level, meaning that we identify up to $n_1 \times n_2$ alignments between two bills, with $n_1$ and $n_2$ being the number of sections in the two bills.
+The similarity score between two bills is calculated as the natural log of the sum of the numeric score associated with each section-pair alignment.
+To adjust for common alignments, we divide the raw alignment score from the SW algorithm by the frequency with which that exact same alignment occurs across the entire database of section-pair alignment.
+In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency–inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results).
+This measure is different and potentially preferable in two ways.
+First, it does not require the use of human coders.
+Second, it places text on a continuum of uniqueness rather than dichotomizes it as boiler plate or not.
 

### 2016-08-26 analysis/ncsl/ncsl_analysis.R
moved ncsl descriptives to analysis script

@@ -55,6 +55,23 @@ align_text <- align_text[order(align_text$count, decreasing = TRUE), ]
 
 head(as.data.frame(align_text))
 
+
+# Distribution stats
+
+# Frequency of scores higher 5 / 10
+sink('ncsl_data_descriptives.txt')
+cat(paste0('Frequency of scores higher than 5: '), 
+    sum(df$score > 6) / nrow(df),
+    '\n')
+cat(paste0('Frequency of scores higher than 7: '), 
+    sum(df$score > 8) / nrow(df),
+    '\n')
+cat(paste0('Proportion in same table: '), 
+    sum(df$same_table) / nrow(df),
+    '\n')
+
+sink()
+
 # Precision recall curve
 # ==============================================================================
 

### 2016-08-26 etl/make_analysis_datasets.R

@@ -219,22 +219,7 @@ df <- filter(bill_pairs, !is.na(score)) %>%
 rm(bill_pairs)
 
 
-cat("Descriptive stats for ncsl\n")
-# ==============================================================================
 
-# Frequency of scores higher 50 / 100
-sink('../analysis/ncsl/ncsl_data_descriptives.txt')
-cat(paste0('Frequency of scores higher than 50: '), 
-    sum(ncsl_alignments$score > 50) / nrow(ncsl_alignments),
-    '\n')
-cat(paste0('Frequency of scores higher than 100: '), 
-    sum(ncsl_alignments$score > 100) / nrow(ncsl_alignments),
-    '\n')
-cat(paste0('Proportion in same table: '), 
-    sum(df$same_table) / nrow(df),
-    '\n')
-
-sink()
 
 # Write out the list of ncsl bill ids (lid format)
 #out_ids <- unique(df$left_doc_id)

### 2016-08-26 etl/boilerplate/alignment_weights.py
sort unique alignments before writing

@@ -6,7 +6,7 @@ from pprint import pprint
 from multiprocessing import Pool
 import numpy as np
 import re
-
+import operator
 
 def add_to_hm(hm, obj):
     if obj in hm:
@@ -143,14 +143,20 @@ if __name__ == "__main__":
     
     # Write out the alignment dictionary
     out_line = '{count}\t{alignment}\n'
+
+    ## Make list of tuples from dict
+    sorted_ualign = sorted(unique_alignments.items(), key=operator.itemgetter(1))
+    
     with io.open(ALIGNFILE, 'w', encoding='utf-8') as outfile:
         outfile.write('count\talignment\n')
-        for ualign in unique_alignments:
+        for t in sorted_ualign:
+            ualign = t[0]
+            count = t[1]
             text = re.sub('[^a-zA-Z0-9 ]', '', ualign)
             if text == '':
                 text = '_'
             o = out_line.format(
                     alignment=text,
-                    count=unique_alignments[ualign])
+                    count=count)
             outfile.write(o)
 

### 2016-08-26 manuscript/main.tex
updated ncsl results in manuscript

@@
 \begin{enumerate}
-    \item Collect all urls returned by the bing search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
+    \item Collect all urls returned by the web search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
     \item Sample 50 urls
@@
 fulfilled the three criteria. From these 22 tables we constructed a dataset of
-950 bills, of which we could match 704 to our bill database. For all bill pairs
-that we do not have alignment scores for (i.e. the bills did not get matched by
-the pre-selection algorithm) we assume a score of 0\footnote{If a bill is not selected in the pre-selection step, this means
-that there are basically no matching sequences in this dyad.}.
+950 bills, of which we could match 704 to our bill database\footnote{We
+    additionally excluded one bill. Indiana 2012 HB1009
+    (\url{www.in.gov/legislative/bills/2012/HE/HE1009.1.html}), which is a
+    very long bill containing technical corrections to a large number of
+    other bills. Due to this fact it contains a large number of sections that
+produce a large outlier alignment when aggregated}. Since this is a
+relatively low number of bills, we then calculate the complete set of pairwise
+alignments for these bills. As described above, we split the
+bills in sections, calculate the pairwise section alignments. This results in
+approximately $10^7$ section-dyads. We then aggregate these section-dyads to the
+bill-dyad level.
+
+For this analysis we additionally employed the boilerplate adjustment strategy
+described above\footnote{We plan to use boiler plate adjustment for all
+    analyses. We are experimenting with the boiler plate removal on this
+    analysis because the smaller size of the data. The final evaluation will be
+    conducted on a held out data set of ncsl tables that is not included in the
+current sample}. Before aggregating the alignments to the bill-dyad level, their
+score is weighted by the inverse frequency of the alignment in the set of all
+alignments for this analysis\footnote{The exact procedure is to compile the
+matching elements of the two aligned sequences to a string that can then be
+matched. This means that mismatches and gaps are ignored, since they would make
+the alignment text unique.}. This results in down-weighting of alignments that occur too often to
+be considered relevant policy language. Table
+\ref{tab:expl_align_freq} displays some example alignments with very high and
+very low frequency. From analysis of these frequencies we find that all alignments
+that occur very frequent are indeed boilerplate. However, there are also still
+many boilerplate alignments that occur infrequently. The currently employed
+approach therefore improves the signal in the alignment score, but could be
+further improved by matching and aggregating not only equal but also similar alignments (e.g. using another alignment
+step or bag-of-words similarity measures).
+
+\begin{table}[]
+\centering
+\caption{Example alignment text of comparable length occurring with high and low frequency.}
+\label{tab:expl_align_freq}
+\begin{tabular}{lll}
+\hline
+Frequency & Matched Alignment Text                           & Rank   \\
+\hline
+1         & to the treasurer of the county in which the      & 1      \\
+1         & shall be for purposes of this                    & 1      \\
+1         & of the higher education act of 1965              & 1      \\
+...       & ...                                              & ...    \\
+7089      & be it enacted by the legislature of the state of & 244747 \\
+19349     & be it enacted by the of the state of             & 244840 \\
+21100     & is amended to read as follows                    & 244847 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 recall---the proportion of same-NCSL-table pairs that exceed a given alignment
-score threshold. We see generally high precision---over 80\% with moderate
-(higher than 50) to high alignment scores (about 3\% of bill-dyad alignment
-scores fall into this category). When alignment scores are very high (over 100)
-we see extremely high precision (1\% of bill-dyad alignment scores fall into
-this category). Recall is generally low, but that is expected for our case, as
+score threshold. We display the results for the alignment scores adjusted for
+boilerplate (left panel) and the unweighted scores (right panel). We see
+moderate to high precision --- 60\% - 100\% with moderate
+(higher than 6) to high alignment scores (about 1\% or 2000 of bill-dyad alignment
+scores fall into this category) for the adjusted scores. The
+threshold-classification using the unweighted scores performs much worse. This
+is due to the fact that some bills with large numbers of section have high
+bill-dyad level alignment scores simply due to the fact that they have many
+boilerplate alignments. These results indicate that down-weighting by inverse
+frequency is a promising direction to take.
+
+Recall is low at thresholds that produce reasonable precision (above 6), but that is expected for our case, as
 (1) the introduction of similar policies in bills in tow different states is a
 rare event, and relatedly, (2) the appearance of two bills in the same NCSL
-table is a rare event ($3*10^{-4}$\% in the current analysis); and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}.
+table is a relatively rare event (8\% in the current analysis); and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}.
 Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.
 
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/ncsl_prec_rec.png}
+\begin{figure}
+\centering     %%% not \center
+\subfigure[Precision recall curve for boilerplate adjusted
+scores]{\label{fig:prec_rec_adj}\includegraphics[width=0.4\textwidth]{figures/ncsl_prec_rec_adj.png}}
+\subfigure[Precision recall curve for unweighted
+scores]{\label{fig:prec_rec_old}\includegraphics[width=0.4\textwidth]{figures/ncsl_prec_rec_old.png}}
 \caption{Precision-Recall curve for classifying two bills being in the same
-    ncsl table by thresholding the bill-dyad alignment score. The x axis
+    ncsl table by thresholding the bill-dyad alignment score.
+The left panel displays the curve for the alignment scores weighted by the inverse frequency of the alignment, the left panel displays the curve for the unweighted scores.
+The x axis
 displays the threshold, the y axis represents precision and recall. The shaded
 area in the background displays the frequency distribution of the alignment
-scores. Note that the figure does not include alignments with score exactly 0.}
+scores.}
 \label{fig:ncsl_prec_rec}
@@
 For bills with several primary sponsors we use the average of those sponsors' ideal points to obtain a single measure.
-Figure \ref{fig:ideology_quantile_plot} displays the distribution of ideological distance and log-alignment score for the roughly 50 million dyads in the dataset.
+Figure \ref{fig:ideology_plot} displays the distribution of ideological distance and log-alignment score for the roughly 50 million dyads in the dataset.
 Each dot is a hexagonal tile, the color of the tile represents the number of dyads in that area.
@@
 
-In order to investigate this pattern more closely, we additionally provide lines for quantile regressions in the Figure \ref{fig:ideology_quantile_plot}.
-Figure \ref{fig:quantile_regression} displays more details about these regression.
-Figure \ref{fig:ideology_plot} displays the distribution without the quantile regression lines.
+In order to investigate this pattern more closely, we additionally calculate
+quantile regressions for the relationship between the alignment score and the
+ideological distance. Figure \ref{fig:quantile_regression} displays the
+coefficients from quantile regressions on a sequence of quantiles from the
+median to the 0.995th quantile.
 Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap proposed by \citet{harden2011bootstrap}.
@@
 
-\begin{figure}[ht!]
+\begin{figure}[ht!]i
     \centering

### 2016-08-28 analysis/ncsl/ncsl_analysis.R
adds regression with clustered bs stderr for ncsl results

@@ -28,6 +28,37 @@ group_by(df, same_table) %>%
               q75 = quantile(old_score, 0.75),
               stdev = sqrt(var(old_score)))
 
+# Clustered bootstrap regression model
+
+## Model
+mod <- lm(score ~ same_table, data = df)
+
+## Uncertainty using the bootstrap
+B <- 1000
+
+clusters <- unique(df$left_doc_id)
+nc <- length(clusters)
+out <- matrix(rep(NA, B * 2), nc = 2, nr = B)
+
+for(i in 1:B) {
+    
+    # Sample clusters and build iteration-dataset
+    sc <- sample(clusters, nc, replace = TRUE)
+    dat <- filter(df, is.element(left_doc_id, sc))
+    
+    # fit models 
+    bs_mod <- lm(score ~ same_table, data = dat)
+    coefs <- coef(bs_mod)
+    out[i, ] <- coefs
+    
+    if(i %% 10 == 0){
+        print(i)
+    }
+}
+
+## Interpret
+
+
 # Difference in means
 t.test(df$score[df$same_table == 0], df$score[df$same_table == 1])
 t.test(df$old_score[df$same_table == 0], df$old_score[df$same_table == 1])

### 2016-08-28 manuscript/main.tex
updated rest of ms
fixed two typos
NSF acknowledgement in manuscript

@@
 \date{\today}
-\author{Fridolin Linder, Bruce Desmarais, Matt Burgess, Eugenia Giraudi}
+\author{Fridolin Linder, Bruce Desmarais, Matthew Burgess, Eugenia
+Giraudy\footnote{This work was supported by National Science Foundation grants
+SES-1558661, SES-1619644, CISE-
+1320219 and DGE-1144860. Any opinions, findings, and conclusions or
+recommendations are those of the
+authors and do not necessarily reflect those of the sponsor.}}
 
@@
 
-\clearpage
+%\clearpage
 

### 2016-09-19 analysis/ideology/ideology_quantile_plot.R
updated analyses with new scores

@@ -35,6 +35,20 @@ cat('Saving plot...\n')
 ggsave(plot = p, '../../manuscript/figures/ideology_plot.png', 
        width = p_width, height = 0.65 * p_width)
 
+
+p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) + 
+    stat_binhex(bins = 150) + 
+    scale_y_log10() + 
+    xlab("Ideological Distance") + 
+    ylab("Alignment Score") + 
+    scale_fill_gradient(low = cbPalette[1], high = cbPalette[2], trans = "log",
+                        labels = function (x) round(x, 0)) +
+    guides(fill=guide_legend(title="Count")) +
+    plot_theme
+cat('Saving plot...\n')
+ggsave(plot = p, '../../manuscript/figures/ideology_plot_log.png', 
+       width = p_width, height = 0.65 * p_width)
+
 p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) + 
     stat_binhex(bins = 300) + 
     stat_quantile(quantiles = quantiles, color = cbPalette[6], 

### 2016-09-19 analysis/ncsl/ncsl_analysis.R

@@ -1,112 +1,38 @@
 library(dplyr)
 library(ggplot2)
 library(xtable)
+library(ROCR)
 
 # Load the data (data preprocessing in `/etl/make_analysis_datasets.R`)
+load('../../data/ncsl_analysis/ncsl_analysis_nosplit.RData')
+df_nosplit <- df
 load('../../data/ncsl_analysis/ncsl_analysis.RData')
+df_cosim <- select(df, -count, -score) %>%
+    mutate(score = cosine_similarity, cosine_similarity = NULL)
 source('../plot_theme.R')
 
 # Descriptives
 # ==============================================================================
 
-# Exclude technical correction bill
-df <- filter(df, score != max(score))
-
-# Summary stats
-# Adjusted score
-group_by(df, same_table) %>% 
-    summarize(mean = mean(score),
-              median = median(score),
-              q25 = quantile(score, 0.25),
-              q75 = quantile(score, 0.75),
-              stdev = sqrt(var(score)))
-# Old score
-group_by(df, same_table) %>% 
-    summarize(mean = mean(old_score),
-              median = median(old_score),
-              q25 = quantile(old_score, 0.25),
-              q75 = quantile(old_score, 0.75),
-              stdev = sqrt(var(old_score)))
-
-# Clustered bootstrap regression model
-
-## Model
-mod <- lm(score ~ same_table, data = df)
-
-## Uncertainty using the bootstrap
-B <- 1000
-
-clusters <- unique(df$left_doc_id)
-nc <- length(clusters)
-out <- matrix(rep(NA, B * 2), nc = 2, nr = B)
-
-for(i in 1:B) {
-    
-    # Sample clusters and build iteration-dataset
-    sc <- sample(clusters, nc, replace = TRUE)
-    dat <- filter(df, is.element(left_doc_id, sc))
-    
-    # fit models 
-    bs_mod <- lm(score ~ same_table, data = dat)
-    coefs <- coef(bs_mod)
-    out[i, ] <- coefs
-    
-    if(i %% 10 == 0){
-        print(i)
-    }
-}
-
-## Interpret
-
-
-# Difference in means
-t.test(df$score[df$same_table == 0], df$score[df$same_table == 1])
-t.test(df$old_score[df$same_table == 0], df$old_score[df$same_table == 1])
-
-# Box Plots
-ggplot(df) +
[…]

### 2016-09-19 etl/alignments/process_ncsl_results.py
a few new etl functions

@@ -26,10 +26,10 @@ if __name__ == "__main__":
 
     # Set parameters
     ## Files
-    FULL_ALIG_FILE = '../../data/alignments_new/ncsl_pair_alignments.json'
-    ALIG_SCORE_FILE = '../../data/alignments_new/ncsl_pair_alignments.csv'
-    ALIG_TEXT_FILE = '../../data/alignments_new/ncsl_align_text.csv' 
-    ADJ_SCORE_FILE = '../../data/alignments_new/ncsl_adjusted.csv'
+    FULL_ALIG_FILE = '../../data/alignments_new/ncsl_pair_alignments_nosplit.json'
+    ALIG_SCORE_FILE = '../../data/alignments_new/ncsl_pair_alignments_nosplit.csv'
+    ALIG_TEXT_FILE = '../../data/alignments_new/ncsl_align_text_nosplit.csv' 
+    ADJ_SCORE_FILE = '../../data/alignments_new/ncsl_adjusted_nosplit.csv'
     
     ## Options
     remove_same_state = False

### 2016-09-19 generate_alignments/ncsl_bill_pairs.py
new ncsl pair scores

@@ -58,6 +58,7 @@ if __name__ == '__main__':
     OUTF = '../data/alignments_new/ncsl_pair_alignments_nosplit.json'
     #OUTF = 'ncsl_pair_alignments.json'
 
+    ## Should bills be split in sections before alignment
     SPLIT=False
      
     # Initialize aligner

### 2016-09-19 analysis/ideology/gen_bs_jobs.py
fixed bug in base quant reg

@@ -10,7 +10,7 @@ N_PROC = 80 # number of processes to start
 N_BS = 1040 # number of bootstrap iterations
 
 n_per_job = int(math.ceil(N_BS / N_PROC)) # number of iterations per job
-print n_per_job
+print(n_per_job)
 
 with io.open('bs_reg_temp.txt', 'r') as infile:
     template = infile.read()
@@ -25,20 +25,21 @@ for n in nos:
     job_file = "bs_job_{}.pbs".format(n)
     with io.open(job_file, 'w') as outfile:
         outfile.write(job)
-    print "Submitted {}".format(n)
+    print("Submitted {}".format(n))
     x = subprocess.check_output(['qsub', job_file]) 
     time.sleep(0.5)
     os.remove(job_file)
 
 
 
-# Base model jobs
-#job = template.format(mode = 'base',
-#                      job_number = 0,
-#                      n_iter = 0)
-#
-#with io.open('base_job.pbs', 'w') as outfile:
-#    outfile.write(job)
-#print "Submitting: \n\n{}\n\n{}\n\n".format(job, "*"*80)
-#x = subprocess.check_output(['qsub', job_file])
-#os.remove('base_job.pbs')
+# Base model job
+job = template.format(mode = 'base',
+                      job_number = 0,
+                      n_iter = 0)
+
+with io.open('base_job.pbs', 'w') as outfile:
+    outfile.write(job)
+
+x = subprocess.check_output(['qsub', 'base_job.pbs'])
+time.sleep(0.5)
+os.remove('base_job.pbs')

### 2016-09-21 manuscript/main.tex
update to paper

@@
 
-\section{Introduction} The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}.
+\section{Introduction}
+
+The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}.
 Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}.
@@
 % What we will provide through the application of the SW algorithm?
-Through the application of the SW algorithm to US state legislation, we will provide a quantitative measure of policy similarity between bill sections.
-We follow \citet{wilkerson2015tracing} in focusing on sections, as bills can contain many separate policy proposals.
-The similarity measures between sections that we identify can be aggregated up to the bill, legislator or state levels.
+Through the application of the SW algorithm to US state legislation, we will
+provide a quantitative measure of policy similarity between bills. The
+similarity measures between bills  that we identify can be aggregated up to the legislator or state levels.
 The measures we provide can be used to test hypotheses regarding, among other topics, public policy diffusion, legislative politics, political parties, and interest groups.
@@
 
-All bills are split up into sections in order to be able to detect all alignments between two bills.
-Because the SW algorithm only returns the one best alignment between two sequences, relevant information might be lost when considering every bill as one large sequence of words.
-The SW algorithm is computationally demanding and an exhaustive comparison of all possible bill-section-pairs is not feasible (with $500,000$ bills, assuming each bill consists on average of four sections this would amount to about $2 * 10^{12}$ comparisons).
+The SW algorithm is computationally demanding and an exhaustive comparison of
+all possible bill-pairs is not feasible (with $500,000$ bills this would amount
+to about $124 * 10^9$ bill pairs).
 \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams.
@@
 
-Once the candidate sections are selected, the alignments are calculated for all possible bill-section-dyads, section-pairs from the same bill and section pairs from the same state are excluded.
+Once the candidate bills are selected, the alignments are calculated for all
+possible bill-dyads, bill pairs from the same state are available but excluded
+for the analyses below.
 We exclude same-state comparisons in the current analysis since our validation exercises are focused on cross-state comparisons.

### 2016-09-21 analysis/diffusion/diffusion_analysis.R
adjusted diffusion analysis script for new data

@@ -4,9 +4,9 @@ state_diffusion_edges <- read.csv("~/dropbox/professional/Research/Active/Diffus
 # subset to 2008 edges
 state_diffusion_edges2008 <- subset(state_diffusion_edges,year==2008)
 
-alignments <- read.csv("~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/diffusion/alignments_1000_s2s.csv",stringsAsFactors=F)
+alignments <- read.csv("../../data/alignments_new/state2state_scores.csv",stringsAsFactors=F)
 
-state_coverage <- read.csv("~/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/diffusion/nbills_by_state.csv",stringsAsFactors=F)
+state_coverage <- read.csv("../../data/lid/nbills_by_state.csv",stringsAsFactors=F)
 
 ustates <- sort(unique(c(alignments$left_state,alignments$right_state)))
 ustates <- ustates[which(!is.element(ustates,c("pr","dc")))]

### 2016-09-22 analysis/ideology/gen_bs_jobs.py
minor changes

@@ -29,13 +29,13 @@ with io.open('bs_reg_temp.txt', 'r') as infile:
 if not BASE:
     print("Generating bootstrap jobs...")
     N_PROC = 80 # number of processes to start
-    N_BS = 1040 # number of bootstrap iterations
+    N_BS = 65 # number of bootstrap iterations
 
     n_per_job = int(math.ceil(N_BS / N_PROC)) # number of iterations per job
     print('{} iterations per job'.format(n_per_job))
 
     # Bootstrap jobs
-    for n in range(N_PROC):
+    for n in range(80, 80 + N_PROC):
         if specific_job is not None:
             if n != specific_job:
                 continue

### 2016-09-22 analysis/ideology/ideology_regression.R

@@ -93,13 +93,17 @@ if(length(args) > 0) {
         load(paste0(res_dir, file))
         op <- sapply(out, function(x) do.call(cbind, x)[2, ])
         outputs[[i]] <- op
+
         i <- i + 1
+        print(paste('Processed', file))
     }
 
     final_out <- do.call(cbind, outputs)
 
     load(paste0(res_dir, "quantreg_mods.RData"))
     base_model_coefs <- sapply(mods, function(x) x[2])
+
+    print(dim(final_out))
 
     out <- list("bootstrap_results" = final_out, "base_model" = base_model_coefs)
     save(out, file = paste0(data_dir, "regression_results.RData"))

### 2016-09-22 manuscript/main.tex
updated paper for nosplit

@@
 \subsection{Detecting Text Reuse}
+\label{sec:d_t_r}
 To assess the maximal similarity of policies proposed in two pieces of legislation, we seek to identify large segments of equivalent or highly similar text (i.e., text reuse between bills).
@@
 Foundation\footnote{\url{http://sunlightfoundation.com/}}. This data base
-contains approximately 500,000 bills from 2008 to 2015. Not all bills from all
+contains approximately 500,000 bills from 2008 to 2015\footnote{Since
+    computation is very demanding for this problem, the results reported in this
+    version of the paper are based on a random sample of about half of the
+    bills. We are in the process of completing the analyses for the whole
+dataset.}. Not all bills from all
 states are available for the whole time period. Figure \ref{fig:bill_desc}
@@
 
-From this procedure we obtain ca. $10^9$ individual alignments (that is, shared
-text between two sections of two bills) which corresponds to about $2 * 10^6$ bill dyads
-($1.3 * 10^6$ bill dyads excluding within-state alignments). Figure
-\ref{fig:alignment_score_distribution} displays the cumulative frequency
+From this procedure we obtain ca. $1.2 * 10^8$ individual alignments (that is, shared
+text between two bills). Figure \ref{fig:alignment_score_distribution} displays the cumulative frequency
 distribution of the alignments. The vast majority of alignments are very small
-(less than 10).
-We use the alignment score as the quantitative measure of policy similarity.
-However, as we discuss below, due to the presence of extreme outliers, we work with this measure on the log scale.
-In order to aggregate the alignments to the bill level, we sum the alignment scores for each section pair of the corresponding bill dyad.
-Table \ref{tab:alignment_examples} displays three examples of section alignments.
+(less than 50).
+Table \ref{tab:alignment_examples} displays three examples of alignments.
 The `Left Text' and `Right Text' columns display the optimal alignment for the two sections the alignment score is displayed in the `Score' column.
@@
 
-In the second approach we describe, which we have implemented in one analysis below, we do not exclude boiler plate according to a classification dichotomy.
-Rather, we down-weight common alignments in calculating similarity between bills.
-Alignments are identified at the section level, meaning that we identify up to $n_1 \times n_2$ alignments between two bills, with $n_1$ and $n_2$ being the number of sections in the two bills.
-The similarity score between two bills is calculated as the natural log of the sum of the numeric score associated with each section-pair alignment.
-To adjust for common alignments, we divide the raw alignment score from the SW algorithm by the frequency with which that exact same alignment occurs across the entire database of section-pair alignment.
+In the second approach we describe, which we have implemented in one analysis
+below, we do not exclude boiler plate according to a classification dichotomy.
+Rather, we down-weight alignments alignments that consist of language that is
+very common to all alignments. The underlying logic is that language that
+appears in a large number of other alignments is probably not related to
+specific policies. For examples alignments consisting of many stop words such as
+`the' or `a' or of common procedural language like `legislature` or `section'
+are most likely part of phrases that are either very frequent in common language
+or very frequent in the legislative context. 
+In order to quantify the similarity to common alignments, we calculate the
+cosine similarity of the bag-of-words vector of each alignment with a random
+sample of 1000 alignments\footnote{We rely on a random sample for computational
+reasons, calculating the complete similarity matrix is computationally
+unfeasible and unnecessary.}. The adjusted score for two bills $Y$ and $Y$ is
+then:
+
+\begin{equation}
+    S^*_{X,Y} = S_{X,Y} \left(1 -
+    \frac{1}{1000}\sum_{i=1}^{1000}\frac{\mathbf{\mathcal{A}_{X,Y}} \bullet
+    {\mathbf{\mathcal{A}_i}}}{\lVert\mathbf{\mathcal{A}_{X,Y}\rVert\lVert\mathbf{\mathcal{A}_i}}\rVert}\right)
+\end{equation}
+
+Where $S_{X,Y}$ is the alignment score as described in Section \ref{sec:d_t_r},
+$\mathbf{\mathcal{A}_j}$ is the bag-of-word vector representation of the
+matching alignment text and $i = 1,\dots,1000$ are the sample alignments.
+
 In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency–inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results).
@@
 
-For this analysis we additionally employed the boilerplate adjustment strategy
-described above\footnote{We plan to use boiler plate adjustment for all
-    analyses. We are experimenting with the boiler plate removal on this
-    analysis because the smaller size of the data. The final evaluation will be
-    conducted on a held out data set of ncsl tables that is not included in the
-current sample}. Before aggregating the alignments to the bill-dyad level, their
-score is weighted by the inverse frequency of the alignment in the set of all
-alignments for this analysis\footnote{The exact procedure is to compile the
-matching elements of the two aligned sequences to a string that can then be
-matched. This means that mismatches and gaps are ignored, since they would make
-the alignment text unique.}. This results in down-weighting of alignments that occur too often to
-be considered relevant policy language. Table
-\ref{tab:expl_align_freq} displays some example alignments with very high and
-very low frequency. From analysis of these frequencies we find that all alignments
-that occur very frequent are indeed boilerplate. However, there are also still
-many boilerplate alignments that occur infrequently. The currently employed
-approach therefore improves the signal in the alignment score, but could be
-further improved by matching and aggregating not only equal but also similar alignments (e.g. using another alignment
-step or bag-of-words similarity measures).
-
-\begin{table}[]
-\centering
-\caption{Example alignment text of comparable length occurring with high and low frequency.}
-\label{tab:expl_align_freq}
-\begin{tabular}{lll}
-\hline
-Frequency & Matched Alignment Text                           & Rank   \\
-\hline
-1         & to the treasurer of the county in which the      & 1      \\
-1         & shall be for purposes of this                    & 1      \\
-1         & of the higher education act of 1965              & 1      \\
-...       & ...                                              & ...    \\
-7089      & be it enacted by the legislature of the state of & 244747 \\
-19349     & be it enacted by the of the state of             & 244840 \\
-21100     & is amended to read as follows                    & 244847 \\
-\hline
-\end{tabular}
-\end{table}
-
 Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
@@
 recall---the proportion of same-NCSL-table pairs that exceed a given alignment
-score threshold. We display the results for the alignment scores adjusted for
-boilerplate (left panel) and the unweighted scores (right panel). We see
-moderate to high precision --- 60\% - 100\% with moderate
-(higher than 6) to high alignment scores (about 1\% or 2000 of bill-dyad alignment
-scores fall into this category) for the adjusted scores. The
-threshold-classification using the unweighted scores performs much worse. This
-is due to the fact that some bills with large numbers of section have high
-bill-dyad level alignment scores simply due to the fact that they have many
-boilerplate alignments. These results indicate that down-weighting by inverse
-frequency is a promising direction to take.
-
-Recall is low at thresholds that produce reasonable precision (above 6), but that is expected for our case, as
+score threshold. We see very high precision when setting the threshold to
+relatively high scores ($>100$). Recall is low at thresholds that produce
+reasonable precision (above 100), but that is expected for our case, as
 (1) the introduction of similar policies in bills in tow different states is a
 rare event, and relatedly, (2) the appearance of two bills in the same NCSL
-table is a relatively rare event (8\% in the current analysis); and classifier recall is notoriously low in rare event data \citep{weiss2000learning}---even commonly approaching zero, as in our case \citep{weiss2004mining}.
-Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.
+table is a relatively rare event (8\% in the current analysis); and classifier
+recall is notoriously low in rare event data \citep{weiss2000learning}---even
+commonly approaching zero, as in our case \citep{weiss2004mining}. Our results
+suggest that the presence of a large alignment score between bills is an
+effective indicator of policy similarity. Futher more, low recall has
 
 \begin{figure}
-\centering     %%% not \center
-\subfigure[Precision recall curve for boilerplate adjusted
-scores]{\label{fig:prec_rec_adj}\includegraphics[width=0.4\textwidth]{figures/ncsl_prec_rec_adj.png}}
-\subfigure[Precision recall curve for unweighted
-scores]{\label{fig:prec_rec_old}\includegraphics[width=0.4\textwidth]{figures/ncsl_prec_rec_old.png}}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/ncsl_pr_nosplit.png}
 \caption{Precision-Recall curve for classifying two bills being in the same
-    ncsl table by thresholding the bill-dyad alignment score.
-The left panel displays the curve for the alignment scores weighted by the inverse frequency of the alignment, the left panel displays the curve for the unweighted scores.
-The x axis
+    ncsl table by thresholding the bill-dyad alignment score. The x axis
 displays the threshold, the y axis represents precision and recall. The shaded
@@
 
+% latex table generated in R 3.2.3 by xtable 1.8-2 package
+% Wed Sep 21 20:12:14 2016
 \begin{table}[ht]
@@
   \hline
-Intercept & -6760712.2229 & 0.0048 & 8.2122 & 0.0000 \\ 
-  Diffusion Tie & 498466.2990 & 0.0496 & 0.2683 & 0.0968 \\ 
-  Coverage & 2199070.8445 & 0.0000 & 1.4324 & 0.0000 \\ 
+Intercept & -33577305.97 & 0.00 & 10.04 & 0.00 \\ 
+  Diffusion Tie & 2423709.31 & 0.05 & 0.27 & 0.10 \\ 
+  Coverage & 10938819.90 & 0.00 & 1.38 & 0.00 \\ 
   \hline
@@
 In the following sections we present several analyses to assess this correlation.
-When we are generating the alignments the bills are split up into sections.
-We generate an alignment score for a bill dyad by first taking the logarithm and then summing over all section dyads of the bill dyad.
 The ideal point of the bill is derived from the ideal point of the primary bill sponsor.
@@
 median to the 0.995th quantile.
-Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap proposed by \citet{harden2011bootstrap}.
-We see that there is no relationship between the ideological similarity of bill sponsors and the median alignment scores between bills.
-However, as the quantile we model increases---especially above the 90th percentile, we see that the relationship grows strong and negative in magnitude, and is statistically significant.
+Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap \citet[see e.g.][]{harden2011bootstrap}.
+Coefficients significant at the 95\% level are displayed in black, insignificant coefficients are grey.
+We see that there is only a very weak relationship between the ideological similarity of bill sponsors and the median alignment scores between bills.
+However, as the quantile we model increases we see that the relationship grows strong and negative in magnitude, and is statistically significant.
 These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.
@@
 represent 95\% confidence intervals obtained via the clustered bootstrap, [using
-500 iterations]. Note that the x-axis is not in a natural scale}
+1200 iterations]. Note that the x-axis is not in a natural scale}
     \label{fig:quantile_regression}

### 2016-09-22 analysis/diffusion/diffusion_analysis.R
fixed path and varname in diffusion

@@ -1,5 +1,5 @@
 # Read in complete dyadic dataset from APSR 
-state_diffusion_edges <- read.csv("~/dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/data/apsr_replication_files/dhb2015apsr-networks.csv",stringsAsFactors=F)
+state_diffusion_edges <- read.csv("../../data/diffusion/dhb2015apsr-networks.csv",stringsAsFactors=F)
 
 # subset to 2008 edges
 state_diffusion_edges2008 <- subset(state_diffusion_edges,year==2008)
@@ -30,7 +30,7 @@ align_amat <- matrix(0,length(ustates),length(ustates))
 # assure the nodes are consistent
 rownames(align_amat) <- colnames(align_amat) <- ustates
 # add in ties
-align_amat[cbind(tolower(alignments$left_state),tolower(alignments$right_state))] <- alignments$sum_log_score
+align_amat[cbind(tolower(alignments$left_state),tolower(alignments$right_state))] <- alignments$sum_score
 # make sure it is undirected
 align_amat <- align_amat + t(align_amat)
 
@@ -63,9 +63,9 @@ colnames(results_log) <- c("Coefficient","p-value")
 ## Prepare results for table
 library(xtable)
 results_all <- cbind(results,results_log)
-xtable(results_all,dig=4)
+xtable(results_all,dig=2)
 
-# boxplots 
+# boxplots
 x <- diff_amat[lower.tri(diff_amat)]
 y <- log(align_amat)[lower.tri(align_amat)]
 

### 2016-09-22 analysis/diffusion/diffusion_analysis.R
one tailed p value in diffusion analysis

@@ -49,21 +49,20 @@ diag(coverage_mat) <- 0
 # Run ols with qap uncertainty
 set.seed(5)
 bivariate_qap <- netlm(align_amat,list(diff_amat,coverage_mat),mode="graph",reps=5000)
-results <- cbind(bivariate_qap$coefficients,bivariate_qap$pgreqabs)
+results <- cbind(bivariate_qap$coefficients,bivariate_qap$pgreq)
 rownames(results) <- c("Intercept","Diffusion Tie","Coverage")
 colnames(results) <- c("Coefficient","p-value")
 
-
 set.seed(5)
 bivariate_qap_log <- netlm(log(align_amat),list(diff_amat,coverage_mat),mode="graph",reps=5000)
-results_log <- cbind(bivariate_qap_log$coefficients,bivariate_qap_log$pgreqabs)
+results_log <- cbind(bivariate_qap_log$coefficients,bivariate_qap_log$pgreq)
 rownames(results_log) <- c("Intercept","Diffusion Tie","Coverage")
 colnames(results_log) <- c("Coefficient","p-value")
 
 ## Prepare results for table
 library(xtable)
 results_all <- cbind(results,results_log)
-xtable(results_all,dig=2)
+xtable(results_all,dig=3)
 
 # boxplots
 x <- diff_amat[lower.tri(diff_amat)]

### 2016-09-23 manuscript/main.tex
updated diffusion results with one tailed test
added wordcount to doc
revising intro

@@
 
+%Words in text: 6036
+%Words in headers: 60
+%Words outside text (captions, etc.): 502
+%Number of headers: 17
+%Number of floats/tables/figures: 8
+%Number of math inlines: 67
+%Number of math displayed: 3
+
 \singlespacing
@@
     \noindent The identification of substantively similar policy proposals in both proposed and adopted legislation is important to scholars of public policy diffusion and legislative politics.
-Conventional, manual, approaches are prohibitively costly in constructing datasets that accurately represent policymaking across policy domains, geographic units, and/or time.
+Conventional, manual, approaches are prohibitively costly in constructing datasets that accurately represent policymaking across policy domains, jurisdictions, or time.
 We propose the use of text-sequencing algorithms, applied to legislative text, to identify bills that introduce similar policy proposals.
@@
 Second, we show that bills classified by the National Council of State Legislatures as covering the same policies exhibit a high degree of text re-use.
-Third, we show that rates of text reuse across state borders correlate strongly with the diffusion networks recently introduced by Desmarais, Harden and Boehmke (2015).
+Third, we show that rates of text reuse across state borders correlate with the diffusion networks recently introduced by Desmarais, Harden and Boehmke (2015).
 
@@
 
-Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles.
+Through the development of an automated text analytic approach to measuring policy similarity, we consider several methodological challenges and broader conceptual hurdles.
 The central methodological puzzles are two-fold.
@@
 Second, we need to develop a method for quantitatively scoring the reused text between bills.
-The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purposes of policy diffusion research.
+The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purposes of public policy policy research.
 Considering precedents in the literature, we argue for conceptualizing policy adoption in terms of a continuum of similarity rather than a dichotomy of equivalence.
@@
   \hline
+Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
+  Diffusion Tie & 2423709.311 & 0.042 & 0.266 & 0.050 \\ 
+    Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
  & Coefficient & p-value & Coefficient & p-value \\ 
-  \hline
-Intercept & -33577305.97 & 0.00 & 10.04 & 0.00 \\ 
-  Diffusion Tie & 2423709.31 & 0.05 & 0.27 & 0.10 \\ 
-  Coverage & 10938819.90 & 0.00 & 1.38 & 0.00 \\ 
-  \hline
 \end{tabular}

### 2016-09-23 manuscript/main.tex
revised methods description and background

@@
 In each of these areas of research, scholars make use of measurements of consistent policy actions across jurisdictions.
-Below we review a variety of methods, and conceptual definitions that researchers have used in measuring consistent policy actions.
+Below we review a variety of methods, and conceptual definitions that researchers have used in identifying similar policy actions.
 
 %%% Mechanics of policy measurement %%% 
+We first consider the levels at which measurement has been conducted in past work.
 Public policy research on cross-jurisdiction comparable policy actions has conventionally involved the manual identification of related policies across states, countries or local governments in one or a handful of policy areas \citep[e.g., ][]{walker1969,berry1990,simmons2004,gilardi2009,krause2011policy}.
-This is a manual approach to measurement at the monadic level.
-In the area of policy diffusion research, recognizing the limitations of monadic levels of measurement, researchers have developed dyadic approaches to studying the diffusion relationships between states \citep{volden2006,boehmke2009}.
+This is a manual approach to measurement at the monadic (i.e., governing jurisdiction) level.
+Recognizing the limitations of monadic levels of measurement, researchers have developed dyadic approaches to studying the diffusion relationships between states \citep{volden2006,boehmke2009}.
 In the most recent iteration of dyadic approaches, \cite{desmarais2015} apply network inference algorithms to US state adoption sequences in over 100 policy domains to empirically infer the underlying network through which policies diffuse.
-In another recent innovation in measurement for policy analysis, \cite{garrett2015} analyze the text of US state legislation to identify the influence of model legislation, as introduced by interest groups.
+In another recent innovation in measurement for policy analysis, \cite{garrett2015} analyze the text of US state legislation through pairwise comparison with model legislation introduced by interest groups to identify the influence of model legislation.
 
@@
 
-Sequences in text that convey equivalent content matter often do not match perfectly.
+Sequences in text that convey similar---even equivalent---policy content often do not match perfectly.
 Formatting, white space, typographical errors, etc.
@@
 Elastic search is an open source web search engine which is designed to find
-document that match a search query \citep{gormley2015elasticsearch}. We utilize
+documents that match a search query \citep{gormley2015elasticsearch}. We utilize
 the `more like this' query, which is designed to find documents that are similar

### 2016-09-23 manuscript/main.tex
updated boilerplate section

@@
 The first is that the use of human coders to label data to train the classifier is costly.
-The second is that the classification and exclusion approach treats legislative text as conforming to a procedural-or-not dichotomy, where language in a bill may be situated on a continuum in terms of the degree to which it is specific to the policy proposal(s) offered in the bill.
+The second is that the classification and exclusion approach treats legislative text as conforming to a procedural-or-not dichotomy, where language in a bill may be situated on a continuum in terms of the degree to which it contributes to the policy proposal(s) offered in the bill.
 We discuss two alternative approaches to adjusting for boiler plate text in alignments.
@@
 
-In the second approach we describe, which we have implemented in one analysis
-below, we do not exclude boiler plate according to a classification dichotomy.
-Rather, we down-weight alignments alignments that consist of language that is
+In the second approach we describe, which we have implemented in the analyses we present below, we do not exclude boiler plate according to a classification dichotomy.
+Rather, we down-weight alignments that consist of language that is
 very common to all alignments. The underlying logic is that language that
 appears in a large number of other alignments is probably not related to
-specific policies. For examples alignments consisting of many stop words such as
+specific policies. For example, alignments consisting of many stop words such as
 `the' or `a' or of common procedural language like `legislature` or `section'
@@
 sample of 1000 alignments\footnote{We rely on a random sample for computational
-reasons, calculating the complete similarity matrix is computationally
-unfeasible and unnecessary.}. The adjusted score for two bills $Y$ and $Y$ is
+reasons. Calculating the complete similarity matrix is computationally
+infeasible and unnecessary.}. The adjusted score for two bills $Y$ and $Y$ is
 then:
@@
 
-In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency–inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results).
+In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency--inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results).
 This measure is different and potentially preferable in two ways.
@@
 
-\section{Evaluation of Validity}
+\section{Empirical Evaluation of Validity}
 
-We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence.
+We use three strategies in order to assess the validity of text reuse as a measure of policy similarity.
 First, we evaluate whether there is a disproportionately high number of alignments between bills on the same policy area.

### 2016-09-23 manuscript/main.tex
updated first two validation sections

@@
 In our first validation exercise, we consider whether high alignment scores provide a reliable signal of similar policy proposals.
-To build a ground truth data set in terms of policy proposal, we rely on thematic tables published by the National Council of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}}  We collected a sample of these tables with the following procedure:
+To build a ground truth data set in terms of similar policy proposals, we rely on thematic tables published by the National Council of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}}  We collected a sample of these tables with the following procedure:
 
@@
             \item The website is a NCSL table
-            \item The table refers (at least in part) to legislation introduced in 2011 or later.             \item The table contains less than 100 individual bills. 
+            \item The table refers (at least in part) to legislation introduced in 2011 or later.          
+             \item The table contains less than 100 individual bills. 
         \end{enumerate}
-    \item Scrape all information from these tables
+    \item Scrape all bills from these tables
 \end{enumerate}
@@
 The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}).
-We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad.
+We additionally constrain the number of bills per table to be below 100, in order to avoid tables that cover very broad topics.
 We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
@@
 suggest that the presence of a large alignment score between bills is an
-effective indicator of policy similarity. Futher more, low recall has
+effective indicator of policy similarity.
 
@@
 Since this is dyadic data, we use a matrix permutation method, quadratic assignment procedure, to calculate $p$-values \citep{krackhardt1988}.
-As a robustness check, we run the model with both the identity and log link.\footnote{The $p$-values were calculated using 5,000 random matrix permutations.}
+As a robustness check, we run the model with both the identity and log link.\footnote{The $p$-values were calculated using 5,000 random matrix permutations.} We also control for a dyadic variable (Coverage) equal to the product of the number of years for which we have data for each state in the dyad.
 
@@
 \end{tabular}
-\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
+\caption{Predicting aggregate cross-state alignment scores with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
 \label{tab:qap.diffusion}
@@
 In both specifications there is a positive relationship between the number of diffusion ties and the number of alignments.
-The relationship is statistically significant at the 0.05 level with the identity link and at the 0.10 level with the log link.
+The relationship is statistically significant at the 0.05 level (one tailed) in each analysis.
 Furthermore, the magnitudes of the relationships are substantively significant.
-With the identity link, the presence of a diffusion tie leads to a 0.25 standard deviation increase in the expected aggregate alignment score.Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.2683)-1\right] = 30.77$}.
+With the identity link, the presence of a diffusion tie leads to a 0.25 standard deviation increase in the expected aggregate alignment score {\bf FRIDO, WOULD YOU VERIFY THE SD NUMBER HERE, OR EVEN JUST STANDARDIZE THE COEFFICIENTS IN THE IDENTITY LINK MODEL BY DIVIDING BY THE SD?}.
+Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.266)-1\right] = 30.47$}.
 These results offer further evidence of the validity of quantifying text re-use as a measure of policy similarity, as the aggregate volume of text re-use between states is positively associated with previously-identified diffusion ties between states.

### 2016-09-23 manuscript/main.tex
finished updating validation sections

@@
 effective indicator of policy similarity.
+{\bf FRIDO, I DON"T SEE ANYTHING ABOUT THE ADDITIONAL COMPARISONS YOU HAVE DONE HERE.
+WE DON'T REALLY PROVIDE THE READER WITH A BASELINE FOR COMPARISON HERE.
+WOULD YOU CALCULATE THE AUCPR OF OUR CLASSIFIER VS A RANDOM CLASSIFIER USING THE PRROC R PACKAGE?
+ALSO ADD THE VALUE USING THE COSINE SIMILARITY}
 
@@
 quantile regressions for the relationship between the alignment score and the
-ideological distance. Figure \ref{fig:quantile_regression} displays the
+ideological distance.
+In a quantile regression, the dependent variable is the value of the predicted quantile of the distribution of the dependent variable conditional on the independent variables (e.g., the predicted median for median regression with the quantile set to 0.50 \citep{harden2011linear}).
+Figure \ref{fig:quantile_regression} displays the
 coefficients from quantile regressions on a sequence of quantiles from the

### 2016-09-23 manuscript/main.tex
expanded conclusion

@@
   \hline
+   & Coefficient & p-value & Coefficient & p-value \\  \hline
 Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
@@
     Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
- & Coefficient & p-value & Coefficient & p-value \\ 
+\hline
 \end{tabular}
@@
 
-The log alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time.
+The alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time.
+In a validation experiment, we show that a wide span of quantiles of alignment scores between bills---from the median up through and above the 99$^{th}$ percentile---are negatively correlated with the ideological distance between the legislators who introduced the two bills.
+This result opens the door to many other hypotheses that could be tested using alignment scores for bill pairs.
 Where and when do similar policies cross state borders?
@@
 
-A consistent result in our analysis is that the measure of policy similarity based on text reuse is high precision and low recall.
-As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments, especially when considering measurements at the bill-level.
-This can be done through the use of quantile regression, or through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.
+The nature of our measure of policy similarity based on text reuse is that it is high precision and low recall.
+As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments when the inquiry requires the identification of bills that introduce equivalent policies.
+For predictive modeling, this can be done through the use of quantile regression at high quantiles.
+For searching out bill pairs, this can be done through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.
 

### 2016-09-27 analysis/diffusion/diffusion_analysis.R
divide diffusion coefs by sd

@@ -49,13 +49,15 @@ diag(coverage_mat) <- 0
 # Run ols with qap uncertainty
 set.seed(5)
 bivariate_qap <- netlm(align_amat,list(diff_amat,coverage_mat),mode="graph",reps=5000)
-results <- cbind(bivariate_qap$coefficients,bivariate_qap$pgreq)
+results <- cbind(bivariate_qap$coefficients / sd(alignments$sum_score),
+                 bivariate_qap$pgreq)
 rownames(results) <- c("Intercept","Diffusion Tie","Coverage")
 colnames(results) <- c("Coefficient","p-value")
 
 set.seed(5)
 bivariate_qap_log <- netlm(log(align_amat),list(diff_amat,coverage_mat),mode="graph",reps=5000)
-results_log <- cbind(bivariate_qap_log$coefficients,bivariate_qap_log$pgreq)
+results_log <- cbind(bivariate_qap_log$coefficients / sd(log(alignments$sum_score)),
+                     bivariate_qap_log$pgreq)
 rownames(results_log) <- c("Intercept","Diffusion Tie","Coverage")
 colnames(results_log) <- c("Coefficient","p-value")
 

### 2016-09-27 analysis/ncsl/ncsl_analysis.R
adds some roc analyses to ncsl

@@ -2,6 +2,8 @@ library(dplyr)
 library(ggplot2)
 library(xtable)
 library(ROCR)
+library(pROC)
+library(doParallel)
 
 # Load the data (data preprocessing in `/etl/make_analysis_datasets.R`)
 load('../../data/ncsl_analysis/ncsl_analysis_nosplit.RData')
@@ -100,28 +102,77 @@ prc_auc <- function(dat, cosim=FALSE) {
 }
 
 # Make plots and get measures for all three scores
-auc_tab <- as.data.frame(matrix(NA, nc = 2, nr = 3))
-colnames(auc_tab) <- c("Score", "AUC")
-auc_tab$Score <- c("Alignment No Split", "Alignment Split", "Cosine Similarity")
+auc_tab <- as.data.frame(matrix(NA, nc = 1, nr = 3))
+rownames(auc_tab) <- c("Random", "Cosine", "Alignment")
+auc_tab[, 2] <- NA
+auc_tab[, 3] <- NA
+colnames(auc_tab) <- c("AUC", "P(X<Random)", "P(X<Cosine)")
 
-## No Split
-out_nosplit <- prc_auc(df_nosplit)
-auc_tab[1, 2] <- out_nosplit$auc
-ggsave(filename = '../../manuscript/figures/ncsl_pr_nosplit.png', 
-       plot = out_nosplit$prp, width = p_width, height = 0.65 * p_width)
-
-## Split
-out_split <- prc_auc(df)
-auc_tab[2, 2] <- out_split$auc
-ggsave(filename = '../../manuscript/figures/ncsl_pr_split.png', 
-       plot = out_split$prp, width = p_width, height = 0.65 * p_width)
+## Random classifier
+score <- runif(nrow(df_nosplit))
+p <- prediction(score, dat$same_table)
+auc_tab[1, 1] <- performance(p, measure = 'auc')@y.values[[1]]
 
 ## Cosine similarity
 out_cosim <- prc_auc(df_cosim, cosim=TRUE)
-auc_tab[3, 2] <- out_cosim$auc
+auc_tab[2, 1] <- out_cosim$auc
 ggsave(filename = '../../manuscript/figures/ncsl_pr_cosm.png', 
        plot = out_cosim$prp, width = p_width, height = 0.65 * p_width)
 
+## Alignment Score
+out_nosplit <- prc_auc(df_nosplit)
+auc_tab[3, 1] <- out_nosplit$auc
[…]

### 2016-09-27 manuscript/main.tex
revisions to paper

@@
 
-\externaldocument{tables/ideology_regressions.tex}
-\externaldocument{tables/ncsl_crosstab.tex}
-\externaldocument{tables/time_diff_reg.tex}
+\externaldocument{tables/ncsl_auc.tex}
 
@@
 
-There are a variety of algorithms designed to automatically detect text reuse between documents mostly originating in the plagiarism detection literature \citep[see e.g.][for an overview]{potthast2013overview}.
-In political science, \citet{wilkerson2015tracing} introduced the Smith-Waterman local alignment algorithm (SW algorithm) to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US Congress.
-We use the same algorithm to detect text reuse in US state bills, however, our implementation of the algorithm differs slightly.
-The SW algorithm was developed by \citet{smith1981identification} in molecular biology, in order to match genetic sequences.
-Given two sequences (of genes or words) it calculates the optimal alignment (match) between these sequences.
+There are a variety of algorithms designed to automatically detect text reuse
+between documents mostly originating in the plagiarism detection literature
+\citep[see e.g.][for an overview]{potthast2013overview}. In political science,
+\citet{wilkerson2015tracing} introduced the Smith-Waterman local alignment
+algorithm (SW algorithm) to detect overlapping language in congressional bills
+in order to trace policy ideas through the legislative process of the US
+Congress. We use the same algorithm to detect text reuse in US state bills,
+however, our implementation of the algorithm differs slightly. The SW algorithm
+was developed by \citet{smith1981identification} in molecular biology, in order
+to match genetic sequences. Given two sequences (of genes or words) it
+calculates the optimal local alignment (match) between these sequences.
 
-Sequences in text that convey similar---even equivalent---policy content often do not match perfectly.
-Formatting, white space, typographical errors, etc.
-would decrease the precision dramatically if only exact matches were used.
-The SW algorithm, therefore, returns the optimal alignment while allowing for mismatches and gaps.
-The extent to which such imperfections are tolerated is governed by parameters that are set by the researcher.
-There are three such parameters: the match score (reward for exactly matching words), the mismatch score (penalty for including words that do not match), and the gap score (penalty for including placeholder words in matching a shorter sequence to a longer sequence).
-The goal of the algorithm is to return the the alignment with the highest score given the input sequences and the parameters.
+Sequences in text that convey similar---even equivalent---policy content often
+do not match perfectly. Formatting, white space, typographical errors, etc.
+would decrease the recall dramatically if only exact matches were used. The SW
+algorithm, therefore, returns the optimal alignment while allowing for
+mismatches and gaps. The extent to which such imperfections are tolerated is
+governed by parameters that are set by the researcher. There are three such
+parameters: the match score (reward for exactly matching words), the mismatch
+score (penalty for including words that do not match), and the gap score
+(penalty for including placeholder words in matching a shorter sequence to a
+longer sequence).
+The goal of the algorithm is to return the alignment with the highest score given the input sequences and the parameters.
 Consider the following two excerpts from Alaska State Bill 203 (28th session) and North Carolina House Bill 366 (2015) respectively:
@@
 
-There is a large number of possibilities of how these sequences could be aligned.
+These sequences could be aligned in a large number of possible ways.
 There is a trade-off between short sequences that match perfectly, and longer sequences with imperfections.
@@
 	\includegraphics[width=1.05\textwidth]{figures/sm.png}
-    \caption{Dynamic programming array of local alignment algorithm.
-The parameters in this instance are: Match Score: 5, Mismatch Score: -2, Gap Score: -1.
-The optimal alignment is displayed on the right side of the matrix.
-The left column corresponds to the text sequence in the rows of the matrix, the right column to the sequence in the columns.
-Mismatches are colored in red, gaps are indicated by "-" and orange color.
-The blue cells in the matrix display the path of the optimal alignment.}
+    \caption{Dynamic programming array of local alignment algorithm. The
+    parameters in this instance are: Match Score: 5, Mismatch Score: -2, Gap
+Score: -1. The optimal alignment is displayed on the right side of the matrix.
+The left column corresponds to the text sequence in the rows of the matrix, the
+right column to the sequence in the columns. Mismatches are colored in red, gaps
+are indicated by "-" and orange color. The highlighted (blue) cells in the matrix display the path of the optimal alignment.}
     \label{fig:score_matrix}
@@
 the score in the cell is 0 meaning that no step is taken and every potential
-alignment stops at this point.
-This can be observed in Figure \ref{fig:score_matrix}.
-The blue path describes the optimal alignment.
+alignment stops at this point. This can be observed in Figure
+\ref{fig:score_matrix}.
+The highlighted (blue) path describes the optimal alignment.
 The first two elements in both sequences don't match, therefore the score remains zero.
@@
 all possible bill-pairs is not feasible (with $500,000$ bills this would amount
-to about $124 * 10^9$ bill pairs).
+to about $1.24 * 10^11$ bill pairs).
 \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams.
@@
 details on the exact algorithm we refer the reader to the elastic search
-documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
+documentation
+(\url{https://www.elastic.co/guide/en/elasticsearch/reference/current/query-dsl-mlt-query.html} as well as the lucene engine
 documentation
@@
 to a sufficiently high value, does not lead to such bias because the set of
-potentially relevant bills is always much smaller than 1000.}
+potentially relevant bills is always much smaller than 1000.}.
 
@@
 Once the candidate bills are selected, the alignments are calculated for all
-possible bill-dyads, bill pairs from the same state are available but excluded
-for the analyses below.
-We exclude same-state comparisons in the current analysis since our validation exercises are focused on cross-state comparisons.
-We refer to the two sections involved in each alignment process as `left' and `right' sections.
-The algorithm returns parts of the left and right section that are determined to be aligned as well as a score.
-We refer to these three pieces of information as an alignment.
+possible bill-dyads. Bill pairs from the same state are available but excluded
+for the analyses below. We exclude same-state comparisons in the current
+analysis since our validation exercises are focused on cross-state comparisons.
+We refer to the two bills involved in each alignment process as `left' and
+`right' bills. The algorithm returns parts of the left and right bills that are determined to be aligned as well as a score. We refer to these three pieces of information as an alignment.
 
@@
 
+%\begin{table}[ht!]
+%\centering
+%\caption{Alignment Examples. Yellow highlighting shows matching sections. Dashes stand for gaps introduced by the alignment algorithm. Non highlighted text are mismatches.}
+%\label{tab:alignment_examples}
+%\bgroup
+%\def\arraystretch{2}
+%\begin{tabular}{p{0.45\textwidth}|p{0.45\textwidth}|p{0.1\textwidth}}
+%Left Text & Right Text & Score\\
+%\hline
+%\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the} renewable energy property \hl{is placed in service but must be taken in five equal} - \hl{installments beginning with the taxable year in which the} renewable energy property \hl{is placed in service.
+if, in one of the years in which the installment of a credit accrues, the} renewable energy property \hl{with respect to which the credit was claimed is disposed of}, \hl{taken out of service, or moved out of state, the credit expires and the taxpayer may not take any remaining installment of the credit.
+the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & \textbf{nc\_2011\_SB747}: "\hl{the entire credit may not be taken for the taxable year in which the} facility - - \hl{is placed in service but must be taken in five equal} annual \hl{installments beginning with the taxable year in which the} facility - - \hl{is placed in service.
+if, in one of the years in which the installment of a credit accrues,} the facility - - \hl{with respect to which the credit was claimed is disposed} - - - \hl{of} - \hl{or taken out of service, the credit expires and the taxpayer may not take any remaining installment of the credit.
+the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & $388$ \\
+%
+%\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the} taxable \hl{year in which the} renewable energy \hl{property is placed in service but must be taken in} five \hl{equal installments} - - - - - \hl{beginning with the taxable year in which the}" & \textbf{ga\_2011\_12\_HB146}: "\hl{the entire credit may not be taken for the} - \hl{year in which the} - - \hl{property is placed in service but must be taken in} four \hl{equal installments} over four successive taxable years \hl{beginning with the taxable year in which the}" & 110 \\
+%
+%\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the}" renewable energy property is placed in service \hl{but must be taken in five equal installments beginning with the taxable year in which the} & \textbf{nc\_2009\_SB305}: "\hl{the entire credit may not be taken for the taxable year in which the} costs are paid - - - - \hl{but must be taken in five equal installments beginning with the taxable year in which the}" & 108\\
+%\hline
+%\end{tabular}
+%\egroup
+%\end{table}
+
 \begin{table}[ht!]
 \centering
-\caption{Alignment Examples. Yellow highlighting shows matching sections. Dashes stand for gaps introduced by the alignment algorithm. Non highlighted text are mismatches.}
+\footnotesize
+\caption{Alignment Examples. Bold (red) text are mismatches. Dashes (orange,
+light text) are  gaps introduced by the alignment algorithm. Non highlighted
+text are matches.}
 \label{tab:alignment_examples}
@@
 \hline
+\textbf{nj\_214\_A1167}: ``the entire credit may not be taken for the taxable
+year in which the \textcolor{red}{\textbf{renewable}} \textcolor{orange}{energy
+property} is placed in service but must be taken in five equal
+\textcolor{orange}{-} installments beginning with the taxable year in which the
+\textcolor{red}{\textbf{renewable}} \textcolor{orange}{energy property} is
+placed in service. if, in one of the years in which the installment of a credit
+accrues, the \textcolor{red}{\textbf{renewable}} \textcolor{orange}{energy
+property} with respect to which the credit was claimed is disposed
+\textcolor{orange}{of, taken out} of \textcolor{orange}{service}, or
+\textcolor{red}{\textbf{moved}} out of \textcolor{red}{\textbf{state,}} the
+credit expires and the taxpayer may not take any remaining installment of the
+credit. the taxpayer may, however, take the portion of an installment that
+accrued in a previous year and was carried forward to the extent permitted
+under'' & \textbf{nc\_2011\_SB747}: ''the entire credit may not be taken for the
+taxable year in which the \textcolor{red}{\textbf{facility}}
+\textcolor{orange}{- -} is placed in service but must be taken in five equal
+\textcolor{orange}{annual} installments beginning with the taxable year in
+which the \textcolor{red}{\textbf{facility}} \textcolor{orange}{- -} is placed
+in service. if, in one of the years in which the installment of a credit
+accrues, the \textcolor{red}{\textbf{facility}} \textcolor{orange}{- -} with
+respect to which the credit was claimed is disposed \textcolor{orange}{- - -} of
+\textcolor{orange}{-} or \textcolor{red}{\textbf{taken}} out of 
+\textcolor{red}{\textbf{service,}} the credit expires and the
+taxpayer may not take any remaining installment of the credit. the taxpayer may,
+however, take the portion of an installment that accrued in a previous year and
+was carried forward to the extent permitted under'' & $388$ \\
 
-\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the} renewable energy property \hl{is placed in service but must be taken in five equal} - \hl{installments beginning with the taxable year in which the} renewable energy property \hl{is placed in service.
-if, in one of the years in which the installment of a credit accrues, the} renewable energy property \hl{with respect to which the credit was claimed is disposed of}, \hl{taken out of service, or moved out of state, the credit expires and the taxpayer may not take any remaining installment of the credit.
-the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & \textbf{nc\_2011\_SB747}: "\hl{the entire credit may not be taken for the taxable year in which the} facility - - \hl{is placed in service but must be taken in five equal} annual \hl{installments beginning with the taxable year in which the} facility - - \hl{is placed in service.
-if, in one of the years in which the installment of a credit accrues,} the facility - - \hl{with respect to which the credit was claimed is disposed} - - - \hl{of} - \hl{or taken out of service, the credit expires and the taxpayer may not take any remaining installment of the credit.
-the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & $388$ \\
+\textbf{nj\_214\_A1167}: ``the entire credit may not be taken for the
+\textcolor{orange}{taxable} year in which the
+\textcolor{orange}{renewable energy} property is placed in service but
+must be taken in \textcolor{red}{\textbf{five}} equal installments
+\textcolor{orange}{- - - - -} beginning with the taxable year in which the'' &
+\textbf{ga\_2011\_12\_HB146}: ``the entire credit may not be taken for the
+\textcolor{orange}{-} year in which the \textcolor{orange}{- -} property is
+placed in service but must be taken in \textcolor{red}{\textbf{four}} equal
+installments \textcolor{orange}{over four successive taxable years}
+beginning with the taxable year in which the'' & 110 \\
 
-\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the} taxable \hl{year in which the} renewable energy \hl{property is placed in service but must be taken in} five \hl{equal installments} - - - - - \hl{beginning with the taxable year in which the}" & \textbf{ga\_2011\_12\_HB146}: "\hl{the entire credit may not be taken for the} - \hl{year in which the} - - \hl{property is placed in service but must be taken in} four \hl{equal installments} over four successive taxable years \hl{beginning with the taxable year in which the}" & 110 \\
-
-\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the}" renewable energy property is placed in service \hl{but must be taken in five equal installments beginning with the taxable year in which the} & \textbf{nc\_2009\_SB305}: "\hl{the entire credit may not be taken for the taxable year in which the} costs are paid - - - - \hl{but must be taken in five equal installments beginning with the taxable year in which the}" & 108\\
+\textbf{nj\_214\_A1167}: ``the entire credit may not be taken for the taxable
+year in which the \textcolor{red}{\textbf{renewable energy property}}
+\textcolor{orange}{is placed in
+service} but must be taken in five equal installments beginning with the
+taxable year in which the'' & \textbf{nc\_2009\_SB305}: ``the entire credit
+may not be taken for the taxable year in which the \textcolor{red}{\textbf{costs
+are paid}} \textcolor{orange}{- - - -}
+but must be taken in five equal installments beginning with the taxable year
+in which the'' & 108\\
 \hline
@@
 
-From this procedure we obtain ca. $1.2 * 10^8$ individual alignments (that is, shared
-text between two bills). Figure \ref{fig:alignment_score_distribution} displays the cumulative frequency
-distribution of the alignments. The vast majority of alignments are very small
-(less than 50).
  Table \ref{tab:alignment_examples} displays three examples of alignments.
@@
 This example shows the reuse of legislative text in three states (New Jersey, North Carolina and Georgia).
+
+For our data we obtain from this procedure ca. $1.2 * 10^8$ individual alignments (that is, shared
+text between two bills). Figure \ref{fig:alignment_score_distribution} displays the cumulative frequency
+distribution of the alignments. The lowest score is $2.3$, the highest $28811$ with a mean
+alignment score of $18.8$ (median $14.9$). From this distribution it is clear that the
+majority of alignments is small with only relatively few bill pairs having
+large alignments. Of the $120$ million bill-pairs about $800,000$ have scores
+larger than $100$ and ca. $44,000$ have scores larger than $1000$.
 
@@
 that is passed several times (i.e., in separate bills) within the same state is likely to be
-substantively irrelevant.
-Using these facts allows us to accumulate a large amount of labeled data---all alignments between bills that have both passed in the same state---which we use to train a machine learning classifier to exclude boiler plate alignments.
-In addition to the text
-itself, we use the position in the text as a feature in the classifier.
-This approach is very similar to that taken by \citet{wilkerson2015tracing}, except we would not use human coders to label boiler plate alignments.
+substantively irrelevant. Using these facts allows us to accumulate a large
+amount of labeled data---all alignments between bills that have both passed in
+the same state---which could be used to train a machine learning classifier to exclude boiler plate alignments. In addition to the text
+itself, the position in the text can be used as a feature in the classifier.
+This approach is very similar to that taken by \citet{wilkerson2015tracing},
+except that no human coders would be required to label boiler plate alignments.
 
@@
 reasons. Calculating the complete similarity matrix is computationally
-infeasible and unnecessary.}. The adjusted score for two bills $Y$ and $Y$ is
+infeasible and unnecessary.}. The adjusted score for two bills $X$ and $Y$ is
 then:
@@
 
-Where $S_{X,Y}$ is the alignment score as described in Section \ref{sec:d_t_r},
-$\mathbf{\mathcal{A}_j}$ is the bag-of-word vector representation of the
-matching alignment text and $i = 1,\dots,1000$ are the sample alignments.
+Where $S_{X,Y}$ is the alignment score, calculated as described in Section \ref{sec:d_t_r},
+$\mathbf{\mathcal{A}_i}$ is the bag-of-word vector representation of the
+matching alignment text where $i = 1,\dots,1000$ are the sample alignments.
 
@@
     \item Sample 50 urls
-    \item Select bills that fulfill these three conditions:
+    \item Select bills that fulfill the following three conditions:
         \begin{enumerate}
@@
 fulfilled the three criteria. From these 22 tables we constructed a dataset of
-950 bills, of which we could match 704 to our bill database\footnote{We
-    additionally excluded one bill. Indiana 2012 HB1009
-    (\url{www.in.gov/legislative/bills/2012/HE/HE1009.1.html}), which is a
-    very long bill containing technical corrections to a large number of
-    other bills. Due to this fact it contains a large number of sections that
-produce a large outlier alignment when aggregated}. Since this is a
+950 bills, of which we could match 704 to our bill database. Since this is a
 relatively low number of bills, we then calculate the complete set of pairwise
-alignments for these bills. As described above, we split the
-bills in sections, calculate the pairwise section alignments. This results in
-approximately $10^7$ section-dyads. We then aggregate these section-dyads to the
-bill-dyad level.
+alignments for these bills. After removing same state bill pairs we obtained ca. $216,000$ alignments.
 
@@
 rare event, and relatedly, (2) the appearance of two bills in the same NCSL
-table is a relatively rare event (8\% in the current analysis); and classifier
+table is a relatively rare event (8\% in the current analysis); classifier
 recall is notoriously low in rare event data \citep{weiss2000learning}---even
-commonly approaching zero, as in our case \citep{weiss2004mining}. Our results
-suggest that the presence of a large alignment score between bills is an
-effective indicator of policy similarity.
-{\bf FRIDO, I DON"T SEE ANYTHING ABOUT THE ADDITIONAL COMPARISONS YOU HAVE DONE HERE.
-WE DON'T REALLY PROVIDE THE READER WITH A BASELINE FOR COMPARISON HERE.
-WOULD YOU CALCULATE THE AUCPR OF OUR CLASSIFIER VS A RANDOM CLASSIFIER USING THE PRROC R PACKAGE?
-ALSO ADD THE VALUE USING THE COSINE SIMILARITY}
+commonly approaching zero, as in our case \citep{weiss2004mining}. Further more,
+using a high precision - low recall classifier in our scenario where the total
+number of bill pairs is extremely large, produces a large number of interesting
+bill pairings in absolute terms.
+
+\input{tables/ncsl_auc.tex}
+
+For a better understanding how the alignment score classification performs in
+comparison to other methods, in Table \ref{tab:ncsl_auc} we report the area under the ROC curve for the
+alignment classifier compared to a classifier based on cosine similarity of bill
+pairs and a random classifier. The first column contains the AUC values for each
+classifier. The remaining two columns display bootstrapped one-tailed p-values for the
+differences between the classifiers.Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.
 
@@
 \end{figure}
+
+%\begin{figure}[t!]
+%    \centering
+%    \begin{subfigure}[b]{0.5\textwidth}
+%        \centering
+%        \includegraphics[height=1.2in]{figures/ncsl_pr_nosplit.png}
+%        \caption{Lorem ipsum}
+%    \end{subfigure}%
+%    ~ 
+%    \begin{subfigure}[b]{0.5\textwidth}
+%        \centering
+%        \includegraphics[height=1.2in]{figures/ncsl_pr_cosim.png}
+%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
+%    \end{subfigure}
+%    \caption{Caption place holder}
+%\end{figure}
 
@@
   \hline
-   & Coefficient & p-value & Coefficient & p-value \\  \hline
-Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
-  Diffusion Tie & 2423709.311 & 0.042 & 0.266 & 0.050 \\ 
-    Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
+    & Coefficient & p-value & Coefficient & p-value \\
+    Intercept & -3.297 & 0.997 & 9.014 & 0.000 \\ 
+    Diffusion Tie & 0.238 & 0.042 & 0.239 & 0.050 \\ 
+    Coverage & 1.074 & 0.000 & 1.238 & 0.000 \\ 
 \hline
 \end{tabular}
-\caption{Predicting aggregate cross-state alignment scores with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
+\caption{Predicting aggregate cross-state alignment scores with diffusion ties.
+Coefficients calculated with OLS regression and normalized with standard
+deviation of cross state alignment scores. $p$-values based on 5,000 QAP permuations.}
 \label{tab:qap.diffusion}
@@
 Furthermore, the magnitudes of the relationships are substantively significant.
-With the identity link, the presence of a diffusion tie leads to a 0.25 standard deviation increase in the expected aggregate alignment score {\bf FRIDO, WOULD YOU VERIFY THE SD NUMBER HERE, OR EVEN JUST STANDARDIZE THE COEFFICIENTS IN THE IDENTITY LINK MODEL BY DIVIDING BY THE SD?}.
+With the identity link, the presence of a diffusion tie leads to a 0.23 standard deviation increase in the expected aggregate alignment score.
 Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.266)-1\right] = 30.47$}.

### 2016-09-28 manuscript/main.tex
Plot updates (ncsl, ideology)
- Ideology plot in greyscale
- Added ideology plot with alignments on log scale
- Added ncsl cosine similarity plot
- Updated ncsl caption with linetypes

@@
 \usepackage{amsfonts}
-\usepackage{subfigure}
+%\usepackage{subfigure}
+\usepackage{subcaption}
 
@@
 
-\begin{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.8\textwidth]{figures/ncsl_pr_nosplit.png}
+%\caption{Precision-Recall curve for classifying two bills being in the same
+%    ncsl table by thresholding the bill-dyad alignment score. The x axis
+%displays the threshold, the y axis represents precision and recall. The shaded
+%area in the background displays the frequency distribution of the alignment
+%scores.}
+%\label{fig:ncsl_prec_rec}
+%\end{figure}
+
+\begin{figure}[ht!]
     \centering
-\includegraphics[width=0.8\textwidth]{figures/ncsl_pr_nosplit.png}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/ncsl_pr_nosplit.png}
+        \caption{Precision-Recall curve for classifier based on alignment scores.}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/ncsl_pr_cosm.png}
+        \caption{Precision-Recall curve for classifier based on cosine similarity.}
+    \end{subfigure}
     \caption{Precision-Recall curve for classifying two bills being in the same
-    ncsl table by thresholding the bill-dyad alignment score. The x axis
+    ncsl table by thresholding the bill-dyad alignment score. The dotted (yellow) line is recall, the solid (black) line is precision. The x axis
 displays the threshold, the y axis represents precision and recall. The shaded
@@
 \end{figure}
-
-%\begin{figure}[t!]
-%    \centering
-%    \begin{subfigure}[b]{0.5\textwidth}
-%        \centering
-%        \includegraphics[height=1.2in]{figures/ncsl_pr_nosplit.png}
-%        \caption{Lorem ipsum}
-%    \end{subfigure}%
-%    ~ 
-%    \begin{subfigure}[b]{0.5\textwidth}
-%        \centering
-%        \includegraphics[height=1.2in]{figures/ncsl_pr_cosim.png}
-%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
-%    \end{subfigure}
-%    \caption{Caption place holder}
-%\end{figure}
 
@@
 
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/ideology_plot.png}
+        \caption{Hexbin plot with alignments on natural scale.}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/ideology_plot_log.png}
+        \caption{Hexbin plot with alignments on $log_{10}$ scale.}
+    \end{subfigure}
+    \caption{Hexbin plot of alignment score and ideological distance of all 50
+    million bill-dyads. The shading of the bins indicates the density of data in
+    the bin.}
+    \label{fig:ideology_plot}
+\end{figure}
+
 In order to investigate this pattern more closely, we additionally calculate
@@
 coefficients from quantile regressions on a sequence of quantiles from the
-median to the 0.995th quantile.
-Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap \citet[see e.g.][]{harden2011bootstrap}.
+median to the 0.995th quantile. Confidence intervals are calculated by
+resampling bills, which represents an implementation of the clustered
+nonparametric bootstrap \citep{harden2011bootstrap}.
 Coefficients significant at the 95\% level are displayed in black, insignificant coefficients are grey.
@@
 
-\begin{figure}[ht!]i
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
-    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads.}
-    \label{fig:ideology_plot}
-\end{figure}
+%\begin{figure}[ht!]i
+%    \centering
+%    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
+%    \caption{Hexbin plot of alignment score and ideological distance of all 50
+%    million bill dyads. The shading of the bins indicates the density of data in
+%the bin.}
+%    \label{fig:ideology_plot}
+%\end{figure}
 
@@
     ideological distance. Dots indicate the point estimate. Horizontal bar
-represent 95\% confidence intervals obtained via the clustered bootstrap, [using
-1200 iterations]. Note that the x-axis is not in a natural scale}
+represent 95\% confidence intervals obtained with clustered bootstrap. 
+Note that the x-axis is not in a natural scale.}
     \label{fig:quantile_regression}

### 2016-09-28 analysis/ideology/ideology_plot.R
updates ideology_plot code

@@ -1,7 +1,5 @@
-library(microbenchmark)
 library(ggplot2)
 library(dplyr)
-library(quantreg)
 library(xtable)
 
 #Plotting parameters
@@ -19,15 +17,14 @@ load("../../data/ideology_analysis/ideology.RData")
 #df <- bak[sample(c(1:nrow(bak)), 1e6), ]
 #df <- bak
 
-## Descriptive scatterplot on sample of points
-quantiles <- c(seq(0.5, 0.9, by = 0.1), seq(0.91, 0.99, by = 0.01), 
-               seq(0.991, 0.995, by =0.001))
+# Descriptive scatterplot on sample of points
 
+## ALignments on natural scale
 p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) + 
-    stat_binhex(bins = 150) + 
+    stat_binhex(bins = 80) + 
     xlab("Ideological Distance") + 
     ylab("Alignment Score") + 
-    scale_fill_gradient(low = cbPalette[1], high = cbPalette[2], trans = "log",
+    scale_fill_gradient(low = "grey60", high = "grey1", trans = "log",
                         labels = function (x) round(x, 0)) +
     guides(fill=guide_legend(title="Count")) +
     plot_theme
@@ -35,16 +32,8 @@ cat('Saving plot...\n')
 ggsave(plot = p, '../../manuscript/figures/ideology_plot.png', 
        width = p_width, height = 0.65 * p_width)
 
-
-p <- ggplot(df, aes(x = ideology_dist, y = alignment_score)) + 
-    stat_binhex(bins = 150) + 
-    scale_y_log10() + 
-    xlab("Ideological Distance") + 
-    ylab("Alignment Score") + 
-    scale_fill_gradient(low = cbPalette[1], high = cbPalette[2], trans = "log",
-                        labels = function (x) round(x, 0)) +
-    guides(fill=guide_legend(title="Count")) +
-    plot_theme
+## Alignments on log scale
+p <- p + scale_y_log10() + ylab("Log Alignment Score")
 cat('Saving plot...\n')
 ggsave(plot = p, '../../manuscript/figures/ideology_plot_log.png', 
        width = p_width, height = 0.65 * p_width)

### 2016-09-28 manuscript/main.tex
more minor revisions

@@
 \citet{burgess2016legislative} and the Sunlight
-Foundation\footnote{\url{http://sunlightfoundation.com/}}. This data base
+Foundation.\footnote{\url{http://sunlightfoundation.com/}} This data base
 contains approximately 500,000 bills from 2008 to 2015\footnote{Since
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{figures/year_count_by_state.png}
+    \includegraphics[width=0.8\textwidth]{figures/year_count_by_state.png}
     \caption{Description of the bill database.
@@
 and the $m$ bills with the highest scores are selected for further analysis. For
-this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
+this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000.\footnote{For
 details on the exact algorithm we refer the reader to the elastic search
@@
 to a sufficiently high value, does not lead to such bias because the set of
-potentially relevant bills is always much smaller than 1000.}.
+potentially relevant bills is always much smaller than 1000.}
 
@@
 cosine similarity of the bag-of-words vector of each alignment with a random
-sample of 1000 alignments\footnote{We rely on a random sample for computational
+sample of 1000 alignments.\footnote{We rely on a random sample for computational
 reasons. Calculating the complete similarity matrix is computationally
-infeasible and unnecessary.}. The adjusted score for two bills $X$ and $Y$ is
+infeasible and unnecessary.} The adjusted score for two bills $X$ and $Y$ is
 then:
@@
 
-Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
-in predicting if two bills are in the same NCSL table. We present
+Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score (left panel)
+in predicting if two bills are in the same NCSL table compared to the performance of a simple cosine similarity measure (right panel). We present
 precision---the proportion of bill pairs with a given alignment score that
@@
 A tie from state $i$ to state $j$ in the diffusion network indicates that state $j$ has frequently emulated state $i$'s policies in the preceding thirty-five years.
-To calculate an aggregate alignment score for each state-pair we calculate the sum of the natural logs of the alignment scores associated with each pair of bills across the two states.
-We use the log since a handful of large alignment scores lead to extreme outliers on the original scales.
+To calculate an aggregate alignment score for each state-pair we calculate the sum of the alignment scores associated with each pair of bills across the two states.
 The ``Diffusion Ties'' variable indicates the presence of a diffusion edge between states in the 2008 diffusion network, as measured by \citet{desmarais2015}.
@@
 Coefficients calculated with OLS regression and normalized with standard
-deviation of cross state alignment scores. $p$-values based on 5,000 QAP permuations.}
+deviation of cross state alignment scores. One-tailed $p$-values based on 5,000 QAP permuations.}
 \label{tab:qap.diffusion}
@@
 With the identity link, the presence of a diffusion tie leads to a 0.23 standard deviation increase in the expected aggregate alignment score.
-Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.266)-1\right] = 30.47$}.
-These results offer further evidence of the validity of quantifying text re-use as a measure of policy similarity, as the aggregate volume of text re-use between states is positively associated with previously-identified diffusion ties between states.
+Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.266)-1\right] = 30.47$.} These results offer further evidence of the validity of quantifying text re-use as a measure of policy similarity, as the aggregate volume of text re-use between states is positively associated with previously-identified diffusion ties between states.
 
@@
 Figure \ref{fig:ideology_plot} displays the distribution of ideological distance and log-alignment score for the roughly 50 million dyads in the dataset.
-Each dot is a hexagonal tile, the color of the tile represents the number of dyads in that area.
+The left panel displays the alignment scores on the natural scale.
+In order to get a better view of the distribution for small alignments, the right panel on the logarithmic scale.
+Each dot is a hexagonal tile, the shading of the tile represents the density in the area of the tile.
 Two major observations can be made in this plot.

### 2016-09-28 manuscript/main.tex
revised proof

@@
 
-\textit{Sketch for a proof that SW alignment is globally optimal}
+\textit{Proof that SW alignment is globally optimal}
 
-Notation $F_i$ is the alignment of size $i$ with $i = 1,2,...,(n + k - 1)$. $S(F_i)$ is the score of the alignment.
+$F_i$ is the alignment of size $i$ with $i = 1,2,...,(n + k - 1)$. $S(F_i)$ is the score of the alignment.
 
-First show that the score in each cell is optimal:
 \begin{enumerate}
-\item There are three options for $F_1$ (Gap in $\mathcal{A}$, Gap in $\mathcal{B}$, . This alignment is optimal when $S(F_1)$ is maximized
+\item There are four options for $F_1$ (Gap in $\mathcal{A}$, Gap in
+    $\mathcal{B}$, Mismatch, Match) . This alignment is optimal when $S(F_1)$ is maximized
 \item Every alignment's score $S(F_i)$ with $i > 1$ when maximized, is composed of the score of the `one-shorter' alignment $S(F_{i-1})$ and the score of the $i$-th element.
 If not the score could be increased by choosing a different $F_{i-1}$ that has a higher score.
-\item The dp matrix contains all possible alignments. Since every cell is optimal, the highest score in the dp matrix must be globally optimal
+\item By induction therefore follows that every alignment represented in the
+    dynamic programming matrix (\ref{fig:score_matrix}) and calculated according
+        to Equations \ref{eqn:scoring} and \ref{eqn:fill} is an optimal alignment
+    ending in the locations specified by the row and column index in the matrix.
+\item The dynamic programming matrix contains all possible alignments. Since
+    every cell is optimal, the highest score in the matrix must be globally
+    optimal.
 \end{enumerate}

### 2016-09-28 manuscript/main.tex
typo in manuscript

@@
 all possible bill-pairs is not feasible (with $500,000$ bills this would amount
-to about $1.24 * 10^11$ bill pairs).
+to about $1.24 * 10^{11}$ bill pairs).
 \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams.

### 2016-10-01 manuscript/main.tex
typo in manuscript
reformatted bibliography

@@
 represent 95\% confidence intervals obtained with clustered bootstrap. 
-Note that the x-axis is not in a natural scale.}
+Note that the y-axis is not in a natural scale.}
     \label{fig:quantile_regression}
@@
 
-\bibliographystyle{chicago}
+\bibliographystyle{authoryear1}
 \bibliography{bibliography}
@@
 \item By induction therefore follows that every alignment represented in the
-    dynamic programming matrix (\ref{fig:score_matrix}) and calculated according
+    dynamic programming matrix (Figure \ref{fig:score_matrix}) and calculated according
         to Equations \ref{eqn:scoring} and \ref{eqn:fill} is an optimal alignment

### 2017-02-06 manuscript/ajps/reviews_response.md
adds ajps reviews and response

### Reviewer 1.

*Stronger conceptualization of influence through text reuse required*

We should add a more thorough discussion of what text reuse might mean in our context. This also relates to point 3 that the reviewer makes. We could add a more theoretical discussion of different situations from which text reuse might arise (common source, direct influence, chance, formal boiler plate, substantive boiler plate), and discuss effects for our measure

*Does text reuse indicate a continuous or a binary concept (“influence”)*

Maybe add a paragraph discussing this more explicitly. A binary concept still requires a decision for a threshold that maps the continuous score to the binary concept. Discuss that conceptualizing as continuous does not preclude binarizing but should rather be done by researchers using the scores.

*Issues about comparability of text are not addressed*

See 1.

*Arbitrary choice of SW parameters and pre selection parameters*

Easy solution: Refer to the KDD paper where parameters are tuned using the ground truth dataset. Or do separate validation. What objective could we use? One from the validation exercises?

*Expand weighting of alignemnts (discuss approaches other than tf-idf, e.g word2vec)*

Maybe just add a footnote that there are other options to interpret the substantive relevance of a piece of text. This could also be connected to the discussion mentioned in 1. I’m not sure why exactly he brings up word2vec. Embeddigns could be used in a supervised approach to downweight language that is close (in the embedding space) to a set of known boiler plate or irrelevant language.

*Too little information on the NCSL data as validation dataset, how are bills selected by ncsl, variation between tables, etc.*

For now we randomly sample the tables. We discussed previously that we could hand select tables that are of high quality (high similarity between bills). Reviewer makes a good point that there is a lot of variation between the tables in terms of inclusivity.

*Dynamic implementation section in SW algo description is hard to follow*

Revise (see also Reviewer 2)

*Optimal alignment next to the visualization is confusing*

Easy fix

*Scores in SW figure don’t match scores in text*

Easy fix

### Reviewer 2.

*Language is too jargony and paper is hard to follow for not technical audience*

Revise and more explicitly introduce jargon

*No reference to other political science literature using text as data*

Add in some citations, when introducing the algorighm

*Validation studies ‘do not bring any additional knowledge’ (in terms of substantive political science). Method should be applied to data in other areas*

I don’t think we should follow this advice. The point of a validation study is to assess the quality of a measurement not to generate new substantive insights.

### Full reviews

Reviewer #2: The paper proposes a modified measurement tool to study similarities between legislative texts in the US politics field (state legislatures), based on text-sequencing algorithms. The authors conduct several validity tests to confirm that ideologically similar bill sponsors reveal a high degree of text reuse, that bills that cover similar policies also reveal text reuse, and that text reuse correlate with the diffusion networks. I think that by and large, an informed reader is able to follow the explanation of the method, the structure is clear - it is a good paper overall.

I do not consider myself a methodologist as such; therefore I will comment from the point of view as a possible user of such a method in other substantive areas. Does the paper do enough scholarly contribution to the discipline to be accepted to the premier journal in political science?

Even though an informed reader familiar with the text analytics will be able to follow the analyses presented, since the submission is t AJPS as opposed to Pol Analysis, I think the authors need to revise it to a considerable degree so that a general political science practitioner interested in applying such methods in his or research will be able to follow. At the very least, the authors need to address and revise frequent methods-related jargon, e.g., "boiler plate removal" encountered in text. I am not sure an average reader of AJPS is familiar with it. I was also surprised that the authors omit several important references to applied text analytics in political science, such as those of Laver, Benoit, Garry 2003, Slapin and Proksch; Lowe; Grimmer, etc (I am not one of these authors and am not related to them, only think it is important to relate to the growing literature on political text so that this paper does not look like a niche paper but as a part of a growing
research program instead).

After reading the paper my overall impression is that it will be very suitable for a special volume on political text, or perhaps for a more specialized journal such as State Politics & Policy Quarterly. As it stands, I think it requires very considerable revisions to be considered for publication in AJPS.

The authors do not introduce any new data - they rely on the existing dataset. They do not offer a new theory that explains the logic behind the re-use of legislative bills, whether based on interest groups literature or the diffusion literature, for example. As such, it is a measurement paper. The SW text re-use algorithm has been previously employed in Political Science in Wilkerson et al (2015), as the authors themselves acknowledge. The authors here re-use the same algorithm, with slight modifications to improve it.  On p. 11 they underline that "In our analyses we use a slightly modified version of the local alignment algorithm, in which the first gap in a series of multiple gaps receives a higher penalty then the following ones (Wilkerson et al., 2015, use the same modification)." "The idea behind this modification is that someone who changes text in a bill might insert several words into an existing piece of text."

Following the estimations of text re-use, the authors report three validation exercises to demonstrate that the texts that they find to be similar based on their analyses are in fact (expected to be) similar, based on other analyses, such as from the ideological distances of bill sponsors. The validation exercises do not bring any additional knowledge since it is expected that ideologically similar bill sponsors will reveal a high degree of text reuse, that bills that cover similar policies will reveal text reuse also. Even though such external validation is important, it does not tell me however, as a possible user of such method, as to the value of the method in my own applied work.

In my humble opinion, the authors can follow two possible avenues. First, if they frame it as mainly a methods paper as they do now, they need to demonstrate the usage of their methods in at least two empirical applications at the back of the paper --- not external validity tests but applications, preferably in different fields and using different text corpora, e.g., one in US politics and another in IR or in European politics. For example, they could take an existing study of policy-making in the US and reveal how their method can be employed by other scholars working in the same area; they can also take the data from the UK parliament or EU parliament and equally apply the text reuse method, to a different corpus however. As it stands, the authors only suggest that the method could be useful, but they do not demonstrate the applications.

The second possibility of course is to reframe the paper altogether by explaining a substantive puzzle in US politics field, using the method to address that puzzle. On p. 26 they suggest several possible applications. The validation analyses can be trimmed or placed into the supplementary materials. Because this paper only improves on the method that is already introduced to the literature, I think the authors could make it into a much more "substantive" piece that still relies on the same method but also explains factors behind the likelihood of text re-use in state legislatures, again possibly utilizing several avenues suggested on p. 26. For example, the paper by Wilkerson et al. 2015 --- that introduced the method to political science --- has a substantive focus on how policy ideas relate to the legislative history of various pieces of legislation, with several examples and illustrations. This paper could be revised along similar lines, with a substantive focus. But I
think the first possibility --- 2 empirical applications to demonstrate the applicability - would require less effort and fewer revisions.

Reviewer #1: As I read it, this manuscript makes three primary contributions. First, the manuscript provides a conceptualization of "policy similarity," and argues that text re-use is related to that conceptual viewpoint. Second, the manuscript provides a description of Smith-Waterman Algorithm (SWAlign), and offers advice and variants on the basic algorithm for potential users. Third, the manuscript provides a series of ground-truth validity tests of the procedure.

Overall, this article makes a noteworthy contribution to the text-as-data literature. Text re-use analyses are becoming increasingly popular throughout political science, and this article advances the state of the literature on these methods. I have some concerns regarding the framing of the article as well as some more specific methodological critiques, but overall I think this is a worthwhile article.

First, in Section 3, I'm convinced that text re-use is an important, politically significant phenomenon, but I'd like a stronger case to be made for the specific conceptual frame used in the paper. Text re-use might indicate policy similarity, or it might indicate a hazier influence relationship of the sort you use in your third section (e.g. through shared drafting norms or databases). The authors should make a stronger case for their preferred conceptualization (e.g. how and why we might know that their particular conceptualization is the right one).

Some further questions on this point:
 - Do we really believe that the measure proposed in this paper is interval-level interpretable? The probability of a long string of text being replicated verbatim or near-verbatim by chance is approximately zero, so we could instead treat similarity scores over a certain threshold as evidence that the authors of a given text were "influenced" by reading a second text. If the latent concept of interest is "policy similarity" (however defined), then presumably we care about more than the simple text on the page. At minimum, we care about implementation, and the relationship between text and implementation is not addressed in this paper. The authors might consider re-framing their notion of policy similarity as "formal similarity," or some similar term.

 - If we do want to treat policy similarity as an interval-level concept, do we really believe that we can compare blocks of text directly? Some pieces of text are surely more influential than others, and the authors should at least address the issue of text comparability. The discussion of "boilerplate" text addresses this point implicitly, but problems with comparability of text chunks should be made explicit.

Second, in Sections 4-5, parameter setting decisions throughout the paper are not clearly justified. Is there any reason why we might favor a particular gap/mismatch penalization scheme in SWAlign, or the particular search scheme as articulated the last paragraph in Section 4.2? If parameter setting is essentially arbitrary, are there any opportunities for parameter optimization (e.g. cross-validation against some ground-truth objective), or existing values in the literature?

Third, the discussion of TF-IDF weighting to identify boilerplate text is interesting and novel, and I would like to see it expanded further. Other weighting schemes or boilerplate adjustment mechanisms should be discussed (e.g. using word2vec embeddings to classify boilerplate language). The reason for selecting TF-IDF weights in particular should be described in more detail.

Fourth, I'd like a clearer justification for the choice of the NCSL classification task as a validity exercise. Relatively little detail is given in the paper about methodology that the NCSL used to build their tables and identify comparable documents, the underlying level of variation in the NCSL tables, or similar concerns.

Finally, some smaller notes:
- The discussion of SWAlign is generally good, but the description of the dynamic implementation is somewhat tough to follow.

- In Figure 1, placing the optimal alignment alongside the table is confusing, and suggests that the terms match the axes in the figure.

- Scores inside cells in Figure 1 do not appear to match the parameter values and scores given in text.

### 2017-02-06 manuscript/ajps/submission/make_diff.sh
started revising to address reviews

@@ -1,0 +1,22 @@
+# Compiled diff between two versions of a latex document
+# Arguments:
+#  1: filename
+#  2: commit id
+
+cp $1 backup
+cp $1 temp
+git checkout $2 $1
+latexdiff $1 temp > diff.tex
+pdflatex diff.tex
+bibtex diff
+pdflatex diff.tex
+pdflatex diff.tex
+
+git checkout HEAD $1
+rm temp
+rm diff.aux
+rm diff.log
+rm diff.out
+rm diff.tex
+rm diff.bbl
+rm diff.blg

### 2017-02-07 manuscript/ajps/reviews_response.md
started revising to address reviews
addressed dichotomy point

@@
 
+[Addressed] First, regarding the enactment vs implementation issue, I noted that policy implementation differs from policy enactment through legislation, citing lit on bureaucratic discretion.
+Second, regarding dichotomization, I recognized in the evaluation section that we use interval level scores, but discuss the possibility of dichotomization in the conclusion.
+
  - If we do want to treat policy similarity as an interval-level concept, do we really believe that we can compare blocks of text directly?

### 2017-02-07 manuscript/main.tex
addressed dichotomy point

@@
 Rather, text re-use serves as a summary measure of the greatest overlap observed across all relevant policy dimensions represented in legislative text.
+Furthermore, we note that by focusing on legislative text, we are measuring the similarity of the intended policies in terms of how those policies reflect in formal enacting legislation.
+Once enacted, the policies that are implemented in different states, under different bureaucratic and judicial regimes, will likely differ even if hey are enacted under equivalent legislative language.
+This divergence in policy implementation is attributable to the inevitable discretion exercised by bureaucratic officials in implementing policy \citep{weingast1983bureaucratic,scott1997assessing,gerber2005state}.
 
@@
 If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect an inverse relationship between these two measures.
+In the validation experiments that follow, we make use of the quantitative, interval level, alignment scores to construct continuous measures of policy similarity.
+We do this to impose as little information reduction as possible.
+In the conclusion we discuss the possibility of thresholding these scores in order to classify bill pairs as either containing or not containing matching policy content.
 
@@
 For searching out bill pairs, this can be done through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.
+Such thresholding may discard informative variation on policy similarity in terms of bill pairs that exhibit borderline overlap when it comes to containing equivalent policy content.
+On the other hand, high-score thresholding would focus the analysis on bill pairs that reliably contain very similar policy enactments, and pose little risk of a false positive.
 
@@
 
-\bibliographystyle{authoryear1}
+%\bibliographystyle{authoryear1} (frido, did you add this? where's the stylefile?)
+\bibliographystyle{apsr}
 \bibliography{bibliography}

### 2017-02-07 manuscript/ajps/reviews_response.md
addressed point about concept of policy similarity and text reuse

@@
 
+[Addressed] Thanks
+
 First, in Section 3, I'm convinced that text re-use is an important, politically significant phenomenon, but I'd like a stronger case to be made for the specific conceptual frame used in the paper.
@@
 how and why we might know that their particular conceptualization is the right one).
+
+[Adressed] I added a paragraph to our section, "detecting policy similarity through text reuse," to note that we are not the first to propose that text reuse can be used to measure policy similarity.
+In doing this I characterized model legislation and issue evolution as special cases of broader policy similarity, which we are measuring.
 
@@
 The discussion of "boilerplate" text addresses this point implicitly, but problems with comparability of text chunks should be made explicit.
+
+[Addressed] This comment is fairly unclear. I don't think it is worth addressing at this point.
 

### 2017-02-07 manuscript/main.tex
addressed point about concept of policy similarity and text reuse

@@
 This divergence in policy implementation is attributable to the inevitable discretion exercised by bureaucratic officials in implementing policy \citep{weingast1983bureaucratic,scott1997assessing,gerber2005state}.
+
+We should emphasize at this point that we are not the first contributors to the legislative politics, or even state legislative politics, literature to use text similarity between bills to measure policy similarity.
+\citet{wilkerson2015tracing} use text similarity---indeed, the same algorithm we use---to trace the development of very similar policy proposals in legislation produced in the US Congress.
+\cite{garrett2015} and \cite{burgess2016legislative} both use measures of text similarity in US state legislation to identify bills that incorporate similar forms of model legislation, as provided by legislative/policy advocacy groups.
+Our contributions to this developing literature are two-fold.
+First, we broaden the scope of measurement beyond tracing single ideas through bill versions or detecting model legislation---to assessing policy similarity between bills in general.
+Second, we present multiple validation tests to assess whether our text reuse based measure of policy similarity correlates with benchmarks that we deduce from theories of state policymaking.
 

### 2017-02-07 manuscript/main.tex
addressed two more reviewer comments

@@
 
+In their application of the SW algorithm to the dataset that we use, \citet{burgess2016legislative} optimize the SW algorithm parameters through a predictive experiment.
+They collected 165 bills that were hand labeled by experts to reuse text from one or more bills within the 165 bill corpus.
+Looking at all 13,530 pairs of bills that can be formed from the corpus of 165, they used the alignment score to predict whether or not there was text reuse between the bills.
+They found the optimal parameters, in terms of area under the ROC curve, were a match score of 3, mismatch score of -2, and gap score of -3.
+We followed \citet{burgess2016legislative} in setting the parameters of the SW algorithm since they use the same data and have already optimized the parameter values.
+Future work should expand upon treatment of these parameter values in at least two directions.
+First, it would be valuable to develop a criterion function such that one does not need hand labeled data, which is costly and may exhibit its own biases, to select parameter values.
+Second, it would be valuable to develop an approach to representing uncertainty in the parameter values as well as in the optimal alignments and scores.
+
 \subsection{Approaches to Adjusting for Boiler Plate Text}

### 2017-02-07 manuscript/main.tex
addressed point asking about further discusion of inverse frequency weighting

@@
 In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency--inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results).
-This measure is different and potentially preferable in two ways.
-First, it does not require the use of human coders.
-Second, it places text on a continuum of uniqueness rather than dichotomizes it as boiler plate or not.
+Though we cannot speak to whether or not our approach is ultimately better than that taken by \citet{wilkerson2015tracing}, in which they train a classifier to recognize and exclude boilerplate text based on human-labeled data, we note three relative strengths of our approach.
+First, we do not rely on the development and implementation of a human coding scheme, which is costly and always exhibits some degree of coding error.
+Second, our approach results in a continuous measure of the information content of text rather than a dichotomous classification of boilerplate or not.
+Third, and related to the first strength, our approach assigns an informativeness score to all word types, whereas reliance on human classifiers necessarily limits the boilerplate contributions of word types to the word types that were included in the ground truth labeled set.
+All this said, dealing with boilerplate/procedural text is an exciting open area of methodological inquiry for quantitative text-as-data research that is focused on legislation.
 

### 2017-02-07 manuscript/ajps/reviews_response.md
addressed two more reviewer comments
updated memo

@@
 
+[Adressed] Just overview
+
 Overall, this article makes a noteworthy contribution to the text-as-data literature.
@@
 
+[Addressed] I cited the Burgess et al. paper and said that we were using their parameter values. Frido, it does not look like we are using their values. Please check.
+
 Third, the discussion of TF-IDF weighting to identify boilerplate text is interesting and novel, and I would like to see it expanded further.
@@
 The reason for selecting TF-IDF weights in particular should be described in more detail.
+
+[Addressed] I both expanded the discussion of Wilkerson et al. and our approach, and also noted that dealing with boilerplate is an important open area for research in leg politics.
 

### 2017-02-09 generate_alignments/b2b_alignment.py
rewrote alignment generation from scratch

@@ -1,0 +1,187 @@
+from elasticsearch import Elasticsearch as ES
+from text_cleaning import clean_document
+from pprint import pprint
+from time import time
+from urllib3.exceptions import NewConnectionError
+from socket import gaierror
+from local_aligner import align, TimeOutError
+import sys
+import csv
+import os
+
+
+def similar_doc_query(es_connection, text, state_id, num_results):
+    """
+     Query db for similar documents within documents of not the same
+     state
+    """
+    
+    # Elastic search query:
+    query = {
+        "query": {
+            "bool": {
+                "must": [
+                    {
+                        "more_like_this": {
+                            "fields": ["bill_document_last.shingles"],
+                            "like_text": text,
+                            "max_query_terms": 25,
+                            "min_term_freq": 1,
+                            "min_doc_freq": 2,
+                            "minimum_should_match": 1
+                        }
+                    },
+                    {
+                        "bool": { "must_not": { "match": {
+                                    "state": state_id
+                                }
+                            }
+                        }
+                    }
+                ]
+            }
+        }
+    }
+
+    results = es_connection.search(index="state_bills", body=query,
+                                   fields=["state", "bill_document_last"], 
+                                   size=num_results)
+    max_score = results['hits']['max_score']
+    results = results['hits']['hits']
+    result_docs = []
+    for res in results:
+        doc = {}
+        for f in res['fields']:
+            doc[f] = res['fields'][f][0]
+        doc['score'] = res['_score']
+        doc['id'] = res['_id']
+        result_docs.append(doc)
+
+    return result_docs, max_score
+
+def write_outputs(alignments, bill_id, status, time, n_bills, n_success, 
+                  output_dir):
+    
+    alignment_file = os.path.join(output_dir, 'alignments/', 
+                                  bill_id + '_alignments.csv')
+    status_file = os.path.join(output_dir, 'bill_status/', 
+                               bill_id + '_status.csv')
+
+    with open(alignment_file, 'w') as af, open(status_file, 'w') as sf:
+
+        swriter = csv.writer(sf, delimiter=',', quotechar='"', 
+                             quoting=csv.QUOTE_MINIMAL)
+
+        swriter.writerow([bill_id, status, round(time, 4), n_bills, n_success])
+        
+        if len(alignments) > 0:
[…]

### 2017-02-09 generate_alignments/batch_jobs/generate_bill_to_bill_matches.py

@@ -1,115 +1,0 @@
-#!/opt/anaconda/bin/python 
-from __future__ import unicode_literals
-import sys 
-sys.path.append('../policy_diffusion/lid/')
-from lid import LID
-from text_alignment import AffineLocalAligner,LocalAligner
-import database
-import json
-import base64
-import codecs
-import re
-import logging
-import os
-import traceback
-import sys
-from utils.general_utils import deadline,TimedOutExc
-from database import ElasticConnection
-import time
-import io
-
-
-class NoneDocException(Exception):
-    pass
-
-@deadline(10000)
-def get_alignments(query_doc, bill_id):
-    result_docs=lidy.find_state_bill_alignments(query_doc,
-            document_type="state_bill", split_sections=True, 
-            state_id=bill_id[0:2], query_document_id=bill_id)
-    return result_docs
-
-
-def write_output(doc):
-    with io.open(outfile_name, 'a+', encoding='utf-8') as outfile:
-	outfile.write(unicode(json.dumps(doc)) + '\n')
-
-
-if __name__ == "__main__":
-
-    t = time.time() 
-
-    input_file_name = sys.argv[1]
-    output_dir = sys.argv[2]
-
-    ES_IP = "54.244.236.175" 
-
-    #configure logging
-    logfile_name = 'b2b_logfile_job_{}.log'.format(re.sub('[^0-9]', '',
-        input_file_name))
-    outfile_name = os.path.join(output_dir, 
-	'alignment_results_{}.json'.format(re.sub('[^0-9]', '',input_file_name)))
-    
-    log_path = os.path.join(os.environ['TEXT_REUSE'], 
-         	'generate_alignments/logs', logfile_name)
-
-    logging.basicConfig(filename=log_path,level=logging.DEBUG)
-    logging.getLogger('elasticsearch').setLevel(logging.ERROR)
-    logging.getLogger('urllib3').setLevel(logging.ERROR)
-    logging.getLogger('json').setLevel(logging.ERROR)
- 
-    # Initialize aligner
-    aligner = AffineLocalAligner(match_score=4, mismatch_score=-1, gap_start=-3, 
-                                 gap_extend = -1.5)
-
-    # Initialize Elastic Search connectino
-    ec = ElasticConnection(host = ES_IP)
-    
-    # Initialize LID
-    lidy = LID(query_results_limit=1000, elastic_host=ES_IP, 
-               lucene_score_threshold=0, aligner=aligner)
-
[…]

### 2017-02-09 generate_alignments/batch_jobs/get_finished_jobs.py

@@ -1,44 +1,0 @@
-from __future__ import unicode_literals
-import io
-import sys
-import os
-import glob
-import re
-import json
-
-def file_len(fname):
-    with io.open(fname) as f:
-        for i, l in enumerate(f):
-            pass
-    return i + 1
-
-RESULT_DIR = '../data/alignments/'
-files = glob.glob(os.path.join(RESULT_DIR, '*.json'))
-with io.open('processed_bills.txt', 'w+') as outfile:
-    outfile.write('')
-with io.open('../data/alignments_new/alignments_batch_jobs.json', 'w+',
-        encoding='utf-8') as resultfile:
-    resultfile.write('')
- 
-re_nn = re.compile(r'[^0-9]') 
-
-for f in files:
-    print 'processing {}'.format(f)
-    #f_path = os.path.join(RESULT_DIR, f)
-    with io.open(f) as current_file:
-            
-        for line in current_file:
-
-            doc = json.loads(line)
-
-            if 'error' in doc:
-                continue
-            else:
-                query_doc = doc['query_document_id']
-                with io.open('processed_bills.txt', 'a') as outfile:
-                    outfile.write(query_doc)
-                    outfile.write('\n')
-                with io.open('../data/alignments_new/alignments_batch_jobs.json', 'a',
-                        encoding='utf-8') as resultfile:
-                    resultfile.write(unicode(json.dumps(doc)))
-                    resultfile.write('\n')

### 2017-02-09 generate_alignments/ncsl_bill_pairs.py

@@ -1,90 +1,0 @@
-#!/opt/anaconda/bin/python 
-from __future__ import unicode_literals
-import sys 
-sys.path.append('../policy_diffusion/lid/')
-from lid import LID
-from text_alignment import AffineLocalAligner,LocalAligner
-from utils.text_cleaning import clean_document 
-import database
-import json
-import base64
-import codecs
-import re
-import logging
-import os
-import traceback
-import sys
-from utils.general_utils import deadline,TimedOutExc
-from database import ElasticConnection
-import time
-import io
-import itertools
-from pprint import pprint
-import numpy as np
-import sys
-import multiprocessing
-from functools import partial
-
-# TODO: dedicated I/O process for result output. There have been some conflicts
-# (very few though)
-
-def align_pair(c, split):
-    '''
-    c: tuple, (left_bill, right_bill)
-    split: bool, should bills be split in sections
-    '''
-    s = time.time()
-    alignments = lidy.align_bill_pair(right_doc_id=c[0], 
-                                      left_doc_id=c[1],
-                                      split_sections=split)
-    out = {'left_bill': c[0], 
-           'right_bill': c[1], 
-           'alignments':alignments}
-    
-    #with io.open(outfile_name, 'a', encoding='utf-8') as outfile:
-    #    outfile.write(unicode(json.dumps(out)) + '\n')
-    print(time.time() - s) 
-
-    return out
-
-
-if __name__ == '__main__':
-
-    # Parameters
-
-    # Number of processes
-    n_proc = 40
-     
-    OUTF = '../data/alignments_new/ncsl_pair_alignments_nosplit.json'
-    #OUTF = 'ncsl_pair_alignments.json'
-
-    ## Should bills be split in sections before alignment
-    SPLIT=False
-     
-    # Initialize aligner
-    aligner = AffineLocalAligner(match_score=4, mismatch_score=-1, gap_start=-3, 
-                                 gap_extend = -1.5)
-
-    # Initialize LID
-    ES_IP = "54.244.236.175"
-    lidy = LID(query_results_limit=1000, elastic_host=ES_IP, 
-               lucene_score_threshold=0, aligner=aligner)
-
-    # Load list of bills
-    with io.open('../data/ncsl/matched_ncsl_bill_ids.txt') as infile:
-        bill_ids = [s.strip('\n') for s in infile.readlines()]
-
-    # Get all combinations
[…]

### 2017-02-09 generate_alignments/single_bill_to_bill_matches.py

@@ -1,113 +1,0 @@
-#!/opt/anaconda/bin/python 
-from __future__ import unicode_literals
-import sys 
-sys.path.append('/storage/home/fjl128/bruce_shared/text_reuse/policy_diffusion/lid/')
-from lid import LID
-from text_alignment import AffineLocalAligner,LocalAligner
-import database
-import json
-import base64
-import codecs
-import re
-import logging
-import os
-import traceback
-import sys
-from utils.general_utils import deadline,TimedOutExc
-from database import ElasticConnection
-import time
-import io
-
-
-class NoneDocException(Exception):
-    pass
-
-@deadline(10000)
-def get_alignments(query_doc, bill_id):
-    result_docs=lidy.find_state_bill_alignments(query_doc,
-            document_type="state_bill", split_sections=True, 
-            state_id=bill_id[0:2], query_document_id=bill_id)
-    return result_docs
-
-
-def write_output(doc):
-    with io.open(outfile_name, 'a', encoding='utf-8') as outfile:
-	outfile.write(unicode(json.dumps(doc)))
-        outfile.write('\n')
-
-
-if __name__ == "__main__":
-
-    t = time.time() 
-
-    input_file_name = sys.argv[1]
-
-    ES_IP = "54.244.236.175" 
-
-    #configure logging
-    log_path = os.path.join(os.environ['TEXT_REUSE'], 
-         	'generate_alignments/logs/single_bill_jobs.log')
-
-    outfile_name = os.path.join(os.environ['TEXT_REUSE'],
-            'data/alignments_new/alignments_1000.json')
-    #outfile_name = 'lid_test.json' 
-            
-    
-
-    logging.basicConfig(filename=log_path,level=logging.DEBUG)
-    logging.getLogger('elasticsearch').setLevel(logging.ERROR)
-    logging.getLogger('urllib3').setLevel(logging.ERROR)
-    logging.getLogger('json').setLevel(logging.ERROR)
- 
-    # Initialize aligner
-    aligner = AffineLocalAligner(match_score=4, mismatch_score=-1, gap_start=-3, 
-                                 gap_extend = -1.5)
-
-    # Initialize Elastic Search connectino
-    ec = ElasticConnection(host = ES_IP)
-    
-    # Initialize LID
-    lidy = LID(query_results_limit=1000, elastic_host=ES_IP, 
-               lucene_score_threshold=0, aligner=aligner)
-
-    # Loop through the input files and get alignments
-    try:
-        bill_id = sys.argv[1]
-        # Retrieve left bill
[…]

### 2017-02-09 generate_alignments/text_cleaning.py

@@ -1,0 +1,194 @@
+'''
+Clean text in ElasticSearch
+'''
+
+import re
+from elasticsearch import Elasticsearch
+
+#custom modules
+#from database import ElasticConnection
+
+def clean_text(text, lower = True):
+    '''
+    variables:
+        text: string corresponding to text of bill
+        bill_name: string corresponding to bill_id
+
+    returns:
+        string that is cleaned up text 
+    decription:
+        clean text 
+    '''
+    #make text lowercase
+    if lower == True:
+        text = text.lower()
+    
+    #parse by line
+    text_list =  text.splitlines()
+
+    #replace funky symbols and multipe new lines
+    ntext_list = []
+    for line in text_list:
+        line = line.replace(u'\xa0', u' ')
+        line = line.replace(u'>>', u' ')
+        line = line.replace(u'\xa7', u' ')
+        line = line.replace(u'\xe2', u' ')
+        line = line.replace(u'\u201c', u' ')
+        line = line.replace(u'\u201d', u' ')
+        line = line.replace(u'\xbb', u' ')
+        line = line.replace(u'\xa9', u' ')
+        line = line.replace(u'{ font-family: courier, arial, sans-serif; font-size: 10pt; } table { empty-cells:show; }', u' ')
+        line = re.sub( '\s+', ' ', line)
+        line = re.sub( '"', '', line)
+        ntext_list.append(line)
+
+    return "\n".join(ntext_list)
+ 
+ 
+
+
+   
+
+def split_to_sections(cleantext,state):
+    '''
+    variables:
+        cleantext: clean version of text of bill
+        state: abbreviation of state ID
+
+    returns:
+        list of bill sections
+    decription:
+        splits bill text into sections
+    '''
+    if state == 'ak':
+        chunked_list = cleantext.split("\n*")
+    elif state in ('al','ar','mt','or','ri'):
+        chunked_list = cleantext.split('\nsection')
+    elif state in ('nm','tx'):
+        chunked_list = cleantext.split('\n section')
+    elif state in ('az','ia','nv', 'wa', 'vt'):
+        chunked_list = cleantext.split('\nsec.')
+    elif state in ('me', 'mi'):
+        chunked_list = cleantext.split('\n sec.')
[…]

### 2017-02-09 manuscript/ajps/submission/main.tex

--- 2017-02-07 manuscript/main.tex
@@
 Rather, text re-use serves as a summary measure of the greatest overlap observed across all relevant policy dimensions represented in legislative text.
-Furthermore, we note that by focusing on legislative text, we are measuring the similarity of the intended policies in terms of how those policies reflect in formal enacting legislation.
-Once enacted, the policies that are implemented in different states, under different bureaucratic and judicial regimes, will likely differ even if hey are enacted under equivalent legislative language.
-This divergence in policy implementation is attributable to the inevitable discretion exercised by bureaucratic officials in implementing policy \citep{weingast1983bureaucratic,scott1997assessing,gerber2005state}.
-
-We should emphasize at this point that we are not the first contributors to the legislative politics, or even state legislative politics, literature to use text similarity between bills to measure policy similarity.
-\citet{wilkerson2015tracing} use text similarity---indeed, the same algorithm we use---to trace the development of very similar policy proposals in legislation produced in the US Congress.
-\cite{garrett2015} and \cite{burgess2016legislative} both use measures of text similarity in US state legislation to identify bills that incorporate similar forms of model legislation, as provided by legislative/policy advocacy groups.
-Our contributions to this developing literature are two-fold.
-First, we broaden the scope of measurement beyond tracing single ideas through bill versions or detecting model legislation---to assessing policy similarity between bills in general.
-Second, we present multiple validation tests to assess whether our text reuse based measure of policy similarity correlates with benchmarks that we deduce from theories of state policymaking.
+Furthermore, we note that by focusing on legis
 
@@
 If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect an inverse relationship between these two measures.
-In the validation experiments that follow, we make use of the quantitative, interval level, alignment scores to construct continuous measures of policy similarity.
-We do this to impose as little information reduction as possible.
-In the conclusion we discuss the possibility of thresholding these scores in order to classify bill pairs as either containing or not containing matching policy content.
 
@@
 For searching out bill pairs, this can be done through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.
-Such thresholding may discard informative variation on policy similarity in terms of bill pairs that exhibit borderline overlap when it comes to containing equivalent policy content.
-On the other hand, high-score thresholding would focus the analysis on bill pairs that reliably contain very similar policy enactments, and pose little risk of a false positive.
 
@@
 
-%\bibliographystyle{authoryear1} (frido, did you add this? where's the stylefile?)
-\bibliographystyle{apsr}
+\bibliographystyle{authoryear1}
 \bibliography{bibliography}

### 2017-02-09 manuscript/ajps/submission/tables/ncsl_auc.tex

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Tue Sep 27 15:27:52 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & AUC & P(X$<$Random) & P(X$<$Cosine) \\ 
  \hline
Random & 0.50 &  &  \\ 
  Cosine & 0.57 & 0.00 &  \\ 
  Alignment & 0.62 & 0.00 & 0.00 \\ 
   \hline
\end{tabular}
\caption{Area under the curve for classifier based
       on thresholding alignment scores (Alignment), classifier based on 
       thresholding cosine similarity score (Cosine) and random 
       classifier (Random). The last three columns report one-tailed p-values for 
       comparison between the AUCs. p-values are derived from 2000 non-parametric
       bootstrap iterations.} 
\label{tab:ncsl_auc}
\end{table}

### 2017-02-10 generate_alignments/b2b_alignment.py
adapted pbs submission code to refactor

@@ -44,17 +44,19 @@ def similar_doc_query(es_connection, text, state_id, num_results):
     }
 
     results = es_connection.search(index="state_bills", body=query,
-                                   fields=["state", "bill_document_last"], 
+                                   #fields=["state", "bill_document_last"], 
                                    size=num_results)
+     
+
     max_score = results['hits']['max_score']
     results = results['hits']['hits']
     result_docs = []
     for res in results:
         doc = {}
-        for f in res['fields']:
-            doc[f] = res['fields'][f][0]
-        doc['score'] = res['_score']
-        doc['id'] = res['_id']
+        doc["bill_document_last"] = res["_source"]["bill_document_last"]
+        doc["state"] = res["_source"]["state"]
+        doc["score"] = res["_score"]
+        doc["id"] = res["_id"]
         result_docs.append(doc)
 
     return result_docs, max_score
@@ -99,7 +101,7 @@ if __name__ == "__main__":
     BILL_ID = sys.argv[1]
     ES_IP = ["http://elasticsearch.dssg.io:9200/"]
     
-    N_RIGHT_BILLS = 500
+    N_RIGHT_BILLS = 2
     MATCH_SCORE = 3
     MISMATCH_SCORE = -2
     GAP_SCORE = -3
@@ -164,6 +166,8 @@ if __name__ == "__main__":
             alignments.append(alignment)
             n_success += 1
 
+        print("Sucessfully terminated")
+
     # Handle exceptions
     except NoConnectionError:
         status = "connection_error"
@@ -177,11 +181,12 @@ if __name__ == "__main__":
     except KeyboardInterrupt as e:
         raise e
 
-    except Exception as e:
+    except:
         status = "other_error"
-        raise e
+        raise
 
     finally:
         elapsed_time = time() - start_time 
         write_outputs(alignments, BILL_ID, status, elapsed_time, n_right_bills,
                       n_success, OUTPUT_DIR)
+

### 2017-02-10 generate_alignments/mj_queue.py

@@ -13,6 +13,7 @@ import argparse
 import datetime
 import sys
 import shutil
+import csv
 
 
 class PBSQueue(object):
@@ -33,19 +34,20 @@ class PBSQueue(object):
     '''
 
     def __init__(self, user_id, allocation, num_jobs, bill_list, job_template, job_dir,
-            sleep_time):
+                 sleep_time):
+
         self.split_regex = re.compile(r'\s+')
         self.status = None
         self.num_jobs = num_jobs
         self.running_jobs = 0
-	self.user_id = user_id
+        self.user_id = user_id
         self.bill_queue = bill_list
         self.last_difference = 0
         self.template = job_template
-        self.prog_f_name = 'mj_queue_prog.txt'
         self.allocation = allocation
 
         self.job_dir = job_dir
+
         if os.path.exists(self.job_dir):
             shutil.rmtree(self.job_dir)
             os.makedirs(self.job_dir)
@@ -53,16 +55,7 @@ class PBSQueue(object):
             os.makedirs(self.job_dir) 
 
         self.sleep_time = sleep_time
-
-    def _update_prog_file(self, job):
-        '''
-        Update the permanent progress file
-        '''
-
-        with io.open(self.prog_f_name, 'a+', encoding='utf-8') as progfile:
-            progfile.write(job)
-            progfile.write(u'\n')
-            
+   
 
     def update(self):        
         '''
@@ -84,13 +77,10 @@ class PBSQueue(object):
         while response is None:
             try:
                 ntry += 1
-                response = subprocess.check_output(['qstat', '-u', self.user_id])
+                response = subprocess.getoutput("qstat -u {}".format(self.user_id))
             except subprocess.CalledProcessError as error:
                 if ntry > 5:
                     raise
-                rc = error.returncode
-                print "Error in qsub in _submit_job(). Returncode: {}".format(rc) 
-                print "Taking a break..."
                 time.sleep(10)
                 pass
 
@@ -117,9 +107,10 @@ class PBSQueue(object):
         '''
         self.last_difference = self.num_jobs - self.running_jobs
         c = 1
+        n_submitted = 0
 
         # Submit jobs until num_job is reached
-        while c <= self.last_difference:
+        while c <= self.last_difference and len(self.bill_queue) >= 1:
             c += 1
             new_job = self._make_job(self.bill_queue[0])
  
@@ -129,25 +120,23 @@ class PBSQueue(object):
             while response == None:
[…]

### 2017-02-10 generate_alignments/text_cleaning.py

@@ -43,10 +43,6 @@ def clean_text(text, lower = True):
         ntext_list.append(line)
 
     return "\n".join(ntext_list)
- 
- 
-
-
    
 
 def split_to_sections(cleantext,state):
@@ -143,7 +139,6 @@ def delete_numbers_in_lines (chunked_list):
     return chunked_list
 
 
-
 #Delete multiple new lines for each section
 def delete_lines (chunked_list):
     '''
@@ -151,7 +146,6 @@ def delete_lines (chunked_list):
     '''
     chunked_list = [re.sub( '\s+', ' ', x) for x in chunked_list]
     return chunked_list
-        
 
 
 def clean_document(doc_text, state_id):
@@ -166,13 +160,12 @@ def clean_document(doc_text, state_id):
 
     return " ".join(doc_text_sections)
 
+
 #delete boiler plate present in all alec exposed bills after "effective date"
 def delete_boiler_plate_alec_exposed (chunked_list):
     chunked_list = [re.sub('({effective date).*$', ' ', x) for x in chunked_list]
     chunked_list = chunked_list[1:]
     return chunked_list
-
-#good example is test_clean_text_for_alignment('va')
 
 def test_clean_text(state):
    es = Elasticsearch(['54.203.12.145:9200', '54.203.12.145:9200'], timeout=300)

### 2017-02-10 manuscript/main.tex
added cite about NCSL

@@
 First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse.
-Second, we show that bills classified by the National Council of State Legislatures as covering the same policies exhibit a high degree of text re-use.
+Second, we show that bills classified by the National Conference of State Legislatures as covering the same policies exhibit a high degree of text re-use.
 Third, we show that rates of text reuse across state borders correlate with the diffusion networks recently introduced by Desmarais, Harden and Boehmke (2015).
@@
 Second, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states.
-And third, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.
+And third, we use data on equivalent bills collected by the National Conference of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.
 We find that a high degree of text reuse between bills provides a precise signal of the presence of similar policies within the bills.
@@
 In our first validation exercise, we consider whether high alignment scores provide a reliable signal of similar policy proposals.
-To build a ground truth data set in terms of similar policy proposals, we rely on thematic tables published by the National Council of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}}  We collected a sample of these tables with the following procedure:
+To build a ground truth data set in terms of similar policy proposals, we rely on thematic tables published by the National Conference of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}} The NCSL is a non-partisan organization that provides informational assistance to state legislatures, and maintains databases of state-level legislation and law \citep{rivera2014immigration}.
+We collected a sample of these tables with the following procedure:
 

### 2017-02-10 generate_alignments/b2b_alignment.py
moved all configuration to mj_queue

@@ -73,7 +73,6 @@ def write_outputs(alignments, bill_id, status, time, n_bills, n_success,
 
         swriter = csv.writer(sf, delimiter=',', quotechar='"', 
                              quoting=csv.QUOTE_MINIMAL)
-
         swriter.writerow([bill_id, status, round(time, 4), n_bills, n_success])
         
         if len(alignments) > 0:
@@ -99,14 +98,13 @@ if __name__ == "__main__":
     # Config
     # =========================================================================
     BILL_ID = sys.argv[1]
-    ES_IP = ["http://elasticsearch.dssg.io:9200/"]
     
-    N_RIGHT_BILLS = 2
-    MATCH_SCORE = 3
-    MISMATCH_SCORE = -2
-    GAP_SCORE = -3
-    #OUTPUT_DIR = "/storage/group/bbd5087_collab/text_reuse/data/aligner_output"
-    OUTPUT_DIR = "../data/aligner_output"
+    N_RIGHT_BILLS = int(sys.argv[2])
+    MATCH_SCORE = int(sys.argv[3])
+    MISMATCH_SCORE = int(sys.argv[4])
+    GAP_SCORE = int(sys.argv[5])
+    OUTPUT_DIR = sys.argv[6]
+    ES_IP = sys.argv[7]
     # =========================================================================
     
     alignments = []
@@ -117,13 +115,14 @@ if __name__ == "__main__":
 
     try:
         # Establish elastic search connection
-        es = ES(ES_IP, timeout = 100)
+        es = ES(ES_IP, timeout=1000)
 
         if not es.ping():
             raise NoConnectionError()
 
         # Get text of the left bill
-        query_doc = es.get_source(index="state_bills", id=BILL_ID, doc_type="_all")
+        query_doc = es.get_source(index="state_bills", id=BILL_ID, 
+                                  doc_type="_all")
 
         if query_doc is None:
             raise NoBillError()

### 2017-02-10 generate_alignments/mj_queue.py

@@ -2,7 +2,6 @@
 #
 # Author: Fridolin Linder
 
-from __future__ import unicode_literals
 import subprocess
 import re
 import os
@@ -28,13 +27,14 @@ class PBSQueue(object):
     allocation: str, allocation name to submit to
     num_jobs: int, how many jobs sould be running in parallel
     bill_list: list, of bills to generate jobs for
-    job_template: str, template with placeholder for allocation and input bill
-    job_dir: str, directory name to store temporary job files
+    job_template: str, template with placeholder for allocation and input bill 
+        job_dir: str, directory name to store temporary job files
     sleep_time: int, waiting time between submission of single jobs
     '''
 
-    def __init__(self, user_id, allocation, num_jobs, bill_list, job_template, job_dir,
-                 sleep_time):
+    def __init__(self, user_id, allocation, num_jobs, bill_list, job_template, 
+                 job_dir, sleep_time, n_right_bills, match, mismatch, gap, 
+                 output_dir, es_ip, bill_status_file, alignment_master_file):
 
         self.split_regex = re.compile(r'\s+')
         self.status = None
@@ -43,8 +43,16 @@ class PBSQueue(object):
         self.user_id = user_id
         self.bill_queue = bill_list
         self.last_difference = 0
-        self.template = job_template
+        self.template = job_template 
         self.allocation = allocation
+        self.n_right_bills = n_right_bills
+        self.match = match
+        self.mismatch = mismatch
+        self.gap = gap
+        self.output_dir = output_dir
+        self.es_ip = es_ip
+        self.bill_status_file=bill_status_file
+        self.alignment_master_file=alignment_master_file
 
         self.job_dir = job_dir
 
@@ -182,7 +190,13 @@ class PBSQueue(object):
         str, path/name of the jobfile
         '''
         job = self.template.format(bill_id=bill_id,
-                                   allocation=self.allocation)
+                                   allocation=self.allocation,
+                                   n_right_bills=self.n_right_bills,
+                                   match=self.match,
+                                   mismatch=self.mismatch,
+                                   gap=self.gap,
+                                   output_dir=self.output_dir,
+                                   es_ip=self.es_ip)
         bill_id = re.sub('[^A-Za-z0-9]', '_', bill_id)
[…]

### 2017-02-10 generate_alignments/cluster_health.py
script to test cluster health

@@ -1,0 +1,45 @@
+
+
+
+
+from elasticsearch import Elasticsearch
+from pprint import pprint
+
+
+es = Elasticsearch('http://elasticsearch.dssg.io:9200/', timeout=1000)
+pprint(es.cluster.health())
+print(es.ping())
+
+doc = es.get_source(index="state_bills", id='ky_2013RS_HB262', doc_type="_all")
+pprint(doc.keys())
+   
+query = {
+    "query": {
+        "bool": {
+            "must": [
+                {
+                    "more_like_this": {
+                        "fields": ["bill_document_last.shingles"],
+                        "like_text": "this is some example text that serves th",
+                        "max_query_terms": 25,
+                        "min_term_freq": 1,
+                        "min_doc_freq": 2,
+                        "minimum_should_match": 1
+                    }
+                },
+                {
+                    "bool": { "must_not": { "match": {
+                                "state": "ca"
+                            }
+                        }
+                    }
+                }
+            ]
+        }
+    }
+}
+
+
+res = es.search(index="state_bills", body=query, size=500)
+print(res.keys())
+print(len(res['hits']['hits']))

### 2017-02-11 manuscript/ajps/reviews_response.md
added cite about NCSL
updated memo
finished reviewer 2

@@
 
+[Addressed] Thanks!
+
 I do not consider myself a methodologist as such; therefore I will comment from the point of view as a possible user of such a method in other substantive areas.
 Does the paper do enough scholarly contribution to the discipline to be accepted to the premier journal in political science?
+
+[
 
@@
 
+[Addressed] Added a cite explaining what the NCSL is, as well as several references to papers that use the NCSL to identify policy-specific lists of bills/policies across states.
+
 Finally, some smaller notes:
@@
 
+[Addressed] I revised this to clarify.
+
 - In Figure 1, placing the optimal alignment alongside the table is confusing, and suggests that the terms match the axes in the figure.
 
+[FRIDO] Would you circle or bold the terms in each axis that get included in the alignment, rather than writing them to the right?
+
 - Scores inside cells in Figure 1 do not appear to match the parameter values and scores given in text.
+
+[FRIDO] Would you double check this?

### 2017-02-11 manuscript/main.tex
finished reviewer 2

@@
 Dynamic programming refers to algorithms that divide a problem into sub-problems and store results of previous calculations for later ones.
-In the case of the SW algorithm, the property that makes it a dynamic problem is the fact that all the alignments of shorter sub-sequences of an optimal alignment of a sequence are themselves optimal.
+In the case of the SW algorithm, given an existing alignment between two sequences, as more terms are considered across the two sequences, new terms will either be added or skipped.
+The alignment score is never improved by removing terms from the alignment.
+This property makes the SW algorithm a dynamic programming problem.
 Intuitively, if the benefits of including a sub-sequence in an alignment outweigh the penalties from mismatches and gaps in that sub-sequence, that sub-sequence will contribute positively to longer alignments to which it is appended.
@@
 To build a ground truth data set in terms of similar policy proposals, we rely on thematic tables published by the National Conference of State Legislatures (NCSL).\footnote{\url{www.ncsl.org}} The NCSL is a non-partisan organization that provides informational assistance to state legislatures, and maintains databases of state-level legislation and law \citep{rivera2014immigration}.
+The NCSL tables are regularly used in state politics research to identify comparable bills and policies across states \citep[see, e.g., ][]{marquez2013hispanic,witmer2014american,commins2016reappraising,ybarra2016anti, brown2013foreclosing}.
 We collected a sample of these tables with the following procedure:

### 2017-02-11 generate_alignments/b2b_alignment.py
more updates to alignment generation

@@ -69,7 +69,8 @@ def write_outputs(alignments, bill_id, status, time, n_bills, n_success,
     status_file = os.path.join(output_dir, 'bill_status/', 
                                bill_id + '_status.csv')
 
-    with open(alignment_file, 'w') as af, open(status_file, 'w') as sf:
+    with open(alignment_file, 'w', encoding='utf-8') as af,\
+            open(status_file, 'w', encoding='utf-8') as sf:
 
         swriter = csv.writer(sf, delimiter=',', quotechar='"', 
                              quoting=csv.QUOTE_MINIMAL)
@@ -115,7 +116,7 @@ if __name__ == "__main__":
 
     try:
         # Establish elastic search connection
-        es = ES(ES_IP, timeout=1000)
+        es = ES(ES_IP, timeout=10, retry_on_timeout=True, max_retries=100)
 
         if not es.ping():
             raise NoConnectionError()
@@ -125,8 +126,7 @@ if __name__ == "__main__":
                                   doc_type="_all")
 
         if query_doc is None:
-            raise NoBillError()
-
+            raise NoBillError() 
 
         # Get most similar right bills
         if query_doc["bill_document_last"] is not None:
@@ -177,12 +177,8 @@ if __name__ == "__main__":
     except NoBillError:
         status = "no_bill"
 
-    except KeyboardInterrupt as e:
-        raise e
-
     except:
         status = "other_error"
-        raise
 
     finally:
         elapsed_time = time() - start_time 

### 2017-02-11 generate_alignments/mj_queue.py

@@ -137,7 +137,7 @@ class PBSQueue(object):
                         raise
                     c -= 1
                     # Wait before re-trying
-                    time.sleep(60)
+                    time.sleep(10)
                     pass
 
             self.bill_queue.pop(0)
@@ -247,7 +247,9 @@ class PBSQueue(object):
                         outfile.write(line)
                 os.remove(f)
 
-
+def timestamp():
+    ts = time.time()
+    return datetime.datetime.fromtimestamp(ts).strftime('%Y-%m-%d %H:%M:%S')
 
 if __name__ == "__main__":
     
@@ -255,11 +257,11 @@ if __name__ == "__main__":
     # Config
     # =====================================================================
     USER_ID = 'fjl128'
-    NUM_JOBS = 80
+    NUM_JOBS = 90
     BILL_IDS = 'bill_ids.txt'
     ALLOCATION = 'bbd5087-himem_collab'
 
-    N_RIGHT_BILLS = 2
+    N_RIGHT_BILLS = 500
     MATCH_SCORE = 3
     MISMATCH_SCORE = -2
     GAP_SCORE = -3
@@ -278,11 +280,10 @@ if __name__ == "__main__":
     processed_bills = set()
 
     if os.path.exists(BILL_STATUS_FILE):
-        with open(BILL_STATUS_FILE, 'r') as csvfile:
+        with open(BILL_STATUS_FILE, 'r', encoding='utf-8') as csvfile:
              reader = csv.reader(csvfile, delimiter=',', quotechar='"')
              for row in reader:
                  processed_bills.update([row[0]])
-
     temp = io.open(BILL_IDS).readlines()
     all_bills = [e.strip('\n') for e in temp]
     bill_list = [e for e in all_bills if e not in processed_bills]
@@ -298,7 +299,7 @@ if __name__ == "__main__":
                      bill_list=bill_list, 
                      job_template=template, 
                      job_dir=job_dir, 
-                     sleep_time=2, 
+                     sleep_time=10, 
                      allocation=ALLOCATION,
                      n_right_bills=N_RIGHT_BILLS,
                      match=MATCH_SCORE,
@@ -314,34 +315,30 @@ if __name__ == "__main__":
     try:
         while True:
             queue.update()
-            ts = time.time()
-            st = datetime.datetime.fromtimestamp(ts).strftime('%Y-%m-%d %H:%M:%S')
             
             if len(queue.bill_queue) == 0:
                 print("Finished")
                 break
 
             if queue.running_jobs >= queue.num_jobs:
[…]

### 2017-02-11 manuscript/main.tex

@@
 We find that a high degree of text reuse between bills provides a precise signal of the presence of similar policies within the bills.
+The findings and open questions offered by our work contribute beyond the study of public policy diffusion or legislative politics.
+We add to the growing methodological literature in political science and public policy that is focused on the use of text-as-data methods for measurement tasks \citep[see, e.g.,][]{laver2003extracting,martin2008robust,lowe2013validating,grimmer2013text,monroe2008fightin,blair2016national}.
+Furthermore, the methodological approach we present would be applicable to any of the several lines of research in political science and public policy that draw upon text corpora to operationalize variables of interest \citep[see, e.g.,][]{hart1990evolution,van2008parsing,young2012affective,mikhaylov2012coder,mondou2014policy,witting2015measuring}.
 

### 2017-02-11 generate_alignments/b2b_alignment.py
renamed some stuff

@@ -92,21 +92,10 @@ class NoTextError(Exception):
 class NoBillError(Exception):
     pass
 
-if __name__ == "__main__":
 
-    # =========================================================================
-    # Config
-    # =========================================================================
-    BILL_ID = sys.argv[1]
-    
-    N_RIGHT_BILLS = int(sys.argv[2])
-    MATCH_SCORE = int(sys.argv[3])
-    MISMATCH_SCORE = int(sys.argv[4])
-    GAP_SCORE = int(sys.argv[5])
-    OUTPUT_DIR = sys.argv[6]
-    ES_IP = sys.argv[7]
-    # =========================================================================
-    
+def get_bill_alignments(BILL_ID, N_RIGHT_BILLS, MATCH, MISMATCH, GAP, OUTPUT_DIR,
+                        ES_IP)
+
     alignments = []
     status = "successfull"
     start_time = time()
@@ -115,7 +104,7 @@ if __name__ == "__main__":
 
     try:
         # Establish elastic search connection
-        es = ES(ES_IP, timeout=1000)
+        es = ES(ES_IP, timeout=10)
 
         if not es.ping():
             raise NoConnectionError()
@@ -189,3 +178,20 @@ if __name__ == "__main__":
         write_outputs(alignments, BILL_ID, status, elapsed_time, n_right_bills,
                       n_success, OUTPUT_DIR)
 
+if __name__ == "__main__":
+
+    # =========================================================================
+    # Config
+    # =========================================================================
+    BILL_ID = sys.argv[1]
+    
+    N_RIGHT_BILLS = int(sys.argv[2])
+    MATCH_SCORE = int(sys.argv[3])
+    MISMATCH_SCORE = int(sys.argv[4])
+    GAP_SCORE = int(sys.argv[5])
+    OUTPUT_DIR = sys.argv[6]
+    ES_IP = sys.argv[7]
+    # =========================================================================
+    
+    get_bill_alignments(BILL_ID, N_RIGHT_BILLS, MATCH, MISMATCH, GAP, OUTPUT_DIR, 
+                        ES_IP)

### 2017-02-11 generate_alignments/run_local.py

@@ -1,0 +1,3 @@
+import multiprocessing
+
+

### 2017-02-12 manuscript/ajps/reviews_response.md
updated another point of R1's

@@
 
-[
-
 Even though an informed reader familiar with the text analytics will be able to follow the analyses presented, since the submission is t AJPS as opposed to Pol Analysis, I think the authors need to revise it to a considerable degree so that a general political science practitioner interested in applying such methods in his or research will be able to follow.
@@
 
+[Addressed] I added a couple of string cites to emphasize the broader connections and contributions we offer---both to the text as data methods literature and to any substantive applied work that involves analysis of text corpora.
+
 After reading the paper my overall impression is that it will be very suitable for a special volume on political text, or perhaps for a more specialized journal such as State Politics & Policy Quarterly.
 As it stands, I think it requires very considerable revisions to be considered for publication in AJPS.
+
+[Addressed] OK
 
@@
 11 they underline that "In our analyses we use a slightly modified version of the local alignment algorithm, in which the first gap in a series of multiple gaps receives a higher penalty then the following ones (Wilkerson et al., 2015, use the same modification)." "The idea behind this modification is that someone who changes text in a bill might insert several words into an existing piece of text."
+
+[Addressed] I updated the conclusion to note that the all-bill-pairs database is a novel contribution, and that we will distribute it with the supplemental materials for this article.
 

### 2017-02-12 manuscript/main.tex
updated another point of R1's
addressed another R1 point

@@
 Questions such as these can be directly investigated using the policy similarity measures we introduce.
+The alignment scores for all bill pairs---a novel database which we contribute---are available in the supplemental materials with this article.
+The validation exercises assure that researchers can use the alignment scores that we derive for our bill pairs database to study the policy similarity between bills at the level of bill pairs, or aggregated up to higher levels.
 

### 2017-02-16 etl/database/import_bills.py
database etl code

@@ -1,0 +1,72 @@
+from elasticsearch import Elasticsearch
+import json
+
+
+def has_bill_text(b):
+    if b["bill_document_last"] is None and b["bill_document_first"] is None:
+        return False
+    else:
+        return True
+
+
+if __name__ == "__main__":
+
+
+    #==========================================================================
+    # Config
+    #==========================================================================
+    HOST = 'localhost'
+    PORT = 9200
+    INDEX_NAME = 'state_bills'
+    DATA_FILE = '../../data/raw_data/extracted_bills_with_sponsers.json' 
+    MAPPING_FILE = "../../etl/database/state_bill_mapping.json"
+    IDX_SET_FILE = "../../etl/database/state_bill_index.json"
+    #==========================================================================
+
+    # set up es connection
+    es = Elasticsearch([{'host': 'localhost', 'port': 9200}], timeout=200)
+    
+    
+    # Create the state_bill index
+    if es.indices.exists(INDEX_NAME):
+        print("Deleting {} index...".format(INDEX_NAME))
+        es.indices.delete(index=INDEX_NAME)
+
+    mapping_doc = json.loads(open(MAPPING_FILE).read())
+    settings_doc = json.loads(open(IDX_SET_FILE).read())
+
+    print("Creating {} index...".format(INDEX_NAME))    
+    es.indices.create(index=INDEX_NAME, body=settings_doc)
+    
+    print("adding mapping for bill_documents")
+    res = es.indices.put_mapping(index=INDEX_NAME, body=mapping_doc,
+                                 doc_type="bill_document")
+
+    bulk_data = []
+    for i, line in enumerate(open(DATA_FILE)):
+
+        if line == "null\n":
+            continue
+
+        json_obj = json.loads(line.strip())
+
+        if not has_bill_text(json_obj):
+            continue
+
+        op_dict = {
+                "index": {
+                    "_index": INDEX_NAME,
+                    "_type": "bill_document",
+                    "_id": json_obj["unique_id"]
+                }
+        }
+
+        bulk_data.append(op_dict)
+        bulk_data.append(json_obj)
+        if len(bulk_data) == 1000:
+            print(i)
+            es.bulk(index=INDEX_NAME, body=bulk_data)
+            del bulk_data
+            bulk_data = []
+
+

### 2017-02-16 generate_alignments/b2b_alignment.py
updates to alignment geration + local run script

@@ -1,19 +1,19 @@
 from elasticsearch import Elasticsearch as ES
 from text_cleaning import clean_document
 from pprint import pprint
-from time import time
+from time import time, sleep
 from urllib3.exceptions import NewConnectionError
 from socket import gaierror
 from local_aligner import align, TimeOutError
 import sys
 import csv
 import os
+import numpy as np
 
 
 def similar_doc_query(es_connection, text, state_id, num_results):
     """
-     Query db for similar documents within documents of not the same
-     state
+     Query db for similar documents within documents of not the same state
     """
     
     # Elastic search query:
@@ -94,9 +94,10 @@ class NoBillError(Exception):
     pass
 
 
-def get_bill_alignments(BILL_ID, N_RIGHT_BILLS, MATCH, MISMATCH, GAP, OUTPUT_DIR,
-                        ES_IP)
-
+def get_bill_alignments(BILL_ID, N_RIGHT_BILLS, MATCH_SCORE, MISMATCH_SCORE, 
+                        GAP_SCORE, OUTPUT_DIR, ES_IP):
+    
+    sleep(np.random.exponential(1))
     alignments = []
     status = "successfull"
     start_time = time()
@@ -105,7 +106,7 @@ def get_bill_alignments(BILL_ID, N_RIGHT_BILLS, MATCH, MISMATCH, GAP, OUTPUT_DIR
 
     try:
         # Establish elastic search connection
-        es = ES(ES_IP, timeout=10, retry_on_timeout=True, max_retries=100)
+        es = ES(ES_IP, timeout=30, retry_on_timeout=True, max_retries=10)
 
         if not es.ping():
             raise NoConnectionError()
@@ -173,6 +174,8 @@ def get_bill_alignments(BILL_ID, N_RIGHT_BILLS, MATCH, MISMATCH, GAP, OUTPUT_DIR
         elapsed_time = time() - start_time 
         write_outputs(alignments, BILL_ID, status, elapsed_time, n_right_bills,
                       n_success, OUTPUT_DIR)
+
+    return status
 
 if __name__ == "__main__":
 

### 2017-02-16 generate_alignments/cluster_health.py

@@ -1,26 +1,37 @@
-
-
-
-
 from elasticsearch import Elasticsearch
 from pprint import pprint
 import sys
+import numpy as np
 
 
-es = Elasticsearch('http://elasticsearch.dssg.io:9200/', timeout=10, 
-                    retry_on_timeout=True, max_retries=100)
-try:
-    pprint(es.cluster.health())
-    print(es.ping())
-except:
-    print("exception occurred")
+es = Elasticsearch('http://localhost:9200/', timeout=3, 
+                    retry_on_timeout=True, max_retries=1)
+
+pprint(es.cluster.health())
+print(es.ping())
 
 
-sys.exit()
+with open('bill_ids.txt') as infile:
+    ids = [x.strip('\n') for x in infile]
+#
+#o = np.zeros((len(ids)))
 
-doc = es.get_source(index="state_bills", id='ky_2013RS_HB262', doc_type="_all")
-pprint(doc.keys())
-   
+#for i, id_ in enumerate(ids): 
+#    doc = None
+#    s = 'failed'
+#    doc = es.get_source(index="state_bills", id=id_, doc_type="_all")
+#    if doc is not None:
+#        o[i] = 1
+#        s = 'worked'
+#
+#    print('{}: {}, {}'.format(s, i, id_))
+#
+#print(o.sum())
+#sys.exit()   
+
+
+doc = es.get_source(index="state_bills", id="ky_2013RS_HB262", doc_type="_all")
+
 query = {
     "query": {
         "bool": {
@@ -47,7 +58,8 @@ query = {
     }
 }
 
-
 res = es.search(index="state_bills", body=query, size=500)
 print(res.keys())
 print(len(res['hits']['hits']))
+
+

### 2017-02-16 generate_alignments/run_local.py

@@ -1,3 +1,80 @@
-import multiprocessing
+import multiprocessing as mp
+from b2b_alignment import get_bill_alignments
+import os
+import csv
 
 
+def collect_results():
+
+    # If master files don't exist, create them
+    if not os.path.exists(ALIGNMENT_MASTER_FILE):
+        with open(ALIGNMENT_MASTER_FILE, 'w') as outfile:
+            header = ('left_id,right_id,score,left_alignment_text,right_ali'
+                      'gnment_text,lucene_score,max_lucene_score,compute_ti'
+                       'me\n')
+            outfile.write(header)
+
+    if not os.path.exists(BILL_STATUS_FILE):
+        with open(BILL_STATUS_FILE, 'w') as outfile:
+            outfile.write('bill_id,status,time,n_bills,n_successfull\n')
+
+    # Bill status
+    status_dir = os.path.join(OUTPUT_DIR, "bill_status")
+    with open(BILL_STATUS_FILE, 'a+') as outfile:
+        for file in os.listdir(status_dir):
+            f = os.path.join(status_dir, file)
+            with open(f, 'r') as infile:
+                line = infile.read()
+                outfile.write(line)
+            os.remove(f)
+
+    # Alignments
+    alignment_dir = os.path.join(OUTPUT_DIR, "alignments")
+    with open(ALIGNMENT_MASTER_FILE, 'a+') as outfile:
+        for file in os.listdir(alignment_dir):
+            f = os.path.join(alignment_dir, file)
+            with open(f, 'r') as infile:
+                for line in infile:
+                    outfile.write(line)
+            os.remove(f)
+
+if __name__ == "__main__":
+
+
+    # =====================================================================
+    # Config
+    # =====================================================================
+    BILL_IDS = 'bill_ids.txt'
+    N_RIGHT_BILLS = 500
+    MATCH_SCORE = 3
+    MISMATCH_SCORE = -2
+    GAP_SCORE = -3
+    OUTPUT_DIR = '../data/aligner_output/'
+    BILL_STATUS_FILE = os.path.join(OUTPUT_DIR, 'bill_status.csv')
+    ALIGNMENT_MASTER_FILE = os.path.join(OUTPUT_DIR, 'alignments.csv')
+    ES_IP = "http://localhost:9200/"
+    # =====================================================================
+
+    def align(bill_id):
[…]

### 2017-02-16 manuscript/ajps/reviews_response.md
addressed another R1 point

@@
 
+[Addressed] I added a note explaining that passing these validation exercises assures that researchers can use our measure to study policy similarity.
+
 In my humble opinion, the authors can follow two possible avenues.
@@
 As it stands, the authors only suggest that the method could be useful, but they do not demonstrate the applications.
+
+[Addressed] Not going in this direction. This is odd. It seems like the reviewer wants us to write a transfer paper about the SW algorithm.
 
@@
 
+[Addressed] There are lots of measurement papers in the literature that do not involve a full substantive application.
+I find it peculiar that this reviewer makes such close reference to Wilkerson et al.
+We could probably call the sponsor ideology analysis a novel substantive application, as I am not aware of past work that studies whether ideologically similar legislators sponsor bills with similar content.
+Its not a surprising result, but I haven't seen it in the Congress literature.
+Let's see how it goes at PSJ with the current framing.
+
 Reviewer #1: As I read it, this manuscript makes three primary contributions.
@@
 
-[Adressed] Just overview
+[Addressed] Just overview
 

### 2017-04-05 etl/alignments/extract_bill_metadata.py
refactored metadata extraction

@@ -1,98 +1,0 @@
-# Generate a csv with metadata on all bills. 
-# Calculates average ideology of all bill sponsors (from malp data)
-
-from __future__ import unicode_literals
-
-import json
-import io
-from pprint import pprint
-import pandas as pd
-import numpy as np
-import time
-import re
-
-BILL_FILE = '../../data/lid/extracted_bills_with_sponsers.json'
-OUTFILE = '../../data/lid/bill_metadata.csv'
-N_SPON = 3
-
-legislators = pd.read_csv('../../data/lid/legislators.csv')
-header = ['unique_id', 'date_introduced', 'date_signed', 'date_last_action', 
-          'date_passed_upper', 'date_passed_lower', 'state', 'chamber', 
-          'bill_type', 'short_title', 'session', 'bill_title', 'bill_length',
-          'sponsor_idology', 'num_sponsors']
-header = ','.join(header)
-# Get a set of all legislators that we have ideology for
-known_legis = set(legislators['id'])
-
-# Regex to remove chars that mess up the csv
-re_nchar = re.compile(r'[,"\']')
-
-from pprint import pprint
-with io.open(BILL_FILE, 'r', encoding='utf-8') as infile,\
-        io.open(OUTFILE, 'w+', encoding='utf-8') as outfile:
-   
-    counter = 0
-    outfile.write(header + '\n')
-    for i, line in enumerate(infile):
-
-        doc = json.loads(line)
-
-        # Print progress
-        if i % 1000 == 0:
-            print(i)
-
-        # Some documents failed to extract, skip corresponding lines        
-        if doc is None:
-            continue
-
-        # Take quote characters out of string fields
-        if doc['short_title'] is not None:
-            doc['short_title'] = re_nchar.sub('', doc['short_title'])
-        if doc['bill_title'] is not None:
-            doc['bill_title'] = re_nchar.sub('', doc['bill_title'])
-        
-        bill_text = doc['bill_document_last']
-        if bill_text is None:
-            bill_text = doc['bill_document_first']
-        if bill_text is None:
-            bill_length = None
-        else:
-            bill_length = len(bill_text.split())
-
-
-        row = [doc['unique_id'], doc['date_introduced'], doc['date_signed'],
-               doc['action_dates']['last'], doc['action_dates']['passed_upper'],
-               doc['action_dates']['passed_lower'], doc['state'], doc['chamber'],
-               doc['bill_type'][0], doc['short_title'], doc['session'], 
-               doc['bill_title'], bill_length
-               ]
-         
[…]

### 2017-04-05 etl/database/extract_bill_metadata.py

@@ -1,0 +1,108 @@
+# Generate a csv with metadata on all bills. 
+# Calculates average ideology of all bill sponsors (from malp data)
+import json
+from pprint import pprint
+import pandas as pd
+import numpy as np
+import time
+import re
+import csv
+
+
+def has_bill_text(b):
+    if b["bill_document_last"] is None and b["bill_document_first"] is None:
+        return False
+    else:
+        return True
+
+def get_bill_document(doc):
+    last = doc.get("bill_document_last", None)
+    first = doc.get("bill_document_first", None)
+
+    if last is not None:
+        return last
+    elif first is not None:
+        return first
+    else:
+        return None
+
+
+if __name__ == "__main__":
+    
+    # ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+    # Config
+    # ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+    BILL_FILE = '../../data/initial_data/extracted_bills_with_sponsers.json'
+    OUTFILE = '../../data/bill_metadata.csv'
+    BILL_ID_FILE = '../../data/bill_ids.txt'
+    N_SPON = 3
+    # ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+    legislators = pd.read_csv('../../data/initial_data/legislators.csv')
+
+    header = ['unique_id', 'date_introduced', 'date_signed', 'date_last_action', 
+              'date_passed_upper', 'date_passed_lower', 'state', 'chamber', 
+              'bill_type', 'short_title', 'session', 'bill_title', 'bill_length',
+              'sponsor_idology', 'num_sponsors']
+
+    # Get a set of all legislators that we have ideology for
+    known_legis = set(legislators['id'])
+
+    with open(BILL_FILE, 'r', encoding='utf-8') as infile,\
+         open(OUTFILE, 'w+', encoding='utf-8') as outfile,\
+         open(BILL_ID_FILE, 'w', encoding='utf-8') as idfile:
+        
+        writer = csv.writer(outfile, delimiter=',', quotechar='"',
+                            quoting=csv.QUOTE_MINIMAL)
+        writer.writerow(header)
+
+        for i, line in enumerate(infile):
+
+            if i % 1000 == 0:
+                print(i)
+
+            if line == "null\n":
+                continue
+
+            doc = json.loads(line)
+
+            if not has_bill_text(doc):
+                continue
[…]

### 2017-04-05 etl/database/import_bills.py

@@ -18,7 +18,7 @@ if __name__ == "__main__":
     HOST = 'localhost'
     PORT = 9200
     INDEX_NAME = 'state_bills'
-    DATA_FILE = '../../data/raw_data/extracted_bills_with_sponsers.json' 
+    DATA_FILE = '../../data/initial_data/extracted_bills_with_sponsers.json' 
     MAPPING_FILE = "../../etl/database/state_bill_mapping.json"
     IDX_SET_FILE = "../../etl/database/state_bill_index.json"
     #==========================================================================

### 2017-04-05 generate_alignments/ncsl_bill_pairs.py
code to generate and post process ncsl alignments

@@ -1,77 +1,59 @@
-#!/opt/anaconda/bin/python 
-from __future__ import unicode_literals
-import sys 
-sys.path.append('../policy_diffusion/lid/')
-from lid import LID
-from text_alignment import AffineLocalAligner,LocalAligner
-from utils.text_cleaning import clean_document 
-import database
-import json
-import base64
-import codecs
-import re
-import logging
+import sys
+import csv
 import os
-import traceback
-import sys
-from utils.general_utils import deadline,TimedOutExc
-from database import ElasticConnection
-import time
-import io
 import itertools
-from pprint import pprint
-import numpy as np
-import sys
 import multiprocessing
-from functools import partial
 
-# TODO: dedicated I/O process for result output. There have been some conflicts
-# (very few though)
+import numpy as np
 
-def align_pair(c, split):
+from elasticsearch import Elasticsearch as ES
+from text_cleaning import clean_document
+from local_aligner import align, TimeOutError
+from b2b_alignment import get_bill_document
+
+
+def align_pair(pair):
     '''
-    c: tuple, (left_bill, right_bill)
-    split: bool, should bills be split in sections
+    pair: tuple, (left_bill, right_bill)
     '''
-    s = time.time()
-    alignments = lidy.align_bill_pair(right_doc_id=c[0], 
-                                      left_doc_id=c[1],
-                                      split_sections=split)
-    out = {'left_bill': c[0], 
-           'right_bill': c[1], 
-           'alignments':alignments}
+    # Get bill text
+    left_source = es.get_source(index="state_bills", id=pair[0], 
+                                doc_type="_all") 
+    right_source = es.get_source(index="state_bills", id=pair[1], 
+                                 doc_type="_all")
+
+    left_doc = get_bill_document(left_source)
+    right_doc = get_bill_document(right_source)
     
-    #with io.open(outfile_name, 'a', encoding='utf-8') as outfile:
-    #    outfile.write(unicode(json.dumps(out)) + '\n')
-    print(time.time() - s) 
+    if (left_doc is None or right_doc is None or
+        len(left_doc) > 3e5 or len(right_doc) > 3e5):
+        return None
+    
+    left_doc = clean_document(left_doc, state_id=left_source["state"])
[…]

### 2017-04-05 generate_alignments/process_ncsl_alignments.py

@@ -1,0 +1,86 @@
+import Stemmer
+import os 
+import csv
+import logging
+import pickle
+import sys
+
+import numpy as np
+import scipy.sparse as sps
+
+from gensim import corpora, matutils
+from sklearn.metrics.pairwise import cosine_similarity
+from multiprocessing import Pool
+from generate_alignments import matches_only, proc_text, calc_similarities
+
+
+
+
+if __name__ == "__main__":
+
+    # Config
+    DATA_DIR = '../data/aligner_output/'
+    ALIGNMENT_OUTPUT = os.path.join(DATA_DIR, 'ncsl_alignments.csv')
+    SCORES = os.path.join(DATA_DIR, 'ncsl_alignments_notext.csv')
+
+    n = 1000 # size of comparison samples
+    stemmer = Stemmer.Stemmer('english').stemWord 
+    
+    logging.basicConfig(level=logging.INFO)
+
+    with open(ALIGNMENT_OUTPUT, 'r', encoding='utf-8') as infile,\
+         open(SCORES, 'w') as scorefile:
+        
+        reader = csv.reader(infile, delimiter=',', quotechar='"')
+        score_writer = csv.writer(scorefile, delimiter=',', quotechar='"',
+                                  quoting=csv.QUOTE_MINIMAL)
+
+        # Count total number of rows in data
+        m = sum([1 for row in reader])
+        infile.seek(0)
+        
+        logging.info(f'{m} alignments in {ALIGNMENT_OUTPUT}')
+
+        # Next pass through the data. Generate dictionary and sample matrix
+
+        np.random.seed(3468934)
+        logging.info('Select sample alignments...')
+        sample = set(np.random.choice(m, size=n, replace=False))
+
+        logging.info(('Making sample matrix and dictionary'))
+        sample_bow = []
+        dictionary = corpora.Dictionary()
+        for i,row in enumerate(reader):
+
+            # If selected for sample, process and append to sample corpus
+            if i in sample:
+                matched_text = matches_only(row[3], row[4])
+                tokens = proc_text(matched_text, stemmer)
+                sample_bow.append(dictionary.doc2bow(tokens, 
+                                                     allow_update=True))
+        
+        sample_tdm = matutils.corpus2csc(sample_bow, 
+                                         num_terms=len(dictionary), 
+                                         num_docs=n)
+        logging.info(f'Shape of sample matrix: {sample_tdm.shape}')
+        mtype = type(sample_tdm)
+        logging.info(f'Type of sample matrix: {mtype}')
[…]

### 2017-04-05 etl/ncsl_tables/match_bills.R
code to generate matched ncsl bill list

@@ -1,13 +1,13 @@
 library(dplyr)
 
-ncsl_bills <- tbl_df(read.csv('../data/ncsl/ncsl_data_from_sample.csv', 
+ncsl_bills <- tbl_df(read.csv('../../data/ncsl/ncsl_data_from_sample.csv', 
                        header = TRUE, stringsAsFactors = FALSE))
 # Check for duplicates
 ncsl_bills <- mutate(ncsl_bills, unique_id = paste0(id, '_', state, '_', year)) %>%
     select(-table, -description)
 ncsl_bills <- ncsl_bills[!duplicated(ncsl_bills$unique_id),]
 
-db_bills <- tbl_df(read.csv('../data/lid/bill_metadata.csv', header = TRUE,
+db_bills <- tbl_df(read.csv('../../data/bill_metadata.csv', header = TRUE,
                      stringsAsFactors = FALSE))
 
 # Preprocess db bills
@@ -103,5 +103,7 @@ print(paste('Found', one_match, 'matches'))
 print(paste(no_match, 'not matched'))
 print(paste(multi_match, 'multiple matches'))
 
-write.csv(ncsl_bills, file = '../data/ncsl/ncsl_data_from_sample_matched.csv', 
-          row.names = FALSE)
+out <- select(ncsl_bills, matched_from_db) %>%
+    filter(!is.na(matched_from_db))
+write.table(out, file = '../../data/ncsl/matched_ncsl_bill_ids.txt', 
+          row.names = FALSE, quote = FALSE, sep = ",", col.names = FALSE)

### 2017-04-05 etl/unique_alignments.py

@@ -1,30 +1,0 @@
-from __future__ import unicode_literals
-import io
-  
-
-if __name__ == "__main__":
-
-    INFILE = '../data/alignments_new/ncsl_align_text_nosplit.csv'
-    OUTFILE = '../data/ncsl/ncsl_unique_align.csv'
-
-    #INFILE = sys.argv[1]
-    #OUTFILE = sys.argv[2]
-    
-    outline = '{count},{text}\n'
-
-    ualign = {}
-
-    with io.open(INFILE, 'r', encoding='utf-8') as infile:
-
-
-        for line in infile:
-            text = line.strip('\n').split(',')[2]
-            ualign[text] = ualign.get(text, 0) + 1
-        
-        
-    with io.open(OUTFILE, 'w', encoding='utf-8') as outfile:
-
-        outfile.write(outline.format(text='text', count='count'))
-
-        for e in ualign:
-            outfile.write(outline.format(text=e, count=ualign[e]))

### 2017-04-05 analysis/topic_modeling/test_serial.R
deleted old topic modeling code

@@ -1,11 +1,0 @@
-### Test batch script
-rm(list=ls())
-N=100
-n=1000
-m1 = m2 = vector(length=n)
-for(i in 1:n){
-  x = rnorm(N)
-  m1[i] = mean(x)
-  m2[i] = median(x)
-}
-save.image(file="image.RData")

### 2017-04-05 analysis/topic_modeling/topic_modeling40.R

@@ -1,39 +1,0 @@
-setwd("/storage/group/bbd5087_collab/text_reuse/analysis")
-load("text_for_mallet.RData")
-
-options( java.parameters = "-Xmx40g" )
-
-#install.packages("mallet",lib="/storage/group/bbd5087_collab/r_packages",repos="http://cran.stat.ucla.edu/")
-
-.libPaths("/storage/group/bbd5087_collab/r_packages")
-
-library(mallet)
-
-set.seed(10)
-
-filenamesRS <- filenames
-aligned_textRS <- aligned_text
-
-mallet.instances <- mallet.import(filenamesRS,aligned_textRS,"en.txt")
-
-topic.model <- MalletLDA(num.topics=40)
-	
-topic.model$loadDocuments(mallet.instances)
-	
-vocabulary <- topic.model$getVocabulary()
-word.freqs <- mallet.word.freqs(topic.model)
-
-topic.model$setAlphaOptimization(20, 50)
-
-topic.model$train(300)
-	
-topic.model$maximize(10)
-	
-doc.topics <- mallet.doc.topics(topic.model, smoothed=T, normalized=T)
-topic.words <- mallet.topic.words(topic.model, smoothed=T, normalized=T)
-
-topic.probs <- apply(doc.topics,2,mean)
-
-mallet.top.words(topic.model, topic.words[6,],20)
-
-save(list=c("topic.model","doc.topics","topic.words","topic.probs","vocabulary","word.freqs"),file="topic_model_results40.RData")

### 2017-04-05 analysis/topic_modeling/topic_modeling_results.R

@@ -1,37 +1,0 @@
-setwd("/Users/bdesmarais/Dropbox/professional/Research/Active/Diffusion_Networks/text_reuse/analysis/analysis")
-load("text_for_mallet.RData")
-load("topic_model_results.RData")
-
-options( java.parameters = "-Xmx4g" )
-
-library(mallet)
-
-
-# top 100 words
-topwords <- as.character(word.freqs$words[order(-word.freqs$term.freq)[1:100]]) 
-topWordMat <- matrix(topwords,10,10,byrow=T)
-library(xtable)
-xtable(topWordMat)
-
-topwords_c <- paste(topwords,collapse = " ")
-
-# get alignment length
-align_length <- nchar(aligned_text)
-
-topic_top_words <- NULL
-for(i in 1:nrow(topic.words)){
-	top_wordsi <- order(-topic.words[i,])[1:10]
-	top_wordsi <- vocabulary[top_wordsi]
-	top_wordsi <- paste(top_wordsi,collapse=" ")
-	topic_top_words <- c(topic_top_words,top_wordsi)
-}
-
-topic_top_words <- cbind(topic_top_words[order(-topic.probs)])
-row.names(topic_top_words) <- order(-topic.probs)
-xtable(topic_top_words)
-
-# Alignments on Topic 17
-biggest17 <- order(-doc.topics[,17])[1:10]
-aligned_text[biggest17]
-
-

### 2017-04-05 analysis/exploratory/bill_meta_exp.R
zipped old submission

@@ -41,7 +41,7 @@ ggplot(state_desc, aes(x=year_introduced, y=state)) +
     ylab("State") + xlab("Year") + 
     guides(size=guide_legend(title="Count")) +
     plot_theme
-ggsave('../../manuscript/figures/year_count_by_state.png', width = p_width,
+ggsave('../../paper/figures/year_count_by_state.png', width = p_width,
        height = 0.7*p_width)
 
 ## Amount of text by state

### 2017-11-13 RRMemo/PSJMemo.tex
writing R&R memo

\documentclass[12pt]{article}
\usepackage{fullpage,color,graphicx}

%\documentclass[11pt]{article}
\usepackage{graphicx}
%\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{sans}
\usepackage{color}

\newcommand{\pjm}[1]{{\color{blue}#1}}
\definecolor{MyGreen}{cmyk}{1.0,0.0,1.0,0.2}
\newcommand{\sjc}[1]{{\color{MyGreen}#1}}
\definecolor{MyFuschia}{cmyk}{0.07,0.95,0,0}
\newcommand{\ejm}[1]{{\color{MyFuschia}#1}}
\definecolor{bloodred}{RGB}{102,0,0}
\newcommand{\blood}[1]{{\color{bloodred}#1}}
\definecolor{mygrey}{gray}{0.45}
\newcommand{\grey}[1]{{\color{mygrey}#1}}
\definecolor{orange}{RGB}{255,102,0}
\newcommand{\orange}[1]{{\color{orange}#1}}
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
% The official Dartmouth green: 
\definecolor{dartmouthgreen}{rgb}{0,.41,.24}

%\usepackage{scicite}

\newcommand{\compresslist}{%
\setlength{\itemsep}{1pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

\oddsidemargin=0.25in
\evensidemargin=\oddsidemargin
\textwidth=6in
\topmargin=-0.5in
\textheight=9in

\begin{document}

\thispagestyle{empty}

\noindent \textbf{Point-by-point discussion of Reviews and Response to Comments}\\

First, we thank the editor...

\bigskip
\bigskip

\noindent \underline{\textbf{Response to the Editor's Comments}}\\

\noindent {\bf E1} \grey{\emph{Overall, the referees are quite supportive of the manuscript, however, they raise several issues that require attention. As at least two referees note, the manuscript needs to be geared to an audience that may not be familiar with text based analysis, thus more hand holding is needed, such as tucking the highly technical aspects into an appendix and incorporating a discussion of how to apply this technique (i.e., workflow) }}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor..

\noindent  {\bf E2} \grey{\emph{In addition, including an application that demonstrates its value is necessary. One of the reviewers suggests a full blown theoretical contribution, but that is not necessary.  }}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor...

\noindent \underline{\textbf{Response to Comments by Reviewer 1}}\\

\noindent {\bf R1.1} \grey{\emph{ The shortcoming in my view is that there is no innovative example application. Other scholars are already using similar methods and state bills to investigate, for example, the role of interest groups in promoting policy diffusion and the state level variables that impact diffusion. So suggesting that these are potential uses of the method seems well... Can the authors think of any other innovative applications? After all, they now have millions of bill comparisons at their disposal.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R1.2} \grey{\emph{  A final sugestions is that much of the discussion of the method is directed at scholars who are familiar with text reuse methods (rather than the target audience) and is probably best reserved for an appendix (freeing up space for an example application!)}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R1.3} \grey{\emph{  One other thought. They validate with the limited similar bills listed by the NCSL. One possible application might be to explore how many other bills meet that similarity threshold and how they are similar and different in terms of substance, states, sponsors etc to those identified by NCSL}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent \underline{\textbf{Response to Comments by Reviewer 2}}\\

\noindent {\bf R2.1} \grey{\emph{   I was unsure to what extent the algorithm used in this paper overlaps with the Smith-Waterman algorithm. The authors make clear the use the same algorithm but with some adjustments. What's part of the original algorithm and what's new was not clear to me. The authors should explain the difference more clearly.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R2.2} \grey{\emph{  I found the paper quite reader friendly but the authors can further improve this aspect, for instance with a section before the conclusion in which the authors lay down very simply and clearly the workflow for someone wanting to use their approach.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R2.3} \grey{\emph{ Relatedly, it's great that the authors make their dataset available, but they should also share their code (ideally, if possible, in the form a package).}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R2.4} \grey{\emph{ The conclusion is currently quite short. There is scope for outlining more in detail the added value of the approach and how the data generated by it can be used in policy analysis. There is some discussion of these points in the conclusion, but it can be expanded.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R2.5} \grey{\emph{ I encourage the authors to further improve the clarity, especially at the end of the paper, to make their approach as accessible as possible to a non-technical audience.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent \underline{\textbf{Response to Comments by Reviewer 3}}\\

\noindent {\bf R3.1} \grey{\emph{ While the analytics are very tempting I am greatly disappointed in the paper as it doesn?t really provide any substantive use of the method.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R3.2} \grey{\emph{ As it stands this manuscript doesn?t seek to make a theoretical contribution to the field even though the authors have at their disposal a unique dataset which I am sure would allow for several interesting theoretical questions to be asked.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R3.3} \grey{\emph{ Take out section 3. I don?t think it?s interesting to political scientists. Leave in an appendix or publish in a CS journal.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R3.4} \grey{\emph{ Use the space left by removing section 3 to propose a theoretical mechanism for policy diffusion and text reuse. This can include all the findings that you currently have ?and perhaps some others- ideology, policy area, geographic area, etc.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R3.5} \grey{\emph{ Reconsider the elements of section 4 moving elements of validity to an appendix or to the CS piece.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\noindent {\bf R3.5} \grey{\emph{ Properly present the results of your analysis based on the new theoretical argument.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer...

\end{document}
